### 2018-03-22 abstract.tex
Initial commit of abstract

% use paper, or submit
% use 11 pt (preferred), 12 pt, or 10 pt only

%\documentclass[letterpaper, preprint, paper,11pt]{AAS}	% for preprint proceedings
\documentclass[letterpaper, paper,11pt]{AAS}		% for final proceedings (20-page limit)
%\documentclass[letterpaper, paper,12pt]{AAS}		% for final proceedings (20-page limit)
%\documentclass[letterpaper, paper,10pt]{AAS}		% for final proceedings (20-page limit)
%\documentclass[letterpaper, submit]{AAS}			% to submit to JAS

\usepackage{AAS_packages}
%\usepackage{subfigure} % have subcaption in use instead
%\usepackage[notref,notcite]{showkeys}  % use this to temporarily show labels

\PaperNumber{XX-XXX}

\begin{document}

\title{Asteroid shape reconstruction}

\author{Shankar Kulumani and Taeyoung Lee\thanks{Mechanical and Aerospace Engineering, George Washington University, 800 22nd St NW, Washington, DC 20052, Tel: 202-994-8710, Email: \href{mailto:skulumani@gwu.edu}{\{skulumani,tylee\}@gwu.edu}.}
}

\maketitle{}

\begin{abstract}
    Abstract for paper
\end{abstract}

\section{Introduction}\label{sec:introduction}
% Motivation for missions/studying asteroids

\section{Problem Formulation}\label{sec:problem}
In this paper, we consider the landing of a dumbbell model of an under actuated spacecraft onto an asteroid.
The dumbbell model is a well-known representation of a multi body spacecraft.
Furthermore, the dumbbell model captures the important interactions of the coupling between orbital and attitude dynamics. 
The dumbbell spacecraft consists of two masses connected by a massless rod.
This simple model is useful to capture the main characteristics of a wide variety of spacecraft configurations.
Typically, spacecraft have mass concentrated in a central structure, referred to as the bus, which houses the command and control system, actuators, fuel, sensors etc. 
In addition, comparatively light-weight solar panels extend from the bus to provide electrical energy from solar radiation. 
As a result, the distributed mass of the spacecraft is captured with the dumbbell representation.

% most use a spherical harmonic model or a ellipsoid model but we use a polyhedron model
An accurate gravitational potential model is necessary for the operation of spacecraft about asteroids.
Additionally, a detailed shape model of the asteroid is needed for trajectories passing close to the body.
The classic approach is to expand the gravitational potential into a harmonic series and compute the series coefficients.
However, the harmonic expansion is always an approximation as a result of the infinite order series used in the representation.
Additionally, the harmonic model used outside of the circumscribing sphere is not guaranteed to converge inside the sphere, which makes it unsuitable for trajectories near the surface.
Instead, we use the polyhedron potential model to represent the shape of the asteroid and also the gravitational potential assuming a constant density~\cite{werner1994,werner1997}.

The equations of motion of the dumbbell spacecraft about an asteroid are derived using Hamilton's Principle. 
The first step is to choose generalized coordinates \( q \) and a corresponding configuration space \( Q \).
The Lagrangian is then formed as the difference between the kinetic and potential energy in terms of our generalized coordinates. 
Hamilton's principle then states that the variation of the action integral
\begin{align}
    \mathsf{G} = \int_{t_0}^{t_f} T(\dot{q}) - V(q) dt,
\end{align}
is stationary with fixed endpoints. 
From this we obtain the Euler-Lagrange equations for the system.
Applying the Legendre transformation allows for the same dynamics to be expressed in an equivalent form as Hamilton's equations~\cite{lanczos1970}.

There is a key issue that arises in applying this process for the coupled motion about an asteroid.
The configuration space for rigid body motion is the semi-direct product, \(\SE = \R^3 \rtimes \SO \), namely the special euclidean group.
The variations should be carefully constructed such that they respect the geometry of the configuration space.
By expressing the motion of the dumbbell directly on the special euclidean group, we avoid the issues inherent in using other kinematic representations which fail to preserve the geometric properties of the configuration space.

\subsection{Equations of Motion}

The kinematics of the dumbbell and asteroid are described in the inertial frame by
\begin{itemize}
    \item \( \vecbf{x} \) - the position of the center of mass of the dumbbell spacecraft represented in the inertial frame \( \vecbf{e}_i\)
    \item \( R \) - the rotation matrix which transforms vectors defined in the spacecraft fixed frame, \( \vecbf{b}_i \), to the inertial frame, \( \vecbf{e}_i \)
    \item \( \vecbf{\Omega} \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame \( \vecbf{b}_i \)
    \item \( R_A \) - the rotation matrix which transforms vectors defined in the asteroid fixed frame, \( \vecbf{f}_i \), to the inertial frame, \( \vecbf{e}_i \)
\end{itemize}
In this work, we assume that the asteroid is much more massive than the spacecraft and it's motion is not affected by that of the spacecraft.
This assumption allows us to treat the motion of the vehicle independently from that of the asteroid.

Using our kinematic variables we can define the kinetic and potential energy as
\begin{align}\label{eq:kinetic_energy}
    T &= \frac{1}{2} m \norm{\dot{\vb{x}}}^2 + \frac{1}{2} \tr{S(\vb{\Omega}) J_d S(\vb{\Omega})^T} , \\
    V( \vecbf{x}, R ) &=  - m_1 U \parenth{R_A^T \parenth{\vecbf{x} + R \vecbf{\rho}_1}} - m_2 U \parenth{R_A^T \parenth{\vecbf{x} + R \vecbf{\rho}_2}} ,
\end{align}
where the polyhedron potential is defined as 
\begin{align}
    U(\vecbf{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vecbf{r}_e \cdot \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vecbf{r}_f \cdot \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f,
\end{align}
and \( \vecbf{r}_e\) and \(\vecbf{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
The position of each mass \(m_i\) of the dumbbell is defined in the dumbbell fixed frame by the vector \(\vb{\rho}_i\). 
The next step is to define the variations of the kinetic and potential energy to derive the equations of motion.
The variation of the potential and kinetic energy can then be defined as
\begin{align} 
    \delta V &= -\sum_{i=1}^2  m_i \parenth{R_A \deriv{U}{\vb{z}_i} }^T \delta \vb{x} + m_i \hat{\vb{\eta}}\cdot \hat{\vb{\rho}_1} R^T R_A \deriv{U}{\vb{z}_i}, \\
    \delta T &= \parenth{m_1 + m_2} \dot{\vecbf{x}}^T \delta \dot{\vb{x}} + \frac{1}{2} \tr{ - \dot{\hat{\vb{\eta}}} S(J \vb{\Omega}) + \hat{\vb{\eta}} S(\hat{ \vb{\Omega}} J \vb{\Omega})} , 
\end{align}
Finally, applying Hamilton's principle gives the inertial equations of motion of the dumbbell spacecraft as
\begin{align}
    \dot{\vb{x}} &= \vb{v}, \\
    \parenth{m_1 + m_2} \dot{\vecbf{v}} &= m_1 R_A \deriv{U}{\vecbf{z}_1} + m_2 R_A \deriv{U}{\vecbf{z}_2}, \\
    \dot{R} &= R S(\vb{\Omega}) , \\
    J \dot{\vecbf{\Omega}} + \vecbf{\Omega} \times J \vecbf{\Omega} &= \vecbf{M}_1 + \vecbf{M}_2.
\end{align}
The vectors \( \vecbf{z}_1 \) and \( \vecbf{z}_2\) define the position of the dumbbell masses as represented in the asteroid fixed frame and are defined as
\begin{align}
    \vecbf{z}_1 &= R_A^T \parenth{\vecbf{x} + R \vecbf{\rho}_1} , \\
    \vecbf{z}_2 &= R_A^T \parenth{\vecbf{x} + R \vecbf{\rho}_2}.
\end{align}
The gravitational moment on the dumbbell \( \vecbf{M}_i\) is defined as
\begin{align}
    \vecbf{M}_i = m_i \parenth{S(R_A^T \vb{\rho}_i) R^T \deriv{U}{\vb{z}_i}}.
\end{align}

In Reference~\citenum{kulumani2016d}, a methodology was developed to design general transfer trajectories about the asteroid 4769 Castalia.
That previous work utilized the polyhedron potential method and a reachability analysis to allow for a spacecraft to transition  between orbits of the asteroid.
\Cref{fig:trajectory} shows an example transfer between two planar equatorial orbits of 4769 Castalia.
Reference~\citenum{kulumani2016d} only considered the orbital dynamics of a point mass spacecraft. 
In this work, we incorporate the attitude dynamics and consider the coupled motion of the spacecraft.
In addition, a desired landing trajectory is followed using nonlinear control techniques.
\subsection{Nonlinear Landing Controller}\label{sec:landing}

\section{Expected Results and Significance}\label{sec:expected}

\bibliographystyle{AAS_publication} 
\bibliography{library}

\end{document}

### 2018-03-23 abstract.tex
Starting on extended abstract

@@
 % Motivation for missions/studying asteroids
+
+\begin{itemize}
+    \item Spacecraft missions around asteroid require long periods of mapping
+        \begin{itemize}
+            \item Several months/years are spent in a quiescent state devoted solely to mapping the surface
+            \item Depending on the mission this time spent mapping is unnecessary and resource limiting - such as impact mitigation misions
+            \item The main goal of this mapping process is to generate an accurate shape model of the asteroid and measure the surface features.
+            \item The current methods rely on sending all data to the ground in order to compute the shape. 
+            \item Furthermore this limits the abiilty  of teh spacecraft to operate without  reliable Earth communications and support
+        \end{itemize}
+\end{itemize}
 

### 2018-03-23 abstract.tex
Working on outline

@@
             \item Furthermore this limits the abiilty  of teh spacecraft to operate without  reliable Earth communications and support
+        \end{itemize}
+    \item The surface shape is necessary in order to allow the spacecraft to operate near the surface of the a steroid
+        \begin{itemize}
+            \item The polyhedron potential model is a function of the shape and highly dependent on an accurate shape model.
+            \item It is not possible to accurately determine the shape of the asteroid from ground based measurements.
+                Due to the limitations of optical and radar measurements the typical best shape approximation prior to arrival is a coarse ellispoid shape CITE a paper.
+            \item The shape is
         \end{itemize}

### 2018-03-23 abstract.tex
Adding more to intro

@@
 
-\begin{itemize}
+\begin{enumerate}
     \item Spacecraft missions around asteroid require long periods of mapping
@@
                 Due to the limitations of optical and radar measurements the typical best shape approximation prior to arrival is a coarse ellispoid shape CITE a paper.
-            \item The shape is
+            \item An accurate shape model is critical for not only the gravitational model but also to enable accurate landing operations.
+                An accurate model of the surface is required for the gravity model, surface landing operations, and obstacle avoidance.
         \end{itemize}
+    \item Due to the previous issues it is critical to be able to generate the shape of the asteroid surface accurately and quickly.
+        \begin{itemize}
+            \item This work develops a method to efficiently determine the shape of the an asteroid given LIDAR range measurements of the surface.
+            \item The shape is updated in near real time (QUANTIFY THIS IN SOME MEANINGFUL FASHION) to  enable:
+                \begin{itemize}
+                    \item Updated gravity/dynamic model 
+                    \item Utilize this updated dynamic model in the spacecraft controller
+                    \item Allow for simulataenous shape reconstruction and spacecraft control
                 \end{itemize}
+            \item This alleviates teh need for a long term mapping campaign
+        \end{itemize}
+\end{enumerate}
 

### 2018-03-23 abstract.tex
Commit new title

--- 2018-03-23 abstract.tex
@@
 
-\title{Asteroid shape reconstruction}
+\title{Real Time Shape Reconstruction for Near Earth Asteroid Landing}
 
@@
 
-\begin{itemize}
-    \item Spacecraft missions around asteroid require long periods of mapping
-        \begin{itemize}
-            \item Several months/years are spent in a quiescent state devoted solely to mapping the surface
-            \item Depending on the mission this time spent mapping is unnecessary and resource limiting - such as impact mitigation misions
-            \item The main goal of this mapping process is to generate an accurate shape model of the asteroid and measure the surface features.
-            \item The current methods rely on sending all data to the ground in order to compute the shape. 
-            \item Furthermore this limits the abiilty  of teh spacecraft to operate without  reliable Earth communications and support
-        \end{itemize}
-\end{itemize}
-
+% 
 \section{Problem Formulation}\label{sec:problem}

### 2018-03-31 abstract.tex
Add some notes
Add intro paragraph on dynamics being difficult

--- 2018-03-23 abstract.tex
@@
 % Motivation for missions/studying asteroids
+Small solar system bodies, such as asteroids and comets, continue to remain a focus of scientific study.
+The small size of these bodies prevents the formation of large internal pressures and temperatures which help to preserve the early chemistry of the solar system.
+This insight offers additional detail into the formation of the Earth and also of the probable formation of other extrasolar planetary bodies.
+Of particular interest are those near-Earth asteroids (NEA) which inhabit heliocentric orbits in the vicinity of the Earth. 
+These easily accessible bodies provide attractive targets to support space industrialization, mining operations, and scientific missions.
+In spite of the significant interest, and the extensive research by the community, the operation of spacecraft near small bodies remains a challenging problem.
+
+% dynamics are difficult around asteroids
+The dynamic environment around asteroids is strongly perturbed and challenging for analysis and mission operations~\cite{scheeres2012}.
+Due to their low mass, which in turn causes a low gravitational attraction, asteroids may have irregular shapes.
+Furthermore, asteroids may also have a chaotic spin state due to the absorption and emmitance of solar radiation~\cite{rubincam2000}.
+As a result, approaches utilizing an inverse square gravitational model do not capture the  true dynamic environment.
+In addition, the vast majority of asteroids are difficult to track and characterize using ground based sensors.
+Due to their small size, frequently less than \SI{1}{\kilo\meter}, and low albedo, the reflected energy of these asteroids is insufficient for reliable detection or tracking.
+Therefore, the dynamics model of the asteroid is relatively coarse prior to insitu measurements from a dedicated spacecraft.
+As a result, any spacecraft mission to an asteroid must include the ability to update the dynamic model given insitu measurements and robustness to unmodelled forces.
+
+ % Types of missions near asteroids (impact mitigation, mining, science)
+
+% Challenges invovled in operation near asteroids (gravity, shpae, distance)
+
+% Gravity model is important and dependent on shape
+
+% Current approach relies on long periods of mapping to generate the shape
+
+% our approach for paper. Real time method to update asteroid shape model and use updated model in closed loop control
+
+% Benefits and contribution of our approach
 

### 2018-03-31 abstract.tex
Add more introduction

@@
 
+Another key dynamic consideration is the coupling between rotational and translational states around the asteroid.
+The coupling is induced due to the different gravitational forces experienced on various portions of the spacecraft. 
+The effect of the gravitational coupling is related to the ratio of the spacecraft size and orbital radius~\cite{hughes2004}.
+For operations around asteroids, the ratio is relatively large which causes a much larger coupling between the translational and rotational states.
+References~\cite{elmasri2005} and~\cite{sanyal2004a} investigated the copuling of an elastic dumbbell spacecraft in orbit about a central body, but only considered teh case of a spherically symmetric central body.
+Furthermore, the spacecraft model is assumed to remain in a planar orbit.
+As a result, these developments are not directly applicable to motion about an asteroid, which experiences highly non-Keplerian motion.
+Reference~\cite{misra2015b}
  % Types of missions near asteroids (impact mitigation, mining, science)

### 2018-03-31 abstract.tex
More detail

@@
 As a result, these developments are not directly applicable to motion about an asteroid, which experiences highly non-Keplerian motion.
-Reference~\cite{misra2015b}
- % Types of missions near asteroids (impact mitigation, mining, science)
+Reference~\cite{misra2015b} investigated the effect of coupled motion on long term trajectories around asteroids.
+However, the analysis only considered a second order spherical harmonic gravitational potential model. 
+Therefore, these results are only valid when far from the asteroid surface and will diverge when used within the Brillouin sphere.
+
+% Gravity model is important and dependent on shape
+An accurate gravitational potential model is critical for performing low alititude and/or surface operations around asteroids.
+Due to the irregular shape, trajectories will pass within the Brillouin sphere where the typical spherical harmonic model diverges from the true gravitational potential.
+With respect to asteroid missions, the standard approach to compute the gravitational potential is the polyhedron potential model~\cite{werner1996}.
+The polyhedral potential model provides the exact gravitational potential, and subsequently the gravitational acceleration, for a given triangular faceted shape model of an asteroid.
+The method provides the exact potential for a given faceted shape model.
+As a result, the accuracy of the gravitational potential is a function of the accuracy with which the shape modelrepresents the true surface topology.
+A high fidelity shape, which necessarily has many vertices and faces, is required for an accurate computation of the true gravitational acceleration.
+The determination of the shape of the asteroid surface is crucial for both determining the gravitational potential as well as operations near the surface.
+
+% generating the shape from the ground is difficult
+
+% on arrival spacecraft spend long periods mapping, and depending on misison this might be unallowable
+
+% we want to generate the shape in real time and then use this shape for updated and better control
 
 % Challenges invovled in operation near asteroids (gravity, shpae, distance)
-
-% Gravity model is important and dependent on shape
 
@@
 \end{enumerate}
+
+\section{Asteroid shape representation}
 

### 2018-03-31 abstract.tex
Update intro

@@
 The method provides the exact potential for a given faceted shape model.
-As a result, the accuracy of the gravitational potential is a function of the accuracy with which the shape modelrepresents the true surface topology.
-A high fidelity shape, which necessarily has many vertices and faces, is required for an accurate computation of the true gravitational acceleration.
+As a result, the accuracy of the gravitational potential is primarily dependent on the accuracy with which the shape modelrepresents the true surface topology.
+A high fidelity shape, which necessarily has many vertices and faces, is required for an accurate computation of the gravitational acceleration.
 The determination of the shape of the asteroid surface is crucial for both determining the gravitational potential as well as operations near the surface.
 
+% Challenges invovled in operation near asteroids (gravity, shpae, distance)
 % generating the shape from the ground is difficult
+Prior to the arrival of a spacecraft at an asteroid, Earth based sensors are used to characterize the body.
+Using both optical and radar sensors allows for the precise orbit of the asteorid to be determined.
+Another vital task is the determination of the asteroid shape from radar data~\cite{hudson1994,busch2011}.
+This is a challenging problem as it requires the simultaneous estimation of the asteroid spin state and shape.
+Furthermore, determining the shape from radar is currently the only Earth-based technique that can produce detailed three-dimensional shape information of near-Earth objects~\cite{greenberg2015}.
+The current approach is based on an estimation scheme which iteratively perturbs a shape to match given radar data.
+This computationally intensive approach is only able to capture the gross size and shape and is unable to capture the minute surface features of the asteroid.
+Frequently, only a rough triaxial ellipsoid model is possible from the ground and an accurate shape must be determined only after a spacecraft has rendezvouzed with the asteroid.
+As a result, on arrival the gravitional environment near the asteroid is unknown as the shape of the asteroid is poorly modelled.
 
 % on arrival spacecraft spend long periods mapping, and depending on misison this might be unallowable
+On approach to an asteroid, spacecraft navigation and guidance is primarily based on ground measurements.
+After arrival, a spacecraft will generally spend months or years in a mapping mission phase~\cite{kubota2003,cole1998}.
+During this period, spacecraft sensors, such as onboard optical telescopes or Light radio Detection and Ranging (LIDAR), are used to characterize the asteroid.
+The resulting imagery and range data is transmitted to the ground and the resulting asteroid shape and motion is estimated. 
+During this mapping phase the spacecraft must remain in a quiescent state devotes entirely to mapping the surface.
+Depending on the mission type this long period of mapping is crucial to determining an ideal landing location, such as the Asteroid Redirect Mission~\cite{gates2015}. 
+However, other missions, such as asteroid mitigation, may be severely limited by the time and ground resources required to generate a surface shape.
+Furthermore, the long distances involved necessitate on-board autonomy to enable to spacecraft to operate without ground communications.
+The dependency on expensive ground based shape reconstruction techniques limit the ability for spacecraft autonomously operate and land at asteroids.
 
 % we want to generate the shape in real time and then use this shape for updated and better control
-
-% Challenges invovled in operation near asteroids (gravity, shpae, distance)
-
-% Current approach relies on long periods of mapping to generate the shape
+In this paper, we develop a method to compute the surface shape of an asteroid from range measurements.
+Our approach is able to operate in real time and incrementally update the shape model of an asteroid as new range measurements are collected.
 

### 2018-03-31 abstract.tex
Finish introduction

@@
 Our approach is able to operate in real time and incrementally update the shape model of an asteroid as new range measurements are collected.
+This approach allows for the shape to be continually updated as range measurements are used to locally modify the shape estimate instead of a global operation.
+Furthermore, this updated shape is then used in a nonlinear controller to enable the tracking of a landing trajectory to the surface.
+In contrast to previous work, we explicitly consider the gravitational coupling between orbit and attitude dynamics.
+Furthermore, instead of computationally expensive surface reconstruction methods we present a straightforward and conceptually simple method to enable real time shape updates.
 
@@
 % Benefits and contribution of our approach
+In short, this paper presents a method to incrementally update the shape  model of an asteroid from range measurements. 
+Our approach alleviates the need for a dedicated mapping phase as the spacecraft is able to update its shape model in real time and without expensive computations.
+This type of approach allows for the spacecraft to maneuver and land on the asteroid immediately upon arrival rather than spending several months mapping the surface.
+This updated shape model is then used to in a nonlinear controller to track a desired state trajectory for the dynamics of a rigid body spacecraft.
+The dynamics are developed on the nonlinear manifold of rigid body motions, namely the special euclidean group.
+This formulation is based on an intrinsic geometric description of the motion and accurately captures the coupling between orbit and attitude dynamics. 
+The presented approach allows for a spacecraft to transition directly from arrival to the surface while reconstructing the surface shape in real time.
 

### 2018-03-31 abstract.tex
Startgin on problem formulation

@@
 
-\begin{enumerate}
-    \item Spacecraft missions around asteroid require long periods of mapping
-        \begin{itemize}
-            \item Several months/years are spent in a quiescent state devoted solely to mapping the surface
-            \item Depending on the mission this time spent mapping is unnecessary and resource limiting - such as impact mitigation misions
-            \item The main goal of this mapping process is to generate an accurate shape model of the asteroid and measure the surface features.
-            \item The current methods rely on sending all data to the ground in order to compute the shape. 
-            \item Furthermore this limits the abiilty  of teh spacecraft to operate without  reliable Earth communications and support
-        \end{itemize}
-    \item The surface shape is necessary in order to allow the spacecraft to operate near the surface of the a steroid
-        \begin{itemize}
-            \item The polyhedron potential model is a function of the shape and highly dependent on an accurate shape model.
-            \item It is not possible to accurately determine the shape of the asteroid from ground based measurements.
-                Due to the limitations of optical and radar measurements the typical best shape approximation prior to arrival is a coarse ellispoid shape CITE a paper.
-            \item An accurate shape model is critical for not only the gravitational model but also to enable accurate landing operations.
-                An accurate model of the surface is required for the gravity model, surface landing operations, and obstacle avoidance.
-        \end{itemize}
-    \item Due to the previous issues it is critical to be able to generate the shape of the asteroid surface accurately and quickly.
-        \begin{itemize}
-            \item This work develops a method to efficiently determine the shape of the an asteroid given LIDAR range measurements of the surface.
-            \item The shape is updated in near real time (QUANTIFY THIS IN SOME MEANINGFUL FASHION) to  enable:
-                \begin{itemize}
-                    \item Updated gravity/dynamic model 
-                    \item Utilize this updated dynamic model in the spacecraft controller
-                    \item Allow for simulataenous shape reconstruction and spacecraft control
-                \end{itemize}
-            \item This alleviates teh need for a long term mapping campaign
-        \end{itemize}
-\end{enumerate}
+\section{Problem Formulation}\label{sec:problem}
 
-\section{Asteroid shape representation}
-
-\section{Problem Formulation}\label{sec:problem}
-In this paper, we consider the landing of a dumbbell model of an under actuated spacecraft onto an asteroid.
-The dumbbell model is a well-known representation of a multi body spacecraft.
-Furthermore, the dumbbell model captures the important interactions of the coupling between orbital and attitude dynamics. 
-The dumbbell spacecraft consists of two masses connected by a massless rod.
-This simple model is useful to capture the main characteristics of a wide variety of spacecraft configurations.
-Typically, spacecraft have mass concentrated in a central structure, referred to as the bus, which houses the command and control system, actuators, fuel, sensors etc. 
-In addition, comparatively light-weight solar panels extend from the bus to provide electrical energy from solar radiation. 
-As a result, the distributed mass of the spacecraft is captured with the dumbbell representation.
-
-% most use a spherical harmonic model or a ellipsoid model but we use a polyhedron model
-An accurate gravitational potential model is necessary for the operation of spacecraft about asteroids.
-Additionally, a detailed shape model of the asteroid is needed for trajectories passing close to the body.
-The classic approach is to expand the gravitational potential into a harmonic series and compute the series coefficients.
-However, the harmonic expansion is always an approximation as a result of the infinite order series used in the representation.
-Additionally, the harmonic model used outside of the circumscribing sphere is not guaranteed to converge inside the sphere, which makes it unsuitable for trajectories near the surface.
-Instead, we use the polyhedron potential model to represent the shape of the asteroid and also the gravitational potential assuming a constant density~\cite{werner1994,werner1997}.
-
-The equations of motion of the dumbbell spacecraft about an asteroid are derived using Hamilton's Principle. 
-The first step is to choose generalized coordinates \( q \) and a corresponding configuration space \( Q \).
-The Lagrangian is then formed as the difference between the kinetic and potential energy in terms of our generalized coordinates. 
-Hamilton's principle then states that the variation of the action integral
-\begin{align}
-    \mathsf{G} = \int_{t_0}^{t_f} T(\dot{q}) - V(q) dt,
-\end{align}
-is stationary with fixed endpoints. 
-From this we obtain the Euler-Lagrange equations for the system.
-Applying the Legendre transformation allows for the same dynamics to be expressed in an equivalent form as Hamilton's equations~\cite{lanczos1970}.
-
-There is a key issue that arises in applying this process for the coupled motion about an asteroid.
-The configuration space for rigid body motion is the semi-direct product, \(\SE = \R^3 \rtimes \SO \), namely the special euclidean group.
-The variations should be carefully constructed such that they respect the geometry of the configuration space.
-By expressing the motion of the dumbbell directly on the special euclidean group, we avoid the issues inherent in using other kinematic representations which fail to preserve the geometric properties of the configuration space.
-
-\subsection{Equations of Motion}
-
+In this paper, we consider the motion of a dumbbell model of spacecraft around an asteroid.
+The dumbbell model captures the important interactions of the coupling between orbital and attitude dynamics.
+In this model, the spacecraft consists of two masses connected by a massless rod.
+The asteroid is modeled as a constant density polyhedron with constant, and known, spin about its maximum moment of inertia. 
+Without loss of generality, we define body fixed frames for both the spacecraft and asteroid which are aligned with the principle axes of each body and originate at their respective center of mass. 
 The kinematics of the dumbbell and asteroid are described in the inertial frame by
@@
 
-Using our kinematic variables we can define the kinetic and potential energy as
-\begin{align}\label{eq:kinetic_energy}
-    T &= \frac{1}{2} m \norm{\dot{\vb{x}}}^2 + \frac{1}{2} \tr{S(\vb{\Omega}) J_d S(\vb{\Omega})^T} , \\
-    V( \vecbf{x}, R ) &=  - m_1 U \parenth{R_A^T \parenth{\vecbf{x} + R \vecbf{\rho}_1}} - m_2 U \parenth{R_A^T \parenth{\vecbf{x} + R \vecbf{\rho}_2}} ,
-\end{align}
+Assumptions used
+
+\subsection{Polyhedron Potential Model}
 where the polyhedron potential is defined as 
@@
 The position of each mass \(m_i\) of the dumbbell is defined in the dumbbell fixed frame by the vector \(\vb{\rho}_i\). 
-The next step is to define the variations of the kinetic and potential energy to derive the equations of motion.
-The variation of the potential and kinetic energy can then be defined as
-\begin{align} 
-    \delta V &= -\sum_{i=1}^2  m_i \parenth{R_A \deriv{U}{\vb{z}_i} }^T \delta \vb{x} + m_i \hat{\vb{\eta}}\cdot \hat{\vb{\rho}_1} R^T R_A \deriv{U}{\vb{z}_i}, \\
-    \delta T &= \parenth{m_1 + m_2} \dot{\vecbf{x}}^T \delta \dot{\vb{x}} + \frac{1}{2} \tr{ - \dot{\hat{\vb{\eta}}} S(J \vb{\Omega}) + \hat{\vb{\eta}} S(\hat{ \vb{\Omega}} J \vb{\Omega})} , 
-\end{align}
 Finally, applying Hamilton's principle gives the inertial equations of motion of the dumbbell spacecraft as
@@
 
-In Reference~\citenum{kulumani2016d}, a methodology was developed to design general transfer trajectories about the asteroid 4769 Castalia.
-That previous work utilized the polyhedron potential method and a reachability analysis to allow for a spacecraft to transition  between orbits of the asteroid.
-\Cref{fig:trajectory} shows an example transfer between two planar equatorial orbits of 4769 Castalia.
-Reference~\citenum{kulumani2016d} only considered the orbital dynamics of a point mass spacecraft. 
-In this work, we incorporate the attitude dynamics and consider the coupled motion of the spacecraft.
-In addition, a desired landing trajectory is followed using nonlinear control techniques.
+\subsection{Shape Reconstruction}
+
+\section{Preliminary Results}
+
+Reconstruction of asteroid Castalia
+
+\section{Expected Results and Significance}
+
+\subsection{Equations of Motion}
+
 \subsection{Nonlinear Landing Controller}\label{sec:landing}

### 2018-03-31 abstract.tex
Working on math section

@@
 
-Assumptions used
-
-\subsection{Polyhedron Potential Model}
-where the polyhedron potential is defined as 
-\begin{align}
-    U(\vecbf{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vecbf{r}_e \cdot \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vecbf{r}_f \cdot \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f,
-\end{align}
-and \( \vecbf{r}_e\) and \(\vecbf{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
-The position of each mass \(m_i\) of the dumbbell is defined in the dumbbell fixed frame by the vector \(\vb{\rho}_i\). 
-Finally, applying Hamilton's principle gives the inertial equations of motion of the dumbbell spacecraft as
+Using Hamiltons principle gives the inertial equations of motion of the dumbbell spacecraft as
 \begin{align}
@@
 \end{align}
+where the polyhedron potential is defined as 
+\begin{align}
+    U(\vecbf{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vecbf{r}_e \cdot \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vecbf{r}_f \cdot \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f,
+\end{align}
+and \( \vecbf{r}_e\) and \(\vecbf{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
+The position of each mass \(m_i\) of the dumbbell is defined in the dumbbell fixed frame by the vector \(\vb{\rho}_i\).
 
 \subsection{Shape Reconstruction}
+
+We assume that the spacecraft contains an initial estimate for the shape of the asteroid.
+This shape can be a coarse estimate computed from radar measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid.
+This model is defined as a sequence of vertices and triangular facets defined by the vertices.
+This shape model is a widely used format for defining three-dimensional shapes in computer applications and has become the standard method for representing asteroid shapes~\cite{neese2004}.
+
+We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid.
+This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
+Given the time total time of flight the distance can be accurately computed using \( d = \frac{t_f}{2 c} \) where \( c \) is the constant speed of light.
+Assuming accurate knowledge of the pointing direction of the spacecraft we can compute a direction from the spacecraft to the measurement location on the surface.
+The output of this sensor is a vector, \( \vb{d}_i \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface of the asteroid. 
+Using the state of the asteroid, we can transform this measurement to the asteroid fixed frame using the simple t transformation
+\begin{align*}
+    \vb{p}_i = R_A^T R \vb{d}_i .
+\end{align*}
+
+Model a lidar on spacecraft which gives vector of the surface in spacecraft fixed frame.
+
+This vector is transformed to the asteroid frame using \( R_A \).
+
+Present algorithm for mesh update
 

### 2018-03-31 abstract.tex
Starting to describe our algorithm

@@
 We assume that the spacecraft contains an initial estimate for the shape of the asteroid.
-This shape can be a coarse estimate computed from radar measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid.
+This shape can be a coarse estimate computed from radar measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid, such as that shown in~\cref{fig:initial_ellipsoid} which represents the maximum axes for asteroid Castalia.
 This model is defined as a sequence of vertices and triangular facets defined by the vertices.
 This shape model is a widely used format for defining three-dimensional shapes in computer applications and has become the standard method for representing asteroid shapes~\cite{neese2004}.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{example-image-golden}
+    \caption{Triaxial Ellipsoid Triangular Shape Model~\label{fig:initial_ellipsoid}}
+\end{figure}
 
-We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid.
+We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid~\cite{zuber1997,zuber2000}.
 This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
@@
 \end{align*}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{example-image-golden}
+    \caption{Simulated LIDAR measurements of asteroid Castalia~\label{fig:lidar_example}}
+\end{figure}
+Given many measurements, \( \vb{p}_i \), of the asteroid surface we can efficiently update our initial shape estimate to that of the true surface.
 
-Model a lidar on spacecraft which gives vector of the surface in spacecraft fixed frame.
+Compute angle between measurement and all vertices of shape
 
-This vector is transformed to the asteroid frame using \( R_A \).
+Figure out geodesic distance
 
-Present algorithm for mesh update
+Update both radius of vertex and weight
 

### 2018-03-31 abstract.tex
Starting on algorithm description

@@
 This shape can be a coarse estimate computed from radar measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid, such as that shown in~\cref{fig:initial_ellipsoid} which represents the maximum axes for asteroid Castalia.
-This model is defined as a sequence of vertices and triangular facets defined by the vertices.
+This model is defined as a sequence of vertices, \( \vb{v}_i\), in the asteroid fixed frame and triangular facets, \( f_i = \bracket{\vb{v}_1, \vb{v}_2, \vb{v}_3}\), which are defined by the three vertices making up the facet.
 This shape model is a widely used format for defining three-dimensional shapes in computer applications and has become the standard method for representing asteroid shapes~\cite{neese2004}.
@@
 
+Our algorithm applies a Bayesian framework to radially modify each vertex \( \vb{v}_i\) of the shape estimate based on measurement \( \vb{p}_i\). 
+This approach alleviates much of complexity of incorporating new vertices or surface triangulation common in surface reconstruction methods~\cite{berg2008}.
+This assumption means that the total number of vertices of the shape model is fixed.
+However, additional detail, in the form of additional vertices, is possible by using standard mesh subdivision algorithms~\cite{orourke1998}.
+
+The radial distance of each vertex is assumed to be distributed according to the Gaussian distribution
+\begin{align*}
+    \norm{\vb{v}_i} \sim \mathcal{N}(r_0, w_0^2)
+\end{align*}
+where \( r_0 \) is the initial estimate of the radial distance of vertex \( \vb{v}_i\) and \( w_0 \) is the initial variance, or confidence, in the radial distance.
+The radial distance of each measurement \( \vb{p}_i\) is also assumed to be distributed according to the Gaussian distribution
+\begin{align*}
+    \norm{\vb{p}_i} \sim \mathcal{N}(r_{m,i}, w_{m,i}^2)
+\end{align*}
+where \( r_m = \norm{\vb{p}_i} \) defines the true radial distance of the surface vector measurement and \( w_m\) defines the variance of the measurement with respect to vertex \( \vb{v}_i\).
+
+The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vb{v}_i \).
+Here we use the geodesic distance to parameterize the difference, and hence  uncertainty, or associating the measurement with a given vertex.
+From spherical trigonometry the central angle between measurement \( \vb{p}_i \) and vertex \( \vb{v}_i \) of the shape estimate is
+\begin{align}
+    \Delta \sigma_i = \arctan \parenth{\frac{\norm{\vb{p}_i \times \vb{v}_i}}{\vb{p}_i \cdot \vb{v}_i }}.
+\end{align}
+The variance of measurement \( \vb{p}_i \) with respect to vertex \( \vb{v}_i \) is then defined as the arc length as
+\begin{align}
+    w_{m, i} = \norm{\vb{p}_i} \Delta \sigma .
+\end{align}
+This approach relates the uncertainty of the measurement with the distance to a given vertex.
+As a result, measurements which are far from a vertex, where \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty.
+
+From Bayes' theorem, the 
 Compute angle between measurement and all vertices of shape

### 2018-04-01 abstract.tex
Add some  todo for rest of abstract

@@
 As a result, measurements which are far from a vertex, where \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty. 
+From Bayes' theorem, the a posterior probability is
+\begin{align}
+    p(\norm{\vb{v}_i} | \norm{\vb{p}_i}) = \frac{p(\norm{\vb{p}_i} | \norm{\vb{v}_i}) p(\norm{\vb{v}_i})}{p(\norm{\vb{p}_i}} \propto p(\norm{\vb{p}_i} | \norm{\vb{v}_i}) p(\norm{\vb{v}_i}).
+\end{align}
+From the properties of a Gaussian the a posterior probability is also distributed according to a Gaussian distribution
+\begin{align}
+    Gaussian
+\end{align}
 
-From Bayes' theorem, the 
+When a measurement is far away from a given vertex, the influence of the measurement on the radial position of the vertex is diminished.
+
 Compute angle between measurement and all vertices of shape
@@
 
+Describe the simulation
+
+Assume initial ellipsoid
+
+Vertices are taken from the shape model and serve to emulate measurements from a lidar
+
+Each vertex is added in real time and only those within a certain area/angle are considered
+
 Reconstruction of asteroid Castalia
@@
 \section{Expected Results and Significance}
+Fast way to update mesh
 
-\subsection{Equations of Motion}
+Final paper will demonstrate how to use this updated mesh with the gravity model in the controller
 
-\subsection{Nonlinear Landing Controller}\label{sec:landing}
-
-\section{Expected Results and Significance}\label{sec:expected}
-
+Also compare the gravity of  estimate and truth model
 \bibliographystyle{AAS_publication} 

### 2018-04-01 abstract.tex
Working on abstract

@@
 \end{align}
-From the properties of a Gaussian the a posterior probability is also distributed according to a Gaussian distribution
+From the properties of a Gaussian the a posterior probability given a measurement is also distributed according to a Gaussian distribution
 \begin{align}
-    Gaussian
+    \mathcal{N} \parenth{\frac{w_{m, i}^2 r_0 + w_0^2 r_{m, i}}{w_0^2 + w_{m, i}^2} , \frac{w_0^2 + w_{m, i}^2}{w_0^2 + w_{m, i}^2}} .
 \end{align}
+The a posterior probability conditioned on the measurement is the weighted average of the prior knowledge and the measurement. 
+Measurements that are far from the vertex will have a high uncertainty or variance and will have a reduced impact on the vertex.
+Additional measurements are incoporated using a weighted average of prior belief and the measurement uncertainty.
+
+In order to improve the computational efficiency measurement updates are assumed to be local in nature.
+Instead of applying a measurement to all vertices of the mesh the measurement is only applied to the vertices which are within a specified region of the measurement.
 

### 2018-04-01 abstract.tex
Update abstract

@@
 The a posterior probability conditioned on the measurement is the weighted average of the prior knowledge and the measurement. 
-Measurements that are far from the vertex will have a high uncertainty or variance and will have a reduced impact on the vertex.
+Measurements that are far from the vertex will have a high uncertainty or variance and will have a reduced impact on the radial position of the vertex.
 Additional measurements are incoporated using a weighted average of prior belief and the measurement uncertainty.
@@
 In order to improve the computational efficiency measurement updates are assumed to be local in nature.
-Instead of applying a measurement to all vertices of the mesh the measurement is only applied to the vertices which are within a specified region of the measurement.
-
-When a measurement is far away from a given vertex, the influence of the measurement on the radial position of the vertex is diminished.
-
-Compute angle between measurement and all vertices of shape
-
-Figure out geodesic distance
-
-Update both radius of vertex and weight
+Instead of applying a measurement to all vertices of the mesh, the measurement is only applied to the vertices which are within a specified region of the measurement. 
+We define a region of interest, \( \Delta S \), about each measurement which defines the surface area over which the measurement will affect the mesh estimate.
+We relate \( \Delta S \) to an equivalent angular constraint using
+\begin{align}
+    \Delta \sigma_{max} = \sqrt \frac{\Delta S}{r_b^2}
+\end{align}
+where \( r_b \) defines the Brillouin  sphere radius, or the radius of the circumscribing sphere of the asteroid.
+Only vertices which satisy \( \Delta \sigma_i \leq \Delta \sigma_{max} \) are considered in the Bayesian update.
 
@@
 
-Describe the simulation
+Initial parameters for the simulation
 
-Assume initial ellipsoid
+Show the initial ellipsoid with  vertices in red
 
@@
 
+Show the final result
 \section{Expected Results and Significance}

### 2018-04-01 abstract.tex
Starting on example results

@@
 \section{Preliminary Results}
+Here we present initial results of reconstructing the shape of asteroid 4769 Castalia.
+Castalia is a potentially  hazardous asteroid and the first asteroid which used radar imaging to generate a 3D surface shape~\cite{hudson1994}.
+In this example, we seek to incrementally build and accurate shape of Castalia from an initial coarse triaxial ellipsoid model.
+Our initial shape for Castalia is a triaxial ellipsoid with semi-axes equal to \( \SI{1.8}{\kilo\meter} \times \SI{0.8}{\kilo\meter} \times \SI{0.8}{\kilo\meter}\) and shown in~\cref{fig:initial_mesh}.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{example-image}
+    \caption{Initial estimate for 4769 Castalia~\label{fig:initial_mesh}}
+\end{figure}
+
+Simulated measurements of the surface of 4769 Castalia are used to update the initial mesh estimate.
+The truth shape model, and the associated vertices, are used as simulated measurements of the shape of Castalia~\cite{neese2004}.
+The true shape model of 4769 Castalia is composed of \num{2048} vertices and \num{4092} triangular faces.
 

### 2018-04-01 abstract.tex
Finished with summary of results

@@
 \end{figure}
-
 Simulated measurements of the surface of 4769 Castalia are used to update the initial mesh estimate.
@@
 The true shape model of 4769 Castalia is composed of \num{2048} vertices and \num{4092} triangular faces.
+The initial ellipsoid is chosen to have approximately the same number of vertices as the final true shape and such that the total number of required vertices remains relatively constant.
+It is possible to incorporate more vertices, for example by spliting faces into numerous other faces, but this does not affect the general approach.
 
-Initial parameters for the simulation
+The vertices of the truth model are sorted according to increasing \( x \) component and incorporated into the mesh estimate one at a time. 
+Several views of the progress of the reconstruction is shown in~\cref{fig:reconstruction}.
+The initial mesh is modified by radially moving each vertex to best match the measurements.
+\begin{figure}
+    \centering
+    \subcaptionbox{Initial mesh estimate\label{fig:start}}{\includegraphics[width=0.5\textwidth]{figures/partial_initial.jpg}}~
+    \subcaptionbox{First vertex added\label{fig:first}}{\includegraphics[width=0.5\textwidth]{figures/partial_0.jpg}}
 
-Show the initial ellipsoid with  vertices in red
+    \subcaptionbox{\SI{25}{\percent} of vertices added\label{fig:quarter}}{\includegraphics[width=0.5\textwidth]{figures/partial_512.jpg}}~
+    \subcaptionbox{\SI{50}{\percent} of vertices added\label{fig:half}}{\includegraphics[width=0.5\textwidth]{figures/partial_1024.jpg}}
 
-Vertices are taken from the shape model and serve to emulate measurements from a lidar
+\subcaptionbox{\SI{75}{\percent} of vertices added\label{fig:threequarter}}{\includegraphics[width=0.5\textwidth]{figures/partial_1536.jpg}}~
+\subcaptionbox{Final reconstruction\label{fig:final}}{\includegraphics[width=0.5\textwidth]{figures/partial_2047.jpg}}
+\caption{4769 Castalia incremental reconstruction. The initial ellipsoid is incrementally modified by radially moving vertices to match the true shape model.~\label{fig:reconstruction}}
+\end{figure}
+\Cref{fig:first} shows that the first measurement only affects the mesh in a small local area.
+As a result, the mesh update is only considered over those vertices within \( \Delta S \) rather than the entire mesh. 
+Furthermore, regardless of the size of the shape model, or the total number of measurements the computational load will remain relatively constant and can be adjusted through \( \Delta S\).
 
-Each vertex is added in real time and only those within a certain area/angle are considered
-
-Reconstruction of asteroid Castalia
-
-Show the final result
 \section{Expected Results and Significance}

### 2018-04-01 abstract.tex
Finish a beta draft of abstract

@@
 The initial mesh is modified by radially moving each vertex to best match the measurements.
-\begin{figure}
+\begin{figure}[h]
     \centering
@@
 \section{Expected Results and Significance}
-Fast way to update mesh
+This work will present an efficient method of reconstructing the shape of an asteroid from range measurements. 
+The method allows for a real time approach to incrementally update a shape model of an asteroid.
+Instead of performing a global update, each measurement is only treated locally to the shape. 
+This updated shape model is then used in a polyhedron potential model to enable a more accurate dynamic model near the asteroid.
+This approach avoids the lengthy mapping phase of many spacecraft missions to asteroids and enables a more responsive mission profile which allows the spacecraft to directly transition from arrival to surface operations.
+Utilizing the updated shape model allows for real time feedback control as the dynamic model is continually updated to best match measurements of the surfac.
 
-Final paper will demonstrate how to use this updated mesh with the gravity model in the controller
-
-Also compare the gravity of  estimate and truth model
 \bibliographystyle{AAS_publication} 

### 2018-04-02 abstract.tex
Write abstract

@@
 \begin{abstract}
-    Abstract for paper
+    Knowledge of the shape of an asteroid is crucial for spacecraft operations.
+    The standard method of determining the gravitational potential, through the use of a polyhedral potential model, is dependent on the shape model.
+    Furthermore, accurate landing or low altitude operations requires an accurate knowledge of the surface topology. 
+    The typical approach to shape determination requires an extensive ``mapping'' phase of the mission over which extensive measurements are collected and transmitted for Earth-based processing.
+    Instead, we present an efficient method for estimating the shape of an asteroid in real time.
+    Range measurements of the surface are used to incrementally correct an initial shape estimate.
+    This update procedure occurs in real time and provides a more accurate model of the asteroid shape.
+    This shape model is then used in a nonlinear controller to track a desired trajectory about the asteroid.
+    The closed loop approach allows a spacecraft to approach and operate near an unknown asteroid while autonomously generating a surface shape model.
+    We demonstrate this approach through a dynamic simulation about asteroid 4769 Castalia.
+
 \end{abstract}

### 2018-04-02 abstract.tex
Correct typos

@@
 Due to their low mass, which in turn causes a low gravitational attraction, asteroids may have irregular shapes.
-Furthermore, asteroids may also have a chaotic spin state due to the absorption and emmitance of solar radiation~\cite{rubincam2000}.
+Furthermore, asteroids may also have a chaotic spin state due to the absorption and emittance of solar radiation~\cite{rubincam2000}.
 As a result, approaches utilizing an inverse square gravitational model do not capture the  true dynamic environment.
@@
 Due to their small size, frequently less than \SI{1}{\kilo\meter}, and low albedo, the reflected energy of these asteroids is insufficient for reliable detection or tracking.
-Therefore, the dynamics model of the asteroid is relatively coarse prior to insitu measurements from a dedicated spacecraft.
-As a result, any spacecraft mission to an asteroid must include the ability to update the dynamic model given insitu measurements and robustness to unmodelled forces.
+Therefore, the dynamics model of the asteroid is relatively coarse prior to in situ measurements from a dedicated spacecraft.
+As a result, any spacecraft mission to an asteroid must include the ability to update the dynamic model given in situ measurements and robustness to unmodelled forces.
 
@@
 For operations around asteroids, the ratio is relatively large which causes a much larger coupling between the translational and rotational states.
-References~\cite{elmasri2005} and~\cite{sanyal2004a} investigated the copuling of an elastic dumbbell spacecraft in orbit about a central body, but only considered teh case of a spherically symmetric central body.
+References~\cite{elmasri2005} and~\cite{sanyal2004a} investigated the coupling of an elastic dumbbell spacecraft in orbit about a central body, but only considered the case of a spherically symmetric central body.
 Furthermore, the spacecraft model is assumed to remain in a planar orbit.
@@
 % Gravity model is important and dependent on shape
-An accurate gravitational potential model is critical for performing low alititude and/or surface operations around asteroids.
+An accurate gravitational potential model is critical for performing low altitude and/or surface operations around asteroids.
 Due to the irregular shape, trajectories will pass within the Brillouin sphere where the typical spherical harmonic model diverges from the true gravitational potential.
@@
 The method provides the exact potential for a given faceted shape model.
-As a result, the accuracy of the gravitational potential is primarily dependent on the accuracy with which the shape modelrepresents the true surface topology.
+As a result, the accuracy of the gravitational potential is primarily dependent on the accuracy with which the shape model represents the true surface topology.
 A high fidelity shape, which necessarily has many vertices and faces, is required for an accurate computation of the gravitational acceleration.
@@
 
-% Challenges invovled in operation near asteroids (gravity, shpae, distance)
+% Challenges involved in operation near asteroids (gravity, shape, distance)
 % generating the shape from the ground is difficult
 Prior to the arrival of a spacecraft at an asteroid, Earth based sensors are used to characterize the body.
-Using both optical and radar sensors allows for the precise orbit of the asteorid to be determined.
+Using both optical and radar sensors allows for the precise orbit of the asteroid to be determined.
 Another vital task is the determination of the asteroid shape from radar data~\cite{hudson1994,busch2011}.
@@
 This computationally intensive approach is only able to capture the gross size and shape and is unable to capture the minute surface features of the asteroid.
-Frequently, only a rough triaxial ellipsoid model is possible from the ground and an accurate shape must be determined only after a spacecraft has rendezvouzed with the asteroid.
-As a result, on arrival the gravitional environment near the asteroid is unknown as the shape of the asteroid is poorly modelled.
+Frequently, only a rough triaxial ellipsoid model is possible from the ground and an accurate shape must be determined only after a spacecraft has rendezvoused with the asteroid.
+As a result, on arrival the gravitational environment near the asteroid is unknown as the shape of the asteroid is poorly modeled.
 
-% on arrival spacecraft spend long periods mapping, and depending on misison this might be unallowable
+% on arrival spacecraft spend long periods mapping, and depending on mission this might be unallocable
 On approach to an asteroid, spacecraft navigation and guidance is primarily based on ground measurements.
 After arrival, a spacecraft will generally spend months or years in a mapping mission phase~\cite{kubota2003,cole1998}.
-During this period, spacecraft sensors, such as onboard optical telescopes or Light radio Detection and Ranging (LIDAR), are used to characterize the asteroid.
+During this period, spacecraft sensors, such as on board optical telescopes or Light radio Detection and Ranging (LIDAR), are used to characterize the asteroid.
 The resulting imagery and range data is transmitted to the ground and the resulting asteroid shape and motion is estimated. 
@@
 
-Using Hamiltons principle gives the inertial equations of motion of the dumbbell spacecraft as
+Using Hamilton's principle gives the inertial equations of motion of the dumbbell spacecraft as
 \begin{align}
@@
 The output of this sensor is a vector, \( \vb{d}_i \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface of the asteroid. 
-Using the state of the asteroid, we can transform this measurement to the asteroid fixed frame using the simple t transformation
+Using the state of the asteroid, we can transform this measurement to the asteroid fixed frame using the simple transformation
 \begin{align*}
@@
 As a result, measurements which are far from a vertex, where \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty. 
-From Bayes' theorem, the a posterior probability is
+From Bayes' theorem, the posterior probability is
 \begin{align}
@@
 \end{align}
-From the properties of a Gaussian the a posterior probability given a measurement is also distributed according to a Gaussian distribution
+From the properties of a Gaussian the posterior probability given a measurement is also distributed according to a Gaussian distribution
 \begin{align}
@@
 \end{align}
-The a posterior probability conditioned on the measurement is the weighted average of the prior knowledge and the measurement. 
+The posterior probability conditioned on the measurement is the weighted average of the prior knowledge and the measurement. 
 Measurements that are far from the vertex will have a high uncertainty or variance and will have a reduced impact on the radial position of the vertex.
-Additional measurements are incoporated using a weighted average of prior belief and the measurement uncertainty.
+Additional measurements are incorporated using a weighted average of prior belief and the measurement uncertainty.
 
@@
 where \( r_b \) defines the Brillouin  sphere radius, or the radius of the circumscribing sphere of the asteroid.
-Only vertices which satisy \( \Delta \sigma_i \leq \Delta \sigma_{max} \) are considered in the Bayesian update.
+Only vertices which satisfy \( \Delta \sigma_i \leq \Delta \sigma_{max} \) are considered in the Bayesian update.
 
@@
 The initial ellipsoid is chosen to have approximately the same number of vertices as the final true shape and such that the total number of required vertices remains relatively constant.
-It is possible to incorporate more vertices, for example by spliting faces into numerous other faces, but this does not affect the general approach.
+It is possible to incorporate more vertices, for example by splitting faces into numerous other faces, but this does not affect the general approach.
 
@@
 This approach avoids the lengthy mapping phase of many spacecraft missions to asteroids and enables a more responsive mission profile which allows the spacecraft to directly transition from arrival to surface operations.
-Utilizing the updated shape model allows for real time feedback control as the dynamic model is continually updated to best match measurements of the surfac.
+Utilizing the updated shape model allows for real time feedback control as the dynamic model is continually updated to best match measurements of the surface.
 

### 2018-04-02 abstract.tex
Correct some typos and remove extra plots

@@
     We demonstrate this approach through a dynamic simulation about asteroid 4769 Castalia.
-
 \end{abstract}
@@
 Therefore, the dynamics model of the asteroid is relatively coarse prior to in situ measurements from a dedicated spacecraft.
-As a result, any spacecraft mission to an asteroid must include the ability to update the dynamic model given in situ measurements and robustness to unmodelled forces.
+As a result, any spacecraft mission to an asteroid must include the ability to update the dynamic model given in situ measurements and remain robust to unmodelled forces.
 
@@
 For operations around asteroids, the ratio is relatively large which causes a much larger coupling between the translational and rotational states.
-References~\cite{elmasri2005} and~\cite{sanyal2004a} investigated the coupling of an elastic dumbbell spacecraft in orbit about a central body, but only considered the case of a spherically symmetric central body.
+References~\citenum{elmasri2005} and~\citenum{sanyal2004a} investigated the coupling of an elastic dumbbell spacecraft in orbit about a central body, but only considered the case of a spherically symmetric central body.
 Furthermore, the spacecraft model is assumed to remain in a planar orbit.
 As a result, these developments are not directly applicable to motion about an asteroid, which experiences highly non-Keplerian motion.
-Reference~\cite{misra2015b} investigated the effect of coupled motion on long term trajectories around asteroids.
+Reference~\citenum{misra2015b} investigated the effect of coupled motion on long term trajectories around asteroids.
 However, the analysis only considered a second order spherical harmonic gravitational potential model. 
@@
 An accurate gravitational potential model is critical for performing low altitude and/or surface operations around asteroids.
-Due to the irregular shape, trajectories will pass within the Brillouin sphere where the typical spherical harmonic model diverges from the true gravitational potential.
-With respect to asteroid missions, the standard approach to compute the gravitational potential is the polyhedron potential model~\cite{werner1996}.
+Due to the irregular shape, trajectories will pass within the Brillouin sphere, where the typical spherical harmonic model diverges from the true gravitational potential.
+The standard approach for asteroid missions is to compute the gravitational potential using a polyhedron potential model~\cite{werner1996}.
 The polyhedral potential model provides the exact gravitational potential, and subsequently the gravitational acceleration, for a given triangular faceted shape model of an asteroid.
-The method provides the exact potential for a given faceted shape model.
-As a result, the accuracy of the gravitational potential is primarily dependent on the accuracy with which the shape model represents the true surface topology.
-A high fidelity shape, which necessarily has many vertices and faces, is required for an accurate computation of the gravitational acceleration.
-The determination of the shape of the asteroid surface is crucial for both determining the gravitational potential as well as operations near the surface.
+The method provides the exact potential at any point outside the body for a given shape model.
+As a result, the accuracy of the gravitational potential is primarily dependent on the accuracy with which the shape model represents the true surface.
+A high fidelity shape, which necessarily has many vertices and faces, is required for an accurate computation of the gravitational acceleration and enabling low altitude operations.
 
@@
 The current approach is based on an estimation scheme which iteratively perturbs a shape to match given radar data.
-This computationally intensive approach is only able to capture the gross size and shape and is unable to capture the minute surface features of the asteroid.
-Frequently, only a rough triaxial ellipsoid model is possible from the ground and an accurate shape must be determined only after a spacecraft has rendezvoused with the asteroid.
-As a result, on arrival the gravitational environment near the asteroid is unknown as the shape of the asteroid is poorly modeled.
+This computationally intensive approach is only able to capture the gross size and shape and is unable to capture the small surface features of the asteroid.
+Frequently, only a coarse model is possible from the ground and an accurate shape must be determined only after a spacecraft has rendezvoused with the asteroid.
+As a result, upon arrival the gravitational environment near the asteroid is poorly modeled as the shape of the asteroid is not accurate.
+Therefore, the polyhedron potential model is not appropriate immediately upon arrival but rather only after the shape has been determined.
 
@@
 The resulting imagery and range data is transmitted to the ground and the resulting asteroid shape and motion is estimated. 
-During this mapping phase the spacecraft must remain in a quiescent state devotes entirely to mapping the surface.
-Depending on the mission type this long period of mapping is crucial to determining an ideal landing location, such as the Asteroid Redirect Mission~\cite{gates2015}. 
+During this mapping phase the spacecraft must remain in a quiescent state devoted entirely to mapping the surface.
+Depending on the mission type this long period of mapping is crucial to the mission, such as sample collection~\cite{gates2015}. 
 However, other missions, such as asteroid mitigation, may be severely limited by the time and ground resources required to generate a surface shape.
 Furthermore, the long distances involved necessitate on-board autonomy to enable to spacecraft to operate without ground communications.
-The dependency on expensive ground based shape reconstruction techniques limit the ability for spacecraft autonomously operate and land at asteroids.
+The dependency on expensive ground based shape reconstruction techniques limit the ability of spacecraft to autonomously operate at asteroids.
+Mitigation of this ground based surface modeling will greatly expand the range of missions possible.
 
@@
 Our approach is able to operate in real time and incrementally update the shape model of an asteroid as new range measurements are collected.
-This approach allows for the shape to be continually updated as range measurements are used to locally modify the shape estimate instead of a global operation.
+This approach allows for the shape to be continually updated as range measurements are used to locally modify the shape estimate.
 Furthermore, this updated shape is then used in a nonlinear controller to enable the tracking of a landing trajectory to the surface.
@@
 The asteroid is modeled as a constant density polyhedron with constant, and known, spin about its maximum moment of inertia. 
-Without loss of generality, we define body fixed frames for both the spacecraft and asteroid which are aligned with the principle axes of each body and originate at their respective center of mass. 
+Without loss of generality, we define body fixed frames for both the spacecraft and asteroid, which are aligned with the principle axes of each body and originate at their respective center of mass. 
 The kinematics of the dumbbell and asteroid are described in the inertial frame by
@@
 
-Using Hamilton's principle gives the inertial equations of motion of the dumbbell spacecraft as
+Using Hamilton's principle gives the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
 \begin{align}
@@
 \end{align}
-The vectors \( \vecbf{z}_1 \) and \( \vecbf{z}_2\) define the position of the dumbbell masses as represented in the asteroid fixed frame and are defined as
+The vectors \( \vecbf{z}_1 \) and \( \vecbf{z}_2\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
 \begin{align}
@@
 We assume that the spacecraft contains an initial estimate for the shape of the asteroid.
-This shape can be a coarse estimate computed from radar measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid, such as that shown in~\cref{fig:initial_ellipsoid} which represents the maximum axes for asteroid Castalia.
+This shape can be a coarse estimate computed from ground measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid, such as that shown in~\cref{fig:start} which represents the maximum axes for asteroid Castalia.
 This model is defined as a sequence of vertices, \( \vb{v}_i\), in the asteroid fixed frame and triangular facets, \( f_i = \bracket{\vb{v}_1, \vb{v}_2, \vb{v}_3}\), which are defined by the three vertices making up the facet.
-This shape model is a widely used format for defining three-dimensional shapes in computer applications and has become the standard method for representing asteroid shapes~\cite{neese2004}.
+The vertices are assumed to be ordered in a counterclockwise fashion about each facet. 
+As a result, the outward facing normal vector to each face is implicitly defined without any additional data.
+This shape representation is a widely used format for defining three-dimensional shapes in computer applications and has become the standard method for representing asteroid shapes~\cite{neese2004}.
 \begin{figure}
     \centering
-    \includegraphics[width=0.5\textwidth]{example-image-golden}
-    \caption{Triaxial Ellipsoid Triangular Shape Model~\label{fig:initial_ellipsoid}}
+    \includegraphics[width=0.75\textwidth]{figures/castalia_raycasting_plot.jpg}
+    \caption{Simulated LIDAR measurements of asteroid Castalia~\label{fig:lidar_example}}
 \end{figure}
@@
 This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
-Given the time total time of flight the distance can be accurately computed using \( d = \frac{t_f}{2 c} \) where \( c \) is the constant speed of light.
+Given the time total time of flight, the distance can be accurately computed using \( d = \frac{\Delta TOF}{2 c} \) where \( c \) is the constant speed of light.
 Assuming accurate knowledge of the pointing direction of the spacecraft we can compute a direction from the spacecraft to the measurement location on the surface.
@@
 \end{align*}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{example-image-golden}
-    \caption{Simulated LIDAR measurements of asteroid Castalia~\label{fig:lidar_example}}
-\end{figure}
 Given many measurements, \( \vb{p}_i \), of the asteroid surface we can efficiently update our initial shape estimate to that of the true surface.
+\Cref{fig:lidar_example} shows asteroid 4769 Castalia and a representation of several LIDAR measurements. 
+The spacecraft measures the range between itself and the asteroid surface to several points within the field of view of the sensor. 
+These measurements provide a collection of points which lie on the surface of the asteroid, and by combining many points, a so called ``point cloud'', allows us to reconstruct the shape.
 
@@
 
-The radial distance of each vertex is assumed to be distributed according to the Gaussian distribution
+The radial distance of each vertex, \( v_i = \norm{\vb{v}_i}\), is assumed to be distributed according to the Gaussian distribution
 \begin{align*}
-    \norm{\vb{v}_i} \sim \mathcal{N}(r_0, w_0^2)
+    v_i \sim \mathcal{N}(r_i, w_i^2)
 \end{align*}
-where \( r_0 \) is the initial estimate of the radial distance of vertex \( \vb{v}_i\) and \( w_0 \) is the initial variance, or confidence, in the radial distance.
-The radial distance of each measurement \( \vb{p}_i\) is also assumed to be distributed according to the Gaussian distribution
+where \( r_i \) is the initial estimate of the radial distance of vertex \( \vb{v}_i\) and \( w_i \) is the initial variance, or confidence, in the radial distance.
+The radial distance of each measurement, \( p_{j,i} = \vb{p}_j\), is also assumed to be distributed according to the Gaussian distribution
 \begin{align*}
-    \norm{\vb{p}_i} \sim \mathcal{N}(r_{m,i}, w_{m,i}^2)
+    p_{j,i} \sim \mathcal{N}(r_{j,i}, w_{j,i}^2)
 \end{align*}
-where \( r_m = \norm{\vb{p}_i} \) defines the true radial distance of the surface vector measurement and \( w_m\) defines the variance of the measurement with respect to vertex \( \vb{v}_i\).
+where \( r_{j,i} = \norm{\vb{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i}\) defines the variance of the measurement with respect to vertex \( \vb{v}_i\).
 
 The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vb{v}_i \).
-Here we use the geodesic distance to parameterize the difference, and hence  uncertainty, or associating the measurement with a given vertex.
+Here we use the geodesic distance to parameterize the difference, and hence  uncertainty, of associating the measurement with a given vertex.
 From spherical trigonometry the central angle between measurement \( \vb{p}_i \) and vertex \( \vb{v}_i \) of the shape estimate is
 \begin{align}
-    \Delta \sigma_i = \arctan \parenth{\frac{\norm{\vb{p}_i \times \vb{v}_i}}{\vb{p}_i \cdot \vb{v}_i }}.
+    \Delta \sigma_{j,i} = \arctan \parenth{\frac{\norm{\vb{p}_j \times \vb{v}_i}}{\vb{p}_j \cdot \vb{v}_i }}.
 \end{align}
@@
 \begin{align}
-    w_{m, i} = \norm{\vb{p}_i} \Delta \sigma .
+    w_{j, i} = \norm{\vb{p}_j} \Delta \sigma_{j,i} .
 \end{align}
-This approach relates the uncertainty of the measurement with the distance to a given vertex.
+This approach relates the uncertainty of the measurement, \( \vb{p}_j \) with the geodesic distance to a given vertex, \( \vb{v}_i \).
 As a result, measurements which are far from a vertex, where \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty. 
@@
 \begin{align}
-    p(\norm{\vb{v}_i} | \norm{\vb{p}_i}) = \frac{p(\norm{\vb{p}_i} | \norm{\vb{v}_i}) p(\norm{\vb{v}_i})}{p(\norm{\vb{p}_i}} \propto p(\norm{\vb{p}_i} | \norm{\vb{v}_i}) p(\norm{\vb{v}_i}).
+    p(v_i | p_{j, i}) = \frac{p(p_{j, i} | v_i) p(v_i)}{p( p_{j, i})} \propto p(p_{j,i} | v_i) p(v_i).
 \end{align}
-From the properties of a Gaussian the posterior probability given a measurement is also distributed according to a Gaussian distribution
-\begin{align}
-    \mathcal{N} \parenth{\frac{w_{m, i}^2 r_0 + w_0^2 r_{m, i}}{w_0^2 + w_{m, i}^2} , \frac{w_0^2 + w_{m, i}^2}{w_0^2 + w_{m, i}^2}} .
+From the properties of a Gaussian, the posterior probability given a measurement is also distributed according to a Gaussian distribution
+\begin{align}\label{eq:posterior_probability}
+    \mathcal{N} \parenth{\frac{w_{j, i}^2 r_i + w_i^2 r_{j, i}}{w_i^2 + w_{j, i}^2} , \frac{w_i^2 + w_{j, i}^2}{w_i^2  w_{j, i}^2}} .
 \end{align}
-The posterior probability conditioned on the measurement is the weighted average of the prior knowledge and the measurement. 
+From~\cref{eq:posterior_probability}, the posterior probability conditioned on the measurement is the weighted average of the prior knowledge and the measurement. 
 Measurements that are far from the vertex will have a high uncertainty or variance and will have a reduced impact on the radial position of the vertex.
@@
 where \( r_b \) defines the Brillouin  sphere radius, or the radius of the circumscribing sphere of the asteroid.
-Only vertices which satisfy \( \Delta \sigma_i \leq \Delta \sigma_{max} \) are considered in the Bayesian update.
+Only vertices which satisfy \( \Delta \sigma_i \leq \Delta \sigma_{max} \) are considered in the Bayesian update shown in~\cref{eq:posterior_probability}.
 
 \section{Preliminary Results}
-Here we present initial results of reconstructing the shape of asteroid 4769 Castalia.
-Castalia is a potentially  hazardous asteroid and the first asteroid which used radar imaging to generate a 3D surface shape~\cite{hudson1994}.
-In this example, we seek to incrementally build and accurate shape of Castalia from an initial coarse triaxial ellipsoid model.
-Our initial shape for Castalia is a triaxial ellipsoid with semi-axes equal to \( \SI{1.8}{\kilo\meter} \times \SI{0.8}{\kilo\meter} \times \SI{0.8}{\kilo\meter}\) and shown in~\cref{fig:initial_mesh}.
 \begin{figure}[h]
     \centering
-    \includegraphics[width=0.5\textwidth]{example-image}
-    \caption{Initial estimate for 4769 Castalia~\label{fig:initial_mesh}}
-\end{figure}
-Simulated measurements of the surface of 4769 Castalia are used to update the initial mesh estimate.
-The truth shape model, and the associated vertices, are used as simulated measurements of the shape of Castalia~\cite{neese2004}.
-The true shape model of 4769 Castalia is composed of \num{2048} vertices and \num{4092} triangular faces.
-The initial ellipsoid is chosen to have approximately the same number of vertices as the final true shape and such that the total number of required vertices remains relatively constant.
-It is possible to incorporate more vertices, for example by splitting faces into numerous other faces, but this does not affect the general approach.
-
-The vertices of the truth model are sorted according to increasing \( x \) component and incorporated into the mesh estimate one at a time. 
-Several views of the progress of the reconstruction is shown in~\cref{fig:reconstruction}.
-The initial mesh is modified by radially moving each vertex to best match the measurements.
-\begin{figure}[h]
-    \centering
-    \subcaptionbox{Initial mesh estimate\label{fig:start}}{\includegraphics[width=0.5\textwidth]{figures/partial_initial.jpg}}~
+    \subcaptionbox{Initial mesh estimate\label{fig:start}}{\includegraphics[height=0.2\textheight,width=0.5\textwidth,keepaspectratio]{figures/partial_initial.jpg}}~
     \subcaptionbox{First vertex added\label{fig:first}}{\includegraphics[width=0.5\textwidth]{figures/partial_0.jpg}}
@@
     \subcaptionbox{Final reconstruction\label{fig:final}}{\includegraphics[width=0.5\textwidth]{figures/partial_2047.jpg}}
-\caption{4769 Castalia incremental reconstruction. The initial ellipsoid is incrementally modified by radially moving vertices to match the true shape model.~\label{fig:reconstruction}}
+    \caption{4769 Castalia incremental reconstruction. The initial ellipsoid is incrementally modified by radially moving each vertex to best match the measurements.~\label{fig:reconstruction}}
 \end{figure}
+Here we present initial results of reconstructing the shape of asteroid 4769 Castalia.
+Castalia is a potentially  hazardous asteroid and the first asteroid which used radar imaging to generate a 3D surface shape~\cite{hudson1994}.
+In this example, we seek to incrementally build an accurate shape of Castalia from an initial triaxial ellipsoid model.
+Our initial shape for Castalia is a triaxial ellipsoid with semi-axes equal to \( \SI{1.8}{\kilo\meter} \times \SI{0.8}{\kilo\meter} \times \SI{0.8}{\kilo\meter}\) and shown in~\cref{fig:start}.
+We use this choice of initial estimate since the semi-major axes of an asteroid are able to be computed based on Earth-measurements~\cite{busch2011}.
+Furthermore, this type of model also allows for the use of analytical gravitational models for use in preliminary analysis or in the absence of higher fidelity shape information~\cite{scheeres1994}.
+
+Simulated measurements of the surface of 4769 Castalia are used to update the initial mesh estimate.
+The truth shape model, and the associated vertices, are used as simulated measurements of the shape of Castalia~\cite{neese2004}.
+The true shape model of 4769 Castalia is composed of \num{2048} vertices and \num{4092} triangular faces.
+The initial ellipsoid is chosen to have approximately the same number of vertices as the final true shape and such that the total number of vertices remains constant.
+It is possible to incorporate more vertices, for example by splitting faces into smaller faces, but this does not affect the general approach.
+
+The vertices of the truth model are sorted according to increasing \( x \) component and incorporated into the mesh estimate one at a time. 
+Several views of the progress of the reconstruction is shown in~\cref{fig:reconstruction}.
+The initial mesh is modified by radially moving each vertex to best match the measurements.
 \Cref{fig:first} shows that the first measurement only affects the mesh in a small local area.
 As a result, the mesh update is only considered over those vertices within \( \Delta S \) rather than the entire mesh. 
-Furthermore, regardless of the size of the shape model, or the total number of measurements the computational load will remain relatively constant and can be adjusted through \( \Delta S\).
+Furthermore, regardless of the size of the shape model, or the total number of measurements, the computational load can be adjusted through the choice of \( \Delta S \).
+Changing the value of \( \Delta S \) will impact the number of vertices that are considered in the Bayesian updated.
 
@@
 The method allows for a real time approach to incrementally update a shape model of an asteroid.
-Instead of performing a global update, each measurement is only treated locally to the shape. 
+Instead of performing a global update, each measurement is applied locally to the shape. 
 This updated shape model is then used in a polyhedron potential model to enable a more accurate dynamic model near the asteroid.
-This approach avoids the lengthy mapping phase of many spacecraft missions to asteroids and enables a more responsive mission profile which allows the spacecraft to directly transition from arrival to surface operations.
+This approach avoids the lengthy mapping phase of many spacecraft missions and enables a more responsive mission profile which allows the spacecraft to directly transition from arrival to surface operations.
 Utilizing the updated shape model allows for real time feedback control as the dynamic model is continually updated to best match measurements of the surface.

### 2018-04-03 abstract.tex
Correct error in equation
Update abstract with comments from Dr. Lee

@@
 
-\title{Real Time Shape Reconstruction for Near Earth Asteroid Landing}
+\title{Real Time Adaptive Shape Reconstruction for Asteroid Landing}
 
@@
 Furthermore, the long distances involved necessitate on-board autonomy to enable to spacecraft to operate without ground communications.
+Similarly, during landing the spacecraft will require the ability to sense and model the surface topography in order to safely land in an unknown enviornment.
 The dependency on expensive ground based shape reconstruction techniques limit the ability of spacecraft to autonomously operate at asteroids.
@@
 where \( r_i \) is the initial estimate of the radial distance of vertex \( \vb{v}_i\) and \( w_i \) is the initial variance, or confidence, in the radial distance.
-The radial distance of each measurement, \( p_{j,i} = \vb{p}_j\), is also assumed to be distributed according to the Gaussian distribution
+The radial distance of each measurement, \( p_{j,i} = \norm{\vb{p}_j}\), is also assumed to be distributed according to the Gaussian distribution
 \begin{align*}
@@
 where \( r_{j,i} = \norm{\vb{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i}\) defines the variance of the measurement with respect to vertex \( \vb{v}_i\).
+Each measurement is defined by the index \( j \) while the associated vertex is defined by \( i \). 
+As a result, the measurement \( p_{j, i} \) defines the distribution of measurement \( j \) with respect to vertex \( i \). 
+A given measurement may be used to update one or several vertices.
 
@@
 \end{align}
-From the properties of a Gaussian, the posterior probability given a measurement is also distributed according to a Gaussian distribution
+From the properties of a Gaussian, the posterior probability given a measurement is also distributed according to a Gaussian distribution~\cite{bishop2006} and given by
 \begin{align}\label{eq:posterior_probability}
-    \mathcal{N} \parenth{\frac{w_{j, i}^2 r_i + w_i^2 r_{j, i}}{w_i^2 + w_{j, i}^2} , \frac{w_i^2 + w_{j, i}^2}{w_i^2  w_{j, i}^2}} .
+    \mathcal{N} \parenth{\frac{w_{j, i}^2 r_i + w_i^2 r_{j, i}}{w_i^2 + w_{j, i}^2} , \frac{w_i^2  w_{j, i}^2}{w_i^2 +  w_{j, i}^2}} .
 \end{align}
@@
     \centering
-    \subcaptionbox{Initial mesh estimate\label{fig:start}}{\includegraphics[height=0.2\textheight,width=0.5\textwidth,keepaspectratio]{figures/partial_initial.jpg}}~
-    \subcaptionbox{First vertex added\label{fig:first}}{\includegraphics[width=0.5\textwidth]{figures/partial_0.jpg}}
+    \subcaptionbox{Initial mesh estimate\label{fig:start}}{\includegraphics[height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/partial_initial.jpg}}~
+    \subcaptionbox{First measurement added\label{fig:first}}{\includegraphics[width=0.5\textwidth]{figures/partial_0.jpg}}
 
-    \subcaptionbox{\SI{25}{\percent} of vertices added\label{fig:quarter}}{\includegraphics[width=0.5\textwidth]{figures/partial_512.jpg}}~
-    \subcaptionbox{\SI{50}{\percent} of vertices added\label{fig:half}}{\includegraphics[width=0.5\textwidth]{figures/partial_1024.jpg}}
+    \subcaptionbox{\SI{25}{\percent} of measurments added\label{fig:quarter}}{\includegraphics[width=0.5\textwidth]{figures/partial_512.jpg}}~
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:half}}{\includegraphics[width=0.5\textwidth]{figures/partial_1024.jpg}}
 
-    \subcaptionbox{\SI{75}{\percent} of vertices added\label{fig:threequarter}}{\includegraphics[width=0.5\textwidth]{figures/partial_1536.jpg}}~
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:threequarter}}{\includegraphics[width=0.5\textwidth]{figures/partial_1536.jpg}}~
     \subcaptionbox{Final reconstruction\label{fig:final}}{\includegraphics[width=0.5\textwidth]{figures/partial_2047.jpg}}

### 2018-04-08 abstract.tex
Incorporate some corrections from christine

@@
     The standard method of determining the gravitational potential, through the use of a polyhedral potential model, is dependent on the shape model.
-    Furthermore, accurate landing or low altitude operations requires an accurate knowledge of the surface topology. 
+    Furthermore, accurate landing or low altitude operations requires accurate knowledge of the surface topology. 
     The typical approach to shape determination requires an extensive ``mapping'' phase of the mission over which extensive measurements are collected and transmitted for Earth-based processing.
@@
 Small solar system bodies, such as asteroids and comets, continue to remain a focus of scientific study.
-The small size of these bodies prevents the formation of large internal pressures and temperatures which help to preserve the early chemistry of the solar system.
+The small size of these bodies prevents the formation of large internal pressures and temperatures which helps to preserve the early chemistry of the solar system.
 This insight offers additional detail into the formation of the Earth and also of the probable formation of other extrasolar planetary bodies.
@@
 In addition, the vast majority of asteroids are difficult to track and characterize using ground based sensors.
-Due to their small size, frequently less than \SI{1}{\kilo\meter}, and low albedo, the reflected energy of these asteroids is insufficient for reliable detection or tracking.
+Due to their small size, frequently with a maximum radius less than \SI{1}{\kilo\meter}, and low albedo, the reflected energy of these asteroids is insufficient for reliable detection or tracking.
 Therefore, the dynamics model of the asteroid is relatively coarse prior to in situ measurements from a dedicated spacecraft.
@@
 The standard approach for asteroid missions is to compute the gravitational potential using a polyhedron potential model~\cite{werner1996}.
-The polyhedral potential model provides the exact gravitational potential, and subsequently the gravitational acceleration, for a given triangular faceted shape model of an asteroid.
+The polyhedron potential model provides the exact gravitational potential, and subsequently the gravitational acceleration, for a given triangular faceted shape model of an asteroid.
 The method provides the exact potential at any point outside the body for a given shape model.
@@
 % generating the shape from the ground is difficult
-Prior to the arrival of a spacecraft at an asteroid, Earth based sensors are used to characterize the body.
+Prior to the arrival of a spacecraft at an asteroid, Earth-based sensors are used to characterize the body.
 Using both optical and radar sensors allows for the precise orbit of the asteroid to be determined.
@@
 During this mapping phase the spacecraft must remain in a quiescent state devoted entirely to mapping the surface.
-Depending on the mission type this long period of mapping is crucial to the mission, such as sample collection~\cite{gates2015}. 
+Depending on the mission type, this long period of mapping is crucial to the mission, such as sample collection~\cite{gates2015}. 
 However, other missions, such as asteroid mitigation, may be severely limited by the time and ground resources required to generate a surface shape.
 Furthermore, the long distances involved necessitate on-board autonomy to enable to spacecraft to operate without ground communications.
-Similarly, during landing the spacecraft will require the ability to sense and model the surface topography in order to safely land in an unknown enviornment.
-The dependency on expensive ground based shape reconstruction techniques limit the ability of spacecraft to autonomously operate at asteroids.
+Similarly, during landing the spacecraft will require the ability to sense and model the surface topography in order to safely land in an unknown environment.
+The dependency on expensive ground-based shape reconstruction techniques limits the ability of spacecraft to autonomously operate at asteroids.
 Mitigation of this ground based surface modeling will greatly expand the range of missions possible.
@@
 In contrast to previous work, we explicitly consider the gravitational coupling between orbit and attitude dynamics.
-Furthermore, instead of computationally expensive surface reconstruction methods we present a straightforward and conceptually simple method to enable real time shape updates.
+Furthermore, instead of computationally expensive surface reconstruction methods, we present a straightforward and conceptually simple method to enable real time shape updates.
 
@@
 \begin{itemize}
-    \item \( \vecbf{x} \) - the position of the center of mass of the dumbbell spacecraft represented in the inertial frame \( \vecbf{e}_i\)
-    \item \( R \) - the rotation matrix which transforms vectors defined in the spacecraft fixed frame, \( \vecbf{b}_i \), to the inertial frame, \( \vecbf{e}_i \)
-    \item \( \vecbf{\Omega} \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame \( \vecbf{b}_i \)
+    \item \( \vecbf{x} \) - the position of the center of mass of the dumbbell spacecraft represented in the inertial frame, \( \vecbf{e}_i\),
+    \item \( R \) - the rotation matrix which transforms vectors defined in the spacecraft fixed frame, \( \vecbf{b}_i \), to the inertial frame, \( \vecbf{e}_i \),
+    \item \( \vecbf{\Omega} \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame, \( \vecbf{b}_i \), and
     \item \( R_A \) - the rotation matrix which transforms vectors defined in the asteroid fixed frame, \( \vecbf{f}_i \), to the inertial frame, \( \vecbf{e}_i \)
-\end{itemize}
-In this work, we assume that the asteroid is much more massive than the spacecraft and it's motion is not affected by that of the spacecraft.
+\end{itemize}.
+In this work, we assume that the asteroid is much more massive than the spacecraft and its motion is not affected by that of the spacecraft.
 This assumption allows us to treat the motion of the vehicle independently from that of the asteroid.
@@
 The spacecraft measures the range between itself and the asteroid surface to several points within the field of view of the sensor. 
-These measurements provide a collection of points which lie on the surface of the asteroid, and by combining many points, a so called ``point cloud'', allows us to reconstruct the shape.
+These measurements provide a collection of points which lie on the surface of the asteroid, and by combining many points, a so called ``point cloud'' allows us to reconstruct the shape.
 
@@
 The vertices of the truth model are sorted according to increasing \( x \) component and incorporated into the mesh estimate one at a time. 
-Several views of the progress of the reconstruction is shown in~\cref{fig:reconstruction}.
+Several views of the progress of the reconstruction are shown in~\cref{fig:reconstruction}.
 The initial mesh is modified by radially moving each vertex to best match the measurements.

### 2018-08-02 utilities/setup_repo.sh
Change links for repo

@@ -1,9 +1,9 @@
 #!/bin/bash
 
 # add the correct remote repositories
-git_repo="git@github.com:skulumani/2018_aas_abstract.git"
-bb_repo="git@bitbucket.org:shankarkulumani/2018_aas_abstract.git"
-fdcl_repo="git@github.com:fdcl-gwu/2018_aas_abstract.git"
+git_repo="git@github.com:skulumani/2018_aas_manuscript.git"
+bb_repo="git@bitbucket.org:shankarkulumani/2018_aas_manuscript.git"
+fdcl_repo="git@github.com:fdcl-gwu/2018_aas_manuscript.git"
 
 printf "Setting the origin remote to point to Github and Bitbucket:\n\n"
 printf "Github: $git_repo\n"

### 2018-08-07 manuscript.tex
Rename to manuscript
Update some sections
Add details from dissertation

--- 2018-04-08 abstract.tex
@@
 
-\PaperNumber{XX-XXX}
+\PaperNumber{18--319}
 
@@
     Knowledge of the shape of an asteroid is crucial for spacecraft operations.
-    The standard method of determining the gravitational potential, through the use of a polyhedral potential model, is dependent on the shape model.
+    The standard method of determining the gravitational potential, through the use of a polyhedron potential model, is dependent on the shape model.
     Furthermore, accurate landing or low altitude operations requires accurate knowledge of the surface topology. 
@@
 
-\subsection{Shape Reconstruction}
+\subsection{Spacecraft Dynamic Model}
 
-We assume that the spacecraft contains an initial estimate for the shape of the asteroid.
-This shape can be a coarse estimate computed from ground measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid, such as that shown in~\cref{fig:start} which represents the maximum axes for asteroid Castalia.
-This model is defined as a sequence of vertices, \( \vb{v}_i\), in the asteroid fixed frame and triangular facets, \( f_i = \bracket{\vb{v}_1, \vb{v}_2, \vb{v}_3}\), which are defined by the three vertices making up the facet.
-The vertices are assumed to be ordered in a counterclockwise fashion about each facet. 
-As a result, the outward facing normal vector to each face is implicitly defined without any additional data.
-This shape representation is a widely used format for defining three-dimensional shapes in computer applications and has become the standard method for representing asteroid shapes~\cite{neese2004}.
+\subsection{Polyhedron Potential Model}
+
+\section{Range Measurement Model}
+
+Absolute distance measuring devices are a crucial sensor in spacecraft rendezvous or landing applications.
+In addition, they are a critical component for spacecraft operating near small bodies.
+Activate ranging devices allow for precise measurements of the surface shape and enable accurate and safe surface landing~\cite{berry2013}.
+
+The basic principle for all active range-finding devices is to transmit a signal onto an object and process the returned signal to determine the distance~\cite{amann2001}.
+The transmitted signal can fall into one of three categories: radio, ultrasonic, or optical.
+The benefit of an optical signal is that they can be highly focused to enable high resolution distance measurements.
+Optical distance measurement, such as laser range finders, can be further divided into three categories based on the method of operation: interferometry, time of flight, or triangulation.
+In this section, we'll briefly summarize the principles of operation of optical distance measurement devices and highlight their specific uses with respect to spacecraft missions to asteroids.
+
+Originally developed for military and surveying application, the basic principle of laser ranging is based on utilizing the fixed speed of light to measure distance.
+The time required for a pulse of energy to travel from the transmitter to the object and return is measured, \( t_d \). 
+Measuring this round trip time of flight and using the speed of light, approximately \( c = \SI{30}{\centi\meter\per\nano\second}\), allows one to easily compute the range to the object as
+\begin{align}
+    \rho = \frac{t_d}{2 c}. 
+\end{align}
+A main benefit of the time of flight ranging system is that a single pulse of energy is sufficient to accurately determine the distance with meter level precision in the case of spacecraft or millimeter level in industrial applications~\cite{zuber1997,cole1998,amann2001}.
+
+A pulsed time of flight laser distance device consists of a laser transmitter which emits pulses with a duration between \SIrange{5}{50}{\nano\second}~\cite{amann2001}.
+The emitted light pulse triggers a start signal in the onboard timing device and the reflected energy from the object provides the stop command.
+A block diagram of the laser range finder is shown in~\cref{fig:lidar_block_diagram}.
+A signal is generated by the transmitter and directed through the optics towards the target. 
+At the same time a pulse is sent to a high precision clock to record the outgoing transmission. 
+The energy reflects off the target and is passed through a detector which signal the stop command. 
+The time of flight is then recorded and used to compute the range.
+\begin{figure}[htbp]
+    \centering
+    \input{tikz/laser_range_finder.tikz}
+    \caption{ Block diagram of a time of flight laser range finder\label{fig:lidar_block_diagram}}
+\end{figure}
+A wide variety of lasers are used depending on the intended measurements range.
+In the spacecraft case, lasers providing peak energy in the range of \SI{15}{\mega\joule} are often required to measure distance of over \SI{50}{\kilo\meter}~\cite{berry2013}.
+
+The laser range finder is frequently equipped with angle encoders to enable the definition of the position of the measurement point with respect to the sensor. 
+Mechanical scanning is performed using a control system which  either moves the entire laser range finder or only the measuring beam.
+Focal plane scanning is another approach which reduces the mechanical complexity of a mechanical scanning system.
+The laser energy illuminates the entire field of view on the surface.
+An array of detectors are arranged to view the surface.
+Each detector only views a portion of the total field of view and the signals are analyzed in the time domain.
+Using this methodology, the system can simultaneously measure distance in multiple directions without any moving parts~\cite{amann2001}.
+
+\paragraph{Ray casting}
+
+In the computer graphics field, a major problem is the determination of which objects are visible to the user.
+This problem arises in many computer graphics rendering algorithms, such as ray tracing.
+Ray tracing is a rendering technique for generating an image by tracing the path of light, in the form of pixels, as it travels through a virtual world, reflects off of surfaces, and eventually lands on an image plane.
+As the light strikes the virtual objects the surface properties are used to determine the amount of energy that is reflected, absorbed, or scattered from the surface to accurately render the virtual image.
+Ray casting is a similar but noticeably simpler approach for the rendering of virtual scenes.
+In a method similar to the photographic process in reverse, for each pixel of the image a ray is cast towards the scene and the intersections of this ray with any objects is recorded.
+The first object which intersects the ray is defined as visible while those beyond would be occluded.
+Given this intersection point, the surface normal is computed and surface shading can be determined to render the scene.
+This provides a much simpler approach to virtual scene rendering but does not allow for the determination of high fidelity surface interactions of the light.
+
+Our application is adopted from the field of computational geometry and known as the ray shooting problem.
+The ray shooting problem is defined as follows: given a set of objects in \( d \) dimensional space, such as the shape model of a small body, create a data structure such that for any given query ray, e.g.\ the point of view of a camera, the initial object and its location can be determined quickly.
+Our goal is to use the true shape model of a small body and simulate the intersection of many rays with the surface.
+These rays will serve to emulate the range measurements of the surface using a LIDAR sensor.
+As a result, we must also implement a ray casting algorithm that will find the intersection of a measurement of the surface.
+
+\begin{figure}[htbp]
+    \centering
+    \input{tikz/frustrum.tikz}
+    \caption{View frustum for spacecraft sensor modeling\label{fig:view_frustrum}}
+\end{figure}
+We assume that the spacecraft is located at \(\rpos\) in the asteroid fixed frame.
+We define a camera fixed frame, \( \vc{c}_i \in \R^3 \), which is defined with respect to the spacecraft body fixed frame, \( \vc{b}_i \).
+The camera/sensor is aligned with \gls{view_axis} in the spacecraft fixed frame and we define an additional vector, termed the up axis \gls{up_axis} as the vertical direction of the image plane. 
+Finally, the standard basis is completed with \(  \gls{right_axis} = \gls{view_axis} \times \gls{up_axis} \) which defines a reference frame attached to the image plane of the sensor.
+Furthermore, we model the laser ranging sensor as having a fixed field of view defined by the angles \( \gls{fov_h}, \gls{fov_v}\), defining the vertical and horizontal fields of view.
+In order to simulate depth measurements we need to determine the transformation of locations in the image frame to the small body fixed frame. 
+Given the view axis, and a chosen distance \gls{view_distance}, we can define a viewing \gls{frustum} associated with the sensor. 
+We can compute the vectors associated with the maximum extents of the far plane as follows.
+The half height and width of the far plane, at a distance \( d \), are computed as
+\begin{align*}
+    H = d \tan \frac{\alpha}{2} , \\
+    W = d \tan \frac{\beta}{2} .
+\end{align*}
+From these values, the extents of the far plane are defined by the vectors
+\begin{align*}
+    A = \vc{c}_1 + H \vc{c}_3 - W \vc{c}_2 , \\
+    B = \vc{c}_1 + H \vc{c}_3 + W \vc{c}_2, \\
+    C = \vc{c}_1 - H \vc{c}_3 + W \vc{c}_2, \\
+    D = \vc{c}_1 - H \vc{c}_3 - W \vc{c}_2.
+\end{align*}
+The view frustum is visualized in~\cref{fig:view_frustrum} and allows for any vector in the field of view to be defined as a linear combination of the extents of the far plane.
+% tylee: not sure what "befined" means? 
+% shankar: should have been "defined"
+
+\section{Incremental Shape Reconstruction}\label{sec:radius_update}
+
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Coarse Uniform Mesh\label{fig:coarse_uniform_mesh}}{\includegraphics[trim={10cm 0 10cm 0}, clip,width=0.49\textwidth,keepaspectratio]{figures/computational_geometry/uniform_mesh_coarse.jpg}}
+    \subcaptionbox{Fine Uniform Mesh\label{fig:fine_uniform_mesh}}{\includegraphics[trim={10cm 0 10cm 0}, clip,width=0.49\textwidth,keepaspectratio]{figures/computational_geometry/uniform_mesh_fine.jpg}}
+    \caption{Examples of Resolution of Uniform Meshes of Triaxial Ellipsoid~\label{fig:uniform_mesh}}
+\end{figure}
+
+One of the first tasks for any spacecraft mission to a small body is to generate an estimate of the shape.
+This shape model is used for a variety of purposes, such as the polyhedron potential model, like that presented in~\cref{sec:polyhedron_potential} or landing site section and guidance.
+We assume that upon arrival at a target body, the spacecraft contains an initial estimate for the shape of the small body.
+This shape can be a coarse estimate computed from ground measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid, such as that shown in~\cref{fig:uniform_mesh} which represents the maximum axes for asteroid Castalia.
+Additionally, we assume that the shape estimate is closed and a triangular faceted surface mesh, emulating those used in practice to represent asteroids.
+Furthermore, the number of vertices in the estimate can be scaled according to the desired final accuracy or computational capabilities.
+For example,~\cref{fig:uniform_mesh} demonstrates two surface mesh representation for a triaxial ellipsoid at varying levels of detail. 
+A wide variety of algorithms are available to generate a near uniformly spaced mesh for an arbitrary surface~\cite{persson2004,boissonnat2005}.
+
+We assume the spacecraft contains a range sensor, such as \gls{lidar}, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid~\cite{zuber1997,zuber2000}.
+This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
+Given the time total time of flight, the distance can be accurately computed using \( d = \frac{\Delta TOF}{2 c} \) where \gls{sym:c} is the constant speed of light.
+Assuming accurate knowledge of the pointing direction of the spacecraft, in the form of the rotation matrix \gls{sym:iatt}, we can compute a direction from the spacecraft to the measurement location on the surface.
+The output of this sensor is a vector, \( \vc{d}_i \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface. 
+Using the state of the asteroid, we can transform this measurement to the asteroid fixed frame using the simple transformation
+\begin{align*}
+    \vc{p}_i = R_A^T R \vc{d}_i .
+\end{align*}
+Given many measurements, \( \vc{p}_i \in \R^3 \), of the asteroid surface we can efficiently update our initial shape estimate to that of the true surface.
+\Cref{fig:lidar_example} shows asteroid 4769 Castalia and a representation of several LIDAR measurements. 
+The spacecraft measures the range between itself and the asteroid surface to several points within the field of view of the sensor. 
+These measurements provide a collection of points which lie on the surface of the asteroid, and by combining many points, a so called ``point cloud'', allows us to reconstruct the shape.
 \begin{figure}
     \centering
-    \includegraphics[width=0.75\textwidth]{figures/castalia_raycasting_plot.jpg}
+    \includegraphics[width=0.75\textwidth]{figures/2018_SSPI/castalia_raycasting_plot.jpg}
     \caption{Simulated LIDAR measurements of asteroid Castalia~\label{fig:lidar_example}}
@@
 
-We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid~\cite{zuber1997,zuber2000}.
-This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
-Given the time total time of flight, the distance can be accurately computed using \( d = \frac{\Delta TOF}{2 c} \) where \( c \) is the constant speed of light.
-Assuming accurate knowledge of the pointing direction of the spacecraft we can compute a direction from the spacecraft to the measurement location on the surface.
-The output of this sensor is a vector, \( \vb{d}_i \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface of the asteroid. 
-Using the state of the asteroid, we can transform this measurement to the asteroid fixed frame using the simple transformation
-\begin{align*}
-    \vb{p}_i = R_A^T R \vb{d}_i .
-\end{align*}
-Given many measurements, \( \vb{p}_i \), of the asteroid surface we can efficiently update our initial shape estimate to that of the true surface.
-\Cref{fig:lidar_example} shows asteroid 4769 Castalia and a representation of several LIDAR measurements. 
-The spacecraft measures the range between itself and the asteroid surface to several points within the field of view of the sensor. 
-These measurements provide a collection of points which lie on the surface of the asteroid, and by combining many points, a so called ``point cloud'' allows us to reconstruct the shape.
+\paragraph{Bayesian Shape Update}
 
-Our algorithm applies a Bayesian framework to radially modify each vertex \( \vb{v}_i\) of the shape estimate based on measurement \( \vb{p}_i\). 
+Our algorithm applies a Bayesian framework to radially modify each vertex \( \vc{v}_i \in \R^3\) of the shape estimate based on measurement \( \vc{p}_i \in \R^3 \). 
 This approach alleviates much of complexity of incorporating new vertices or surface triangulation common in surface reconstruction methods~\cite{berg2008}.
 This assumption means that the total number of vertices of the shape model is fixed.
-However, additional detail, in the form of additional vertices, is possible by using standard mesh subdivision algorithms~\cite{orourke1998}.
+However, additional detail, in the form of additional vertices, is possible by using standard mesh subdivision algorithms~\cite{orourke1998}, which we later demonstrate in~\cref{sec:landing_refinement}.
 
-The radial distance of each vertex, \( v_i = \norm{\vb{v}_i}\), is assumed to be distributed according to the Gaussian distribution
+The radial distance of each vertex, \( v_i = \norm{\vc{v}_i}\), is assumed to be distributed according to the Gaussian distribution
 \begin{align*}
@@
 \end{align*}
-where \( r_i \) is the initial estimate of the radial distance of vertex \( \vb{v}_i\) and \( w_i \) is the initial variance, or confidence, in the radial distance.
-The radial distance of each measurement, \( p_{j,i} = \norm{\vb{p}_j}\), is also assumed to be distributed according to the Gaussian distribution
+where \( r_i \) is the initial estimate of the radial distance of vertex \( \vc{v}_i\) and \( w_i \) is the initial variance, or confidence, in the radial distance.
+The radial distance of each measurement, \( p_{j,i} = \norm{\vc{p}_j}\), is also assumed to be distributed according to the Gaussian distribution
 \begin{align*}
@@
 \end{align*}
-where \( r_{j,i} = \norm{\vb{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i}\) defines the variance of the measurement with respect to vertex \( \vb{v}_i\).
+where \( r_{j,i} = \norm{\vc{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i}\) defines the variance of the measurement with respect to vertex \( \vc{v}_i\).
 Each measurement is defined by the index \( j \) while the associated vertex is defined by \( i \). 
 As a result, the measurement \( p_{j, i} \) defines the distribution of measurement \( j \) with respect to vertex \( i \). 
-A given measurement may be used to update one or several vertices.
+Any given measurement may be used to update one or several vertices.
 
-The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vb{v}_i \).
-Here we use the geodesic distance to parameterize the difference, and hence  uncertainty, of associating the measurement with a given vertex.
-From spherical trigonometry the central angle between measurement \( \vb{p}_i \) and vertex \( \vb{v}_i \) of the shape estimate is
+The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vc{v}_i \).
+Here, we use the \gls{geodesic} distance to parameterize the difference, and hence  uncertainty, of associating the measurement with a given vertex.
+From spherical trigonometry~\cite{gade2010}, the central angle between measurement \( \vc{p}_i \) and vertex \( \vc{v}_i \) of the shape estimate is
+\begin{align}\label{eq:geodesic_distance}
+    \Delta \sigma_{j,i} = \arctan \parenth{\frac{\norm{\vc{p}_j \times \vc{v}_i}}{\vc{p}_j \cdot \vc{v}_i }}.
+\end{align}
+The variance of measurement \( \vc{p}_i \) with respect to vertex \( \vc{v}_i \) is then defined by the geodesic distance as
 \begin{align}
-    \Delta \sigma_{j,i} = \arctan \parenth{\frac{\norm{\vb{p}_j \times \vb{v}_i}}{\vb{p}_j \cdot \vb{v}_i }}.
+    w_{j, i} = \norm{\vc{p}_j} \Delta \sigma_{j,i} .
 \end{align}
-The variance of measurement \( \vb{p}_i \) with respect to vertex \( \vb{v}_i \) is then defined as the arc length as
-\begin{align}
-    w_{j, i} = \norm{\vb{p}_j} \Delta \sigma_{j,i} .
-\end{align}
-This approach relates the uncertainty of the measurement, \( \vb{p}_j \) with the geodesic distance to a given vertex, \( \vb{v}_i \).
-As a result, measurements which are far from a vertex, where \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty. 
-From Bayes' theorem, the posterior probability is
+This approach relates the uncertainty of the measurement \( \vc{p}_j \) with the geodesic distance to a given vertex, \( \vc{v}_i \).
+As a result, measurements which are far from a vertex, i.e.\ \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty. 
+This approach can be considered as a form of a correlation based sensor model~\cite{thrun2005}.
+The main benefit of a correlation based approach, in contrast to feature extraction is the relative simplicity of implementation.
+However, the resulting correlation values do not posses any physical significance and do not represent the noise or uncertainty characteristics of the sensor.
+
+From Bayes' theorem, the posterior probability is defined as
 \begin{align}
@@
 We relate \( \Delta S \) to an equivalent angular constraint using
-\begin{align}
+\begin{align}\label{eq:region_of_interest}
     \Delta \sigma_{max} = \sqrt \frac{\Delta S}{r_b^2}
 \end{align}
+% shankar: brillouin is correct. https://arc.aiaa.org/doi/10.2514/6.2014-4302
 where \( r_b \) defines the Brillouin  sphere radius, or the radius of the circumscribing sphere of the asteroid.
@@
 
-\section{Preliminary Results}
-\begin{figure}[h]
+The approach presented in this section allows one to update the shape of small body given a single range measurement of the surface.
+A sequential process can be used to iteratively update the shape estimate given many measurements of the surface. 
+For example,~\cref{sec:reconstruction_examples} shows the Bayesian update approach applied to several different asteroids.
+
+\section{Optimal Guidance for Shape Reconstruction}\label{sec:explore_asteroid}
+
+The mesh update algorithm presented in~\cref{sec:radius_update} does not offer a method to determine which portion of the surface needs to be updated. 
+In this section, we present an optimal approach for the guidance of the vehicle in order to update the shape estimate.
+Utilizing the nonlinear controllers developed in~\cref{sec:se3_control}, allows the spacecraft to maneuver to the best location that will update the shape estimate.
+This guidance schemes enables autonomous operations around a small body.
+% TODO talk about the basics of guidance/control for systems here and add tikz of block diagram
+
+% \gls{gnc} refers to the design of systems to control the operations of vehicles, specifically automobiles, aircraft, or spacecraft.
+% For spacecraft, many of these operations are computed ahead of time by operators and executed on board in an open loop fashion.
+% Guidance refers to the determination of the desired future states, or trajectory, that the spacecraft should follow to achieve some goals.
+% Navigation, or estimation, refers to the determination of the current state of the spacecraft given measurements.
+% Control refers to the application of forces, \( u_m, u_f \), required by the spacecraft to follow the desired trajectory while maintaining stability and other criteria. 
+% A block diagram representation of the entire \gls{gnc} system is shown in~\cref{fig:gnc}.
+% The approach presented in this section addresses the guidance and control portions of \cref{fig:gnc} but does not address the navigation. 
+% We assume that we have precise knowledge of the spacecraft state and small body rotation.
+
+% \begin{figure}[htbp]
+%     \centering
+%     \includegraphics[width=\textwidth]{example-image-golden}
+%     \caption{Block diagram of GNC system\label{fig:gnc}}
+% \end{figure}
+
+The ideal guidance approach involves solving a global optimal control problem which satisfies the system dynamics from~\cref{sec:dumbbell_model} while minimizing the shape uncertainty.
+There are a wide variety of optimal control techniques which may be utilized to solve the problem, such as indirect methods based on the calculus of variations or direction methods based on solving a related nonlinear programming problem~\cite{kirk2012,bryson1975}.
+The difficulty lies in implementing an algorithm that can operate in real time.
+Since the \gls{lidar} will be operating at upwards of \SI{1}{\hertz} efficient processing of the measurement and computation of the guidance commands is critical.
+Our approach solves this complexity by determining the vertex that should be measured to optimally update the shape estimate.
+
+We define a cost associated with each vertex \( \vc{v}_i \) of the shape estimate
+\begin{align}\label{eq:explore_cost}
+    J_i (\ipos, \iatt, \aatt) = \alpha_w J_{w_i} + \alpha_d J_{d_i}(\rpos) + \alpha_c J_{c_i}(\rpos)
+\end{align}
+where the weighting factors \( \alpha_w, \alpha_d, \alpha_c \in \R^1 \) are chosen such that \( \alpha_w + \alpha_d + \alpha_c = 1 \).
+The cost function is defined as a function of the current inertial position, \gls{sym:ipos}, and the attitude, \gls{sym:iatt} of the spacecraft.
+Furthermore, knowledge of the small body rotation is required in order to determine the position of the spacecraft in the small body fixed frame, \( \gls{sym:rpos} = \gls{sym:aatt}[^T] \gls{sym:ipos}\).
+
+The term \( J_{w_i} \in \R^1 \) represents the cost associated with the uncertainty of vertex \( i \) as
+\begin{align}\label{eq:weight_cost}
+    J_{w_i} &= - \frac{w_i}{w_m}
+\end{align}
+where \( w_i \) is the uncertainty of vertex \( i \) and \( w_m \) is a maximum uncertainty used to scale the values.
+The term \( J_{d_i} \) represents the scaled geodesic distance between the current state of the spacecraft and vertex \( i \),
+\begin{align}\label{eq:distance_cost}
+    J_{d_i}(\rpos) &= \frac{1}{\pi} \arctan \parenth{ \frac{\norm{\rpos \times \vc{v}_i}}{\rpos \cdot \vc{v}_i}}.
+\end{align}
+
+Finally, a control component is included in the cost function which penalizes vertices that are difficult to reach.
+Consider, the current position of the spacecraft in the small body fixed frame as \( \rpos\) and a desired vertex \( \vc{v}_i \) of the shape estimate.
+We can define a normal vector to the plane spanned by \( \rpos, \vc{v}_i \) as
+\begin{align}\label{eq:normal_to_plane}
+    \vc{n}_i = \frac{\rpos \times \vc{v}_i}{\norm{\rpos} \norm{\vc{v}_i}}.
+\end{align}
+Then a trajectory \( x_d(\theta) \) as
+\begin{align}\label{eq:spherical_waypoint}
+    x_d(\theta) = r_d \exp{\parenth{\theta \hat{\vc{n}_i}} } \frac{\rpos}{\norm{\rpos}},
+\end{align}
+where \( \theta : \bracket{0, \frac{\rpos \cdot \vc{v}_i}{\norm{\rpos}\norm{\vc{v}_i}}} \to \R^1\) parameterizes the desired trajectory.
+\Cref{eq:spherical_waypoint} simply describes a portion of a great circle trajectory between the current state, \( \rpos \), and the desired vertex \( \vc{v}_i \)~\cite{chen2016}.
+The altitude of the spacecraft, \( r_d \in \R \), can be chosen based on sensor characteristics of safety concerns.
+For example, \( r_d \) can be chosen as the distance of the Biroullin sphere with an additional safety margin to mitigate any surface collision~\cite{scheeres2012a}.
+The translational controller presented in~\cref{eq:translational_control} is used to determine the control input to follow \( x_d\).
+We assume that the tracking errors are small, such that \( e_x, e_v \) are negligible, therefore the control becomes
+\begin{align}\label{eq:tracking_control_cost}
+    u_f(\theta) = -F_{ext}(x_d(\theta)), 
+\end{align}
+where the external force is defined by the polyhedron potential model given in~\cref{eq:inertial_velocity_dynamics}.
+The control cost is then defined as the integral over the desired trajectory~\cref{eq:spherical_waypoint} between the current state and the desired vertex as
+\begin{align}\label{eq:control_cost}
+    J_{c_i}(\rpos) = \frac{1}{u_m} \int_{\theta_0}^{\theta_f} u_f(\theta)^T R u_f(\theta) d\theta,
+\end{align}
+where \( u_m \) is used to normalize and scale \( J_{c_i} \).
+\Cref{eq:control_cost} is numerically integrated over the trajectory \( x_d(t) \) and used to penalize vertices which have a larger cost.
+
+The vertex which minimizes~\cref{eq:explore_cost} 
+\begin{align*}
+    \vc{v}_{min} = \min_{i} J_i(\ipos, \iatt, \aatt),
+\end{align*}
+is determined and used to determine the optimum vertex of the shape model to measure.
+This vertex is then used to determine the required state of the spacecraft in order to collect a measurement.
+We assume that the spacecraft will maneuver to a location directly above the selected vertex, \( \vc{v}_{min} \), and point in the nadir direction to collect a measurement.
+The desired state is transformed into the inertial frame and chosen as a location above \( \vc{v}_{min} \) as
+\begin{align}
+    \ipos_d = r_d \aatt \vc{v}_{min}, 
+\end{align}
+where \( r_d \) is again chosen to ensure a safety margin above the surface.
+The desired attitude command, \( R_d\), is chosen such that the spacecraft camera axis, \( \vc{b}_1 \), is directed along the nadir towards the small body.
+It is sufficient to define two orthogonal vectors to uniquely determine the attitude of the spacecraft.
+The \( \vc{b}_{3d} \) vector is chosen to lie in the plane spanned by \(\vc{b}_{1d} \) and \( \vc{e}_3 = \vc{f}_3 \).
+The desired attitude command is defined as
+\begin{align}
+    \vc{b}_{1d} &= - \frac{\vc{x}}{\norm{\vc{x}}} , \\
+    \vc{b}_{3d} &= \frac{\vc{f}_3 - \parenth{\vc{f}_3 \cdot \vc{b}_{1d}} \vc{b}_{1d}}{\norm{\vc{f}_3 - \parenth{\vc{f}_3 \cdot \vc{b}_{1d}} \vc{b}_{1d}}}, \\
+    \vc{b}_{2d} &= \vc{b}_{3d} \times \vc{b}_{1d} , \\
+    R_d &= \begin{bmatrix} \vc{b}_{1d} & \vc{b}_{2d} & \vc{b}_{3d} \end{bmatrix} .
+\end{align}
+This form of \( R_d \) will direct the \( \bvec{1} \) axis towards the small body, and can be modified for a different camera orientation.
+
+\section{Multi-resolution Landing Area Refinement}\label{sec:landing_refinement}
+
+The shape update approach presented in~\cref{sec:radius_update} is designed with autonomous operations in mind. 
+It is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
+Furthermore, the original mesh is uniformly distributed and as a result many small topological features such as rocks or small craters are not be captured by the shape model. 
+However, these small features are critical for surface operations and safe landings.
+In addition, it would be computationally prohibitive to have a uniformly high resolution mesh.
+In this section, we extend the previous shape update approach to enable a much higher fidelity in a specific location.
+
+Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
+As shown in~\cite{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
+The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
+As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
+However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.
+
+The selection of a landing site will typically require a vast quantity of data and weigh a multitude of possible metrics, such as scientific value, hardware constraints, timing and communication limits, or safety considerations.
+In our analysis we consider the surface slope, the distance to the surface, and a fictitious science metric in order to determine the best landing site based on the complete shape estimate.
+This approach allows for a spacecraft to autonomously select and land on small body.
+
+The surface slope is computed according to the method developed in~\cite{scheeres1996}.
+Due to the small size, and therefore low gravitational attraction, the force at each point on the surface is a combination of the gravitational attraction and the centripetal acceleration.
+At the center of each face, \( f_i = \begin{bmatrix} f_x & f_y & f_z \end{bmatrix} \), we compute a modified surface acceleration as
+\begin{align}\label{eq:surface_force}
+    U_m = \omega^2 \begin{bmatrix} f_x \\ f_y \\ 0 \end{bmatrix} + \begin{bmatrix} U_x \\ U_y \\ U_z \end{bmatrix},
+\end{align}
+where \( \omega \in \R^1 \) is the angular velocity of the asteroid and \( U_i \) is computed from~\cref{eq:attraction}.
+Then the surface slope can be computed from
+\begin{align}\label{eq:surface_slope}
+    \cos \parenth{ \pi - \phi } = \frac{\vc{n}_f \cdot U_m}{\norm{U_m}},
+\end{align}
+where \( \phi \in \R^1 \) is the surface slope defines the angle between the surface normal \( \vc{n}_f \in \R^3 \) and the force vector at the surface.
+If \( \phi = \SI{0}{\degree} \) then the force vector and the surface normal are anti-parallel, while \( \phi > \SI{90}{\degree} \) means that a particle on the surface would be thrown off the body as the centripetal force is larger than the gravitational attraction.
+
+Additionally, we compute the distance, using~\cref{eq:geodesic_distance}, between the spacecraft state and each face of the asteroid. 
+Finally, we also assign a random science value to the surface in the form of two dimensional Gaussian.
+Utilizing these metric, a landing site is chosen to minimize the surface cost given as
+\begin{align}\label{eq:surface_cost}
+    J_l =  J_{\text{distance}} - J_{\text{science}},
+\end{align}
+where the surface slope is considered a hard constraint such that any candidate landing site must satisfy \( \phi \leq \phi_m \).
+
+\paragraph{Mesh Refinement}\label{sec:refinement}
+
+Once a suitable landing site is selected, the surrounding area is isolated and refined by adding new vertices and faces in the specified area.
+The goal of refinement, or more generally remeshing, is given a mesh ( or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
+In this work, we utilize the isotropic remeshing algorithm implemented in \gls{cgal}.
+This algorithm uses an iterative method which repeatedly splits long edges, collapses short edges, and relocates vertices until all edges are approximately the desired target edge length.
+% TODO Think about adding PMP 6.12 image here
+
+For example,~\cref{fig:cube_remesh} shows the isotropic remeshing result for the selected faces of a unit cube.
+The original unit cube is composed of \num{8} vertices and \num{12} faces.
+The two triangular faces of the visible side of the cube are selected for the isotropic remeshing operation as shown in~\cref{fig:cube_original_mesh}.
+A target edge length of \num{0.1} is selected for these faces and used to generate~\cref{fig:cube_refine_mesh}.
+The two large triangular faces are divided into a number of smaller triangular faces.
+Furthermore, the additional faces are all approximately the same size and preserve the original surface of the cube.
+After the isotropic remeshing operation the number of vertices has increased from \num{8} to \num{140}.
+\begin{figure}[htbp]
     \centering
-    \subcaptionbox{Initial mesh estimate\label{fig:start}}{\includegraphics[height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/partial_initial.jpg}}~
-    \subcaptionbox{First measurement added\label{fig:first}}{\includegraphics[width=0.5\textwidth]{figures/partial_0.jpg}}
+    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.49\textwidth]{figures/computational_geometry/isotropic/original_cube.jpg}}~
+    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.49\textwidth]{figures/computational_geometry/isotropic/remesh_cube.jpg}}
+    \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
+\end{figure}
 
-    \subcaptionbox{\SI{25}{\percent} of measurments added\label{fig:quarter}}{\includegraphics[width=0.5\textwidth]{figures/partial_512.jpg}}~
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:half}}{\includegraphics[width=0.5\textwidth]{figures/partial_1024.jpg}}
+In order to demonstrate the multi resolution surface refinement we require a true shape model that contains small scale surface features.
+In this dissertation, we utilize the true radar shape model of asteroid 4769 Castalia.
+However, the shape model is not highly detailed as it does not contain small craters or surface features.
+In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme in~\cref{sec:radius_update} to measure the surface.
+The augmented model of Castalia is shown in~\cref{fig:castalia_refinement}.
+\Cref{fig:castalia_refinement} shows that the increased resolution is required in order to reconstruct these small surface details.
 
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:threequarter}}{\includegraphics[width=0.5\textwidth]{figures/partial_1536.jpg}}~
-    \subcaptionbox{Final reconstruction\label{fig:final}}{\includegraphics[width=0.5\textwidth]{figures/partial_2047.jpg}}
-    \caption{4769 Castalia incremental reconstruction. The initial ellipsoid is incrementally modified by radially moving each vertex to best match the measurements.~\label{fig:reconstruction}}
+\section{Numerical Examples}\label{sec:reconstruction_examples}
+
+In this section, we demonstrate the use of the results presented in~\cref{sec:mathematical_background,sec:se3_control,sec:shape_reconstruction} with several numerical examples.
+The incremental shape reconstruction approach from~\cref{sec:radius_update} is used to iteratively reconstruct the shape of several asteroid given \gls{lidar} measurements.
+We utilize radar shape models of asteroids \num{4769} Castalia, (\num{52760}) \num{1998} \(\text{ML}_{14}\), \num{1620} Geographos, and 6489 Golevka~\cite{neese2004}.
+The asteroids exhibit a wide range of shapes and demonstrate the effectiveness of the mesh update approach.
+\Cref{sec:kinematic_exploration} focuses on the application of the incremental mesh update scheme of~\cref{sec:radius_update} for several different asteroids.
+\Cref{sec:dynamic_exploration} incorporates the full dynamic model on \( \SE \) of a dumbbell spacecraft given in~\cref{sec:inertial_dumbbell_eoms}, the polyhedron potential model from~\cref{sec:polyhedron_potential}, and the mesh update and guidance scheme presented in~\cref{sec:radius_update}.
+
+\subsection{Shape Reconstruction}\label{sec:kinematic_exploration}
+
+The results in this section utilize a kinematics only model of the spacecraft and dynamics instead of the full dynamic simulation. 
+We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction.
+\Cref{tab:kinematic_asteroids} lists the true shape model parameters of asteroids Geographos and Golevka.
+\begin{table}[htbp]
+    \centering
+    \begin{tabular}{lccc}
+        \toprule
+        Asteroid & Semi-major axes (\si{\kilo\meter}) & Vertices & Faces\\
+        \midrule
+        \num{1620} Geographos & \( 2.5 \times 1.0 \times 1.05 \) & \num{8192} & \num{16380}  \\
+        \num{6489} Golevka & \( 0.53 \times 0.53 \times 0.53 \)  & \num{2048} & \num{4092} \\
+        \bottomrule
+    \end{tabular} 
+    \caption{Asteroid properties for kinematic only exploration~\label{tab:kinematic_asteroids}}
+\end{table}
+The spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
+The simulations begin with an triaxial ellipsoid mesh that is sized to match the semi-major axes of each asteroid.
+With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
+\Gls{lidar} measurements are generated until the total uncertainty
+\begin{align*}
+    \sum_i w_i,
+\end{align*}
+is sufficiently small.
+In addition, we compute the volume of the estimate shape throughout the simulation using the algorithm presented in~\cref{sec:polyhedron_volume}.
+
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/geographos/partial_0.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_1872.jpg}}
+
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_3745.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_5617.jpg}}
+
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_7489.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/truth.jpg}}
+    \caption[Asteroid Geographos incremental reconstruction]{Incremental reconstruction of asteroid Geographos~\label{fig:geographos_reconstruction}}
 \end{figure}
-Here we present initial results of reconstructing the shape of asteroid 4769 Castalia.
-Castalia is a potentially  hazardous asteroid and the first asteroid which used radar imaging to generate a 3D surface shape~\cite{hudson1994}.
-In this example, we seek to incrementally build an accurate shape of Castalia from an initial triaxial ellipsoid model.
-Our initial shape for Castalia is a triaxial ellipsoid with semi-axes equal to \( \SI{1.8}{\kilo\meter} \times \SI{0.8}{\kilo\meter} \times \SI{0.8}{\kilo\meter}\) and shown in~\cref{fig:start}.
-We use this choice of initial estimate since the semi-major axes of an asteroid are able to be computed based on Earth-measurements~\cite{busch2011}.
-Furthermore, this type of model also allows for the use of analytical gravitational models for use in preliminary analysis or in the absence of higher fidelity shape information~\cite{scheeres1994}.
 
-Simulated measurements of the surface of 4769 Castalia are used to update the initial mesh estimate.
-The truth shape model, and the associated vertices, are used as simulated measurements of the shape of Castalia~\cite{neese2004}.
-The true shape model of 4769 Castalia is composed of \num{2048} vertices and \num{4092} triangular faces.
-The initial ellipsoid is chosen to have approximately the same number of vertices as the final true shape and such that the total number of vertices remains constant.
-It is possible to incorporate more vertices, for example by splitting faces into smaller faces, but this does not affect the general approach.
+\num{1620} Geographos is a highly elongated stony asteroid of the Apollo group.
+Discovered in \num{1951}, Geographos is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
+\Cref{fig:geographos_reconstruction} shows the shape reconstruction for asteroid Geographos at several distinct points during the process.
+Comparing~\cref{fig:geographos_partial_100,fig:geographos_truth} shows that the final shape closely matches the true radar model.
+In~\cref{fig:geographos_metrics} we display the vertex uncertainty and mesh volume as a function of time.
+The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.
 
-The vertices of the truth model are sorted according to increasing \( x \) component and incorporated into the mesh estimate one at a time. 
-Several views of the progress of the reconstruction are shown in~\cref{fig:reconstruction}.
-The initial mesh is modified by radially moving each vertex to best match the measurements.
-\Cref{fig:first} shows that the first measurement only affects the mesh in a small local area.
-As a result, the mesh update is only considered over those vertices within \( \Delta S \) rather than the entire mesh. 
-Furthermore, regardless of the size of the shape model, or the total number of measurements, the computational load can be adjusted through the choice of \( \Delta S \).
-Changing the value of \( \Delta S \) will impact the number of vertices that are considered in the Bayesian updated.
+\begin{figure}[htbp]
+    \centering
+    \input{tikz/geographos_metrics.tikz}
+    \caption{Normalized uncertainty and volume percent error for Geographos\label{fig:geographos_metrics}}
+\end{figure}
 
-\section{Expected Results and Significance}
-This work will present an efficient method of reconstructing the shape of an asteroid from range measurements. 
-The method allows for a real time approach to incrementally update a shape model of an asteroid.
-Instead of performing a global update, each measurement is applied locally to the shape. 
-This updated shape model is then used in a polyhedron potential model to enable a more accurate dynamic model near the asteroid.
-This approach avoids the lengthy mapping phase of many spacecraft missions and enables a more responsive mission profile which allows the spacecraft to directly transition from arrival to surface operations.
-Utilizing the updated shape model allows for real time feedback control as the dynamic model is continually updated to best match measurements of the surface.
+\num{6489} Golevka is a small angular shaped asteroid of the Apollo group.
+Discovered in \num{1995}, Golevka is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
+\Cref{fig:golevka_reconstruction} shows the shape reconstruction for asteroid Golevka at several distinct points during the process.
+Comparing~\cref{fig:golevka_partial_100,fig:golevka_truth} shows that the final shape closely matches the true radar model.
+In~\cref{fig:golevka_metrics} we display the vertex uncertainty and mesh volume as a function of time.
+
+\begin{figure}[htbp]
+    \centering
+    \input{tikz/golevka_metrics.tikz}
+    \caption{Normalized uncertainty and volume percent error for Golevka\label{fig:golevka_metrics}}
+\end{figure}
+
+The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.
+It is interesting to note that the reconstruction of Golevka achieves an accurate shape reconstruction in a much smaller amount of time as compared to Geographos.
+This is primarily due to the smaller size of Golevka and the relatively spherical shape of the body in contrast to the highly elliptical shape of Geographos.
+
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_0.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_1321.jpg}}\\%
+
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_2643.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_3964.jpg}}\\%
+
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_5285.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/truth.jpg}}
+    \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
+\end{figure}
+
+\subsection{Full Dynamic Model }\label{sec:dynamic_exploration}
+
+In this section, we simulate a dumbbell spacecraft in motion around asteroid \num{52760} and asteroid Castalia.
+The dynamic simulation utilizes the inertial equations of motion from~\cref{sec:inertial_dumbbell_eoms} and are given as
+\begin{align*}
+    \dot{\ipos} &= \ivel, \\
+    \parenth{m_1 + m_2} \dot{\ivel} &= - \sum_{i=0}^2 m_i \aatt \deriv{U}{\apos_i} + u_f, \\
+    \dot{\iatt} &= \iatt \iangvel, \\
+    J \dot{\iangvel} + \hat{\iangvel} J \iangvel &= \sum_{i=0}^2 m_i \hat{\spos}_i \iatt^T \aatt \deriv{U}{\apos_i} + u_m. 
+\end{align*}
+The nonlinear controllers described in~\cref{sec:se3_control} are used to control both the translational and rotational states of the vehicle.
+The control inputs are duplicated from~\cref{sec:se3_control} as
+\begin{align*}
+    \vc{u}_f &= -k_x e_x - k_v e_v - F_{ext} + m \ddot{x}_d . \\
+    \vc{u}_m &= -k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - M_{ext}.
+\end{align*}
+Throughout the simulation the control inputs are computed using the current shape estimate of the asteroid. 
+As measurements are collected, the spacecraft autonomously updates its shape estimate and uses this estimate to compute the control inputs and desired future states using the details provided in~\cref{sec:radius_update,sec:explore_asteroid}.
+These simulations demonstrate the ability of a spacecraft to autonomously explore and maneuver around an unknown small body.
+
+We consider two simulations about asteroids \num{52760} and Castalia.
+The asteroids are assumed to constantly rotate about the \( \vc{f}_3 = \vc{e}_3\) axis according to the parameters given in~\cref{tab:dynamic_asteroids}.
+Furthermore, the state of the asteroid, namely the rotation matrix \( \aatt \), is assumed to be known based on ground measurements or previous data.
+\begin{table}[htbp]
+    \centering
+    \begin{tabular}{lcc}
+        \toprule
+        Property & \num{4769} Castalia & (\num{52760}) \num{1998} \(\text{ML}_{14}\) \\
+        \midrule
+        Semi-major axes(\si{\kilo\meter}) & \( 0.8065 \times 0.4905 \times 0.413 \) & \( 1.1 \times 1.1 \times 1.1 \) \\
+        Rotational Period (\si{\hour}) & \num{4.095} & \num{14.98} \\
+        Density (\si{\gram\per\centi\meter^3}) & \num{2.1} & \num{2.1} \\
+        Vertices & \num{2048}  & \num{8192} \\
+        Faces & \num{4092} & \num{16320} \\
+        \bottomrule
+    \end{tabular}
+    \caption{Asteroid properties for dynamic exploration~\label{tab:dynamic_asteroids}}
+\end{table}
+At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( \ipos(0) = \begin{bmatrix} x_0 & 0 & 0 \end{bmatrix} \si{\kilo\meter} \).
+In addition, at the initial state the spacecraft is orientated such that the \( b_1 \) axis is aligned with the inertial \( e_2 \) axis.
+In other words the initial orientation is given by \( \iatt(0) = \exp(\frac{\pi}{2} \hat{e}_3)\).
+The shape reconstruction phase of the simulation is performed over \SI{15000}{\second}, over which time the spacecraft will take \gls{lidar} measurements of the surface at \SI{1}{\hertz}.
+Once the total uncertainty has been reduced sufficiently the spacecraft maneuvers to a ``home'' position aligned with the \( f_1 \) axis of the asteroid.
+
+\paragraph{Asteroid 52760 Reconstruction}
+
+Asteroid (\num{52760}) \num{1998} \(\text{ML}_{14}\) was discovered in \num{1998} and is near Earth asteroid of the Apollo group and classified as a potentially hazardous body.
+The asteroid is roughly spherical with a mean radius of approximately \SI{1}{\kilo\meter}.
+The initial shape estimate is assumed to be spherical with approximately the same number of vertices as the truth model.
+\Cref{fig:52760_reconstruction,fig:52760_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
+Due to the roughly spherical shape of the asteroid large portions of the surface are quickly modified to match the measurements.
+In addition~\cref{fig:52760_weights_reconstruction} displays the vertex uncertainty \( w_i \) as a colormap on the surface. 
+Areas of high uncertainty are denoted in yellow while areas of low uncertainty are in purple/blue.
+
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_0}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:52760_partial_25}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/dynamic_exploration/52760/partial_3749.jpg}}
+
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:52760_partial_50}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/dynamic_exploration/52760/partial_7499.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:52760_partial_75}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/dynamic_exploration/52760/partial_11249.jpg}}
+
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:52760_partial_100}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/dynamic_exploration/52760/partial_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:52760_truth}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/52760/truth.jpg}}
+    \caption[Asteroid 52760 incremental reconstruction]{Incremental reconstruction of asteroid 52760~\label{fig:52760_reconstruction}}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_3749.jpg}}
+
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_7499.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_11249.jpg}}
+
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_14998.jpg}}%
+    % \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.18\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/52760/truth.jpg}}
+    \caption[Asteroid 52760 shape reconstruction with uncertainty]{Incremental reconstruction of asteroid 52760.
+The images colored according to the shape uncertainty.
+Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:52760_weights_reconstruction}}
+\end{figure}
+\Cref{fig:52760_metrics} shows the total normalized uncertainty and percent error for the volume estimate. 
+The plots show that the reconstruction  converges to an accurate shape estimate after approximately \SI{8000}{\second}.
+
+\begin{figure}[htbp]
+    \centering
+    \input{tikz/52760_metrics.tikz}
+    \caption{Normalized uncertainty and volume percent error for 52760\label{fig:52760_metrics}}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{3D visualization of the trajectory\label{fig:52760_explore_trajectory}}{\includegraphics[trim={0 0 0 0},clip,keepaspectratio,width=0.99\textwidth]{figures/computational_geometry/dynamic_exploration/52760/state/asteroid_trajectory.jpg}
+}\\%
+    \subcaptionbox{Components of position\label{fig:52760_explore_components}}{\input{tikz/52760_asteroid_position.tikz}}
+    \caption{Spacecraft trajectory in the rotating asteroid frame for the exploration of 52760~\label{fig:52760_trajectory}}
+\end{figure}
+
+\paragraph{Asteroid 4769 Castalia Reconstruction}
+
+Asteroid 4769 Castalia is a small near Earth asteroid of the Apollo group.
+In addition, it is classified as a potentially hazardous object with a closed approach distance of less than \SI{0.05}{\astronomicalunit}.
+Castalia was discovered in \num{1989} and is the first asteroid to be modeled using radar imagery~\cite{hudson1994}.
+Castalia is composed of two distinct lobes suggesting that it is a contact binary of two smaller objects held together by their mutual gravity.
+\Cref{fig:castalia_reconstruction,fig:castalia_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
+In addition~\cref{fig:castalia_weights_reconstruction} displays the vertex uncertainty \( w_i \) as a colormap on the surface. 
+Areas of high uncertainty are denoted in yellow while areas of low uncertainty are in purple/blue.
+Within \SI{50}{\percent} of the simulation span the spacecraft is able to achieve an accurate estimate of the true shape of Castalia.
+
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_3749.jpg}}
+
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_7499.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_11249.jpg}}
+
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:castalia_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/castalia/truth.jpg}}
+    \caption[Asteroid Castalia incremental reconstruction]{Incremental reconstruction of asteroid Castalia~\label{fig:castalia_reconstruction}}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_weights_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_weights_3749.jpg}}
+
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_weights_7499.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_weights_11249.jpg}}
+
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_weights_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/castalia/truth.jpg}}
+    \caption[Asteroid Castalia shape reconstruction with uncertainty]{Incremental reconstruction of asteroid Castalia.
+The images colored according to the shape uncertainty.
+Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:castalia_weights_reconstruction}}
+\end{figure}
+
+\Cref{fig:castalia_metrics} shows the total normalized uncertainty and percent error for the volume estimate. 
+The plots show that the reconstruction converges to an accurate shape estimate after approximately \SI{8000}{\second}.
+In addition, the volume estimate is initially a much larger value but quickly converges to the true value.
+\begin{figure}[htbp]
+    \centering
+    \input{tikz/castalia_metrics.tikz}
+    \caption{Normalized uncertainty and volume percent error for Castalia\label{fig:castalia_metrics}}
+\end{figure}
+
+The spacecraft autonomously navigates around asteroid Castalia to best minimize the cost function in~\cref{eq:control_cost}.
+The state trajectory is visualized in the asteroid frame in~\cref{fig:castalia_explore_trajectory}.
+The component plots of the trajectory are shown in~\cref{fig:castalia_explore_components}.
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{3D visualization of the trajectory\label{fig:castalia_explore_trajectory}}{\includegraphics[trim={15cm 0cm 15cm 0cm},clip,keepaspectratio,width=\textwidth,height=0.5\textheight]{figures/computational_geometry/dynamic_exploration/castalia/state/asteroid_trajectory.jpg}}\\%
+    \subcaptionbox{Components of position\label{fig:castalia_explore_components}}{\input{tikz/castalia_asteroid_position.tikz}}
+    \caption{Spacecraft trajectory in the rotating asteroid frame for the exploration of Castalia~\label{fig:castalia_trajectory}}
+\end{figure}
+
+\paragraph{Castalia Landing Site Selection}
+
+With an appropriate shape estimate, the spacecraft can autonomously transition from a shape reconstruction to a landing mode.
+Based on the shape estimate we seek to determine the best location to land. 
+In reality, any landing site selection would be based on a wide variety of factors and constraints, however we highlight a few which can be determined autonomously and from the shape estimate.
+The first metric is related to the surface slope which is computed using the completed shape estimate and~\cref{eq:surface_slope}.
+Areas which violate the slope constraint of \( \phi < \SI{5}{\degree} \) are excluded from further consideration.
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=\textwidth]{figures/computational_geometry/dynamic_exploration/castalia/refine/slope.pdf}}\\%
+    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/refine/slope_masked.pdf}}
+    \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}
+\end{figure}
+
+The next metric is related to the distance from the current spacecraft position to all candidate landing sites on the surface.
+We utilize~\cref{eq:geodesic_distance} to compute a distance metric to the surface.
+Landing sites which are closer will be considered preferentially over those at a larger distance.
+\Cref{fig:distance_castalia_both} shows a surface plot of the distance to the surface. 
+The area immediately beneath the spacecraft has a small cost while those on the opposite side of the asteroid have a much larger cost.
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=\textwidth]{figures/computational_geometry/dynamic_exploration/castalia/refine/dist.pdf}}\\%
+    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/refine/dist_masked.pdf}}
+    \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
+\end{figure}
+We can combine~\cref{fig:distance_castalia_both,fig:surface_slope_castalia_both} to determine the best landing site. 
+The combination of the two is shown in~\cref{fig:landing_site_cost} with the desired landing site shown by the blue marker.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/refine/cost.pdf}
+    \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
+\end{figure}
+After selecting the appropriate landing site we then prepare for landing by collecting more measurements in the region around the landing area.
+
+\paragraph{Castalia Landing Site Refinement}
+One key benefit of an in-situ spacecraft is the ability to measure surface features at a much higher resolution than is possible from the ground. 
+This detail provides a much higher fidelity data source than ground based measurements. 
+In order to emulate this in the simulation we augment the shape model of Castalia with several small craters and outcroppings as shown in~\cref{fig:castalia_refinement}.
+However, these small features would be difficult to capture with the current low resolution shape model of approximately \num{4000} faces.
+The lower number of faces is useful for the evaluation of the polyhedron potential model, it is not ideal for the capture of minute surface features. 
+As a result, we utilize the isotropic remeshing operation described previously to selectively increase the fidelity in the region about the desired landing site.
+\Cref{fig:castalia_refine_density} shows that the vertex density increases by approximately an order of magnitude in region immediately surround the landing site.
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=1.0\textwidth]{figures/computational_geometry/dynamic_exploration/castalia/refine/density.pdf}}
+
+    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=1.0\textwidth]{figures/computational_geometry/dynamic_exploration/castalia/land/density.pdf}}
+    \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
+\end{figure}
+
+The increased number of faces and vertices in the landing area allows for the capture of the small surface features.
+\Cref{fig:castalia_refinement} shows that given \gls{lidar} measurements alone and the algorithm presented in~\cref{sec:radius_update} the small craters and features are effectively estimated.
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,width=0.49\textwidth]{figures/computational_geometry/dynamic_exploration/castalia_bump_true.jpg}}~
+    \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,width=0.49\textwidth]{figures/computational_geometry/dynamic_exploration/castalia_bump_est.jpg}}
+    \caption{Asteroid Castalia with augmented with additional surface features~\label{fig:castalia_refinement}}
+\end{figure}
+
+\paragraph{Castalia Vertical Descent}
+
+The final phase of the simulation is to utilize the mixed resolution model and vertically descend to the desired landing site. 
+This is accomplished using the closed loop control of~\cref{sec:se3_control} and a trajectory which transitions from the home position to the surface over \SI{3600}{\second}.
+The landing trajectory, using the estimated shape, is visualized in the asteroid frame in~\cref{fig:castalia_landing}.
+During the vertical descent the vehicle is able to accurately track the desired trajectory using the estimated shape to compute the gravitational potential.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\textwidth]{figures/computational_geometry/dynamic_exploration/castalia/land/asteroid_trajectory.jpg}
+    \caption{Vertical descent onto 4769 Castalia~\label{fig:castalia_landing}}
+\end{figure}
+
+\section{Summary}
+
+The developments of this chapter, when combined with the details of~\cref{sec:mathematical_background,sec:lowthrust_transfers,sec:se3_control}, provide a complete approach for the operation of a spacecraft around a small body.
+This chapter developed a Bayesian update scheme to reconstruct the shape of a small body from range measurements. 
+The approach allows for a local update operation that is able to reconstruct the shape in real time. 
+This is in contrast to standard shape reconstruction algorithms which operate over the entire surface and require signification computational resources.
+Next, an optimal guidance scheme is derived which determines the desired state to best update the shape estimate. 
+This allows for a spacecraft to autonomously maneuver and reconstruct the shape of a small body without operator intervention.
+Finally, a mixed resolution shape representation is presented to allow for an increased fidelity in a specific region of the asteroid.
+This allows for a much greater shape accuracy in a local area while avoiding the computational costs associated with a uniformly high resolution mesh.
+Several numerical examples were presented which demonstrates the approach on a number of real asteroids.
 

### 2018-08-07 manuscript.tex
Update manuscript and correct errors

@@
 We define a camera fixed frame, \( \vc{c}_i \in \R^3 \), which is defined with respect to the spacecraft body fixed frame, \( \vc{b}_i \).
-The camera/sensor is aligned with \gls{view_axis} in the spacecraft fixed frame and we define an additional vector, termed the up axis \gls{up_axis} as the vertical direction of the image plane. 
-Finally, the standard basis is completed with \(  \gls{right_axis} = \gls{view_axis} \times \gls{up_axis} \) which defines a reference frame attached to the image plane of the sensor.
-Furthermore, we model the laser ranging sensor as having a fixed field of view defined by the angles \( \gls{fov_h}, \gls{fov_v}\), defining the vertical and horizontal fields of view.
+The camera/sensor is aligned with \( \vc{c}_1 \) in the spacecraft fixed frame and we define an additional vector, termed the up axis \( \vc{c}_3 \) as the vertical direction of the image plane. 
+Finally, the standard basis is completed with \(  \vc{c}_2 = \vc{c}_1 \times \vc{c}_3 \) which defines a reference frame attached to the image plane of the sensor.
+Furthermore, we model the laser ranging sensor as having a fixed field of view defined by the angles \( \alpha, \beta \), defining the vertical and horizontal fields of view.
 In order to simulate depth measurements we need to determine the transformation of locations in the image frame to the small body fixed frame. 
-Given the view axis, and a chosen distance \gls{view_distance}, we can define a viewing \gls{frustum} associated with the sensor. 
+Given the view axis, and a chosen distance \( d  \in \R^1 \), we can define a viewing frustum associated with the sensor. 
 We can compute the vectors associated with the maximum extents of the far plane as follows.

### 2018-08-08 manuscript.tex
Correct errorsr

@@
     \centering
-    \subcaptionbox{Coarse Uniform Mesh\label{fig:coarse_uniform_mesh}}{\includegraphics[trim={10cm 0 10cm 0}, clip,width=0.49\textwidth,keepaspectratio]{figures/computational_geometry/uniform_mesh_coarse.jpg}}
-    \subcaptionbox{Fine Uniform Mesh\label{fig:fine_uniform_mesh}}{\includegraphics[trim={10cm 0 10cm 0}, clip,width=0.49\textwidth,keepaspectratio]{figures/computational_geometry/uniform_mesh_fine.jpg}}
+    \subcaptionbox{Coarse Uniform Mesh\label{fig:coarse_uniform_mesh}}{\includegraphics[trim={10cm 0 10cm 0}, clip,width=0.49\textwidth,keepaspectratio]{figures/uniform_mesh_coarse.jpg}}
+    \subcaptionbox{Fine Uniform Mesh\label{fig:fine_uniform_mesh}}{\includegraphics[trim={10cm 0 10cm 0}, clip,width=0.49\textwidth,keepaspectratio]{figures/uniform_mesh_fine.jpg}}
     \caption{Examples of Resolution of Uniform Meshes of Triaxial Ellipsoid~\label{fig:uniform_mesh}}
@@
 
-We assume the spacecraft contains a range sensor, such as \gls{lidar}, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid~\cite{zuber1997,zuber2000}.
+We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid~\cite{zuber1997,zuber2000}.
 This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
-Given the time total time of flight, the distance can be accurately computed using \( d = \frac{\Delta TOF}{2 c} \) where \gls{sym:c} is the constant speed of light.
-Assuming accurate knowledge of the pointing direction of the spacecraft, in the form of the rotation matrix \gls{sym:iatt}, we can compute a direction from the spacecraft to the measurement location on the surface.
+Given the time total time of flight, the distance can be accurately computed using \( d = \frac{\Delta TOF}{2 c} \) where \( c = \SI{2.998e8}{\meter\per\second}\) is the constant speed of light.
+Assuming accurate knowledge of the pointing direction of the spacecraft, in the form of the rotation matrix \( R \in \R^{3 \times 3 } \), we can compute a direction from the spacecraft to the measurement location on the surface.
 The output of this sensor is a vector, \( \vc{d}_i \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface. 
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{figures/2018_SSPI/castalia_raycasting_plot.jpg}
+    \includegraphics[width=0.75\textwidth]{figures/castalia_raycasting_plot.jpg}
     \caption{Simulated LIDAR measurements of asteroid Castalia~\label{fig:lidar_example}}
@@
 The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vc{v}_i \).
-Here, we use the \gls{geodesic} distance to parameterize the difference, and hence  uncertainty, of associating the measurement with a given vertex.
+Here, we use the geodesic distance to parameterize the difference, and hence  uncertainty, of associating the measurement with a given vertex.
 From spherical trigonometry~\cite{gade2010}, the central angle between measurement \( \vc{p}_i \) and vertex \( \vc{v}_i \) of the shape estimate is
@@
 The difficulty lies in implementing an algorithm that can operate in real time.
-Since the \gls{lidar} will be operating at upwards of \SI{1}{\hertz} efficient processing of the measurement and computation of the guidance commands is critical.
+Since the LIDAR will be operating at upwards of \SI{1}{\hertz} efficient processing of the measurement and computation of the guidance commands is critical.
 Our approach solves this complexity by determining the vertex that should be measured to optimally update the shape estimate.
@@
 \begin{align}\label{eq:explore_cost}
-    J_i (\ipos, \iatt, \aatt) = \alpha_w J_{w_i} + \alpha_d J_{d_i}(\rpos) + \alpha_c J_{c_i}(\rpos)
+    J_i (x, R, R_A) = \alpha_w J_{w_i} + \alpha_d J_{d_i}(x_r) + \alpha_c J_{c_i}(x_r)
 \end{align}
 where the weighting factors \( \alpha_w, \alpha_d, \alpha_c \in \R^1 \) are chosen such that \( \alpha_w + \alpha_d + \alpha_c = 1 \).
-The cost function is defined as a function of the current inertial position, \gls{sym:ipos}, and the attitude, \gls{sym:iatt} of the spacecraft.
-Furthermore, knowledge of the small body rotation is required in order to determine the position of the spacecraft in the small body fixed frame, \( \gls{sym:rpos} = \gls{sym:aatt}[^T] \gls{sym:ipos}\).
+The cost function is defined as a function of the current inertial position, \( x \in \R^3 \), and the attitude, \( R \in \R^{3\times3}\) of the spacecraft.
+Furthermore, knowledge of the small body rotation is required in order to determine the position of the spacecraft in the small body fixed frame, \( x_r = R_A^T x\).
 
@@
 \begin{align*}
-    \vc{v}_{min} = \min_{i} J_i(\ipos, \iatt, \aatt),
+    \vc{v}_{min} = \min_{i} J_i(x, R, R_A),
 \end{align*}
@@
 \begin{align}
-    \ipos_d = r_d \aatt \vc{v}_{min}, 
+    x_d = r_d R_A \vc{v}_{min}, 
 \end{align}
@@
 \end{align}
-This form of \( R_d \) will direct the \( \bvec{1} \) axis towards the small body, and can be modified for a different camera orientation.
+This form of \( R_d \) will direct the \( b_1 \) axis towards the small body, and can be modified for a different camera orientation.
 
@@
 The goal of refinement, or more generally remeshing, is given a mesh ( or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
-In this work, we utilize the isotropic remeshing algorithm implemented in \gls{cgal}.
+In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL).
 This algorithm uses an iterative method which repeatedly splits long edges, collapses short edges, and relocates vertices until all edges are approximately the desired target edge length.
@@
 \begin{align*}
-    \dot{\ipos} &= \ivel, \\
-    \parenth{m_1 + m_2} \dot{\ivel} &= - \sum_{i=0}^2 m_i \aatt \deriv{U}{\apos_i} + u_f, \\
-    \dot{\iatt} &= \iatt \iangvel, \\
-    J \dot{\iangvel} + \hat{\iangvel} J \iangvel &= \sum_{i=0}^2 m_i \hat{\spos}_i \iatt^T \aatt \deriv{U}{\apos_i} + u_m. 
+    \dot{x} &= \ivel, \\
+    \parenth{m_1 + m_2} \dot{\ivel} &= - \sum_{i=0}^2 m_i R_A \deriv{U}{\apos_i} + u_f, \\
+    \dot{R} &= R \iangvel, \\
+    J \dot{\iangvel} + \hat{\iangvel} J \iangvel &= \sum_{i=0}^2 m_i \hat{\spos}_i R^T R_A \deriv{U}{\apos_i} + u_m. 
 \end{align*}
@@
 The asteroids are assumed to constantly rotate about the \( \vc{f}_3 = \vc{e}_3\) axis according to the parameters given in~\cref{tab:dynamic_asteroids}.
-Furthermore, the state of the asteroid, namely the rotation matrix \( \aatt \), is assumed to be known based on ground measurements or previous data.
+Furthermore, the state of the asteroid, namely the rotation matrix \( R_A \), is assumed to be known based on ground measurements or previous data.
 \begin{table}[htbp]
@@
 \end{table}
-At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( \ipos(0) = \begin{bmatrix} x_0 & 0 & 0 \end{bmatrix} \si{\kilo\meter} \).
+At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( x_0 = \begin{bmatrix} x_0 & 0 & 0 \end{bmatrix} \si{\kilo\meter} \).
 In addition, at the initial state the spacecraft is orientated such that the \( b_1 \) axis is aligned with the inertial \( e_2 \) axis.
-In other words the initial orientation is given by \( \iatt(0) = \exp(\frac{\pi}{2} \hat{e}_3)\).
+In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat{e}_3)\).
 The shape reconstruction phase of the simulation is performed over \SI{15000}{\second}, over which time the spacecraft will take \gls{lidar} measurements of the surface at \SI{1}{\hertz}.

### 2018-08-08 manuscript.tex
Fix compile errors for dissertation additions

@@
     \centering
-    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.49\textwidth]{figures/computational_geometry/isotropic/original_cube.jpg}}~
-    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.49\textwidth]{figures/computational_geometry/isotropic/remesh_cube.jpg}}
+    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.49\textwidth]{figures/original_cube.jpg}}~
+    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.49\textwidth]{figures/remesh_cube.jpg}}
     \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
@@
 In this section, we demonstrate the use of the results presented in~\cref{sec:mathematical_background,sec:se3_control,sec:shape_reconstruction} with several numerical examples.
-The incremental shape reconstruction approach from~\cref{sec:radius_update} is used to iteratively reconstruct the shape of several asteroid given \gls{lidar} measurements.
+The incremental shape reconstruction approach from~\cref{sec:radius_update} is used to iteratively reconstruct the shape of several asteroid given LIDAR measurements.
 We utilize radar shape models of asteroids \num{4769} Castalia, (\num{52760}) \num{1998} \(\text{ML}_{14}\), \num{1620} Geographos, and 6489 Golevka~\cite{neese2004}.
@@
 With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
-\Gls{lidar} measurements are generated until the total uncertainty
+LIDAR measurements are generated until the total uncertainty
 \begin{align*}
@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/geographos/partial_0.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_1872.jpg}}
+    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/geographos/partial_0.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_1872.jpg}}
 
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_3745.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_5617.jpg}}
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_3745.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_5617.jpg}}
 
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_7489.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/truth.jpg}}
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_7489.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/truth.jpg}}
     \caption[Asteroid Geographos incremental reconstruction]{Incremental reconstruction of asteroid Geographos~\label{fig:geographos_reconstruction}}
@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_0.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_1321.jpg}}\\%
+    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_0.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_1321.jpg}}\\%
 
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_2643.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_3964.jpg}}\\%
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_2643.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_3964.jpg}}\\%
 
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_5285.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/truth.jpg}}
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_5285.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/truth.jpg}}
     \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
@@
 \begin{align*}
-    \dot{x} &= \ivel, \\
-    \parenth{m_1 + m_2} \dot{\ivel} &= - \sum_{i=0}^2 m_i R_A \deriv{U}{\apos_i} + u_f, \\
-    \dot{R} &= R \iangvel, \\
-    J \dot{\iangvel} + \hat{\iangvel} J \iangvel &= \sum_{i=0}^2 m_i \hat{\spos}_i R^T R_A \deriv{U}{\apos_i} + u_m. 
+    \dot{x} &= v, \\
+    \parenth{m_1 + m_2} \dot{v} &= - \sum_{i=0}^2 m_i R_A \deriv{U}{z_i} + u_f, \\
+    \dot{R} &= R \Omega, \\
+    J \dot{\Omega} + \hat{\Omega} J \Omega &= \sum_{i=0}^2 m_i \hat{\rho}_i R^T R_A \deriv{U}{z_i} + u_m. 
 \end{align*}
@@
 Throughout the simulation the control inputs are computed using the current shape estimate of the asteroid. 
-As measurements are collected, the spacecraft autonomously updates its shape estimate and uses this estimate to compute the control inputs and desired future states using the details provided in~\cref{sec:radius_update,sec:explore_asteroid}.
+As measurements are collected, the spacecraft autonomously updates its shape estimate and uses this estimate to compute the control inputs and desired future states using the details provided in TODO.
 These simulations demonstrate the ability of a spacecraft to autonomously explore and maneuver around an unknown small body.
@@
 In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat{e}_3)\).
-The shape reconstruction phase of the simulation is performed over \SI{15000}{\second}, over which time the spacecraft will take \gls{lidar} measurements of the surface at \SI{1}{\hertz}.
+The shape reconstruction phase of the simulation is performed over \SI{15000}{\second}, over which time the spacecraft will take LIDAR measurements of the surface at \SI{1}{\hertz}.
 Once the total uncertainty has been reduced sufficiently the spacecraft maneuvers to a ``home'' position aligned with the \( f_1 \) axis of the asteroid.
@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_0}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:52760_partial_25}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/dynamic_exploration/52760/partial_3749.jpg}}
+    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_0}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:52760_partial_25}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/dynamic_exploration/52760/partial_3749.jpg}}
 
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:52760_partial_50}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/dynamic_exploration/52760/partial_7499.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:52760_partial_75}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/dynamic_exploration/52760/partial_11249.jpg}}
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:52760_partial_50}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/dynamic_exploration/52760/partial_7499.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:52760_partial_75}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/dynamic_exploration/52760/partial_11249.jpg}}
 
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:52760_partial_100}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/dynamic_exploration/52760/partial_14998.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:52760_truth}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/52760/truth.jpg}}
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:52760_partial_100}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/dynamic_exploration/52760/partial_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:52760_truth}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/52760/truth.jpg}}
     \caption[Asteroid 52760 incremental reconstruction]{Incremental reconstruction of asteroid 52760~\label{fig:52760_reconstruction}}
@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_3749.jpg}}
+    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_3749.jpg}}
 
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_7499.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_11249.jpg}}
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_7499.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_11249.jpg}}
 
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_14998.jpg}}%
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_14998.jpg}}%
     % \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.18\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/52760/truth.jpg}}
@@
     \centering
-    \subcaptionbox{3D visualization of the trajectory\label{fig:52760_explore_trajectory}}{\includegraphics[trim={0 0 0 0},clip,keepaspectratio,width=0.99\textwidth]{figures/computational_geometry/dynamic_exploration/52760/state/asteroid_trajectory.jpg}
+    \subcaptionbox{3D visualization of the trajectory\label{fig:52760_explore_trajectory}}{\includegraphics[trim={0 0 0 0},clip,keepaspectratio,width=0.99\textwidth]{figures/dynamic_exploration/52760/state/asteroid_trajectory.jpg}
 }\\%
@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_3749.jpg}}
+    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_3749.jpg}}
 
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_7499.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_11249.jpg}}
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_7499.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_11249.jpg}}
 
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_14998.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:castalia_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/castalia/truth.jpg}}
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:castalia_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/castalia/truth.jpg}}
     \caption[Asteroid Castalia incremental reconstruction]{Incremental reconstruction of asteroid Castalia~\label{fig:castalia_reconstruction}}
@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_weights_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_weights_3749.jpg}}
+    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_3749.jpg}}
 
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_weights_7499.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_weights_11249.jpg}}
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_7499.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_11249.jpg}}
 
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_weights_14998.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/castalia/truth.jpg}}
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/castalia/truth.jpg}}
     \caption[Asteroid Castalia shape reconstruction with uncertainty]{Incremental reconstruction of asteroid Castalia.
@@
     \centering
-    \subcaptionbox{3D visualization of the trajectory\label{fig:castalia_explore_trajectory}}{\includegraphics[trim={15cm 0cm 15cm 0cm},clip,keepaspectratio,width=\textwidth,height=0.5\textheight]{figures/computational_geometry/dynamic_exploration/castalia/state/asteroid_trajectory.jpg}}\\%
+    \subcaptionbox{3D visualization of the trajectory\label{fig:castalia_explore_trajectory}}{\includegraphics[trim={15cm 0cm 15cm 0cm},clip,keepaspectratio,width=\textwidth,height=0.5\textheight]{figures/dynamic_exploration/castalia/state/asteroid_trajectory.jpg}}\\%
     \subcaptionbox{Components of position\label{fig:castalia_explore_components}}{\input{tikz/castalia_asteroid_position.tikz}}
@@
     \centering
-    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=\textwidth]{figures/computational_geometry/dynamic_exploration/castalia/refine/slope.pdf}}\\%
-    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/refine/slope_masked.pdf}}
+    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=\textwidth]{figures/dynamic_exploration/castalia/refine/slope.pdf}}\\%
+    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/slope_masked.pdf}}
     \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}
@@
     \centering
-    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=\textwidth]{figures/computational_geometry/dynamic_exploration/castalia/refine/dist.pdf}}\\%
-    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/refine/dist_masked.pdf}}
+    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=\textwidth]{figures/dynamic_exploration/castalia/refine/dist.pdf}}\\%
+    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/dist_masked.pdf}}
     \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
@@
     \centering
-    \includegraphics[width=\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/refine/cost.pdf}
+    \includegraphics[width=\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/cost.pdf}
     \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
@@
     \centering
-    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=1.0\textwidth]{figures/computational_geometry/dynamic_exploration/castalia/refine/density.pdf}}
+    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=1.0\textwidth]{figures/dynamic_exploration/castalia/refine/density.pdf}}
 
-    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=1.0\textwidth]{figures/computational_geometry/dynamic_exploration/castalia/land/density.pdf}}
+    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=1.0\textwidth]{figures/dynamic_exploration/castalia/land/density.pdf}}
     \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
@@
 The increased number of faces and vertices in the landing area allows for the capture of the small surface features.
-\Cref{fig:castalia_refinement} shows that given \gls{lidar} measurements alone and the algorithm presented in~\cref{sec:radius_update} the small craters and features are effectively estimated.
+\Cref{fig:castalia_refinement} shows that given LIDAR measurements alone and the algorithm presented in~\cref{sec:radius_update} the small craters and features are effectively estimated.
 \begin{figure}[htbp]
     \centering
-    \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,width=0.49\textwidth]{figures/computational_geometry/dynamic_exploration/castalia_bump_true.jpg}}~
-    \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,width=0.49\textwidth]{figures/computational_geometry/dynamic_exploration/castalia_bump_est.jpg}}
+    \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,width=0.49\textwidth]{figures/dynamic_exploration/castalia_bump_true.jpg}}~
+    \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,width=0.49\textwidth]{figures/dynamic_exploration/castalia_bump_est.jpg}}
     \caption{Asteroid Castalia with augmented with additional surface features~\label{fig:castalia_refinement}}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/computational_geometry/dynamic_exploration/castalia/land/asteroid_trajectory.jpg}
+    \includegraphics[width=\textwidth]{figures/dynamic_exploration/castalia/land/asteroid_trajectory.jpg}
     \caption{Vertical descent onto 4769 Castalia~\label{fig:castalia_landing}}

### 2018-08-09 manuscript.tex
Update abstract

@@
     This shape model is then used in a nonlinear controller to track a desired trajectory about the asteroid.
-    The closed loop approach allows a spacecraft to approach and operate near an unknown asteroid while autonomously generating a surface shape model.
-    We demonstrate this approach through a dynamic simulation about asteroid 4769 Castalia.
+    Finally, a multi resolution approach is presented which enables for a higher fidelity shape representation in a specified location while avoiding the inherent burdens of a uniformly high resolution mesh.
+    This approach enables for an accurate shape determination around a potential landing site.
+    We demonstrate this approach using several radar shape models of asteroids and provide a full dynamic simulation about asteroid 4769 Castalia.
 \end{abstract}

### 2018-08-09 manuscript.tex

@@
 \begin{itemize}
-    \item \( \vecbf{x} \) - the position of the center of mass of the dumbbell spacecraft represented in the inertial frame, \( \vecbf{e}_i\),
-    \item \( R \) - the rotation matrix which transforms vectors defined in the spacecraft fixed frame, \( \vecbf{b}_i \), to the inertial frame, \( \vecbf{e}_i \),
-    \item \( \vecbf{\Omega} \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame, \( \vecbf{b}_i \), and
-    \item \( R_A \) - the rotation matrix which transforms vectors defined in the asteroid fixed frame, \( \vecbf{f}_i \), to the inertial frame, \( \vecbf{e}_i \)
-\end{itemize}.
+    \item \( \vc{x} \) - the position of the center of mass of the dumbbell spacecraft represented in the inertial frame, \( \vc{e}_i\),
+    \item \( R \) - the rotation matrix which transforms vectors defined in the spacecraft fixed frame, \( \vc{b}_i \), to the inertial frame, \( \vc{e}_i \),
+    \item \( \vc{\Omega} \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame, \( \vc{b}_i \), and
+    \item \( R_A \) - the rotation matrix which transforms vectors defined in the asteroid fixed frame, \( \vc{f}_i \), to the inertial frame, \( \vc{e}_i \).
+\end{itemize}
 In this work, we assume that the asteroid is much more massive than the spacecraft and its motion is not affected by that of the spacecraft.
@@
 
-Using Hamilton's principle gives the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
+\subsection{Spacecraft Dynamic Model}
+Using Hamilton's principle one can derive the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
 \begin{align}
-    \dot{\vb{x}} &= \vb{v}, \\
-    \parenth{m_1 + m_2} \dot{\vecbf{v}} &= m_1 R_A \deriv{U}{\vecbf{z}_1} + m_2 R_A \deriv{U}{\vecbf{z}_2}, \\
-    \dot{R} &= R S(\vb{\Omega}) , \\
-    J \dot{\vecbf{\Omega}} + \vecbf{\Omega} \times J \vecbf{\Omega} &= \vecbf{M}_1 + \vecbf{M}_2.
+    \dot{\vc{x}} &= \vc{v}, \\
+    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2}, \\
+    \dot{R} &= R S(\vc{\Omega}) , \\
+    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2.
 \end{align}
-The vectors \( \vecbf{z}_1 \) and \( \vecbf{z}_2\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
+The vectors \( \vc{z}_1 \) and \( \vc{z}_2\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
 \begin{align}
-    \vecbf{z}_1 &= R_A^T \parenth{\vecbf{x} + R \vecbf{\rho}_1} , \\
-    \vecbf{z}_2 &= R_A^T \parenth{\vecbf{x} + R \vecbf{\rho}_2}.
+    \vc{z}_1 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_1} , \\
+    \vc{z}_2 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_2}.
 \end{align}
-The gravitational moment on the dumbbell \( \vecbf{M}_i\) is defined as
+The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as
 \begin{align}
-    \vecbf{M}_i = m_i \parenth{S(R_A^T \vb{\rho}_i) R^T \deriv{U}{\vb{z}_i}}.
+    \vc{M}_i = m_i \parenth{S(R_A^T \vc{\rho}_i) R^T \deriv{U}{\vb{z}_i}}.
 \end{align}
@@
 \begin{align}
-    U(\vecbf{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vecbf{r}_e \cdot \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vecbf{r}_f \cdot \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f,
+    U(\vc{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vc{r}_e \cdot \vc{E}_e \cdot \vc{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vc{r}_f \cdot \vc{F}_f \cdot \vc{r}_f \cdot \omega_f,
 \end{align}
-and \( \vecbf{r}_e\) and \(\vecbf{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
+and \( \vc{r}_e\) and \(\vc{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
 The position of each mass \(m_i\) of the dumbbell is defined in the dumbbell fixed frame by the vector \(\vb{\rho}_i\).
 
-\subsection{Spacecraft Dynamic Model}
+\subsection{Polyhedron Potential Model}\label{sec:polyhedron_potential}
 
-\subsection{Polyhedron Potential Model}
+% most use a spherical harmonic model or a ellipsoid model but we use a polyhedron model
+An accurate gravitational potential model is necessary for the operation of spacecraft about asteroids.
+Additionally, a detailed shape model of the asteroid is needed for trajectories passing close to the body.
+The classic approach is to expand the gravitational potential into a harmonic series and compute the series coefficients.
+However, the harmonic expansion is always an approximation as a result of the infinite order series used in the representation.
+Additionally, the harmonic model used outside of the circumscribing sphere is not guaranteed to converge inside the sphere, which makes it unsuitable for trajectories near the surface.
 
-\section{Range Measurement Model}
+We represent the gravitational potential of the asteroid using a polyhedron gravitation model.
+This model is composed of a polyhedron, which is a three-dimensional solid body, that is defined by a series of vectors in the body-fixed frame.
+The vectors define vertices in the body-fixed frame as well as planar faces which compose the surface of the asteroid.
+We assume that each face is a triangle composed of three vertices and three edges.
+As a result, only two faces meet at each edge while three faces meet at each vertex.
+Only the body-fixed vectors, and their associated topology, is required to define the exterior gravitational model.
+References~\cite{werner1994} and~\cite{werner1996} give a detailed derivation of the polyhedron model.
+Here, we summarize the key developments and equations required for implementation.
+
+Consider three vectors \( \vc{v}_1, \vc{v}_2, \vc{v}_3 \in \R^{3 \times 1} \), assumed to be ordered in a counterclockwise direction about an outward facing normal vector, which define a face.
+It is easy to define the three edges of each face as
+\begin{align}\label{eq:edges}
+    \vc{e}_{i+1,i} = \vc{v}_{i+1} - \vc{v}_i \in \R^{3 \times 1 },
+\end{align}
+where the index \( i \in \parenth{1,2,3} \) is used to permute all edges of each face.
+Since each edge is a member of two faces, there exist two edges which are defined in opposite directions between the same vertices.
+We can also define the outward normal vector to face \( f\)  as
+\begin{align}\label{eq:face_normal}
+    \hat{\vc{n}}_f &= \parenth{\vc{v}_{2} - \vc{v}_1} \times \parenth{\vc{v}_{3} - \vc{v}_2} \in \R^{3 \times 1},
+\end{align}
+and the outward facing normal vector to each edge as
+\begin{align}\label{eq:edge_normal}
+    \hat{\vc{n}}_{i+1,i}^f &= \parenth{\vc{v}_{i+1} - \vc{v}_i} \times \hat{\vc{n}}_f \in \R^{3 \times 1}.
+\end{align}
+For each face we define the face dyad \( \vc{F}_f \) as
+\begin{align}\label{eq:face_dyad}
+    \vc{F}_f &= \hat{\vc{n}}_f \hat{\vc{n}}_f \in \R^{3 \times 3}.
+\end{align}
+Each edge is a member of two faces and has an outward pointing edge normal vector, given in~\cref{eq:edge_normal}, perpendicular to both the edge and the face normal.
+For the edge connecting the vectors \( \vc{v}_1 \) and \( \vc{v}_2 \), which are shared between the faces \(A\) and \( B\), the per edge dyad is given by
+\begin{align}\label{eq:edge_dyad}
+    \vc{E}_{12} = \hat{\vc{n}}_A \hat{\vc{n}}_{12}^A + \hat{\vc{n}}_B \hat{\vc{n}}_{21}^B \in \R^{3 \times 3}.
+\end{align}
+The edge dyad \( \vc{E}_e  \), is defined for each edge and is a function of the two adjacent faces meeting at that edge.
+The face dyad \( \vc{F}_f \), is defined for each face and is a function of the face normal vectors.
+
+Let \( \vc{r}_i \in \R^{3 \times 1} \) be the vector from the spacecraft to the vertex \( \vc{v}_i \) and it's length is given by \( r_i = \norm{\vc{r}_i} \in \R^{1} \).
+The per-edge factor \( L_e \in \R^{1}\), for the edge connecting vertices \( \vc{v}_i \) and \( \vc{v}_j \), with a constant length \( e_{ij} = \norm{\vc{e}_{ij}} \in \R^1\) is
+\begin{align}\label{eq:edge_factor}
+    L_e &= \ln \frac{r_i + r_j + e_{ij}}{r_i + r_j - e_{ij}}.
+\end{align}
+For the face defined by the vertices \( \vc{v}_i, \vc{v}_j, \vc{v}_k \) the per-face factor \( \omega_f \in \R^{1} \) is
+\begin{align}\label{eq:face_factor}
+    \omega_f &= 2 \arctan \frac{\vc{r}_i \cdot \vc{r}_j \times \vc{r}_k}{r_i r_j r_k + r_i \parenth{\vc{r}_j \cdot \vc{r}_k} + r_j \parenth{\vc{r}_k \cdot \vc{r}_i} + r_k \parenth{\vc{r}_i \cdot \vc{r}_j}} .
+\end{align}
+The gravitational potential due to a constant density polyhedron is given as
+\begin{align}\label{eq:potential}
+    U(\vc{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vc{r}_e \cdot \vc{E}_e \cdot \vc{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vc{r}_f \cdot \vc{F}_f \cdot \vc{r}_f \cdot \omega_f \in \R^1,
+\end{align}
+where \( \vc{r}_e\) and \(\vc{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
+Furthermore we can use these definitions to define the attraction, gravity gradient matrix, and Laplacian as
+\begin{align}
+    \nabla U ( \vc{r} ) &= -G \sigma \sum_{e \in \text{edges}} \vc{E}_e \cdot \vc{r}_e \cdot L_e + G \sigma \sum_{f \in \text{faces}} \vc{F}_f \cdot \vc{r}_f \cdot \omega_f \in \R^{3 \times 1} , \label{eq:attraction}\\
+    \nabla \nabla U ( \vc{r} ) &= G \sigma \sum_{e \in \text{edges}} \vc{E}_e  \cdot L_e - G \sigma \sum_{f \in \text{faces}} \vc{F}_f \cdot \omega_f \in \R^{3 \times 3}, \label{eq:gradient_matrix}\\
+    \nabla^2 U &= -G \sigma \sum_{f \in \text{faces}}  \omega_f \in \R^1 .\label{eq:laplacian}
+\end{align}
+
+One interesting thing to note is that both~\cref{eq:face_dyad,eq:edge_dyad} can be precomputed without knowledge of the position of the satellite.
+They are both solely functions of the vertices and edges of the polyhedral shape model and are computed once and stored.
+Once a position vector \( \vc{r} \) is defined, the scalars given in~\cref{eq:edge_factor,eq:face_factor} can be computed for each face and edge.
+Finally,~\cref{eq:potential} is used to compute the gravitational potential on the spacecraft.
+The Laplacian, defined in~\cref{eq:laplacian}, gives a simple method to determine if the spacecraft has collided with the body~\cite{werner1996}.
+
+\subsection{Range Measurement Model}
 
@@
 
-A pulsed time of flight laser distance device consists of a laser transmitter which emits pulses with a duration between \SIrange{5}{50}{\nano\second}~\cite{amann2001}.
-The emitted light pulse triggers a start signal in the onboard timing device and the reflected energy from the object provides the stop command.
-A block diagram of the laser range finder is shown in~\cref{fig:lidar_block_diagram}.
-A signal is generated by the transmitter and directed through the optics towards the target. 
-At the same time a pulse is sent to a high precision clock to record the outgoing transmission. 
-The energy reflects off the target and is passed through a detector which signal the stop command. 
-The time of flight is then recorded and used to compute the range.
-\begin{figure}[htbp]
-    \centering
-    \input{tikz/laser_range_finder.tikz}
-    \caption{ Block diagram of a time of flight laser range finder\label{fig:lidar_block_diagram}}
-\end{figure}
-A wide variety of lasers are used depending on the intended measurements range.
-In the spacecraft case, lasers providing peak energy in the range of \SI{15}{\mega\joule} are often required to measure distance of over \SI{50}{\kilo\meter}~\cite{berry2013}.
-
-The laser range finder is frequently equipped with angle encoders to enable the definition of the position of the measurement point with respect to the sensor. 
-Mechanical scanning is performed using a control system which  either moves the entire laser range finder or only the measuring beam.
-Focal plane scanning is another approach which reduces the mechanical complexity of a mechanical scanning system.
-The laser energy illuminates the entire field of view on the surface.
-An array of detectors are arranged to view the surface.
-Each detector only views a portion of the total field of view and the signals are analyzed in the time domain.
-Using this methodology, the system can simultaneously measure distance in multiple directions without any moving parts~\cite{amann2001}.
-
-\paragraph{Ray casting}
-
-In the computer graphics field, a major problem is the determination of which objects are visible to the user.
-This problem arises in many computer graphics rendering algorithms, such as ray tracing.
-Ray tracing is a rendering technique for generating an image by tracing the path of light, in the form of pixels, as it travels through a virtual world, reflects off of surfaces, and eventually lands on an image plane.
-As the light strikes the virtual objects the surface properties are used to determine the amount of energy that is reflected, absorbed, or scattered from the surface to accurately render the virtual image.
-Ray casting is a similar but noticeably simpler approach for the rendering of virtual scenes.
-In a method similar to the photographic process in reverse, for each pixel of the image a ray is cast towards the scene and the intersections of this ray with any objects is recorded.
-The first object which intersects the ray is defined as visible while those beyond would be occluded.
-Given this intersection point, the surface normal is computed and surface shading can be determined to render the scene.
-This provides a much simpler approach to virtual scene rendering but does not allow for the determination of high fidelity surface interactions of the light.
-
-Our application is adopted from the field of computational geometry and known as the ray shooting problem.
-The ray shooting problem is defined as follows: given a set of objects in \( d \) dimensional space, such as the shape model of a small body, create a data structure such that for any given query ray, e.g.\ the point of view of a camera, the initial object and its location can be determined quickly.
-Our goal is to use the true shape model of a small body and simulate the intersection of many rays with the surface.
-These rays will serve to emulate the range measurements of the surface using a LIDAR sensor.
-As a result, we must also implement a ray casting algorithm that will find the intersection of a measurement of the surface.
-
-\begin{figure}[htbp]
-    \centering
-    \input{tikz/frustrum.tikz}
-    \caption{View frustum for spacecraft sensor modeling\label{fig:view_frustrum}}
-\end{figure}
-We assume that the spacecraft is located at \(\rpos\) in the asteroid fixed frame.
-We define a camera fixed frame, \( \vc{c}_i \in \R^3 \), which is defined with respect to the spacecraft body fixed frame, \( \vc{b}_i \).
-The camera/sensor is aligned with \( \vc{c}_1 \) in the spacecraft fixed frame and we define an additional vector, termed the up axis \( \vc{c}_3 \) as the vertical direction of the image plane. 
-Finally, the standard basis is completed with \(  \vc{c}_2 = \vc{c}_1 \times \vc{c}_3 \) which defines a reference frame attached to the image plane of the sensor.
-Furthermore, we model the laser ranging sensor as having a fixed field of view defined by the angles \( \alpha, \beta \), defining the vertical and horizontal fields of view.
-In order to simulate depth measurements we need to determine the transformation of locations in the image frame to the small body fixed frame. 
-Given the view axis, and a chosen distance \( d  \in \R^1 \), we can define a viewing frustum associated with the sensor. 
-We can compute the vectors associated with the maximum extents of the far plane as follows.
-The half height and width of the far plane, at a distance \( d \), are computed as
-\begin{align*}
-    H = d \tan \frac{\alpha}{2} , \\
-    W = d \tan \frac{\beta}{2} .
-\end{align*}
-From these values, the extents of the far plane are defined by the vectors
-\begin{align*}
-    A = \vc{c}_1 + H \vc{c}_3 - W \vc{c}_2 , \\
-    B = \vc{c}_1 + H \vc{c}_3 + W \vc{c}_2, \\
-    C = \vc{c}_1 - H \vc{c}_3 + W \vc{c}_2, \\
-    D = \vc{c}_1 - H \vc{c}_3 - W \vc{c}_2.
-\end{align*}
-The view frustum is visualized in~\cref{fig:view_frustrum} and allows for any vector in the field of view to be defined as a linear combination of the extents of the far plane.
-% tylee: not sure what "befined" means? 
-% shankar: should have been "defined"
-
 \section{Incremental Shape Reconstruction}\label{sec:radius_update}
@@
 One of the first tasks for any spacecraft mission to a small body is to generate an estimate of the shape.
-This shape model is used for a variety of purposes, such as the polyhedron potential model, like that presented in~\cref{sec:polyhedron_potential} or landing site section and guidance.
 We assume that upon arrival at a target body, the spacecraft contains an initial estimate for the shape of the small body.
@@
 This assumption means that the total number of vertices of the shape model is fixed.
-However, additional detail, in the form of additional vertices, is possible by using standard mesh subdivision algorithms~\cite{orourke1998}, which we later demonstrate in~\cref{sec:landing_refinement}.
+However, additional detail, in the form of additional vertices, is possible by using standard mesh subdivision algorithms~\cite{orourke1998}.
 
@@
 A sequential process can be used to iteratively update the shape estimate given many measurements of the surface.
-For example,~\cref{sec:reconstruction_examples} shows the Bayesian update approach applied to several different asteroids.
 
@@
 This guidance schemes enables autonomous operations around a small body.
-% TODO talk about the basics of guidance/control for systems here and add tikz of block diagram
-
-% \gls{gnc} refers to the design of systems to control the operations of vehicles, specifically automobiles, aircraft, or spacecraft.
-% For spacecraft, many of these operations are computed ahead of time by operators and executed on board in an open loop fashion.
-% Guidance refers to the determination of the desired future states, or trajectory, that the spacecraft should follow to achieve some goals.
-% Navigation, or estimation, refers to the determination of the current state of the spacecraft given measurements.
-% Control refers to the application of forces, \( u_m, u_f \), required by the spacecraft to follow the desired trajectory while maintaining stability and other criteria. 
-% A block diagram representation of the entire \gls{gnc} system is shown in~\cref{fig:gnc}.
-% The approach presented in this section addresses the guidance and control portions of \cref{fig:gnc} but does not address the navigation. 
-% We assume that we have precise knowledge of the spacecraft state and small body rotation.
-
-% \begin{figure}[htbp]
-%     \centering
-%     \includegraphics[width=\textwidth]{example-image-golden}
-%     \caption{Block diagram of GNC system\label{fig:gnc}}
-% \end{figure}
 
@@
     \centering
-    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.49\textwidth]{figures/original_cube.jpg}}~
-    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.49\textwidth]{figures/remesh_cube.jpg}}
+    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.25\textwidth]{figures/original_cube.jpg}}~
+    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.25\textwidth]{figures/remesh_cube.jpg}}
     \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
@@
 
-In this section, we demonstrate the use of the results presented in~\cref{sec:mathematical_background,sec:se3_control,sec:shape_reconstruction} with several numerical examples.
-The incremental shape reconstruction approach from~\cref{sec:radius_update} is used to iteratively reconstruct the shape of several asteroid given LIDAR measurements.
-We utilize radar shape models of asteroids \num{4769} Castalia, (\num{52760}) \num{1998} \(\text{ML}_{14}\), \num{1620} Geographos, and 6489 Golevka~\cite{neese2004}.
-The asteroids exhibit a wide range of shapes and demonstrate the effectiveness of the mesh update approach.
-\Cref{sec:kinematic_exploration} focuses on the application of the incremental mesh update scheme of~\cref{sec:radius_update} for several different asteroids.
-\Cref{sec:dynamic_exploration} incorporates the full dynamic model on \( \SE \) of a dumbbell spacecraft given in~\cref{sec:inertial_dumbbell_eoms}, the polyhedron potential model from~\cref{sec:polyhedron_potential}, and the mesh update and guidance scheme presented in~\cref{sec:radius_update}.
+In this section, we demonstrate the use of the incremental shape reconstruction algorithm.
+The approach is used to iteratively reconstruct the shape of several asteroid given LIDAR measurements.
+We utilize radar shape models of asteroids \num{4769} Castalia and (\num{52760}) \num{1998} \(\text{ML}_{14}\).
+The examples demonstrate the full dynamic simulation of a rigid spacecraft with an autonomous closed loop control scheme to both reconstruct the asteroid shape.
 
-\subsection{Shape Reconstruction}\label{sec:kinematic_exploration}
-
-The results in this section utilize a kinematics only model of the spacecraft and dynamics instead of the full dynamic simulation. 
-We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction.
-\Cref{tab:kinematic_asteroids} lists the true shape model parameters of asteroids Geographos and Golevka.
-\begin{table}[htbp]
-    \centering
-    \begin{tabular}{lccc}
-        \toprule
-        Asteroid & Semi-major axes (\si{\kilo\meter}) & Vertices & Faces\\
-        \midrule
-        \num{1620} Geographos & \( 2.5 \times 1.0 \times 1.05 \) & \num{8192} & \num{16380}  \\
-        \num{6489} Golevka & \( 0.53 \times 0.53 \times 0.53 \)  & \num{2048} & \num{4092} \\
-        \bottomrule
-    \end{tabular} 
-    \caption{Asteroid properties for kinematic only exploration~\label{tab:kinematic_asteroids}}
-\end{table}
-The spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
-The simulations begin with an triaxial ellipsoid mesh that is sized to match the semi-major axes of each asteroid.
-With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
-LIDAR measurements are generated until the total uncertainty
-\begin{align*}
-    \sum_i w_i,
-\end{align*}
-is sufficiently small.
-In addition, we compute the volume of the estimate shape throughout the simulation using the algorithm presented in~\cref{sec:polyhedron_volume}.
-
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/geographos/partial_0.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_1872.jpg}}
-
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_3745.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_5617.jpg}}
-
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_7489.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/truth.jpg}}
-    \caption[Asteroid Geographos incremental reconstruction]{Incremental reconstruction of asteroid Geographos~\label{fig:geographos_reconstruction}}
-\end{figure}
-
-\num{1620} Geographos is a highly elongated stony asteroid of the Apollo group.
-Discovered in \num{1951}, Geographos is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
-\Cref{fig:geographos_reconstruction} shows the shape reconstruction for asteroid Geographos at several distinct points during the process.
-Comparing~\cref{fig:geographos_partial_100,fig:geographos_truth} shows that the final shape closely matches the true radar model.
-In~\cref{fig:geographos_metrics} we display the vertex uncertainty and mesh volume as a function of time.
-The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.
-
-\begin{figure}[htbp]
-    \centering
-    \input{tikz/geographos_metrics.tikz}
-    \caption{Normalized uncertainty and volume percent error for Geographos\label{fig:geographos_metrics}}
-\end{figure}
-
-\num{6489} Golevka is a small angular shaped asteroid of the Apollo group.
-Discovered in \num{1995}, Golevka is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
-\Cref{fig:golevka_reconstruction} shows the shape reconstruction for asteroid Golevka at several distinct points during the process.
-Comparing~\cref{fig:golevka_partial_100,fig:golevka_truth} shows that the final shape closely matches the true radar model.
-In~\cref{fig:golevka_metrics} we display the vertex uncertainty and mesh volume as a function of time.
-
-\begin{figure}[htbp]
-    \centering
-    \input{tikz/golevka_metrics.tikz}
-    \caption{Normalized uncertainty and volume percent error for Golevka\label{fig:golevka_metrics}}
-\end{figure}
-
-The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.
-It is interesting to note that the reconstruction of Golevka achieves an accurate shape reconstruction in a much smaller amount of time as compared to Geographos.
-This is primarily due to the smaller size of Golevka and the relatively spherical shape of the body in contrast to the highly elliptical shape of Geographos.
-
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_0.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_1321.jpg}}\\%
-
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_2643.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_3964.jpg}}\\%
-
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_5285.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/truth.jpg}}
-    \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
-\end{figure}
-
-\subsection{Full Dynamic Model }\label{sec:dynamic_exploration}
-
-In this section, we simulate a dumbbell spacecraft in motion around asteroid \num{52760} and asteroid Castalia.
-The dynamic simulation utilizes the inertial equations of motion from~\cref{sec:inertial_dumbbell_eoms} and are given as
-\begin{align*}
-    \dot{x} &= v, \\
-    \parenth{m_1 + m_2} \dot{v} &= - \sum_{i=0}^2 m_i R_A \deriv{U}{z_i} + u_f, \\
-    \dot{R} &= R \Omega, \\
-    J \dot{\Omega} + \hat{\Omega} J \Omega &= \sum_{i=0}^2 m_i \hat{\rho}_i R^T R_A \deriv{U}{z_i} + u_m. 
-\end{align*}
-The nonlinear controllers described in~\cref{sec:se3_control} are used to control both the translational and rotational states of the vehicle.
-The control inputs are duplicated from~\cref{sec:se3_control} as
-\begin{align*}
-    \vc{u}_f &= -k_x e_x - k_v e_v - F_{ext} + m \ddot{x}_d . \\
-    \vc{u}_m &= -k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - M_{ext}.
-\end{align*}
+The nonlinear controllers described previously are used to control both the translational and rotational states of the vehicle.
 Throughout the simulation the control inputs are computed using the current shape estimate of the asteroid. 
@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_0}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:52760_partial_25}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/dynamic_exploration/52760/partial_3749.jpg}}
+    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_3749.jpg}}%
+    \subcaptionbox{\SI{50}{\percent} of measurements\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_7499.jpg}}
 
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:52760_partial_50}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/dynamic_exploration/52760/partial_7499.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:52760_partial_75}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/dynamic_exploration/52760/partial_11249.jpg}}
-
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:52760_partial_100}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/dynamic_exploration/52760/partial_14998.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:52760_truth}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/52760/truth.jpg}}
-    \caption[Asteroid 52760 incremental reconstruction]{Incremental reconstruction of asteroid 52760~\label{fig:52760_reconstruction}}
-\end{figure}
-
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_3749.jpg}}
-
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_7499.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_11249.jpg}}
-
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_14998.jpg}}%
-    % \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.18\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/52760/truth.jpg}}
+    \subcaptionbox{\SI{75}{\percent} of measurements\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_11249.jpg}}%
+    \subcaptionbox{\SI{100}{\percent} of measurements\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/mesh_update/52760/truth.jpg}}
     \caption[Asteroid 52760 shape reconstruction with uncertainty]{Incremental reconstruction of asteroid 52760.
@@
 \end{figure}
+
 \Cref{fig:52760_metrics} shows the total normalized uncertainty and percent error for the volume estimate. 
 The plots show that the reconstruction  converges to an accurate shape estimate after approximately \SI{8000}{\second}.
-
-\begin{figure}[htbp]
-    \centering
-    \input{tikz/52760_metrics.tikz}
-    \caption{Normalized uncertainty and volume percent error for 52760\label{fig:52760_metrics}}
-\end{figure}
-
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{3D visualization of the trajectory\label{fig:52760_explore_trajectory}}{\includegraphics[trim={0 0 0 0},clip,keepaspectratio,width=0.99\textwidth]{figures/dynamic_exploration/52760/state/asteroid_trajectory.jpg}
-}\\%
-    \subcaptionbox{Components of position\label{fig:52760_explore_components}}{\input{tikz/52760_asteroid_position.tikz}}
-    \caption{Spacecraft trajectory in the rotating asteroid frame for the exploration of 52760~\label{fig:52760_trajectory}}
-\end{figure}
 
@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_3749.jpg}}
+    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_3749.jpg}}%
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_7499.jpg}}
 
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_7499.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_11249.jpg}}
-
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_14998.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:castalia_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/castalia/truth.jpg}}
-    \caption[Asteroid Castalia incremental reconstruction]{Incremental reconstruction of asteroid Castalia~\label{fig:castalia_reconstruction}}
-\end{figure}
-
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_3749.jpg}}
-
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_7499.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_11249.jpg}}
-
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_14998.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/castalia/truth.jpg}}
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_11249.jpg}}%
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/mesh_update/castalia/truth.jpg}}
     \caption[Asteroid Castalia shape reconstruction with uncertainty]{Incremental reconstruction of asteroid Castalia.
@@
 \end{figure}
-
 The spacecraft autonomously navigates around asteroid Castalia to best minimize the cost function in~\cref{eq:control_cost}.
-The state trajectory is visualized in the asteroid frame in~\cref{fig:castalia_explore_trajectory}.
-The component plots of the trajectory are shown in~\cref{fig:castalia_explore_components}.
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{3D visualization of the trajectory\label{fig:castalia_explore_trajectory}}{\includegraphics[trim={15cm 0cm 15cm 0cm},clip,keepaspectratio,width=\textwidth,height=0.5\textheight]{figures/dynamic_exploration/castalia/state/asteroid_trajectory.jpg}}\\%
-    \subcaptionbox{Components of position\label{fig:castalia_explore_components}}{\input{tikz/castalia_asteroid_position.tikz}}
-    \caption{Spacecraft trajectory in the rotating asteroid frame for the exploration of Castalia~\label{fig:castalia_trajectory}}
-\end{figure}
 
@@
     \centering
-    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=\textwidth]{figures/dynamic_exploration/castalia/refine/slope.pdf}}\\%
-    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/slope_masked.pdf}}
+    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/slope.pdf}}%
+    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/slope_masked.pdf}}
     \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}
@@
     \centering
-    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=\textwidth]{figures/dynamic_exploration/castalia/refine/dist.pdf}}\\%
-    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/dist_masked.pdf}}
+    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/dist.pdf}}%
+    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/dist_masked.pdf}}
     \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
@@
     \centering
-    \includegraphics[width=\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/cost.pdf}
+    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/cost.pdf}
     \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
@@
     \centering
-    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=1.0\textwidth]{figures/dynamic_exploration/castalia/refine/density.pdf}}
-
-    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=1.0\textwidth]{figures/dynamic_exploration/castalia/land/density.pdf}}
+    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/density.pdf}}%
+    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/density.pdf}}
     \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
@@
     \centering
-    \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,width=0.49\textwidth]{figures/dynamic_exploration/castalia_bump_true.jpg}}~
-    \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,width=0.49\textwidth]{figures/dynamic_exploration/castalia_bump_est.jpg}}
+    \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_true.jpg}}%
+    \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_est.jpg}}
     \caption{Asteroid Castalia with augmented with additional surface features~\label{fig:castalia_refinement}}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/dynamic_exploration/castalia/land/asteroid_trajectory.jpg}
+    \includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/asteroid_trajectory.jpg}
     \caption{Vertical descent onto 4769 Castalia~\label{fig:castalia_landing}}

### 2018-08-09 manuscript.tex
Update conclusions
Update and fix references

@@
 Consider three vectors \( \vc{v}_1, \vc{v}_2, \vc{v}_3 \in \R^{3 \times 1} \), assumed to be ordered in a counterclockwise direction about an outward facing normal vector, which define a face.
-It is easy to define the three edges of each face as
-\begin{align}\label{eq:edges}
-    \vc{e}_{i+1,i} = \vc{v}_{i+1} - \vc{v}_i \in \R^{3 \times 1 },
-\end{align}
-where the index \( i \in \parenth{1,2,3} \) is used to permute all edges of each face.
-Since each edge is a member of two faces, there exist two edges which are defined in opposite directions between the same vertices.
-We can also define the outward normal vector to face \( f\)  as
-\begin{align}\label{eq:face_normal}
-    \hat{\vc{n}}_f &= \parenth{\vc{v}_{2} - \vc{v}_1} \times \parenth{\vc{v}_{3} - \vc{v}_2} \in \R^{3 \times 1},
-\end{align}
-and the outward facing normal vector to each edge as
-\begin{align}\label{eq:edge_normal}
-    \hat{\vc{n}}_{i+1,i}^f &= \parenth{\vc{v}_{i+1} - \vc{v}_i} \times \hat{\vc{n}}_f \in \R^{3 \times 1}.
-\end{align}
 For each face we define the face dyad \( \vc{F}_f \) as
@@
 
-\subsection{Range Measurement Model}
-
-Absolute distance measuring devices are a crucial sensor in spacecraft rendezvous or landing applications.
-In addition, they are a critical component for spacecraft operating near small bodies.
-Activate ranging devices allow for precise measurements of the surface shape and enable accurate and safe surface landing~\cite{berry2013}.
-
-The basic principle for all active range-finding devices is to transmit a signal onto an object and process the returned signal to determine the distance~\cite{amann2001}.
-The transmitted signal can fall into one of three categories: radio, ultrasonic, or optical.
-The benefit of an optical signal is that they can be highly focused to enable high resolution distance measurements.
-Optical distance measurement, such as laser range finders, can be further divided into three categories based on the method of operation: interferometry, time of flight, or triangulation.
-In this section, we'll briefly summarize the principles of operation of optical distance measurement devices and highlight their specific uses with respect to spacecraft missions to asteroids.
-
-Originally developed for military and surveying application, the basic principle of laser ranging is based on utilizing the fixed speed of light to measure distance.
-The time required for a pulse of energy to travel from the transmitter to the object and return is measured, \( t_d \). 
-Measuring this round trip time of flight and using the speed of light, approximately \( c = \SI{30}{\centi\meter\per\nano\second}\), allows one to easily compute the range to the object as
-\begin{align}
-    \rho = \frac{t_d}{2 c}. 
-\end{align}
-A main benefit of the time of flight ranging system is that a single pulse of energy is sufficient to accurately determine the distance with meter level precision in the case of spacecraft or millimeter level in industrial applications~\cite{zuber1997,cole1998,amann2001}.
-
 \section{Incremental Shape Reconstruction}\label{sec:radius_update}
-
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Coarse Uniform Mesh\label{fig:coarse_uniform_mesh}}{\includegraphics[trim={10cm 0 10cm 0}, clip,width=0.49\textwidth,keepaspectratio]{figures/uniform_mesh_coarse.jpg}}
-    \subcaptionbox{Fine Uniform Mesh\label{fig:fine_uniform_mesh}}{\includegraphics[trim={10cm 0 10cm 0}, clip,width=0.49\textwidth,keepaspectratio]{figures/uniform_mesh_fine.jpg}}
-    \caption{Examples of Resolution of Uniform Meshes of Triaxial Ellipsoid~\label{fig:uniform_mesh}}
-\end{figure}
 
@@
 Furthermore, the number of vertices in the estimate can be scaled according to the desired final accuracy or computational capabilities.
-For example,~\cref{fig:uniform_mesh} demonstrates two surface mesh representation for a triaxial ellipsoid at varying levels of detail. 
-A wide variety of algorithms are available to generate a near uniformly spaced mesh for an arbitrary surface~\cite{persson2004,boissonnat2005}.
 
@@
 
-The mesh update algorithm presented in~\cref{sec:radius_update} does not offer a method to determine which portion of the surface needs to be updated. 
+The mesh update algorithm presented does not offer a method to determine which portion of the surface needs to be updated. 
 In this section, we present an optimal approach for the guidance of the vehicle in order to update the shape estimate.
-Utilizing the nonlinear controllers developed in~\cref{sec:se3_control}, allows the spacecraft to maneuver to the best location that will update the shape estimate.
+A nonlinear geometric controller is utilized which allows the spacecraft to maneuver to the best location that will update the shape estimate~\cite{kulumani2017b}.
 This guidance schemes enables autonomous operations around a small body.
-
-The ideal guidance approach involves solving a global optimal control problem which satisfies the system dynamics from~\cref{sec:dumbbell_model} while minimizing the shape uncertainty.
-There are a wide variety of optimal control techniques which may be utilized to solve the problem, such as indirect methods based on the calculus of variations or direction methods based on solving a related nonlinear programming problem~\cite{kirk2012,bryson1975}.
-The difficulty lies in implementing an algorithm that can operate in real time.
-Since the LIDAR will be operating at upwards of \SI{1}{\hertz} efficient processing of the measurement and computation of the guidance commands is critical.
-Our approach solves this complexity by determining the vertex that should be measured to optimally update the shape estimate.
 
@@
 
-The shape update approach presented in~\cref{sec:radius_update} is designed with autonomous operations in mind. 
+The shape update approach presented is designed with autonomous operations in mind. 
 It is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
@@
 Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
-As shown in~\cite{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
+As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
 The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
@@
 
-The surface slope is computed according to the method developed in~\cite{scheeres1996}.
+The surface slope is computed according to the method developed in Reference~\cite{scheeres1996}.
 Due to the small size, and therefore low gravitational attraction, the force at each point on the surface is a combination of the gravitational attraction and the centripetal acceleration.
@@
 Additionally, we compute the distance, using~\cref{eq:geodesic_distance}, between the spacecraft state and each face of the asteroid. 
-Finally, we also assign a random science value to the surface in the form of two dimensional Gaussian.
+Finally, we also assign a random science value to the surface in the form of a two dimensional Gaussian.
 Utilizing these metric, a landing site is chosen to minimize the surface cost given as
@@
 However, the shape model is not highly detailed as it does not contain small craters or surface features.
-In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme in~\cref{sec:radius_update} to measure the surface.
+In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme shown previously to update the surface.
 The augmented model of Castalia is shown in~\cref{fig:castalia_refinement}.
@@
 The initial shape estimate is assumed to be spherical with approximately the same number of vertices as the truth model.
-\Cref{fig:52760_reconstruction,fig:52760_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
+\Cref{fig:52760_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
 Due to the roughly spherical shape of the asteroid large portions of the surface are quickly modified to match the measurements.
@@
 
-\Cref{fig:52760_metrics} shows the total normalized uncertainty and percent error for the volume estimate. 
-The plots show that the reconstruction  converges to an accurate shape estimate after approximately \SI{8000}{\second}.
-
 \paragraph{Asteroid 4769 Castalia Reconstruction}
@@
 Castalia is composed of two distinct lobes suggesting that it is a contact binary of two smaller objects held together by their mutual gravity.
-\Cref{fig:castalia_reconstruction,fig:castalia_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
+\Cref{fig:castalia_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
 In addition~\cref{fig:castalia_weights_reconstruction} displays the vertex uncertainty \( w_i \) as a colormap on the surface. 
@@
 The increased number of faces and vertices in the landing area allows for the capture of the small surface features.
-\Cref{fig:castalia_refinement} shows that given LIDAR measurements alone and the algorithm presented in~\cref{sec:radius_update} the small craters and features are effectively estimated.
+\Cref{fig:castalia_refinement} shows that given LIDAR measurements alone and the shape reconstruction algorithm that the small features are effectively estimated.
 \begin{figure}[htbp]
@@
 The final phase of the simulation is to utilize the mixed resolution model and vertically descend to the desired landing site. 
-This is accomplished using the closed loop control of~\cref{sec:se3_control} and a trajectory which transitions from the home position to the surface over \SI{3600}{\second}.
+This is accomplished using the closed loop control of the vehicle and a trajectory which transitions from the home position to the surface over \SI{3600}{\second}.
 The landing trajectory, using the estimated shape, is visualized in the asteroid frame in~\cref{fig:castalia_landing}.
@@
 
-\section{Summary}
+\section{Conclusions}
 
-The developments of this chapter, when combined with the details of~\cref{sec:mathematical_background,sec:lowthrust_transfers,sec:se3_control}, provide a complete approach for the operation of a spacecraft around a small body.
-This chapter developed a Bayesian update scheme to reconstruct the shape of a small body from range measurements. 
+This paper developed a Bayesian update scheme to reconstruct the shape of a small body from range measurements. 
 The approach allows for a local update operation that is able to reconstruct the shape in real time. 

### 2018-08-10 manuscript.tex
tylee edit

@@
     Instead, we present an efficient method for estimating the shape of an asteroid in real time.
-    Range measurements of the surface are used to incrementally correct an initial shape estimate.
-    This update procedure occurs in real time and provides a more accurate model of the asteroid shape.
+    Range measurements of the surface are used to incrementally correct an initial shape estimate according to Bayesian framework. 
+    Then, an optimal guidance scheme is proposed to control the vantage point of the range sensor to construct a more accurate model of the asteroid shape. 
     This shape model is then used in a nonlinear controller to track a desired trajectory about the asteroid.
@@
 \end{align}
+% // TL: equation eq:edge_normal is not resolved
 Each edge is a member of two faces and has an outward pointing edge normal vector, given in~\cref{eq:edge_normal}, perpendicular to both the edge and the face normal.
@@
 This shape can be a coarse estimate computed from ground measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid, such as that shown in~\cref{fig:uniform_mesh} which represents the maximum axes for asteroid Castalia.
+% // TL: fig:uniform_mesh is missing
 Additionally, we assume that the shape estimate is closed and a triangular faceted surface mesh, emulating those used in practice to represent asteroids.
@@
 For example, \( r_d \) can be chosen as the distance of the Biroullin sphere with an additional safety margin to mitigate any surface collision~\cite{scheeres2012a}.
+% TL: eq:translational_control undefined 
 The translational controller presented in~\cref{eq:translational_control} is used to determine the control input to follow \( x_d\).
@@
 \end{align}
+% TL: eq:inertial_velocity_dynamics undefined
 where the external force is defined by the polyhedron potential model given in~\cref{eq:inertial_velocity_dynamics}.
@@
 As measurements are collected, the spacecraft autonomously updates its shape estimate and uses this estimate to compute the control inputs and desired future states using the details provided in TODO.
+% // TL: TODO is missing. We don't have to provide the details in this paper.
 These simulations demonstrate the ability of a spacecraft to autonomously explore and maneuver around an unknown small body.

### 2018-08-10 manuscript.tex

@@
 \end{align}
-% // TL: equation eq:edge_normal is not resolved
-Each edge is a member of two faces and has an outward pointing edge normal vector, given in~\cref{eq:edge_normal}, perpendicular to both the edge and the face normal.
+Each edge is a member of two faces and has an outward pointing edge normal vector, perpendicular to both the edge and the face normal.
 For the edge connecting the vectors \( \vc{v}_1 \) and \( \vc{v}_2 \), which are shared between the faces \(A\) and \( B\), the per edge dyad is given by
@@
 We assume that upon arrival at a target body, the spacecraft contains an initial estimate for the shape of the small body.
-This shape can be a coarse estimate computed from ground measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid, such as that shown in~\cref{fig:uniform_mesh} which represents the maximum axes for asteroid Castalia.
-% // TL: fig:uniform_mesh is missing
+This shape can be a coarse estimate computed from ground measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid.
 Additionally, we assume that the shape estimate is closed and a triangular faceted surface mesh, emulating those used in practice to represent asteroids.
@@
 For example, \( r_d \) can be chosen as the distance of the Biroullin sphere with an additional safety margin to mitigate any surface collision~\cite{scheeres2012a}.
-% TL: eq:translational_control undefined 
-The translational controller presented in~\cref{eq:translational_control} is used to determine the control input to follow \( x_d\).
 We assume that the tracking errors are small, such that \( e_x, e_v \) are negligible, therefore the control becomes
@@
 \end{align}
-% TL: eq:inertial_velocity_dynamics undefined
-where the external force is defined by the polyhedron potential model given in~\cref{eq:inertial_velocity_dynamics}.
+where the external force is defined by the polyhedron potential model given in~\cref{eq:attraction}.
 The control cost is then defined as the integral over the desired trajectory~\cref{eq:spherical_waypoint} between the current state and the desired vertex as
@@
 Throughout the simulation the control inputs are computed using the current shape estimate of the asteroid. 
-As measurements are collected, the spacecraft autonomously updates its shape estimate and uses this estimate to compute the control inputs and desired future states using the details provided in TODO.
-% // TL: TODO is missing. We don't have to provide the details in this paper.
+As measurements are collected, the spacecraft autonomously updates its shape estimate and uses this estimate to compute the control inputs and desired future states.
 These simulations demonstrate the ability of a spacecraft to autonomously explore and maneuver around an unknown small body.

### 2018-10-12 utilities/setup_repo.sh
Add travis build

@@ -1,0 +1,19 @@
+#!/bin/bash
+
+# add the correct remote repositories
+git_repo="git@github.com:skulumani/2018_aas_manuscript.git"
+bb_repo="git@bitbucket.org:shankarkulumani/2018_aas_manuscript.git"
+fdcl_repo="git@github.com:fdcl-gwu/2018_aas_manuscript.git"
+
+printf "Setting the origin remote to point to Github and Bitbucket:\n\n"
+printf "Github: $git_repo\n"
+printf "Bitbucket: $bb_repo\n\n"
+
+git remote set-url origin --push --add $bb_repo
+git remote set-url origin --push --add $git_repo
+git remote add fdcl ${fdcl_repo}
+
+printf "Finished! The new remotes are listed.\n"
+printf "\n"
+
+git remote -v

### 2018-10-12 utilities/travis_setup.sh

@@ -1,0 +1,29 @@
+#!/bin/bash
+
+# setup script to install texlive and add to path
+texlive_year="2018"
+
+sudo apt-get -qq update
+export PATH=/tmp/texlive/bin/x86_64-linux:$PATH
+
+if ! command -v pdflatex > /dev/null; then
+    echo "Texlive not installed"
+    echo "Downloading texlive and installing"
+    wget http://mirror.ctan.org/systems/texlive/tlnet/install-tl-unx.tar.gz
+    tar -xzf install-tl-unx.tar.gz
+    ./install-tl-*/install-tl --profile=./utilities/texlive.profile
+
+    echo "Finished install TexLive"
+fi
+
+echo "Now updating TexLive"
+# update texlive
+tlmgr option -- autobackup 0
+tlmgr update --self --all --no-auto-install
+
+echo "Finished updating TexLive"
+
+echo "Download and setup texmf tree"
+git clone https://github.com/skulumani/texmf.git ~/texmf
+
+

### 2018-10-14 manuscript.tex
Remove graph

@@
-% use paper, or submit
-% use 11 pt (preferred), 12 pt, or 10 pt only
+\documentclass[journal]{new-aiaa}
+%\documentclass[conf]{new-aiaa} for conference papers
+\usepackage[utf8]{inputenc}
 
-%\documentclass[letterpaper, preprint, paper,11pt]{AAS}	% for preprint proceedings
-\documentclass[letterpaper, paper,11pt]{AAS}		% for final proceedings (20-page limit)
-%\documentclass[letterpaper, paper,12pt]{AAS}		% for final proceedings (20-page limit)
-%\documentclass[letterpaper, paper,10pt]{AAS}		% for final proceedings (20-page limit)
-%\documentclass[letterpaper, submit]{AAS}			% to submit to JAS
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage[version=4]{mhchem}
+\usepackage{siunitx}
+\usepackage{longtable,tabularx}
+\setlength\LTleft{0pt}
 
-\usepackage{AAS_packages}
-%\usepackage{subfigure} % have subcaption in use instead
-%\usepackage[notref,notcite]{showkeys}  % use this to temporarily show labels
+\title{Preparation of Papers for AIAA Technical Journals}
 
-\PaperNumber{18--319}
+\author{First A.
+Author \footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for first author.} and Second B.
+Author Jr.\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for second author.}}
+\affil{Business or Academic Affiliation 1, City, State, Zip Code}
+\author{Third C. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for third author.}}
+\affil{Business or Academic Affiliation 2, City, Province, Zip Code, Country}
+\author{Fourth D. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for fourth author (etc.).}}
+\affil{Business or Academic Affiliation 2, City, State, Zip Code}
 
@@
 
-\title{Real Time Adaptive Shape Reconstruction for Asteroid Landing}
-
-\author{Shankar Kulumani and Taeyoung Lee\thanks{Mechanical and Aerospace Engineering, George Washington University, 800 22nd St NW, Washington, DC 20052, Tel: 202-994-8710, Email: \href{mailto:skulumani@gwu.edu}{\{skulumani,tylee\}@gwu.edu}.}
-}
-
-\maketitle{}
+\maketitle
 
 \begin{abstract}
-    Knowledge of the shape of an asteroid is crucial for spacecraft operations.
-    The standard method of determining the gravitational potential, through the use of a polyhedron potential model, is dependent on the shape model.
-    Furthermore, accurate landing or low altitude operations requires accurate knowledge of the surface topology. 
-    The typical approach to shape determination requires an extensive ``mapping'' phase of the mission over which extensive measurements are collected and transmitted for Earth-based processing.
-    Instead, we present an efficient method for estimating the shape of an asteroid in real time.
-    Range measurements of the surface are used to incrementally correct an initial shape estimate according to Bayesian framework. 
-    Then, an optimal guidance scheme is proposed to control the vantage point of the range sensor to construct a more accurate model of the asteroid shape. 
-    This shape model is then used in a nonlinear controller to track a desired trajectory about the asteroid.
-    Finally, a multi resolution approach is presented which enables for a higher fidelity shape representation in a specified location while avoiding the inherent burdens of a uniformly high resolution mesh.
-    This approach enables for an accurate shape determination around a potential landing site.
-    We demonstrate this approach using several radar shape models of asteroids and provide a full dynamic simulation about asteroid 4769 Castalia.
+These instructions give you guidelines for preparing papers for AIAA Technical Journals using \LaTeX{}.
+If you previously prepared an AIAA Conference Paper using the Papers Template, you may submit using the Papers Template so long as the text is double-spaced.
+Carefully follow the journal paper submission process in Sec.~II of this document.
+Keep in mind that the electronic file you submit will be formatted further at AIAA.
+This first paragraph is formatted in the abstract style.
+Abstracts are required for regular, full-length papers and express articles.
+Be sure to define all symbols used in the abstract, and do not cite references in this section.
+The footnote on the first page should list the Job Title and AIAA Member Grade (if applicable) for each author.
 \end{abstract}
 
-\section{Introduction}\label{sec:introduction}
-% Motivation for missions/studying asteroids
-Small solar system bodies, such as asteroids and comets, continue to remain a focus of scientific study.
-The small size of these bodies prevents the formation of large internal pressures and temperatures which helps to preserve the early chemistry of the solar system.
-This insight offers additional detail into the formation of the Earth and also of the probable formation of other extrasolar planetary bodies.
-Of particular interest are those near-Earth asteroids (NEA) which inhabit heliocentric orbits in the vicinity of the Earth. 
-These easily accessible bodies provide attractive targets to support space industrialization, mining operations, and scientific missions.
-In spite of the significant interest, and the extensive research by the community, the operation of spacecraft near small bodies remains a challenging problem.
+\section*{Nomenclature}
 
-% dynamics are difficult around asteroids
-The dynamic environment around asteroids is strongly perturbed and challenging for analysis and mission operations~\cite{scheeres2012}.
-Due to their low mass, which in turn causes a low gravitational attraction, asteroids may have irregular shapes.
-Furthermore, asteroids may also have a chaotic spin state due to the absorption and emittance of solar radiation~\cite{rubincam2000}.
-As a result, approaches utilizing an inverse square gravitational model do not capture the  true dynamic environment.
-In addition, the vast majority of asteroids are difficult to track and characterize using ground based sensors.
-Due to their small size, frequently with a maximum radius less than \SI{1}{\kilo\meter}, and low albedo, the reflected energy of these asteroids is insufficient for reliable detection or tracking.
-Therefore, the dynamics model of the asteroid is relatively coarse prior to in situ measurements from a dedicated spacecraft.
-As a result, any spacecraft mission to an asteroid must include the ability to update the dynamic model given in situ measurements and remain robust to unmodelled forces.
+\noindent(Nomenclature entries should have the units identified)
 
-Another key dynamic consideration is the coupling between rotational and translational states around the asteroid.
-The coupling is induced due to the different gravitational forces experienced on various portions of the spacecraft. 
-The effect of the gravitational coupling is related to the ratio of the spacecraft size and orbital radius~\cite{hughes2004}.
-For operations around asteroids, the ratio is relatively large which causes a much larger coupling between the translational and rotational states.
-References~\citenum{elmasri2005} and~\citenum{sanyal2004a} investigated the coupling of an elastic dumbbell spacecraft in orbit about a central body, but only considered the case of a spherically symmetric central body.
-Furthermore, the spacecraft model is assumed to remain in a planar orbit.
-As a result, these developments are not directly applicable to motion about an asteroid, which experiences highly non-Keplerian motion.
-Reference~\citenum{misra2015b} investigated the effect of coupled motion on long term trajectories around asteroids.
-However, the analysis only considered a second order spherical harmonic gravitational potential model. 
-Therefore, these results are only valid when far from the asteroid surface and will diverge when used within the Brillouin sphere.
+{\renewcommand\arraystretch{1.0}
+\noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
+$A$  & amplitude of oscillation \\
+$a$ &    cylinder diameter \\
+$C_p$& pressure coefficient \\
+$Cx$ & force coefficient in the \textit{x} direction \\
+$Cy$ & force coefficient in the \textit{y} direction \\
+c   & chord \\
+d$t$ & time step \\
+$Fx$ & $X$ component of the resultant pressure force acting on the vehicle \\
+$Fy$ & $Y$ component of the resultant pressure force acting on the vehicle \\
+$f, g$   & generic functions \\
+$h$  & height \\
+$i$  & time index during navigation \\
+$j$  & waypoint index \\
+$K$  & trailing-edge (TE) nondimensional angular deflection rate\\
+$\Theta$ & boundary-layer momentum thickness\\
+$\rho$ & density\\
+\multicolumn{2}{@{}l}{Subscripts}\\
+cg & center of gravity\\
+$G$ & generator body\\
+iso	& waypoint index
+\end{longtable*}}
 
-% Gravity model is important and dependent on shape
-An accurate gravitational potential model is critical for performing low altitude and/or surface operations around asteroids.
-Due to the irregular shape, trajectories will pass within the Brillouin sphere, where the typical spherical harmonic model diverges from the true gravitational potential.
-The standard approach for asteroid missions is to compute the gravitational potential using a polyhedron potential model~\cite{werner1996}.
-The polyhedron potential model provides the exact gravitational potential, and subsequently the gravitational acceleration, for a given triangular faceted shape model of an asteroid.
-The method provides the exact potential at any point outside the body for a given shape model.
-As a result, the accuracy of the gravitational potential is primarily dependent on the accuracy with which the shape model represents the true surface.
-A high fidelity shape, which necessarily has many vertices and faces, is required for an accurate computation of the gravitational acceleration and enabling low altitude operations.
+\section{Introduction}
+\lettrine{T}{his} document is a \LaTeX{} template for preparation of papers for AIAA Technical Journals.
+If you are reading a hard-copy or .pdf version of this document, download the electronic file, new-aiaa.cls, and use it to prepare your manuscript.
 
-% Challenges involved in operation near asteroids (gravity, shape, distance)
-% generating the shape from the ground is difficult
-Prior to the arrival of a spacecraft at an asteroid, Earth-based sensors are used to characterize the body.
-Using both optical and radar sensors allows for the precise orbit of the asteroid to be determined.
-Another vital task is the determination of the asteroid shape from radar data~\cite{hudson1994,busch2011}.
-This is a challenging problem as it requires the simultaneous estimation of the asteroid spin state and shape.
-Furthermore, determining the shape from radar is currently the only Earth-based technique that can produce detailed three-dimensional shape information of near-Earth objects~\cite{greenberg2015}.
-The current approach is based on an estimation scheme which iteratively perturbs a shape to match given radar data.
-This computationally intensive approach is only able to capture the gross size and shape and is unable to capture the small surface features of the asteroid.
-Frequently, only a coarse model is possible from the ground and an accurate shape must be determined only after a spacecraft has rendezvoused with the asteroid.
-As a result, upon arrival the gravitational environment near the asteroid is poorly modeled as the shape of the asteroid is not accurate.
-Therefore, the polyhedron potential model is not appropriate immediately upon arrival but rather only after the shape has been determined.
+Authors using \url{https://www.overleaf.com} may simply open the AIAA template from the Overleaf gallery to work online; no local installation of any files is required.
+Authors using a local \LaTeX{} installation will need to open the template in Overleaf and use the ``Download as zip'' option from the project menu to download a local copy of the template files.
+To create your formatted manuscript, type your own text over sections of the template, or cut and paste from another document and then use the available markup styles.
+Note that special formatting such as subscripts, superscripts, and italics may be lost when you copy your text into the template from a Word Processing program such as Microsoft Word.
+See Sec.
+IV for more detailed formatting guidelines.
 
-% on arrival spacecraft spend long periods mapping, and depending on mission this might be unallocable
-On approach to an asteroid, spacecraft navigation and guidance is primarily based on ground measurements.
-After arrival, a spacecraft will generally spend months or years in a mapping mission phase~\cite{kubota2003,cole1998}.
-During this period, spacecraft sensors, such as on board optical telescopes or Light radio Detection and Ranging (LIDAR), are used to characterize the asteroid.
-The resulting imagery and range data is transmitted to the ground and the resulting asteroid shape and motion is estimated. 
-During this mapping phase the spacecraft must remain in a quiescent state devoted entirely to mapping the surface.
-Depending on the mission type, this long period of mapping is crucial to the mission, such as sample collection~\cite{gates2015}. 
-However, other missions, such as asteroid mitigation, may be severely limited by the time and ground resources required to generate a surface shape.
-Furthermore, the long distances involved necessitate on-board autonomy to enable to spacecraft to operate without ground communications.
-Similarly, during landing the spacecraft will require the ability to sense and model the surface topography in order to safely land in an unknown environment.
-The dependency on expensive ground-based shape reconstruction techniques limits the ability of spacecraft to autonomously operate at asteroids.
-Mitigation of this ground based surface modeling will greatly expand the range of missions possible.
+\section{Procedure for Paper Submission}
 
-% we want to generate the shape in real time and then use this shape for updated and better control
-In this paper, we develop a method to compute the surface shape of an asteroid from range measurements.
-Our approach is able to operate in real time and incrementally update the shape model of an asteroid as new range measurements are collected.
-This approach allows for the shape to be continually updated as range measurements are used to locally modify the shape estimate.
-Furthermore, this updated shape is then used in a nonlinear controller to enable the tracking of a landing trajectory to the surface.
-In contrast to previous work, we explicitly consider the gravitational coupling between orbit and attitude dynamics.
-Furthermore, instead of computationally expensive surface reconstruction methods, we present a straightforward and conceptually simple method to enable real time shape updates.
+All manuscripts are to be submitted online at \url{https://mc.manuscriptcentral.com/aiaa}.
+Select either “Log In” if you have an existing account or “Create an Account” if this is your first time submitting to one of AIAA’s journals.
+If it’s the latter, please follow the instructions ScholarOne provides.
+Once you have logged into ScholarOne, select “Author Center” then scroll down.
+Under “Author Resources”, select the star beside “Click here to submit a new manuscript”.
+The site will take you step-by-step through the submission process.
+Once you submit your manuscript, you will receive an email containing your manuscript ID number as well as a link to view the status of your manuscript.
 
-% our approach for paper. Real time method to update asteroid shape model and use updated model in closed loop control
+After entering all required submission data, you must use the “Upload Manuscript” feature of the Author Center to upload your submission.
+Remember that your document must be in single-column, double-spaced format (as this template) before you upload it.
+Please be sure that the name of the file you upload for processing is short and simple (i.e., “SmithJPP.pdf”) with no spaces, tildes, symbols, or other special characters.
+Authors are encouraged to upload .pdf files, which are less likely to have conversion errors on upload.
+Failure to meet these requirements could result in a processing error that would require you to re-upload your manuscript.
+Once you have uploaded your manuscript, please inspect the file for accuracy.
+This step is required to complete your submission.
+If you experience difficulties with the upload and/or conversion of your manuscript, please contact ScholarOne Manuscripts Support (\url{https://mchelp.manuscriptcentral.com/gethelpnow/} or +1-888-503-1050) for additional assistance.
 
-% Benefits and contribution of our approach
-In short, this paper presents a method to incrementally update the shape  model of an asteroid from range measurements. 
-Our approach alleviates the need for a dedicated mapping phase as the spacecraft is able to update its shape model in real time and without expensive computations.
-This type of approach allows for the spacecraft to maneuver and land on the asteroid immediately upon arrival rather than spending several months mapping the surface.
-This updated shape model is then used to in a nonlinear controller to track a desired state trajectory for the dynamics of a rigid body spacecraft.
-The dynamics are developed on the nonlinear manifold of rigid body motions, namely the special euclidean group.
-This formulation is based on an intrinsic geometric description of the motion and accurately captures the coupling between orbit and attitude dynamics. 
-The presented approach allows for a spacecraft to transition directly from arrival to the surface while reconstructing the surface shape in real time.
+\emph{Attention Asian Authors: If you are uploading a .pdf file, please remove Asian fonts from your file, under File>Properties.}
 
-\section{Problem Formulation}\label{sec:problem}
+\section{General Guidelines}
 
-In this paper, we consider the motion of a dumbbell model of spacecraft around an asteroid.
-The dumbbell model captures the important interactions of the coupling between orbital and attitude dynamics.
-In this model, the spacecraft consists of two masses connected by a massless rod.
-The asteroid is modeled as a constant density polyhedron with constant, and known, spin about its maximum moment of inertia. 
-Without loss of generality, we define body fixed frames for both the spacecraft and asteroid, which are aligned with the principle axes of each body and originate at their respective center of mass. 
-The kinematics of the dumbbell and asteroid are described in the inertial frame by
-\begin{itemize}
-    \item \( \vc{x} \) - the position of the center of mass of the dumbbell spacecraft represented in the inertial frame, \( \vc{e}_i\),
-    \item \( R \) - the rotation matrix which transforms vectors defined in the spacecraft fixed frame, \( \vc{b}_i \), to the inertial frame, \( \vc{e}_i \),
-    \item \( \vc{\Omega} \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame, \( \vc{b}_i \), and
-    \item \( R_A \) - the rotation matrix which transforms vectors defined in the asteroid fixed frame, \( \vc{f}_i \), to the inertial frame, \( \vc{e}_i \).
-\end{itemize}
-In this work, we assume that the asteroid is much more massive than the spacecraft and its motion is not affected by that of the spacecraft.
-This assumption allows us to treat the motion of the vehicle independently from that of the asteroid.
+The following section outlines general (nonformatting) guidelines to follow.
+These guidelines are applicable to all authors and include information on the policies and practices relevant to the publication of your manuscript.
 
-\subsection{Spacecraft Dynamic Model}
-Using Hamilton's principle one can derive the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
-\begin{align}
-    \dot{\vc{x}} &= \vc{v}, \\
-    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2}, \\
-    \dot{R} &= R S(\vc{\Omega}) , \\
-    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2.
-\end{align}
-The vectors \( \vc{z}_1 \) and \( \vc{z}_2\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
-\begin{align}
-    \vc{z}_1 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_1} , \\
-    \vc{z}_2 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_2}.
-\end{align}
-The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as
-\begin{align}
-    \vc{M}_i = m_i \parenth{S(R_A^T \vc{\rho}_i) R^T \deriv{U}{\vb{z}_i}}.
-\end{align}
-where the polyhedron potential is defined as 
-\begin{align}
-    U(\vc{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vc{r}_e \cdot \vc{E}_e \cdot \vc{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vc{r}_f \cdot \vc{F}_f \cdot \vc{r}_f \cdot \omega_f,
-\end{align}
-and \( \vc{r}_e\) and \(\vc{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
-The position of each mass \(m_i\) of the dumbbell is defined in the dumbbell fixed frame by the vector \(\vb{\rho}_i\).
+\subsection{Publication by AIAA}
+Your manuscript cannot be published by AIAA if:
+\begin{enumerate}
+\item The work is classified or has not been cleared for public release.
+\item The work contains copyright-infringing material.
+\item The work has been published or is currently under consideration for publication or presentation elsewhere.
+(Exception: Papers presented at AIAA conferences may be submitted to AIAA journals for possible publication.)
+\end{enumerate}
 
-\subsection{Polyhedron Potential Model}\label{sec:polyhedron_potential}
+You will be asked to provide the publication or presentation history of your paper (or any similar paper) if it has \emph{ever} been submitted for publication or presentation previously to an AIAA journal or conference.
+Please include the following, if applicable: the full name of the publication or conference, the entire paper number, dates the conference took place, review history, final disposition of manuscript, etc.
 
-% most use a spherical harmonic model or a ellipsoid model but we use a polyhedron model
-An accurate gravitational potential model is necessary for the operation of spacecraft about asteroids.
-Additionally, a detailed shape model of the asteroid is needed for trajectories passing close to the body.
-The classic approach is to expand the gravitational potential into a harmonic series and compute the series coefficients.
-However, the harmonic expansion is always an approximation as a result of the infinite order series used in the representation.
-Additionally, the harmonic model used outside of the circumscribing sphere is not guaranteed to converge inside the sphere, which makes it unsuitable for trajectories near the surface.
+\subsection{Copyright}
 
-We represent the gravitational potential of the asteroid using a polyhedron gravitation model.
-This model is composed of a polyhedron, which is a three-dimensional solid body, that is defined by a series of vectors in the body-fixed frame.
-The vectors define vertices in the body-fixed frame as well as planar faces which compose the surface of the asteroid.
-We assume that each face is a triangle composed of three vertices and three edges.
-As a result, only two faces meet at each edge while three faces meet at each vertex.
-Only the body-fixed vectors, and their associated topology, is required to define the exterior gravitational model.
-References~\cite{werner1994} and~\cite{werner1996} give a detailed derivation of the polyhedron model.
-Here, we summarize the key developments and equations required for implementation.
+Before AIAA can publish any paper, the copyright information must be completed in ScholarOne.
+Failure to complete the form correctly could result in your paper not being published.
+You must select one copyright assignment statement (select A, B, C, or D) and once a statement is picked, changes cannot be made during the proofs stage.
+Read the copyright statements carefully.
+AIAA requires a copyright transfer from the author(s) to AIAA or a license to print your material; government authors can assert that the work is in the public domain.
+Because you will be completing this form online, you do not need to fill out a hard-copy form.
+Do not include a copyright statement anywhere on your paper.
+The correct statement will be included automatically at the time of processing.
+(If your paper was presented at an AIAA conference, then the copyright statement chosen for the journal article should be the same as for your conference paper.)
 
-Consider three vectors \( \vc{v}_1, \vc{v}_2, \vc{v}_3 \in \R^{3 \times 1} \), assumed to be ordered in a counterclockwise direction about an outward facing normal vector, which define a face.
-For each face we define the face dyad \( \vc{F}_f \) as
-\begin{align}\label{eq:face_dyad}
-    \vc{F}_f &= \hat{\vc{n}}_f \hat{\vc{n}}_f \in \R^{3 \times 3}.
-\end{align}
-Each edge is a member of two faces and has an outward pointing edge normal vector, perpendicular to both the edge and the face normal.
-For the edge connecting the vectors \( \vc{v}_1 \) and \( \vc{v}_2 \), which are shared between the faces \(A\) and \( B\), the per edge dyad is given by
-\begin{align}\label{eq:edge_dyad}
-    \vc{E}_{12} = \hat{\vc{n}}_A \hat{\vc{n}}_{12}^A + \hat{\vc{n}}_B \hat{\vc{n}}_{21}^B \in \R^{3 \times 3}.
-\end{align}
-The edge dyad \( \vc{E}_e  \), is defined for each edge and is a function of the two adjacent faces meeting at that edge.
-The face dyad \( \vc{F}_f \), is defined for each face and is a function of the face normal vectors.
+\subsection{Publication Charges for Open Access}
 
-Let \( \vc{r}_i \in \R^{3 \times 1} \) be the vector from the spacecraft to the vertex \( \vc{v}_i \) and it's length is given by \( r_i = \norm{\vc{r}_i} \in \R^{1} \).
-The per-edge factor \( L_e \in \R^{1}\), for the edge connecting vertices \( \vc{v}_i \) and \( \vc{v}_j \), with a constant length \( e_{ij} = \norm{\vc{e}_{ij}} \in \R^1\) is
-\begin{align}\label{eq:edge_factor}
-    L_e &= \ln \frac{r_i + r_j + e_{ij}}{r_i + r_j - e_{ij}}.
-\end{align}
-For the face defined by the vertices \( \vc{v}_i, \vc{v}_j, \vc{v}_k \) the per-face factor \( \omega_f \in \R^{1} \) is
-\begin{align}\label{eq:face_factor}
-    \omega_f &= 2 \arctan \frac{\vc{r}_i \cdot \vc{r}_j \times \vc{r}_k}{r_i r_j r_k + r_i \parenth{\vc{r}_j \cdot \vc{r}_k} + r_j \parenth{\vc{r}_k \cdot \vc{r}_i} + r_k \parenth{\vc{r}_i \cdot \vc{r}_j}} .
-\end{align}
-The gravitational potential due to a constant density polyhedron is given as
-\begin{align}\label{eq:potential}
-    U(\vc{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vc{r}_e \cdot \vc{E}_e \cdot \vc{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vc{r}_f \cdot \vc{F}_f \cdot \vc{r}_f \cdot \omega_f \in \R^1,
-\end{align}
-where \( \vc{r}_e\) and \(\vc{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
-Furthermore we can use these definitions to define the attraction, gravity gradient matrix, and Laplacian as
-\begin{align}
-    \nabla U ( \vc{r} ) &= -G \sigma \sum_{e \in \text{edges}} \vc{E}_e \cdot \vc{r}_e \cdot L_e + G \sigma \sum_{f \in \text{faces}} \vc{F}_f \cdot \vc{r}_f \cdot \omega_f \in \R^{3 \times 1} , \label{eq:attraction}\\
-    \nabla \nabla U ( \vc{r} ) &= G \sigma \sum_{e \in \text{edges}} \vc{E}_e  \cdot L_e - G \sigma \sum_{f \in \text{faces}} \vc{F}_f \cdot \omega_f \in \R^{3 \times 3}, \label{eq:gradient_matrix}\\
-    \nabla^2 U &= -G \sigma \sum_{f \in \text{faces}}  \omega_f \in \R^1 .\label{eq:laplacian}
-\end{align}
+Publication charges are voluntary, and nonpayment has no influence on the review process of the time from acceptance to publication.
+Publication charge payments help defray production costs and keep journal subscription prices low.
 
-One interesting thing to note is that both~\cref{eq:face_dyad,eq:edge_dyad} can be precomputed without knowledge of the position of the satellite.
-They are both solely functions of the vertices and edges of the polyhedral shape model and are computed once and stored.
-Once a position vector \( \vc{r} \) is defined, the scalars given in~\cref{eq:edge_factor,eq:face_factor} can be computed for each face and edge.
-Finally,~\cref{eq:potential} is used to compute the gravitational potential on the spacecraft.
-The Laplacian, defined in~\cref{eq:laplacian}, gives a simple method to determine if the spacecraft has collided with the body~\cite{werner1996}.
+The article publication charge for Open Access is available in ScholarOne and on the AIAA website; the fee is the same regardless of article type.
+There is a fee for Open Access immediately upon publication in AIAA’s electronic library, Aerospace Research Central (ARC) and a fee for Open Access 12 months after publication in ARC.
 
-\section{Incremental Shape Reconstruction}\label{sec:radius_update}
+\section{Instructions}
 
-One of the first tasks for any spacecraft mission to a small body is to generate an estimate of the shape.
-We assume that upon arrival at a target body, the spacecraft contains an initial estimate for the shape of the small body.
-This shape can be a coarse estimate computed from ground measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid.
-Additionally, we assume that the shape estimate is closed and a triangular faceted surface mesh, emulating those used in practice to represent asteroids.
-Furthermore, the number of vertices in the estimate can be scaled according to the desired final accuracy or computational capabilities.
+If you are using the AIAA Journals \LaTeX{} Template file to prepare your manuscript, you can simply type your own text over sections of this document, or cut and paste from another document and use the available markup styles.
+If you choose to cut and paste, select the text from your original document and choose Edit>Copy.
+(Do not select your title and author information, since the document spacing may be affected.
+It is a simple task to reenter your title and author information in the template.) Open the Journals Template.
+Place your cursor in the text area of the template and select Edit>Paste.
+Please note that special formatting (e.g., subscripts, superscripts, italics) may be lost when you copy your text into the template.
 
-We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid~\cite{zuber1997,zuber2000}.
-This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
-Given the time total time of flight, the distance can be accurately computed using \( d = \frac{\Delta TOF}{2 c} \) where \( c = \SI{2.998e8}{\meter\per\second}\) is the constant speed of light.
-Assuming accurate knowledge of the pointing direction of the spacecraft, in the form of the rotation matrix \( R \in \R^{3 \times 3 } \), we can compute a direction from the spacecraft to the measurement location on the surface.
-The output of this sensor is a vector, \( \vc{d}_i \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface. 
-Using the state of the asteroid, we can transform this measurement to the asteroid fixed frame using the simple transformation
-\begin{align*}
-    \vc{p}_i = R_A^T R \vc{d}_i .
-\end{align*}
-Given many measurements, \( \vc{p}_i \in \R^3 \), of the asteroid surface we can efficiently update our initial shape estimate to that of the true surface.
-\Cref{fig:lidar_example} shows asteroid 4769 Castalia and a representation of several LIDAR measurements. 
-The spacecraft measures the range between itself and the asteroid surface to several points within the field of view of the sensor. 
-These measurements provide a collection of points which lie on the surface of the asteroid, and by combining many points, a so called ``point cloud'', allows us to reconstruct the shape.
-\begin{figure}
+To apply the AIAA Journals formatting, use the standard \LaTeX{} commands for sections and subsection, etc; all the styles you will need to format your document are available as standard \LaTeX{} commands.
+The style will automatically adjust your fonts and line spacing.
+Repeat this process to apply formatting to all elements of your paper.
+\emph{Do not change the font sizes, line spacing, or margins.
+Do not manually hyphenate your document.} Use italics for emphasis; do not underline.
+
+Use the Print option under the File tab to view Page Layout and see the most accurate representation of how your final paper will appear.
+Once formatting is complete, be sure to double space all sections of your manuscript.
+
+\subsection{Document Text}
+The default font for the Template is Times New Roman, 10-point size.
+The first line of every paragraph should be indented, and all lines should be double-spaced.
+Default margins are 1 in.
+on all sides.
+In the electronic version of this template, all margins and other formatting are preset.
+There should be no additional (blank) lines between paragraphs.
+
+\emph{NOTE:} If you are using the Template to format your manuscript, the required spacing and formatting will be applied automatically.
+
+\subsection{Headings}
+Format the title of your paper in bold, 18-point type, with capital and lower-case letters, and center it at the top of the page.
+The names of the authors, business or academic affiliation, city, and state/province follow on separate lines below the title.
+The names of authors with the same affiliation can be listed on the same line above their collective affiliation information.
+Author names are centered, and affiliations are centered and in italic type.
+The affiliation line for each author includes that author’s city, state, and zip/postal code (or city, province, zip/postal code and country, as appropriate).
+The first footnote (bottom of first page) contains the job title and department name, and AIAA member grade for each author.
+Author email addresses may be included also.
+
+Major headings in the template (``sections'' in the \LaTeX{} template commands) are bold 11-point font and centered.
+Please omit section numbers before all headings unless you refer frequently to different sections.
+Use Roman numerals for major headings if they must be numbered.
+
+Subheadings (``subsections'' in the \LaTeX{} template commands) are bold, flush left, and either unnumbered or identified with capital letters if necessary for cross-referencing sections within the paper.
+There must be at least 2 of all subheadings and sub-subheadings.
+If there is only a single subheading or sub-subheading, please italicize the title of the subheadings, followed by a period, and run it into the text paragraph.
+
+Sub-subheadings (``subsubsections'' in the \LaTeX{} template commands) are italic, flush left, and either unnumbered or numbered with Arabic numerals (1, 2, 3, etc.) if necessary for cross-referencing sections within the paper.
+
+\subsection{Abstract}
+An abstract appears at the beginning of Full-Length Papers, Regular Articles, and Express Articles.
+(Survey and Design Forum Papers, History of Key Technologies Papers, invited lectures, and Technical/Engineering Notes do not include abstracts.) The abstract is one paragraph (not an introduction) and complete in itself (no reference numbers).
+It should indicate subjects dealt with in the paper and state the objectives of the investigation.
+Newly observed facts and conclusions of the experiment or argument discussed in the paper must be stated in summary form; readers should not have to read the paper to understand the abstract.
+Format the abstract bold, indented 3 picas (1/2 in.) on each side, and separated from the rest of the document by two blank lines.
+
+\subsection{Nomenclature}
+Papers with many symbols may benefit from a nomenclature list that defines all symbols with units, inserted between the abstract and the introduction.
+If one is used, it must contain all the symbology used in the manuscript, and the definitions should not be repeated in the text.
+In all cases, identify the symbols used if they are not widely recognized in the profession.
+Define acronyms in the text, not in the nomenclature.
+
+\subsection{Biographies}
+Survey Papers and some Full-Length Papers include author biographies. These biographies are one paragraph each and should use the abstract formatting style.
+
+\subsection{Footnotes and References}
+Footnotes, where they appear, should be placed above the 1'' margin at the bottom of the page.
+To insert footnotes into the template, use the Insert>Footnote feature from the main menu as necessary.
+Footnotes are formatted automatically in the template, but if another medium is used, should appear in superscript as symbols in the sequence, *, $\dag$, $\ddag$, \S, \P, **, $\dag\dag$, $\ddag\ddag$, \S\S, etc.
+
+List and number all references at the end of the paper.
+Corresponding bracketed numbers are used to cite references in the text \cite{vatistas1986reverse}, including citations that are an integral part of the sentence (e.g., ``It is shown in \cite{dornheim1996planetary} that\ldots '') or follow a mathematical expression: ``$A^{2} + B = C$ (Ref.~\cite{terster1997nasa}).'' For multiple citations, separate reference numbers with commas \cite{peyret2012computational,oates1997aerothermodynamics}, or use a dash to show a range \cite{volpe1994techniques,thompsonspacecraft,chi1993fluid}.
+Reference citations in the text should be in numerical order.
+
+In the reference list, give all authors' names; do not use ``et al.'' unless there are six authors or more.
+Papers that have not been published should be cited as ``unpublished''; papers that have been submitted or accepted for publication should be cited as ``submitted for publication.'' Private communications and personal website should appear as footnotes rather than in the reference list.
+
+References should be cited according to the standard publication reference style (for examples, see the ``References'' section of this template).
+Never edit titles in references to conform to AIAA style of spellings, abbreviations, etc.
+Names and locations of publishers should be listed; month and year should be included for reports and papers.
+For papers published in translation journals, please give the English citation first, followed by the original foreign language citation.
+
+\subsection{Figures and Tables}
+Insert tables and figures within your document; they may be either scattered throughout the text or grouped all together at the end of the file.
+Do not insert your figures in text boxes.
+Figures should have no background, borders, or outlines.
+In the \LaTeX{} template, use the ``caption'' command to type caption text.
+Captions are bold with a single tab (no hyphen or other character) between the figure number and figure description.
+See the Table 1 example for table style and column alignment.
+If you wish to center tables that do not fill the width of the page, simply highlight and “grab” the entire table to move it into proper position.
+
+\begin{table}[hbt!]
+\caption{\label{tab:table1} Transitions selected for thermometry}
 \centering
-    \includegraphics[width=0.75\textwidth]{figures/castalia_raycasting_plot.jpg}
-    \caption{Simulated LIDAR measurements of asteroid Castalia~\label{fig:lidar_example}}
-\end{figure}
+\begin{tabular}{lcccccc}
+\hline
+& Transition& & \multicolumn{2}{c}{}\\\cline{2-2}
+Line& $\nu''$& & $J'' $& Frequency, cm$^{-1}$& $FJ$, cm$^{-1}$& $G\nu $, cm$^{-1}$\\\hline
+a& 0& P$_{12}$& 2.5& 44069.416& 73.58& 948.66\\
+b& 1& R$_{2}$& 2.5& 42229.348& 73.41& 2824.76\\
+c& 2& R$_{21}$& 805& 40562.179& 71.37& 4672.68\\
+d& 0& R$_{2}$& 23.5& 42516.527& 1045.85& 948.76\\
+\hline
+\end{tabular}
+\end{table}
 
-\paragraph{Bayesian Shape Update}
+Line drawings must be clear and sharp.
+Make sure that all lines and graph points are dark and distinct and that lettering is legible; 8- to 10-point type is suitable for artwork that is sized to fit the column width (3 ¼ in.).
+Keep the lettering size and style uniform both within each figure and throughout all of your illustrations.
+Place figure captions below each figure, and limit caption length to 20-25 words.
+If your figure has multiple parts, include the labels “a),” “b),” etc., below and to the left of each part, above the figure caption.
+Please verify that the figures and tables you mention in the text actually exist.
+When citing a figure in the text, use the abbreviation “Fig.” except at the beginning of a sentence.
+Do not abbreviate “Table.” Number each different type of illustration (i.e., figures and tables) sequentially with relation to other illustrations of the same type.
 
-Our algorithm applies a Bayesian framework to radially modify each vertex \( \vc{v}_i \in \R^3\) of the shape estimate based on measurement \( \vc{p}_i \in \R^3 \). 
-This approach alleviates much of complexity of incorporating new vertices or surface triangulation common in surface reconstruction methods~\cite{berg2008}.
-This assumption means that the total number of vertices of the shape model is fixed.
-However, additional detail, in the form of additional vertices, is possible by using standard mesh subdivision algorithms~\cite{orourke1998}.
+Figure labels must be legible after reduction to column width (preferably 8--10 points after reduction).
 
-The radial distance of each vertex, \( v_i = \norm{\vc{v}_i}\), is assumed to be distributed according to the Gaussian distribution
-\begin{align*}
-    v_i \sim \mathcal{N}(r_i, w_i^2)
-\end{align*}
-where \( r_i \) is the initial estimate of the radial distance of vertex \( \vc{v}_i\) and \( w_i \) is the initial variance, or confidence, in the radial distance.
-The radial distance of each measurement, \( p_{j,i} = \norm{\vc{p}_j}\), is also assumed to be distributed according to the Gaussian distribution
-\begin{align*}
-    p_{j,i} \sim \mathcal{N}(r_{j,i}, w_{j,i}^2)
-\end{align*}
-where \( r_{j,i} = \norm{\vc{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i}\) defines the variance of the measurement with respect to vertex \( \vc{v}_i\).
-Each measurement is defined by the index \( j \) while the associated vertex is defined by \( i \). 
-As a result, the measurement \( p_{j, i} \) defines the distribution of measurement \( j \) with respect to vertex \( i \). 
-Any given measurement may be used to update one or several vertices.
+All tables are numbered consecutively and must be cited in the text; give each table a definitive title.
+Be sure that you have a minimum of two columns (with headings) and two rows to constitute a proper table; otherwise reformat as a displayed list or incorporate the data into the text.
+Plan tables to fit the column width (3 ¼ in.) or the journal page width (7 in.).
+Position a double rule at the top and bottom of each table and single rule under the column headings; do not use shading, border lines, or vertical rules between table columns.
+Position each table in the text close to where it is cited
 
-The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vc{v}_i \).
-Here, we use the geodesic distance to parameterize the difference, and hence  uncertainty, of associating the measurement with a given vertex.
-From spherical trigonometry~\cite{gade2010}, the central angle between measurement \( \vc{p}_i \) and vertex \( \vc{v}_i \) of the shape estimate is
-\begin{align}\label{eq:geodesic_distance}
-    \Delta \sigma_{j,i} = \arctan \parenth{\frac{\norm{\vc{p}_j \times \vc{v}_i}}{\vc{p}_j \cdot \vc{v}_i }}.
-\end{align}
-The variance of measurement \( \vc{p}_i \) with respect to vertex \( \vc{v}_i \) is then defined by the geodesic distance as
-\begin{align}
-    w_{j, i} = \norm{\vc{p}_j} \Delta \sigma_{j,i} .
-\end{align}
-This approach relates the uncertainty of the measurement \( \vc{p}_j \) with the geodesic distance to a given vertex, \( \vc{v}_i \).
-As a result, measurements which are far from a vertex, i.e.\ \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty. 
-This approach can be considered as a form of a correlation based sensor model~\cite{thrun2005}.
-The main benefit of a correlation based approach, in contrast to feature extraction is the relative simplicity of implementation.
-However, the resulting correlation values do not posses any physical significance and do not represent the noise or uncertainty characteristics of the sensor.
+\subsection{Equations}
+Equations are numbered consecutively, with equation numbers in parentheses flush right, as in Eq.~\eqref{sample:equation}.
+Insert a blank line on either side of the equation.
+To insert an equation into the \LaTeX{} document, use the \verb|\begin{equation}...\end{equation}| command environment.
 
-From Bayes' theorem, the posterior probability is defined as
-\begin{align}
-    p(v_i | p_{j, i}) = \frac{p(p_{j, i} | v_i) p(v_i)}{p( p_{j, i})} \propto p(p_{j,i} | v_i) p(v_i).
-\end{align}
-From the properties of a Gaussian, the posterior probability given a measurement is also distributed according to a Gaussian distribution~\cite{bishop2006} and given by
-\begin{align}\label{eq:posterior_probability}
-    \mathcal{N} \parenth{\frac{w_{j, i}^2 r_i + w_i^2 r_{j, i}}{w_i^2 + w_{j, i}^2} , \frac{w_i^2  w_{j, i}^2}{w_i^2 +  w_{j, i}^2}} .
-\end{align}
-From~\cref{eq:posterior_probability}, the posterior probability conditioned on the measurement is the weighted average of the prior knowledge and the measurement. 
-Measurements that are far from the vertex will have a high uncertainty or variance and will have a reduced impact on the radial position of the vertex.
-Additional measurements are incorporated using a weighted average of prior belief and the measurement uncertainty.
+A sample equation is included here, formatted using the preceding instructions:
 
-In order to improve the computational efficiency measurement updates are assumed to be local in nature.
-Instead of applying a measurement to all vertices of the mesh, the measurement is only applied to the vertices which are within a specified region of the measurement. 
-We define a region of interest, \( \Delta S \), about each measurement which defines the surface area over which the measurement will affect the mesh estimate.
-We relate \( \Delta S \) to an equivalent angular constraint using
-\begin{align}\label{eq:region_of_interest}
-    \Delta \sigma_{max} = \sqrt \frac{\Delta S}{r_b^2}
-\end{align}
-% shankar: brillouin is correct. https://arc.aiaa.org/doi/10.2514/6.2014-4302
-where \( r_b \) defines the Brillouin  sphere radius, or the radius of the circumscribing sphere of the asteroid.
-Only vertices which satisfy \( \Delta \sigma_i \leq \Delta \sigma_{max} \) are considered in the Bayesian update shown in~\cref{eq:posterior_probability}.
+\begin{equation}
+\label{sample:equation}
+\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = [\sigma r_2/(2\mu_0)]\int^{\infty}_0\exp(-\lambda|z_j-z_i|)\lambda^{-1}J_1 (\lambda r_2)J_0 (\lambda r_i\,\lambda {\rm d}\lambda)
+\end{equation}
 
-The approach presented in this section allows one to update the shape of small body given a single range measurement of the surface.
-A sequential process can be used to iteratively update the shape estimate given many measurements of the surface.
+Be sure that symbols in your equation are defined in the Nomenclature or immediately following the equation.
+Also define abbreviations and acronyms the first time they are used in the main text.
+(Very common abbreviations such as AIAA and NASA, do not have to be defined.)
 
-\section{Optimal Guidance for Shape Reconstruction}\label{sec:explore_asteroid}
+\subsection{General Grammar and Preferred Usage}
+Use only one space after periods or colons.
+Hyphenate complex modifiers: ``zero-field-cooled magnetization.'' Insert a zero before decimal points: ``0.25,'' not ``.25.'' Use ``\si{\centi\meter\squared}'' not ``cc.''
 
-The mesh update algorithm presented does not offer a method to determine which portion of the surface needs to be updated. 
-In this section, we present an optimal approach for the guidance of the vehicle in order to update the shape estimate.
-A nonlinear geometric controller is utilized which allows the spacecraft to maneuver to the best location that will update the shape estimate~\cite{kulumani2017b}.
-This guidance schemes enables autonomous operations around a small body.
+A parenthetical statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
+(A parenthetical sentence is punctuated within parenthesis.) Use American, not English, spellings (e.g., “color,” not “colour”).
+The serial comma is preferred: “A, B, and C” instead of “A, B and C.”
 
-We define a cost associated with each vertex \( \vc{v}_i \) of the shape estimate
-\begin{align}\label{eq:explore_cost}
-    J_i (x, R, R_A) = \alpha_w J_{w_i} + \alpha_d J_{d_i}(x_r) + \alpha_c J_{c_i}(x_r)
-\end{align}
-where the weighting factors \( \alpha_w, \alpha_d, \alpha_c \in \R^1 \) are chosen such that \( \alpha_w + \alpha_d + \alpha_c = 1 \).
-The cost function is defined as a function of the current inertial position, \( x \in \R^3 \), and the attitude, \( R \in \R^{3\times3}\) of the spacecraft.
-Furthermore, knowledge of the small body rotation is required in order to determine the position of the spacecraft in the small body fixed frame, \( x_r = R_A^T x\).
+Be aware of the different meanings of the homophones “affect” (usually a verb) and “effect” (usually a noun), “complement” and “compliment,” “discreet” and “discrete,” “principal” (e.g., “principal investigator”) and “principle” (e.g., “principle of measurement”).
+Do not confuse “imply” and “infer.”
 
-The term \( J_{w_i} \in \R^1 \) represents the cost associated with the uncertainty of vertex \( i \) as
-\begin{align}\label{eq:weight_cost}
-    J_{w_i} &= - \frac{w_i}{w_m}
-\end{align}
-where \( w_i \) is the uncertainty of vertex \( i \) and \( w_m \) is a maximum uncertainty used to scale the values.
-The term \( J_{d_i} \) represents the scaled geodesic distance between the current state of the spacecraft and vertex \( i \),
-\begin{align}\label{eq:distance_cost}
-    J_{d_i}(\rpos) &= \frac{1}{\pi} \arctan \parenth{ \frac{\norm{\rpos \times \vc{v}_i}}{\rpos \cdot \vc{v}_i}}.
-\end{align}
+\section{Conclusion}
+Although a conclusion may review the main points of the paper, it must not replicate the abstract.
+A conclusion might elaborate on the importance of the work or suggest applications and extensions.
+Do not cite references in the conclusion.
+Note that the conclusion section is the last section of the paper to be numbered.
+The appendix (if present), funding information, other acknowledgments, and references are listed without numbers.
 
-Finally, a control component is included in the cost function which penalizes vertices that are difficult to reach.
-Consider, the current position of the spacecraft in the small body fixed frame as \( \rpos\) and a desired vertex \( \vc{v}_i \) of the shape estimate.
-We can define a normal vector to the plane spanned by \( \rpos, \vc{v}_i \) as
-\begin{align}\label{eq:normal_to_plane}
-    \vc{n}_i = \frac{\rpos \times \vc{v}_i}{\norm{\rpos} \norm{\vc{v}_i}}.
-\end{align}
-Then a trajectory \( x_d(\theta) \) as
-\begin{align}\label{eq:spherical_waypoint}
-    x_d(\theta) = r_d \exp{\parenth{\theta \hat{\vc{n}_i}} } \frac{\rpos}{\norm{\rpos}},
-\end{align}
-where \( \theta : \bracket{0, \frac{\rpos \cdot \vc{v}_i}{\norm{\rpos}\norm{\vc{v}_i}}} \to \R^1\) parameterizes the desired trajectory.
-\Cref{eq:spherical_waypoint} simply describes a portion of a great circle trajectory between the current state, \( \rpos \), and the desired vertex \( \vc{v}_i \)~\cite{chen2016}.
-The altitude of the spacecraft, \( r_d \in \R \), can be chosen based on sensor characteristics of safety concerns.
-For example, \( r_d \) can be chosen as the distance of the Biroullin sphere with an additional safety margin to mitigate any surface collision~\cite{scheeres2012a}.
-We assume that the tracking errors are small, such that \( e_x, e_v \) are negligible, therefore the control becomes
-\begin{align}\label{eq:tracking_control_cost}
-    u_f(\theta) = -F_{ext}(x_d(\theta)), 
-\end{align}
-where the external force is defined by the polyhedron potential model given in~\cref{eq:attraction}.
-The control cost is then defined as the integral over the desired trajectory~\cref{eq:spherical_waypoint} between the current state and the desired vertex as
-\begin{align}\label{eq:control_cost}
-    J_{c_i}(\rpos) = \frac{1}{u_m} \int_{\theta_0}^{\theta_f} u_f(\theta)^T R u_f(\theta) d\theta,
-\end{align}
-where \( u_m \) is used to normalize and scale \( J_{c_i} \).
-\Cref{eq:control_cost} is numerically integrated over the trajectory \( x_d(t) \) and used to penalize vertices which have a larger cost.
+\section*{Appendix}
 
-The vertex which minimizes~\cref{eq:explore_cost} 
-\begin{align*}
-    \vc{v}_{min} = \min_{i} J_i(x, R, R_A),
-\end{align*}
-is determined and used to determine the optimum vertex of the shape model to measure.
-This vertex is then used to determine the required state of the spacecraft in order to collect a measurement.
-We assume that the spacecraft will maneuver to a location directly above the selected vertex, \( \vc{v}_{min} \), and point in the nadir direction to collect a measurement.
-The desired state is transformed into the inertial frame and chosen as a location above \( \vc{v}_{min} \) as
-\begin{align}
-    x_d = r_d R_A \vc{v}_{min}, 
-\end{align}
-where \( r_d \) is again chosen to ensure a safety margin above the surface.
-The desired attitude command, \( R_d\), is chosen such that the spacecraft camera axis, \( \vc{b}_1 \), is directed along the nadir towards the small body.
-It is sufficient to define two orthogonal vectors to uniquely determine the attitude of the spacecraft.
-The \( \vc{b}_{3d} \) vector is chosen to lie in the plane spanned by \(\vc{b}_{1d} \) and \( \vc{e}_3 = \vc{f}_3 \).
-The desired attitude command is defined as
-\begin{align}
-    \vc{b}_{1d} &= - \frac{\vc{x}}{\norm{\vc{x}}} , \\
-    \vc{b}_{3d} &= \frac{\vc{f}_3 - \parenth{\vc{f}_3 \cdot \vc{b}_{1d}} \vc{b}_{1d}}{\norm{\vc{f}_3 - \parenth{\vc{f}_3 \cdot \vc{b}_{1d}} \vc{b}_{1d}}}, \\
-    \vc{b}_{2d} &= \vc{b}_{3d} \times \vc{b}_{1d} , \\
-    R_d &= \begin{bmatrix} \vc{b}_{1d} & \vc{b}_{2d} & \vc{b}_{3d} \end{bmatrix} .
-\end{align}
-This form of \( R_d \) will direct the \( b_1 \) axis towards the small body, and can be modified for a different camera orientation.
+An Appendix, if needed, appears \textbf{before} research funding information and other acknowledgments.
 
-\section{Multi-resolution Landing Area Refinement}\label{sec:landing_refinement}
+\section*{Funding Sources}
 
-The shape update approach presented is designed with autonomous operations in mind. 
-It is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
-Furthermore, the original mesh is uniformly distributed and as a result many small topological features such as rocks or small craters are not be captured by the shape model. 
-However, these small features are critical for surface operations and safe landings.
-In addition, it would be computationally prohibitive to have a uniformly high resolution mesh.
-In this section, we extend the previous shape update approach to enable a much higher fidelity in a specific location.
+Sponsorship information and acknowledgments of financial support should be included here.
+\textbf{Authors are responsible for accurately reporting funding data relevant to their research.} Please confirm that you have correctly entered \textbf{all sources} of funding and grant/award numbers \textbf{for all authors} in this section of your article.
+You will also be asked to select the appropriate funding organization from a drop-down menu in ScholarOne when you submit your manuscript.
+Be careful to choose the correct funder name, as organization names can be similar, and also be mindful to select sub-organizations within the registry hierarchy that are the actual funding sources, as appropriate, rather than choosing the name of the parent organization.
+Information provided in your manuscript must match the funding data entered in ScholarOne.
 
-Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
-As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
-The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
-As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
-However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.
+\section*{Acknowledgments}
+An Acknowledgments section, if used, \textbf{immediately precedes} the References.
+Individuals other than the authors who contributed to the underlying research may be acknowledged in this section.
+The use of special facilities and other resources also may be acknowledged.
 
-The selection of a landing site will typically require a vast quantity of data and weigh a multitude of possible metrics, such as scientific value, hardware constraints, timing and communication limits, or safety considerations.
-In our analysis we consider the surface slope, the distance to the surface, and a fictitious science metric in order to determine the best landing site based on the complete shape estimate.
-This approach allows for a spacecraft to autonomously select and land on small body.
-
-The surface slope is computed according to the method developed in Reference~\cite{scheeres1996}.
-Due to the small size, and therefore low gravitational attraction, the force at each point on the surface is a combination of the gravitational attraction and the centripetal acceleration.
-At the center of each face, \( f_i = \begin{bmatrix} f_x & f_y & f_z \end{bmatrix} \), we compute a modified surface acceleration as
-\begin{align}\label{eq:surface_force}
-    U_m = \omega^2 \begin{bmatrix} f_x \\ f_y \\ 0 \end{bmatrix} + \begin{bmatrix} U_x \\ U_y \\ U_z \end{bmatrix},
-\end{align}
-where \( \omega \in \R^1 \) is the angular velocity of the asteroid and \( U_i \) is computed from~\cref{eq:attraction}.
-Then the surface slope can be computed from
-\begin{align}\label{eq:surface_slope}
-    \cos \parenth{ \pi - \phi } = \frac{\vc{n}_f \cdot U_m}{\norm{U_m}},
-\end{align}
-where \( \phi \in \R^1 \) is the surface slope defines the angle between the surface normal \( \vc{n}_f \in \R^3 \) and the force vector at the surface.
-If \( \phi = \SI{0}{\degree} \) then the force vector and the surface normal are anti-parallel, while \( \phi > \SI{90}{\degree} \) means that a particle on the surface would be thrown off the body as the centripetal force is larger than the gravitational attraction.
-
-Additionally, we compute the distance, using~\cref{eq:geodesic_distance}, between the spacecraft state and each face of the asteroid. 
-Finally, we also assign a random science value to the surface in the form of a two dimensional Gaussian.
-Utilizing these metric, a landing site is chosen to minimize the surface cost given as
-\begin{align}\label{eq:surface_cost}
-    J_l =  J_{\text{distance}} - J_{\text{science}},
-\end{align}
-where the surface slope is considered a hard constraint such that any candidate landing site must satisfy \( \phi \leq \phi_m \).
-
-\paragraph{Mesh Refinement}\label{sec:refinement}
-
-Once a suitable landing site is selected, the surrounding area is isolated and refined by adding new vertices and faces in the specified area.
-The goal of refinement, or more generally remeshing, is given a mesh ( or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
-In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL).
-This algorithm uses an iterative method which repeatedly splits long edges, collapses short edges, and relocates vertices until all edges are approximately the desired target edge length.
-% TODO Think about adding PMP 6.12 image here
-
-For example,~\cref{fig:cube_remesh} shows the isotropic remeshing result for the selected faces of a unit cube.
-The original unit cube is composed of \num{8} vertices and \num{12} faces.
-The two triangular faces of the visible side of the cube are selected for the isotropic remeshing operation as shown in~\cref{fig:cube_original_mesh}.
-A target edge length of \num{0.1} is selected for these faces and used to generate~\cref{fig:cube_refine_mesh}.
-The two large triangular faces are divided into a number of smaller triangular faces.
-Furthermore, the additional faces are all approximately the same size and preserve the original surface of the cube.
-After the isotropic remeshing operation the number of vertices has increased from \num{8} to \num{140}.
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.25\textwidth]{figures/original_cube.jpg}}~
-    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.25\textwidth]{figures/remesh_cube.jpg}}
-    \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
-\end{figure}
-
-In order to demonstrate the multi resolution surface refinement we require a true shape model that contains small scale surface features.
-In this dissertation, we utilize the true radar shape model of asteroid 4769 Castalia.
-However, the shape model is not highly detailed as it does not contain small craters or surface features.
-In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme shown previously to update the surface.
-The augmented model of Castalia is shown in~\cref{fig:castalia_refinement}.
-\Cref{fig:castalia_refinement} shows that the increased resolution is required in order to reconstruct these small surface details.
-
-\section{Numerical Examples}\label{sec:reconstruction_examples}
-
-In this section, we demonstrate the use of the incremental shape reconstruction algorithm.
-The approach is used to iteratively reconstruct the shape of several asteroid given LIDAR measurements.
-We utilize radar shape models of asteroids \num{4769} Castalia and (\num{52760}) \num{1998} \(\text{ML}_{14}\).
-The examples demonstrate the full dynamic simulation of a rigid spacecraft with an autonomous closed loop control scheme to both reconstruct the asteroid shape.
-
-The nonlinear controllers described previously are used to control both the translational and rotational states of the vehicle.
-Throughout the simulation the control inputs are computed using the current shape estimate of the asteroid. 
-As measurements are collected, the spacecraft autonomously updates its shape estimate and uses this estimate to compute the control inputs and desired future states.
-These simulations demonstrate the ability of a spacecraft to autonomously explore and maneuver around an unknown small body.
-
-We consider two simulations about asteroids \num{52760} and Castalia.
-The asteroids are assumed to constantly rotate about the \( \vc{f}_3 = \vc{e}_3\) axis according to the parameters given in~\cref{tab:dynamic_asteroids}.
-Furthermore, the state of the asteroid, namely the rotation matrix \( R_A \), is assumed to be known based on ground measurements or previous data.
-\begin{table}[htbp]
-    \centering
-    \begin{tabular}{lcc}
-        \toprule
-        Property & \num{4769} Castalia & (\num{52760}) \num{1998} \(\text{ML}_{14}\) \\
-        \midrule
-        Semi-major axes(\si{\kilo\meter}) & \( 0.8065 \times 0.4905 \times 0.413 \) & \( 1.1 \times 1.1 \times 1.1 \) \\
-        Rotational Period (\si{\hour}) & \num{4.095} & \num{14.98} \\
-        Density (\si{\gram\per\centi\meter^3}) & \num{2.1} & \num{2.1} \\
-        Vertices & \num{2048}  & \num{8192} \\
-        Faces & \num{4092} & \num{16320} \\
-        \bottomrule
-    \end{tabular}
-    \caption{Asteroid properties for dynamic exploration~\label{tab:dynamic_asteroids}}
-\end{table}
-At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( x_0 = \begin{bmatrix} x_0 & 0 & 0 \end{bmatrix} \si{\kilo\meter} \).
-In addition, at the initial state the spacecraft is orientated such that the \( b_1 \) axis is aligned with the inertial \( e_2 \) axis.
-In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat{e}_3)\).
-The shape reconstruction phase of the simulation is performed over \SI{15000}{\second}, over which time the spacecraft will take LIDAR measurements of the surface at \SI{1}{\hertz}.
-Once the total uncertainty has been reduced sufficiently the spacecraft maneuvers to a ``home'' position aligned with the \( f_1 \) axis of the asteroid.
-
-\paragraph{Asteroid 52760 Reconstruction}
-
-Asteroid (\num{52760}) \num{1998} \(\text{ML}_{14}\) was discovered in \num{1998} and is near Earth asteroid of the Apollo group and classified as a potentially hazardous body.
-The asteroid is roughly spherical with a mean radius of approximately \SI{1}{\kilo\meter}.
-The initial shape estimate is assumed to be spherical with approximately the same number of vertices as the truth model.
-\Cref{fig:52760_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
-Due to the roughly spherical shape of the asteroid large portions of the surface are quickly modified to match the measurements.
-In addition~\cref{fig:52760_weights_reconstruction} displays the vertex uncertainty \( w_i \) as a colormap on the surface. 
-Areas of high uncertainty are denoted in yellow while areas of low uncertainty are in purple/blue.
-
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_3749.jpg}}%
-    \subcaptionbox{\SI{50}{\percent} of measurements\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_7499.jpg}}
-
-    \subcaptionbox{\SI{75}{\percent} of measurements\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_11249.jpg}}%
-    \subcaptionbox{\SI{100}{\percent} of measurements\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_14998.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/mesh_update/52760/truth.jpg}}
-    \caption[Asteroid 52760 shape reconstruction with uncertainty]{Incremental reconstruction of asteroid 52760.
-The images colored according to the shape uncertainty.
-Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:52760_weights_reconstruction}}
-\end{figure}
-
-\paragraph{Asteroid 4769 Castalia Reconstruction}
-
-Asteroid 4769 Castalia is a small near Earth asteroid of the Apollo group.
-In addition, it is classified as a potentially hazardous object with a closed approach distance of less than \SI{0.05}{\astronomicalunit}.
-Castalia was discovered in \num{1989} and is the first asteroid to be modeled using radar imagery~\cite{hudson1994}.
-Castalia is composed of two distinct lobes suggesting that it is a contact binary of two smaller objects held together by their mutual gravity.
-\Cref{fig:castalia_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
-In addition~\cref{fig:castalia_weights_reconstruction} displays the vertex uncertainty \( w_i \) as a colormap on the surface. 
-Areas of high uncertainty are denoted in yellow while areas of low uncertainty are in purple/blue.
-Within \SI{50}{\percent} of the simulation span the spacecraft is able to achieve an accurate estimate of the true shape of Castalia.
-
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_3749.jpg}}%
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_7499.jpg}}
-
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_11249.jpg}}%
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_14998.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/mesh_update/castalia/truth.jpg}}
-    \caption[Asteroid Castalia shape reconstruction with uncertainty]{Incremental reconstruction of asteroid Castalia.
-The images colored according to the shape uncertainty.
-Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:castalia_weights_reconstruction}}
-\end{figure}
-
-\Cref{fig:castalia_metrics} shows the total normalized uncertainty and percent error for the volume estimate. 
-The plots show that the reconstruction converges to an accurate shape estimate after approximately \SI{8000}{\second}.
-In addition, the volume estimate is initially a much larger value but quickly converges to the true value.
-\begin{figure}[htbp]
-    \centering
-    \input{tikz/castalia_metrics.tikz}
-    \caption{Normalized uncertainty and volume percent error for Castalia\label{fig:castalia_metrics}}
-\end{figure}
-The spacecraft autonomously navigates around asteroid Castalia to best minimize the cost function in~\cref{eq:control_cost}.
-
-\paragraph{Castalia Landing Site Selection}
-
-With an appropriate shape estimate, the spacecraft can autonomously transition from a shape reconstruction to a landing mode.
-Based on the shape estimate we seek to determine the best location to land. 
-In reality, any landing site selection would be based on a wide variety of factors and constraints, however we highlight a few which can be determined autonomously and from the shape estimate.
-The first metric is related to the surface slope which is computed using the completed shape estimate and~\cref{eq:surface_slope}.
-Areas which violate the slope constraint of \( \phi < \SI{5}{\degree} \) are excluded from further consideration.
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/slope.pdf}}%
-    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/slope_masked.pdf}}
-    \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}
-\end{figure}
-
-The next metric is related to the distance from the current spacecraft position to all candidate landing sites on the surface.
-We utilize~\cref{eq:geodesic_distance} to compute a distance metric to the surface.
-Landing sites which are closer will be considered preferentially over those at a larger distance.
-\Cref{fig:distance_castalia_both} shows a surface plot of the distance to the surface. 
-The area immediately beneath the spacecraft has a small cost while those on the opposite side of the asteroid have a much larger cost.
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/dist.pdf}}%
-    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/dist_masked.pdf}}
-    \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
-\end{figure}
-We can combine~\cref{fig:distance_castalia_both,fig:surface_slope_castalia_both} to determine the best landing site. 
-The combination of the two is shown in~\cref{fig:landing_site_cost} with the desired landing site shown by the blue marker.
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/cost.pdf}
-    \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
-\end{figure}
-After selecting the appropriate landing site we then prepare for landing by collecting more measurements in the region around the landing area.
-
-\paragraph{Castalia Landing Site Refinement}
-One key benefit of an in-situ spacecraft is the ability to measure surface features at a much higher resolution than is possible from the ground. 
-This detail provides a much higher fidelity data source than ground based measurements. 
-In order to emulate this in the simulation we augment the shape model of Castalia with several small craters and outcroppings as shown in~\cref{fig:castalia_refinement}.
-However, these small features would be difficult to capture with the current low resolution shape model of approximately \num{4000} faces.
-The lower number of faces is useful for the evaluation of the polyhedron potential model, it is not ideal for the capture of minute surface features. 
-As a result, we utilize the isotropic remeshing operation described previously to selectively increase the fidelity in the region about the desired landing site.
-\Cref{fig:castalia_refine_density} shows that the vertex density increases by approximately an order of magnitude in region immediately surround the landing site.
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/density.pdf}}%
-    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/density.pdf}}
-    \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
-\end{figure}
-
-The increased number of faces and vertices in the landing area allows for the capture of the small surface features.
-\Cref{fig:castalia_refinement} shows that given LIDAR measurements alone and the shape reconstruction algorithm that the small features are effectively estimated.
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_true.jpg}}%
-    \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_est.jpg}}
-    \caption{Asteroid Castalia with augmented with additional surface features~\label{fig:castalia_refinement}}
-\end{figure}
-
-\paragraph{Castalia Vertical Descent}
-
-The final phase of the simulation is to utilize the mixed resolution model and vertically descend to the desired landing site. 
-This is accomplished using the closed loop control of the vehicle and a trajectory which transitions from the home position to the surface over \SI{3600}{\second}.
-The landing trajectory, using the estimated shape, is visualized in the asteroid frame in~\cref{fig:castalia_landing}.
-During the vertical descent the vehicle is able to accurately track the desired trajectory using the estimated shape to compute the gravitational potential.
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/asteroid_trajectory.jpg}
-    \caption{Vertical descent onto 4769 Castalia~\label{fig:castalia_landing}}
-\end{figure}
-
-\section{Conclusions}
-
-This paper developed a Bayesian update scheme to reconstruct the shape of a small body from range measurements. 
-The approach allows for a local update operation that is able to reconstruct the shape in real time. 
-This is in contrast to standard shape reconstruction algorithms which operate over the entire surface and require signification computational resources.
-Next, an optimal guidance scheme is derived which determines the desired state to best update the shape estimate. 
-This allows for a spacecraft to autonomously maneuver and reconstruct the shape of a small body without operator intervention.
-Finally, a mixed resolution shape representation is presented to allow for an increased fidelity in a specific region of the asteroid.
-This allows for a much greater shape accuracy in a local area while avoiding the computational costs associated with a uniformly high resolution mesh.
-Several numerical examples were presented which demonstrates the approach on a number of real asteroids.
-
-\bibliographystyle{AAS_publication} 
-\bibliography{library}
+\bibliography{sample}
 

### 2018-10-22 manuscript.tex
Add abstract and intro

@@
 
-\title{Preparation of Papers for AIAA Technical Journals}
+\title{Real Time Adaptive Shape Reconstruction for Asteroid Landing}
 
-\author{First A.
-Author \footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for first author.} and Second B.
-Author Jr.\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for second author.}}
-\affil{Business or Academic Affiliation 1, City, State, Zip Code}
-\author{Third C. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for third author.}}
-\affil{Business or Academic Affiliation 2, City, Province, Zip Code, Country}
-\author{Fourth D. Author\footnote{Insert Job Title, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for fourth author (etc.).}}
-\affil{Business or Academic Affiliation 2, City, State, Zip Code}
+\author{Shankar Kulumani \footnote{PhD, Mechanical and Aerospace Engineering, Address/Mail Stop, and AIAA Member Grade (if any) for first author.} and Taeyoung Lee \footnote{Associate Professor, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for second author.}}
+\affil{Goerge Washington University, Washington, DC, 20052}
 
@@
 \begin{abstract}
-These instructions give you guidelines for preparing papers for AIAA Technical Journals using \LaTeX{}.
-If you previously prepared an AIAA Conference Paper using the Papers Template, you may submit using the Papers Template so long as the text is double-spaced.
-Carefully follow the journal paper submission process in Sec.~II of this document.
-Keep in mind that the electronic file you submit will be formatted further at AIAA.
-This first paragraph is formatted in the abstract style.
-Abstracts are required for regular, full-length papers and express articles.
-Be sure to define all symbols used in the abstract, and do not cite references in this section.
-The footnote on the first page should list the Job Title and AIAA Member Grade (if applicable) for each author.
+    Knowledge of the shape of an asteroid is crucial for spacecraft operations.
+    The standard method of determining the gravitational potential, through the use of a polyhedron potential model, is dependent on the shape model.
+    Furthermore, accurate landing or low altitude operations requires accurate knowledge of the surface topology. 
+    The typical approach to shape determination requires an extensive ``mapping'' phase of the mission over which extensive measurements are collected and transmitted for Earth-based processing.
+    Instead, we present an efficient method for estimating the shape of an asteroid in real time.
+    Range measurements of the surface are used to incrementally correct an initial shape estimate according to Bayesian framework. 
+    Then, an optimal guidance scheme is proposed to control the vantage point of the range sensor to construct a more accurate model of the asteroid shape. 
+    This shape model is then used in a nonlinear controller to track a desired trajectory about the asteroid.
+    % Finally, a multi resolution approach is presented which enables for a higher fidelity shape representation in a specified location while avoiding the inherent burdens of a uniformly high resolution mesh.
+    This approach enables for an accurate shape determination around a potential landing site.
+    We demonstrate this approach using several radar shape models of asteroids and provide a full dynamic simulation about asteroid 4769 Castalia.
 \end{abstract}
@@
 \section{Introduction}
-\lettrine{T}{his} document is a \LaTeX{} template for preparation of papers for AIAA Technical Journals.
-If you are reading a hard-copy or .pdf version of this document, download the electronic file, new-aiaa.cls, and use it to prepare your manuscript.
+% Motivation for missions/studying asteroids
+Small solar system bodies, such as asteroids and comets, continue to remain a focus of scientific study.
+The small size of these bodies prevents the formation of large internal pressures and temperatures which helps to preserve the early chemistry of the solar system.
+This insight offers additional detail into the formation of the Earth and also of the probable formation of other extrasolar planetary bodies.
+Of particular interest are those near-Earth asteroids (NEA) which inhabit heliocentric orbits in the vicinity of the Earth. 
+These easily accessible bodies provide attractive targets to support space industrialization, mining operations, and scientific missions.
+In spite of the significant interest, and the extensive research by the community, the operation of spacecraft near small bodies remains a challenging problem.
 
-Authors using \url{https://www.overleaf.com} may simply open the AIAA template from the Overleaf gallery to work online; no local installation of any files is required.
-Authors using a local \LaTeX{} installation will need to open the template in Overleaf and use the ``Download as zip'' option from the project menu to download a local copy of the template files.
-To create your formatted manuscript, type your own text over sections of the template, or cut and paste from another document and then use the available markup styles.
-Note that special formatting such as subscripts, superscripts, and italics may be lost when you copy your text into the template from a Word Processing program such as Microsoft Word.
-See Sec.
-IV for more detailed formatting guidelines.
+% dynamics are difficult around asteroids
+The dynamic environment around asteroids is strongly perturbed and challenging for analysis and mission operations~\cite{scheeres2012}.
+Due to their low mass, which in turn causes a low gravitational attraction, asteroids may have irregular shapes.
+Furthermore, asteroids may also have a chaotic spin state due to the absorption and emittance of solar radiation~\cite{rubincam2000}.
+As a result, approaches utilizing an inverse square gravitational model do not capture the  true dynamic environment.
+In addition, the vast majority of asteroids are difficult to track and characterize using ground based sensors.
+Due to their small size, frequently with a maximum radius less than \SI{1}{\kilo\meter}, and low albedo, the reflected energy of these asteroids is insufficient for reliable detection or tracking.
+Therefore, the dynamics model of the asteroid is relatively coarse prior to in situ measurements from a dedicated spacecraft.
+As a result, any spacecraft mission to an asteroid must include the ability to update the dynamic model given in situ measurements and remain robust to unmodelled forces.
 
+Another key dynamic consideration is the coupling between rotational and translational states around the asteroid.
+The coupling is induced due to the different gravitational forces experienced on various portions of the spacecraft. 
+The effect of the gravitational coupling is related to the ratio of the spacecraft size and orbital radius~\cite{hughes2004}.
+For operations around asteroids, the ratio is relatively large which causes a much larger coupling between the translational and rotational states.
+References~\citenum{elmasri2005} and~\citenum{sanyal2004a} investigated the coupling of an elastic dumbbell spacecraft in orbit about a central body, but only considered the case of a spherically symmetric central body.
+Furthermore, the spacecraft model is assumed to remain in a planar orbit.
+As a result, these developments are not directly applicable to motion about an asteroid, which experiences highly non-Keplerian motion.
+Reference~\citenum{misra2015b} investigated the effect of coupled motion on long term trajectories around asteroids.
+However, the analysis only considered a second order spherical harmonic gravitational potential model. 
+Therefore, these results are only valid when far from the asteroid surface and will diverge when used within the Brillouin sphere.
+
+% Gravity model is important and dependent on shape
+An accurate gravitational potential model is critical for performing low altitude and/or surface operations around asteroids.
+Due to the irregular shape, trajectories will pass within the Brillouin sphere, where the typical spherical harmonic model diverges from the true gravitational potential.
+The standard approach for asteroid missions is to compute the gravitational potential using a polyhedron potential model~\cite{werner1996}.
+The polyhedron potential model provides the exact gravitational potential, and subsequently the gravitational acceleration, for a given triangular faceted shape model of an asteroid.
+The method provides the exact potential at any point outside the body for a given shape model.
+As a result, the accuracy of the gravitational potential is primarily dependent on the accuracy with which the shape model represents the true surface.
+A high fidelity shape, which necessarily has many vertices and faces, is required for an accurate computation of the gravitational acceleration and enabling low altitude operations.
+
+% Challenges involved in operation near asteroids (gravity, shape, distance)
+% generating the shape from the ground is difficult
+Prior to the arrival of a spacecraft at an asteroid, Earth-based sensors are used to characterize the body.
+Using both optical and radar sensors allows for the precise orbit of the asteroid to be determined.
+Another vital task is the determination of the asteroid shape from radar data~\cite{hudson1994,busch2011}.
+This is a challenging problem as it requires the simultaneous estimation of the asteroid spin state and shape.
+Furthermore, determining the shape from radar is currently the only Earth-based technique that can produce detailed three-dimensional shape information of near-Earth objects~\cite{greenberg2015}.
+The current approach is based on an estimation scheme which iteratively perturbs a shape to match given radar data.
+This computationally intensive approach is only able to capture the gross size and shape and is unable to capture the small surface features of the asteroid.
+Frequently, only a coarse model is possible from the ground and an accurate shape must be determined only after a spacecraft has rendezvoused with the asteroid.
+As a result, upon arrival the gravitational environment near the asteroid is poorly modeled as the shape of the asteroid is not accurate.
+Therefore, the polyhedron potential model is not appropriate immediately upon arrival but rather only after the shape has been determined.
+
+% on arrival spacecraft spend long periods mapping, and depending on mission this might be unallocable
+On approach to an asteroid, spacecraft navigation and guidance is primarily based on ground measurements.
+After arrival, a spacecraft will generally spend months or years in a mapping mission phase~\cite{kubota2003,cole1998}.
+During this period, spacecraft sensors, such as on board optical telescopes or Light radio Detection and Ranging (LIDAR), are used to characterize the asteroid.
+The resulting imagery and range data is transmitted to the ground and the resulting asteroid shape and motion is estimated. 
+During this mapping phase the spacecraft must remain in a quiescent state devoted entirely to mapping the surface.
+Depending on the mission type, this long period of mapping is crucial to the mission, such as sample collection~\cite{gates2015}. 
+However, other missions, such as asteroid mitigation, may be severely limited by the time and ground resources required to generate a surface shape.
+Furthermore, the long distances involved necessitate on-board autonomy to enable to spacecraft to operate without ground communications.
+Similarly, during landing the spacecraft will require the ability to sense and model the surface topography in order to safely land in an unknown environment.
+The dependency on expensive ground-based shape reconstruction techniques limits the ability of spacecraft to autonomously operate at asteroids.
+Mitigation of this ground based surface modeling will greatly expand the range of missions possible.
+
+% we want to generate the shape in real time and then use this shape for updated and better control
+In this paper, we develop a method to compute the surface shape of an asteroid from range measurements.
+Our approach is able to operate in real time and incrementally update the shape model of an asteroid as new range measurements are collected.
+This approach allows for the shape to be continually updated as range measurements are used to locally modify the shape estimate.
+Furthermore, this updated shape is then used in a nonlinear controller to enable the tracking of a landing trajectory to the surface.
+In contrast to previous work, we explicitly consider the gravitational coupling between orbit and attitude dynamics.
+Furthermore, instead of computationally expensive surface reconstruction methods, we present a straightforward and conceptually simple method to enable real time shape updates.
+
+% our approach for paper. Real time method to update asteroid shape model and use updated model in closed loop control
+
+% Benefits and contribution of our approach
+In short, this paper presents a method to incrementally update the shape  model of an asteroid from range measurements. 
+Our approach alleviates the need for a dedicated mapping phase as the spacecraft is able to update its shape model in real time and without expensive computations.
+This type of approach allows for the spacecraft to maneuver and land on the asteroid immediately upon arrival rather than spending several months mapping the surface.
+This updated shape model is then used to in a nonlinear controller to track a desired state trajectory for the dynamics of a rigid body spacecraft.
+The dynamics are developed on the nonlinear manifold of rigid body motions, namely the special euclidean group.
+This formulation is based on an intrinsic geometric description of the motion and accurately captures the coupling between orbit and attitude dynamics. 
+The presented approach allows for a spacecraft to transition directly from arrival to the surface while reconstructing the surface shape in real time.
 \section{Procedure for Paper Submission}

### 2018-10-22 manuscript.tex
Add problem statement

@@
 The presented approach allows for a spacecraft to transition directly from arrival to the surface while reconstructing the surface shape in real time.
-\section{Procedure for Paper Submission}
 
-All manuscripts are to be submitted online at \url{https://mc.manuscriptcentral.com/aiaa}.
-Select either “Log In” if you have an existing account or “Create an Account” if this is your first time submitting to one of AIAA’s journals.
-If it’s the latter, please follow the instructions ScholarOne provides.
-Once you have logged into ScholarOne, select “Author Center” then scroll down.
-Under “Author Resources”, select the star beside “Click here to submit a new manuscript”.
-The site will take you step-by-step through the submission process.
-Once you submit your manuscript, you will receive an email containing your manuscript ID number as well as a link to view the status of your manuscript.
+\section{Problem Formulation}\label{sec:problem}
 
-After entering all required submission data, you must use the “Upload Manuscript” feature of the Author Center to upload your submission.
-Remember that your document must be in single-column, double-spaced format (as this template) before you upload it.
-Please be sure that the name of the file you upload for processing is short and simple (i.e., “SmithJPP.pdf”) with no spaces, tildes, symbols, or other special characters.
-Authors are encouraged to upload .pdf files, which are less likely to have conversion errors on upload.
-Failure to meet these requirements could result in a processing error that would require you to re-upload your manuscript.
-Once you have uploaded your manuscript, please inspect the file for accuracy.
-This step is required to complete your submission.
-If you experience difficulties with the upload and/or conversion of your manuscript, please contact ScholarOne Manuscripts Support (\url{https://mchelp.manuscriptcentral.com/gethelpnow/} or +1-888-503-1050) for additional assistance.
-
-\emph{Attention Asian Authors: If you are uploading a .pdf file, please remove Asian fonts from your file, under File>Properties.}
+In this paper, we consider the motion of a dumbbell model of spacecraft around an asteroid.
+The dumbbell model captures the important interactions of the coupling between orbital and attitude dynamics.
+In this model, the spacecraft consists of two masses connected by a massless rod.
+The asteroid is modeled as a constant density polyhedron with constant, and known, spin about its maximum moment of inertia. 
+Without loss of generality, we define body fixed frames for both the spacecraft and asteroid, which are aligned with the principle axes of each body and originate at their respective center of mass. 
+The kinematics of the dumbbell and asteroid are described in the inertial frame by
+\begin{itemize}
+    \item \( \vc{x} \) - the position of the center of mass of the dumbbell spacecraft represented in the inertial frame, \( \vc{e}_i\),
+    \item \( R \) - the rotation matrix which transforms vectors defined in the spacecraft fixed frame, \( \vc{b}_i \), to the inertial frame, \( \vc{e}_i \),
+    \item \( \vc{\Omega} \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame, \( \vc{b}_i \), and
+    \item \( R_A \) - the rotation matrix which transforms vectors defined in the asteroid fixed frame, \( \vc{f}_i \), to the inertial frame, \( \vc{e}_i \).
+\end{itemize}
+In this work, we assume that the asteroid is much more massive than the spacecraft and its motion is not affected by that of the spacecraft.
+This assumption allows us to treat the motion of the vehicle independently from that of the asteroid.
 

### 2018-10-22 manuscript.tex
Add most of paper

@@
 
-\section{General Guidelines}
+\subsection{Spacecraft Dynamic Model}
+Using Hamilton's principle one can derive the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
+\begin{align}
+    \dot{\vc{x}} &= \vc{v}, \\
+    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2}, \\
+    \dot{R} &= R S(\vc{\Omega}) , \\
+    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2.
+\end{align}
+The vectors \( \vc{z}_1 \) and \( \vc{z}_2\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
+\begin{align}
+    \vc{z}_1 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_1} , \\
+    \vc{z}_2 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_2}.
+\end{align}
+The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as
+\begin{align}
+    \vc{M}_i = m_i \parenth{S(R_A^T \vc{\rho}_i) R^T \deriv{U}{\vb{z}_i}}.
+\end{align}
+where the polyhedron potential is defined as 
+\begin{align}
+    U(\vc{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vc{r}_e \cdot \vc{E}_e \cdot \vc{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vc{r}_f \cdot \vc{F}_f \cdot \vc{r}_f \cdot \omega_f,
+\end{align}
+and \( \vc{r}_e\) and \(\vc{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
+The position of each mass \(m_i\) of the dumbbell is defined in the dumbbell fixed frame by the vector \(\vb{\rho}_i\).
 
-The following section outlines general (nonformatting) guidelines to follow.
-These guidelines are applicable to all authors and include information on the policies and practices relevant to the publication of your manuscript.
+\subsection{Polyhedron Potential Model}\label{sec:polyhedron_potential}
 
-\subsection{Publication by AIAA}
-Your manuscript cannot be published by AIAA if:
-\begin{enumerate}
-\item The work is classified or has not been cleared for public release.
-\item The work contains copyright-infringing material.
-\item The work has been published or is currently under consideration for publication or presentation elsewhere.
-(Exception: Papers presented at AIAA conferences may be submitted to AIAA journals for possible publication.)
-\end{enumerate}
+% most use a spherical harmonic model or a ellipsoid model but we use a polyhedron model
+An accurate gravitational potential model is necessary for the operation of spacecraft about asteroids.
+Additionally, a detailed shape model of the asteroid is needed for trajectories passing close to the body.
+The classic approach is to expand the gravitational potential into a harmonic series and compute the series coefficients.
+However, the harmonic expansion is always an approximation as a result of the infinite order series used in the representation.
+Additionally, the harmonic model used outside of the circumscribing sphere is not guaranteed to converge inside the sphere, which makes it unsuitable for trajectories near the surface.
 
-You will be asked to provide the publication or presentation history of your paper (or any similar paper) if it has \emph{ever} been submitted for publication or presentation previously to an AIAA journal or conference.
-Please include the following, if applicable: the full name of the publication or conference, the entire paper number, dates the conference took place, review history, final disposition of manuscript, etc.
+We represent the gravitational potential of the asteroid using a polyhedron gravitation model.
+This model is composed of a polyhedron, which is a three-dimensional solid body, that is defined by a series of vectors in the body-fixed frame.
+The vectors define vertices in the body-fixed frame as well as planar faces which compose the surface of the asteroid.
+We assume that each face is a triangle composed of three vertices and three edges.
+As a result, only two faces meet at each edge while three faces meet at each vertex.
+Only the body-fixed vectors, and their associated topology, is required to define the exterior gravitational model.
+References~\cite{werner1994} and~\cite{werner1996} give a detailed derivation of the polyhedron model.
+Here, we summarize the key developments and equations required for implementation.
 
-\subsection{Copyright}
+Consider three vectors \( \vc{v}_1, \vc{v}_2, \vc{v}_3 \in \R^{3 \times 1} \), assumed to be ordered in a counterclockwise direction about an outward facing normal vector, which define a face.
+For each face we define the face dyad \( \vc{F}_f \) as
+\begin{align}\label{eq:face_dyad}
+    \vc{F}_f &= \hat{\vc{n}}_f \hat{\vc{n}}_f \in \R^{3 \times 3}.
+\end{align}
+Each edge is a member of two faces and has an outward pointing edge normal vector, perpendicular to both the edge and the face normal.
+For the edge connecting the vectors \( \vc{v}_1 \) and \( \vc{v}_2 \), which are shared between the faces \(A\) and \( B\), the per edge dyad is given by
+\begin{align}\label{eq:edge_dyad}
+    \vc{E}_{12} = \hat{\vc{n}}_A \hat{\vc{n}}_{12}^A + \hat{\vc{n}}_B \hat{\vc{n}}_{21}^B \in \R^{3 \times 3}.
+\end{align}
+The edge dyad \( \vc{E}_e  \), is defined for each edge and is a function of the two adjacent faces meeting at that edge.
+The face dyad \( \vc{F}_f \), is defined for each face and is a function of the face normal vectors.
 
-Before AIAA can publish any paper, the copyright information must be completed in ScholarOne.
-Failure to complete the form correctly could result in your paper not being published.
-You must select one copyright assignment statement (select A, B, C, or D) and once a statement is picked, changes cannot be made during the proofs stage.
-Read the copyright statements carefully.
-AIAA requires a copyright transfer from the author(s) to AIAA or a license to print your material; government authors can assert that the work is in the public domain.
-Because you will be completing this form online, you do not need to fill out a hard-copy form.
-Do not include a copyright statement anywhere on your paper.
-The correct statement will be included automatically at the time of processing.
-(If your paper was presented at an AIAA conference, then the copyright statement chosen for the journal article should be the same as for your conference paper.)
+Let \( \vc{r}_i \in \R^{3 \times 1} \) be the vector from the spacecraft to the vertex \( \vc{v}_i \) and it's length is given by \( r_i = \norm{\vc{r}_i} \in \R^{1} \).
+The per-edge factor \( L_e \in \R^{1}\), for the edge connecting vertices \( \vc{v}_i \) and \( \vc{v}_j \), with a constant length \( e_{ij} = \norm{\vc{e}_{ij}} \in \R^1\) is
+\begin{align}\label{eq:edge_factor}
+    L_e &= \ln \frac{r_i + r_j + e_{ij}}{r_i + r_j - e_{ij}}.
+\end{align}
+For the face defined by the vertices \( \vc{v}_i, \vc{v}_j, \vc{v}_k \) the per-face factor \( \omega_f \in \R^{1} \) is
+\begin{align}\label{eq:face_factor}
+    \omega_f &= 2 \arctan \frac{\vc{r}_i \cdot \vc{r}_j \times \vc{r}_k}{r_i r_j r_k + r_i \parenth{\vc{r}_j \cdot \vc{r}_k} + r_j \parenth{\vc{r}_k \cdot \vc{r}_i} + r_k \parenth{\vc{r}_i \cdot \vc{r}_j}} .
+\end{align}
+The gravitational potential due to a constant density polyhedron is given as
+\begin{align}\label{eq:potential}
+    U(\vc{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vc{r}_e \cdot \vc{E}_e \cdot \vc{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vc{r}_f \cdot \vc{F}_f \cdot \vc{r}_f \cdot \omega_f \in \R^1,
+\end{align}
+where \( \vc{r}_e\) and \(\vc{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
+Furthermore we can use these definitions to define the attraction, gravity gradient matrix, and Laplacian as
+\begin{align}
+    \nabla U ( \vc{r} ) &= -G \sigma \sum_{e \in \text{edges}} \vc{E}_e \cdot \vc{r}_e \cdot L_e + G \sigma \sum_{f \in \text{faces}} \vc{F}_f \cdot \vc{r}_f \cdot \omega_f \in \R^{3 \times 1} , \label{eq:attraction}\\
+    \nabla \nabla U ( \vc{r} ) &= G \sigma \sum_{e \in \text{edges}} \vc{E}_e  \cdot L_e - G \sigma \sum_{f \in \text{faces}} \vc{F}_f \cdot \omega_f \in \R^{3 \times 3}, \label{eq:gradient_matrix}\\
+    \nabla^2 U &= -G \sigma \sum_{f \in \text{faces}}  \omega_f \in \R^1 .\label{eq:laplacian}
+\end{align}
 
-\subsection{Publication Charges for Open Access}
+One interesting thing to note is that both~\cref{eq:face_dyad,eq:edge_dyad} can be precomputed without knowledge of the position of the satellite.
+They are both solely functions of the vertices and edges of the polyhedral shape model and are computed once and stored.
+Once a position vector \( \vc{r} \) is defined, the scalars given in~\cref{eq:edge_factor,eq:face_factor} can be computed for each face and edge.
+Finally,~\cref{eq:potential} is used to compute the gravitational potential on the spacecraft.
+The Laplacian, defined in~\cref{eq:laplacian}, gives a simple method to determine if the spacecraft has collided with the body~\cite{werner1996}.
 
-Publication charges are voluntary, and nonpayment has no influence on the review process of the time from acceptance to publication.
-Publication charge payments help defray production costs and keep journal subscription prices low.
+\section{Incremental Shape Reconstruction}\label{sec:radius_update}
 
-The article publication charge for Open Access is available in ScholarOne and on the AIAA website; the fee is the same regardless of article type.
-There is a fee for Open Access immediately upon publication in AIAA’s electronic library, Aerospace Research Central (ARC) and a fee for Open Access 12 months after publication in ARC.
+One of the first tasks for any spacecraft mission to a small body is to generate an estimate of the shape.
+We assume that upon arrival at a target body, the spacecraft contains an initial estimate for the shape of the small body.
+This shape can be a coarse estimate computed from ground measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid.
+Additionally, we assume that the shape estimate is closed and a triangular faceted surface mesh, emulating those used in practice to represent asteroids.
+Furthermore, the number of vertices in the estimate can be scaled according to the desired final accuracy or computational capabilities.
 
-\section{Instructions}
+We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid~\cite{zuber1997,zuber2000}.
+This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
+Given the time total time of flight, the distance can be accurately computed using \( d = \frac{\Delta TOF}{2 c} \) where \( c = \SI{2.998e8}{\meter\per\second}\) is the constant speed of light.
+Assuming accurate knowledge of the pointing direction of the spacecraft, in the form of the rotation matrix \( R \in \R^{3 \times 3 } \), we can compute a direction from the spacecraft to the measurement location on the surface.
+The output of this sensor is a vector, \( \vc{d}_i \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface. 
+Using the state of the asteroid, we can transform this measurement to the asteroid fixed frame using the simple transformation
+\begin{align*}
+    \vc{p}_i = R_A^T R \vc{d}_i .
+\end{align*}
+Given many measurements, \( \vc{p}_i \in \R^3 \), of the asteroid surface we can efficiently update our initial shape estimate to that of the true surface.
+\Cref{fig:lidar_example} shows asteroid 4769 Castalia and a representation of several LIDAR measurements. 
+The spacecraft measures the range between itself and the asteroid surface to several points within the field of view of the sensor. 
+These measurements provide a collection of points which lie on the surface of the asteroid, and by combining many points, a so called ``point cloud'', allows us to reconstruct the shape.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.75\textwidth]{figures/castalia_raycasting_plot.jpg}
+    \caption{Simulated LIDAR measurements of asteroid Castalia~\label{fig:lidar_example}}
+\end{figure}
 
-If you are using the AIAA Journals \LaTeX{} Template file to prepare your manuscript, you can simply type your own text over sections of this document, or cut and paste from another document and use the available markup styles.
-If you choose to cut and paste, select the text from your original document and choose Edit>Copy.
-(Do not select your title and author information, since the document spacing may be affected.
-It is a simple task to reenter your title and author information in the template.) Open the Journals Template.
-Place your cursor in the text area of the template and select Edit>Paste.
-Please note that special formatting (e.g., subscripts, superscripts, italics) may be lost when you copy your text into the template.
+\paragraph{Bayesian Shape Update}
 
-To apply the AIAA Journals formatting, use the standard \LaTeX{} commands for sections and subsection, etc; all the styles you will need to format your document are available as standard \LaTeX{} commands.
-The style will automatically adjust your fonts and line spacing.
-Repeat this process to apply formatting to all elements of your paper.
-\emph{Do not change the font sizes, line spacing, or margins.
-Do not manually hyphenate your document.} Use italics for emphasis; do not underline.
+Our algorithm applies a Bayesian framework to radially modify each vertex \( \vc{v}_i \in \R^3\) of the shape estimate based on measurement \( \vc{p}_i \in \R^3 \). 
+This approach alleviates much of complexity of incorporating new vertices or surface triangulation common in surface reconstruction methods~\cite{berg2008}.
+This assumption means that the total number of vertices of the shape model is fixed.
+However, additional detail, in the form of additional vertices, is possible by using standard mesh subdivision algorithms~\cite{orourke1998}.
 
-Use the Print option under the File tab to view Page Layout and see the most accurate representation of how your final paper will appear.
-Once formatting is complete, be sure to double space all sections of your manuscript.
+The radial distance of each vertex, \( v_i = \norm{\vc{v}_i}\), is assumed to be distributed according to the Gaussian distribution
+\begin{align*}
+    v_i \sim \mathcal{N}(r_i, w_i^2)
+\end{align*}
+where \( r_i \) is the initial estimate of the radial distance of vertex \( \vc{v}_i\) and \( w_i \) is the initial variance, or confidence, in the radial distance.
+The radial distance of each measurement, \( p_{j,i} = \norm{\vc{p}_j}\), is also assumed to be distributed according to the Gaussian distribution
+\begin{align*}
+    p_{j,i} \sim \mathcal{N}(r_{j,i}, w_{j,i}^2)
+\end{align*}
+where \( r_{j,i} = \norm{\vc{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i}\) defines the variance of the measurement with respect to vertex \( \vc{v}_i\).
+Each measurement is defined by the index \( j \) while the associated vertex is defined by \( i \). 
+As a result, the measurement \( p_{j, i} \) defines the distribution of measurement \( j \) with respect to vertex \( i \). 
+Any given measurement may be used to update one or several vertices.
 
-\subsection{Document Text}
-The default font for the Template is Times New Roman, 10-point size.
-The first line of every paragraph should be indented, and all lines should be double-spaced.
-Default margins are 1 in.
-on all sides.
-In the electronic version of this template, all margins and other formatting are preset.
-There should be no additional (blank) lines between paragraphs.
+The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vc{v}_i \).
+Here, we use the geodesic distance to parameterize the difference, and hence  uncertainty, of associating the measurement with a given vertex.
+From spherical trigonometry~\cite{gade2010}, the central angle between measurement \( \vc{p}_i \) and vertex \( \vc{v}_i \) of the shape estimate is
+\begin{align}\label{eq:geodesic_distance}
+    \Delta \sigma_{j,i} = \arctan \parenth{\frac{\norm{\vc{p}_j \times \vc{v}_i}}{\vc{p}_j \cdot \vc{v}_i }}.
+\end{align}
+The variance of measurement \( \vc{p}_i \) with respect to vertex \( \vc{v}_i \) is then defined by the geodesic distance as
+\begin{align}
+    w_{j, i} = \norm{\vc{p}_j} \Delta \sigma_{j,i} .
+\end{align}
+This approach relates the uncertainty of the measurement \( \vc{p}_j \) with the geodesic distance to a given vertex, \( \vc{v}_i \).
+As a result, measurements which are far from a vertex, i.e.\ \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty. 
+This approach can be considered as a form of a correlation based sensor model~\cite{thrun2005}.
+The main benefit of a correlation based approach, in contrast to feature extraction is the relative simplicity of implementation.
+However, the resulting correlation values do not posses any physical significance and do not represent the noise or uncertainty characteristics of the sensor.
 
-\emph{NOTE:} If you are using the Template to format your manuscript, the required spacing and formatting will be applied automatically.
+From Bayes' theorem, the posterior probability is defined as
+\begin{align}
+    p(v_i | p_{j, i}) = \frac{p(p_{j, i} | v_i) p(v_i)}{p( p_{j, i})} \propto p(p_{j,i} | v_i) p(v_i).
+\end{align}
+From the properties of a Gaussian, the posterior probability given a measurement is also distributed according to a Gaussian distribution~\cite{bishop2006} and given by
+\begin{align}\label{eq:posterior_probability}
+    \mathcal{N} \parenth{\frac{w_{j, i}^2 r_i + w_i^2 r_{j, i}}{w_i^2 + w_{j, i}^2} , \frac{w_i^2  w_{j, i}^2}{w_i^2 +  w_{j, i}^2}} .
+\end{align}
+From~\cref{eq:posterior_probability}, the posterior probability conditioned on the measurement is the weighted average of the prior knowledge and the measurement. 
+Measurements that are far from the vertex will have a high uncertainty or variance and will have a reduced impact on the radial position of the vertex.
+Additional measurements are incorporated using a weighted average of prior belief and the measurement uncertainty.
+
+In order to improve the computational efficiency measurement updates are assumed to be local in nature.
+Instead of applying a measurement to all vertices of the mesh, the measurement is only applied to the vertices which are within a specified region of the measurement. 
+We define a region of interest, \( \Delta S \), about each measurement which defines the surface area over which the measurement will affect the mesh estimate.
+We relate \( \Delta S \) to an equivalent angular constraint using
+\begin{align}\label{eq:region_of_interest}
+    \Delta \sigma_{max} = \sqrt \frac{\Delta S}{r_b^2}
+\end{align}
+% shankar: brillouin is correct. https://arc.aiaa.org/doi/10.2514/6.2014-4302
+where \( r_b \) defines the Brillouin  sphere radius, or the radius of the circumscribing sphere of the asteroid.
+Only vertices which satisfy \( \Delta \sigma_i \leq \Delta \sigma_{max} \) are considered in the Bayesian update shown in~\cref{eq:posterior_probability}.
+
+The approach presented in this section allows one to update the shape of small body given a single range measurement of the surface.
+A sequential process can be used to iteratively update the shape estimate given many measurements of the surface.
+
+\section{Optimal Guidance for Shape Reconstruction}\label{sec:explore_asteroid}
+
+The mesh update algorithm presented does not offer a method to determine which portion of the surface needs to be updated. 
+In this section, we present an optimal approach for the guidance of the vehicle in order to update the shape estimate.
+A nonlinear geometric controller is utilized which allows the spacecraft to maneuver to the best location that will update the shape estimate~\cite{kulumani2017b}.
+This guidance schemes enables autonomous operations around a small body.
+
+We define a cost associated with each vertex \( \vc{v}_i \) of the shape estimate
+\begin{align}\label{eq:explore_cost}
+    J_i (x, R, R_A) = \alpha_w J_{w_i} + \alpha_d J_{d_i}(x_r) + \alpha_c J_{c_i}(x_r)
+\end{align}
+where the weighting factors \( \alpha_w, \alpha_d, \alpha_c \in \R^1 \) are chosen such that \( \alpha_w + \alpha_d + \alpha_c = 1 \).
+The cost function is defined as a function of the current inertial position, \( x \in \R^3 \), and the attitude, \( R \in \R^{3\times3}\) of the spacecraft.
+Furthermore, knowledge of the small body rotation is required in order to determine the position of the spacecraft in the small body fixed frame, \( x_r = R_A^T x\).
+
+The term \( J_{w_i} \in \R^1 \) represents the cost associated with the uncertainty of vertex \( i \) as
+\begin{align}\label{eq:weight_cost}
+    J_{w_i} &= - \frac{w_i}{w_m}
+\end{align}
+where \( w_i \) is the uncertainty of vertex \( i \) and \( w_m \) is a maximum uncertainty used to scale the values.
+The term \( J_{d_i} \) represents the scaled geodesic distance between the current state of the spacecraft and vertex \( i \),
+\begin{align}\label{eq:distance_cost}
+    J_{d_i}(\rpos) &= \frac{1}{\pi} \arctan \parenth{ \frac{\norm{\rpos \times \vc{v}_i}}{\rpos \cdot \vc{v}_i}}.
+\end{align}
+
+Finally, a control component is included in the cost function which penalizes vertices that are difficult to reach.
+Consider, the current position of the spacecraft in the small body fixed frame as \( \rpos\) and a desired vertex \( \vc{v}_i \) of the shape estimate.
+We can define a normal vector to the plane spanned by \( \rpos, \vc{v}_i \) as
+\begin{align}\label{eq:normal_to_plane}
+    \vc{n}_i = \frac{\rpos \times \vc{v}_i}{\norm{\rpos} \norm{\vc{v}_i}}.
+\end{align}
+Then a trajectory \( x_d(\theta) \) as
+\begin{align}\label{eq:spherical_waypoint}
+    x_d(\theta) = r_d \exp{\parenth{\theta \hat{\vc{n}_i}} } \frac{\rpos}{\norm{\rpos}},
+\end{align}
+where \( \theta : \bracket{0, \frac{\rpos \cdot \vc{v}_i}{\norm{\rpos}\norm{\vc{v}_i}}} \to \R^1\) parameterizes the desired trajectory.
+\Cref{eq:spherical_waypoint} simply describes a portion of a great circle trajectory between the current state, \( \rpos \), and the desired vertex \( \vc{v}_i \)~\cite{chen2016}.
+The altitude of the spacecraft, \( r_d \in \R \), can be chosen based on sensor characteristics of safety concerns.
+For example, \( r_d \) can be chosen as the distance of the Biroullin sphere with an additional safety margin to mitigate any surface collision~\cite{scheeres2012a}.
+We assume that the tracking errors are small, such that \( e_x, e_v \) are negligible, therefore the control becomes
+\begin{align}\label{eq:tracking_control_cost}
+    u_f(\theta) = -F_{ext}(x_d(\theta)), 
+\end{align}
+where the external force is defined by the polyhedron potential model given in~\cref{eq:attraction}.
+The control cost is then defined as the integral over the desired trajectory~\cref{eq:spherical_waypoint} between the current state and the desired vertex as
+\begin{align}\label{eq:control_cost}
+    J_{c_i}(\rpos) = \frac{1}{u_m} \int_{\theta_0}^{\theta_f} u_f(\theta)^T R u_f(\theta) d\theta,
+\end{align}
+where \( u_m \) is used to normalize and scale \( J_{c_i} \).
+\Cref{eq:control_cost} is numerically integrated over the trajectory \( x_d(t) \) and used to penalize vertices which have a larger cost.
+
+The vertex which minimizes~\cref{eq:explore_cost} 
+\begin{align*}
+    \vc{v}_{min} = \min_{i} J_i(x, R, R_A),
+\end{align*}
+is determined and used to determine the optimum vertex of the shape model to measure.
+This vertex is then used to determine the required state of the spacecraft in order to collect a measurement.
+We assume that the spacecraft will maneuver to a location directly above the selected vertex, \( \vc{v}_{min} \), and point in the nadir direction to collect a measurement.
+The desired state is transformed into the inertial frame and chosen as a location above \( \vc{v}_{min} \) as
+\begin{align}
+    x_d = r_d R_A \vc{v}_{min}, 
+\end{align}
+where \( r_d \) is again chosen to ensure a safety margin above the surface.
+The desired attitude command, \( R_d\), is chosen such that the spacecraft camera axis, \( \vc{b}_1 \), is directed along the nadir towards the small body.
+It is sufficient to define two orthogonal vectors to uniquely determine the attitude of the spacecraft.
+The \( \vc{b}_{3d} \) vector is chosen to lie in the plane spanned by \(\vc{b}_{1d} \) and \( \vc{e}_3 = \vc{f}_3 \).
+The desired attitude command is defined as
+\begin{align}
+    \vc{b}_{1d} &= - \frac{\vc{x}}{\norm{\vc{x}}} , \\
+    \vc{b}_{3d} &= \frac{\vc{f}_3 - \parenth{\vc{f}_3 \cdot \vc{b}_{1d}} \vc{b}_{1d}}{\norm{\vc{f}_3 - \parenth{\vc{f}_3 \cdot \vc{b}_{1d}} \vc{b}_{1d}}}, \\
+    \vc{b}_{2d} &= \vc{b}_{3d} \times \vc{b}_{1d} , \\
+    R_d &= \begin{bmatrix} \vc{b}_{1d} & \vc{b}_{2d} & \vc{b}_{3d} \end{bmatrix} .
+\end{align}
+This form of \( R_d \) will direct the \( b_1 \) axis towards the small body, and can be modified for a different camera orientation.
 

### 2018-10-22 manuscript.tex
Add AAS images adn things

@@
 %\documentclass[conf]{new-aiaa} for conference papers
-\usepackage[utf8]{inputenc}
+\usepackage{AAS_packages}
+% \usepackage[utf8]{inputenc}
 
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage[version=4]{mhchem}
-\usepackage{siunitx}
-\usepackage{longtable,tabularx}
-\setlength\LTleft{0pt}
+% \usepackage[version=4]{mhchem}
+% \usepackage{longtable,tabularx}
+% \setlength\LTleft{0pt}
 
@@
 
-{\renewcommand\arraystretch{1.0}
-\noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
-$A$  & amplitude of oscillation \\
-$a$ &    cylinder diameter \\
-$C_p$& pressure coefficient \\
-$Cx$ & force coefficient in the \textit{x} direction \\
-$Cy$ & force coefficient in the \textit{y} direction \\
-c   & chord \\
-d$t$ & time step \\
-$Fx$ & $X$ component of the resultant pressure force acting on the vehicle \\
-$Fy$ & $Y$ component of the resultant pressure force acting on the vehicle \\
-$f, g$   & generic functions \\
-$h$  & height \\
-$i$  & time index during navigation \\
-$j$  & waypoint index \\
-$K$  & trailing-edge (TE) nondimensional angular deflection rate\\
-$\Theta$ & boundary-layer momentum thickness\\
-$\rho$ & density\\
-\multicolumn{2}{@{}l}{Subscripts}\\
-cg & center of gravity\\
-$G$ & generator body\\
-iso	& waypoint index
-\end{longtable*}}
+% {\renewcommand\arraystretch{1.0}
+% \noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
+% $A$  & amplitude of oscillation \\
+% $a$ &    cylinder diameter \\
+% $C_p$& pressure coefficient \\
+% $Cx$ & force coefficient in the \textit{x} direction \\
+% $Cy$ & force coefficient in the \textit{y} direction \\
+% c   & chord \\
+% d$t$ & time step \\
+% $Fx$ & $X$ component of the resultant pressure force acting on the vehicle \\
+% $Fy$ & $Y$ component of the resultant pressure force acting on the vehicle \\
+% $f, g$   & generic functions \\
+% $h$  & height \\
+% $i$  & time index during navigation \\
+% $j$  & waypoint index \\
+% $K$  & trailing-edge (TE) nondimensional angular deflection rate\\
+% $\Theta$ & boundary-layer momentum thickness\\
+% $\rho$ & density\\
+% \multicolumn{2}{@{}l}{Subscripts}\\
+% cg & center of gravity\\
+% $G$ & generator body\\
+% iso	& waypoint index
+% \end{longtable*}}
 
@@
 
-\subsection{Headings}
-Format the title of your paper in bold, 18-point type, with capital and lower-case letters, and center it at the top of the page.
-The names of the authors, business or academic affiliation, city, and state/province follow on separate lines below the title.
-The names of authors with the same affiliation can be listed on the same line above their collective affiliation information.
-Author names are centered, and affiliations are centered and in italic type.
-The affiliation line for each author includes that author’s city, state, and zip/postal code (or city, province, zip/postal code and country, as appropriate).
-The first footnote (bottom of first page) contains the job title and department name, and AIAA member grade for each author.
-Author email addresses may be included also.
+% \section{Multi-resolution Landing Area Refinement}\label{sec:landing_refinement}
 
-Major headings in the template (``sections'' in the \LaTeX{} template commands) are bold 11-point font and centered.
-Please omit section numbers before all headings unless you refer frequently to different sections.
-Use Roman numerals for major headings if they must be numbered.
+% The shape update approach presented is designed with autonomous operations in mind. 
+% It is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
+% Furthermore, the original mesh is uniformly distributed and as a result many small topological features such as rocks or small craters are not be captured by the shape model. 
+% However, these small features are critical for surface operations and safe landings.
+% In addition, it would be computationally prohibitive to have a uniformly high resolution mesh.
+% In this section, we extend the previous shape update approach to enable a much higher fidelity in a specific location.
 
-Subheadings (``subsections'' in the \LaTeX{} template commands) are bold, flush left, and either unnumbered or identified with capital letters if necessary for cross-referencing sections within the paper.
-There must be at least 2 of all subheadings and sub-subheadings.
-If there is only a single subheading or sub-subheading, please italicize the title of the subheadings, followed by a period, and run it into the text paragraph.
+% Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
+% As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
+% The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
+% As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
+% However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.
 
-Sub-subheadings (``subsubsections'' in the \LaTeX{} template commands) are italic, flush left, and either unnumbered or numbered with Arabic numerals (1, 2, 3, etc.) if necessary for cross-referencing sections within the paper.
+% The selection of a landing site will typically require a vast quantity of data and weigh a multitude of possible metrics, such as scientific value, hardware constraints, timing and communication limits, or safety considerations.
+% In our analysis we consider the surface slope, the distance to the surface, and a fictitious science metric in order to determine the best landing site based on the complete shape estimate.
+% This approach allows for a spacecraft to autonomously select and land on small body.
 
-\subsection{Abstract}
-An abstract appears at the beginning of Full-Length Papers, Regular Articles, and Express Articles.
-(Survey and Design Forum Papers, History of Key Technologies Papers, invited lectures, and Technical/Engineering Notes do not include abstracts.) The abstract is one paragraph (not an introduction) and complete in itself (no reference numbers).
-It should indicate subjects dealt with in the paper and state the objectives of the investigation.
-Newly observed facts and conclusions of the experiment or argument discussed in the paper must be stated in summary form; readers should not have to read the paper to understand the abstract.
-Format the abstract bold, indented 3 picas (1/2 in.) on each side, and separated from the rest of the document by two blank lines.
+% The surface slope is computed according to the method developed in Reference~\cite{scheeres1996}.
+% Due to the small size, and therefore low gravitational attraction, the force at each point on the surface is a combination of the gravitational attraction and the centripetal acceleration.
+% At the center of each face, \( f_i = \begin{bmatrix} f_x & f_y & f_z \end{bmatrix} \), we compute a modified surface acceleration as
+% \begin{align}\label{eq:surface_force}
+%     U_m = \omega^2 \begin{bmatrix} f_x \\ f_y \\ 0 \end{bmatrix} + \begin{bmatrix} U_x \\ U_y \\ U_z \end{bmatrix},
+% \end{align}
+% where \( \omega \in \R^1 \) is the angular velocity of the asteroid and \( U_i \) is computed from~\cref{eq:attraction}.
+% Then the surface slope can be computed from
+% \begin{align}\label{eq:surface_slope}
+%     \cos \parenth{ \pi - \phi } = \frac{\vc{n}_f \cdot U_m}{\norm{U_m}},
+% \end{align}
+% where \( \phi \in \R^1 \) is the surface slope defines the angle between the surface normal \( \vc{n}_f \in \R^3 \) and the force vector at the surface.
+% If \( \phi = \SI{0}{\degree} \) then the force vector and the surface normal are anti-parallel, while \( \phi > \SI{90}{\degree} \) means that a particle on the surface would be thrown off the body as the centripetal force is larger than the gravitational attraction.
 
-\subsection{Nomenclature}
-Papers with many symbols may benefit from a nomenclature list that defines all symbols with units, inserted between the abstract and the introduction.
-If one is used, it must contain all the symbology used in the manuscript, and the definitions should not be repeated in the text.
-In all cases, identify the symbols used if they are not widely recognized in the profession.
-Define acronyms in the text, not in the nomenclature.
+% Additionally, we compute the distance, using~\cref{eq:geodesic_distance}, between the spacecraft state and each face of the asteroid. 
+% Finally, we also assign a random science value to the surface in the form of a two dimensional Gaussian.
+% Utilizing these metric, a landing site is chosen to minimize the surface cost given as
+% \begin{align}\label{eq:surface_cost}
+%     J_l =  J_{\text{distance}} - J_{\text{science}},
+% \end{align}
+% where the surface slope is considered a hard constraint such that any candidate landing site must satisfy \( \phi \leq \phi_m \).
 
-\subsection{Biographies}
-Survey Papers and some Full-Length Papers include author biographies. These biographies are one paragraph each and should use the abstract formatting style.
+% \paragraph{Mesh Refinement}\label{sec:refinement}
 
-\subsection{Footnotes and References}
-Footnotes, where they appear, should be placed above the 1'' margin at the bottom of the page.
-To insert footnotes into the template, use the Insert>Footnote feature from the main menu as necessary.
-Footnotes are formatted automatically in the template, but if another medium is used, should appear in superscript as symbols in the sequence, *, $\dag$, $\ddag$, \S, \P, **, $\dag\dag$, $\ddag\ddag$, \S\S, etc.
+% Once a suitable landing site is selected, the surrounding area is isolated and refined by adding new vertices and faces in the specified area.
+% The goal of refinement, or more generally remeshing, is given a mesh ( or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
+% In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL).
+% This algorithm uses an iterative method which repeatedly splits long edges, collapses short edges, and relocates vertices until all edges are approximately the desired target edge length.
+% % TODO Think about adding PMP 6.12 image here
 
-List and number all references at the end of the paper.
-Corresponding bracketed numbers are used to cite references in the text \cite{vatistas1986reverse}, including citations that are an integral part of the sentence (e.g., ``It is shown in \cite{dornheim1996planetary} that\ldots '') or follow a mathematical expression: ``$A^{2} + B = C$ (Ref.~\cite{terster1997nasa}).'' For multiple citations, separate reference numbers with commas \cite{peyret2012computational,oates1997aerothermodynamics}, or use a dash to show a range \cite{volpe1994techniques,thompsonspacecraft,chi1993fluid}.
-Reference citations in the text should be in numerical order.
+% For example,~\cref{fig:cube_remesh} shows the isotropic remeshing result for the selected faces of a unit cube.
+% The original unit cube is composed of \num{8} vertices and \num{12} faces.
+% The two triangular faces of the visible side of the cube are selected for the isotropic remeshing operation as shown in~\cref{fig:cube_original_mesh}.
+% A target edge length of \num{0.1} is selected for these faces and used to generate~\cref{fig:cube_refine_mesh}.
+% The two large triangular faces are divided into a number of smaller triangular faces.
+% Furthermore, the additional faces are all approximately the same size and preserve the original surface of the cube.
+% After the isotropic remeshing operation the number of vertices has increased from \num{8} to \num{140}.
+% \begin{figure}[htbp]
+%     \centering
+%     \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.25\textwidth]{figures/original_cube.jpg}}~
+%     \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.25\textwidth]{figures/remesh_cube.jpg}}
+%     \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
+% \end{figure}
 
-In the reference list, give all authors' names; do not use ``et al.'' unless there are six authors or more.
-Papers that have not been published should be cited as ``unpublished''; papers that have been submitted or accepted for publication should be cited as ``submitted for publication.'' Private communications and personal website should appear as footnotes rather than in the reference list.
+% In order to demonstrate the multi resolution surface refinement we require a true shape model that contains small scale surface features.
+% In this dissertation, we utilize the true radar shape model of asteroid 4769 Castalia.
+% However, the shape model is not highly detailed as it does not contain small craters or surface features.
+% In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme shown previously to update the surface.
+% The augmented model of Castalia is shown in~\cref{fig:castalia_refinement}.
+% \Cref{fig:castalia_refinement} shows that the increased resolution is required in order to reconstruct these small surface details.
 
-References should be cited according to the standard publication reference style (for examples, see the ``References'' section of this template).
-Never edit titles in references to conform to AIAA style of spellings, abbreviations, etc.
-Names and locations of publishers should be listed; month and year should be included for reports and papers.
-For papers published in translation journals, please give the English citation first, followed by the original foreign language citation.
+\section{Numerical Examples}\label{sec:reconstruction_examples}
 
-\subsection{Figures and Tables}
-Insert tables and figures within your document; they may be either scattered throughout the text or grouped all together at the end of the file.
-Do not insert your figures in text boxes.
-Figures should have no background, borders, or outlines.
-In the \LaTeX{} template, use the ``caption'' command to type caption text.
-Captions are bold with a single tab (no hyphen or other character) between the figure number and figure description.
-See the Table 1 example for table style and column alignment.
-If you wish to center tables that do not fill the width of the page, simply highlight and “grab” the entire table to move it into proper position.
+In this section, we demonstrate the use of the incremental shape reconstruction algorithm.
+The approach is used to iteratively reconstruct the shape of several asteroid given LIDAR measurements.
+We utilize radar shape models of asteroids \num{4769} Castalia and (\num{52760}) \num{1998} \(\text{ML}_{14}\).
+The examples demonstrate the full dynamic simulation of a rigid spacecraft with an autonomous closed loop control scheme to both reconstruct the asteroid shape.
 
-\begin{table}[hbt!]
-\caption{\label{tab:table1} Transitions selected for thermometry}
+The nonlinear controllers described previously are used to control both the translational and rotational states of the vehicle.
+Throughout the simulation the control inputs are computed using the current shape estimate of the asteroid. 
+As measurements are collected, the spacecraft autonomously updates its shape estimate and uses this estimate to compute the control inputs and desired future states.
+These simulations demonstrate the ability of a spacecraft to autonomously explore and maneuver around an unknown small body.
+
+We consider two simulations about asteroids \num{52760} and Castalia.
+The asteroids are assumed to constantly rotate about the \( \vc{f}_3 = \vc{e}_3\) axis according to the parameters given in~\cref{tab:dynamic_asteroids}.
+Furthermore, the state of the asteroid, namely the rotation matrix \( R_A \), is assumed to be known based on ground measurements or previous data.
+\begin{table}[htbp]
     \centering
-\begin{tabular}{lcccccc}
-\hline
-& Transition& & \multicolumn{2}{c}{}\\\cline{2-2}
-Line& $\nu''$& & $J'' $& Frequency, cm$^{-1}$& $FJ$, cm$^{-1}$& $G\nu $, cm$^{-1}$\\\hline
-a& 0& P$_{12}$& 2.5& 44069.416& 73.58& 948.66\\
-b& 1& R$_{2}$& 2.5& 42229.348& 73.41& 2824.76\\
-c& 2& R$_{21}$& 805& 40562.179& 71.37& 4672.68\\
-d& 0& R$_{2}$& 23.5& 42516.527& 1045.85& 948.76\\
-\hline
+    \begin{tabular}{lcc}
+        \toprule
+        Property & \num{4769} Castalia & (\num{52760}) \num{1998} \(\text{ML}_{14}\) \\
+        \midrule
+        Semi-major axes(\si{\kilo\meter}) & \( 0.8065 \times 0.4905 \times 0.413 \) & \( 1.1 \times 1.1 \times 1.1 \) \\
+        Rotational Period (\si{\hour}) & \num{4.095} & \num{14.98} \\
+        Density (\si{\gram\per\centi\meter^3}) & \num{2.1} & \num{2.1} \\
+        Vertices & \num{2048}  & \num{8192} \\
+        Faces & \num{4092} & \num{16320} \\
+        \bottomrule
     \end{tabular}
+    \caption{Asteroid properties for dynamic exploration~\label{tab:dynamic_asteroids}}
 \end{table}
+At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( x_0 = \begin{bmatrix} x_0 & 0 & 0 \end{bmatrix} \si{\kilo\meter} \).
+In addition, at the initial state the spacecraft is orientated such that the \( b_1 \) axis is aligned with the inertial \( e_2 \) axis.
+In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat{e}_3)\).
+The shape reconstruction phase of the simulation is performed over \SI{15000}{\second}, over which time the spacecraft will take LIDAR measurements of the surface at \SI{1}{\hertz}.
+Once the total uncertainty has been reduced sufficiently the spacecraft maneuvers to a ``home'' position aligned with the \( f_1 \) axis of the asteroid.
 
-Line drawings must be clear and sharp.
-Make sure that all lines and graph points are dark and distinct and that lettering is legible; 8- to 10-point type is suitable for artwork that is sized to fit the column width (3 ¼ in.).
-Keep the lettering size and style uniform both within each figure and throughout all of your illustrations.
-Place figure captions below each figure, and limit caption length to 20-25 words.
-If your figure has multiple parts, include the labels “a),” “b),” etc., below and to the left of each part, above the figure caption.
-Please verify that the figures and tables you mention in the text actually exist.
-When citing a figure in the text, use the abbreviation “Fig.” except at the beginning of a sentence.
-Do not abbreviate “Table.” Number each different type of illustration (i.e., figures and tables) sequentially with relation to other illustrations of the same type.
+\paragraph{Asteroid 52760 Reconstruction}
 
-Figure labels must be legible after reduction to column width (preferably 8--10 points after reduction).
+Asteroid (\num{52760}) \num{1998} \(\text{ML}_{14}\) was discovered in \num{1998} and is near Earth asteroid of the Apollo group and classified as a potentially hazardous body.
+The asteroid is roughly spherical with a mean radius of approximately \SI{1}{\kilo\meter}.
+The initial shape estimate is assumed to be spherical with approximately the same number of vertices as the truth model.
+\Cref{fig:52760_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
+Due to the roughly spherical shape of the asteroid large portions of the surface are quickly modified to match the measurements.
+In addition~\cref{fig:52760_weights_reconstruction} displays the vertex uncertainty \( w_i \) as a colormap on the surface. 
+Areas of high uncertainty are denoted in yellow while areas of low uncertainty are in purple/blue.
 
-All tables are numbered consecutively and must be cited in the text; give each table a definitive title.
-Be sure that you have a minimum of two columns (with headings) and two rows to constitute a proper table; otherwise reformat as a displayed list or incorporate the data into the text.
-Plan tables to fit the column width (3 ¼ in.) or the journal page width (7 in.).
-Position a double rule at the top and bottom of each table and single rule under the column headings; do not use shading, border lines, or vertical rules between table columns.
-Position each table in the text close to where it is cited
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_3749.jpg}}%
+    \subcaptionbox{\SI{50}{\percent} of measurements\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_7499.jpg}}
 
-\subsection{Equations}
-Equations are numbered consecutively, with equation numbers in parentheses flush right, as in Eq.~\eqref{sample:equation}.
-Insert a blank line on either side of the equation.
-To insert an equation into the \LaTeX{} document, use the \verb|\begin{equation}...\end{equation}| command environment.
+    \subcaptionbox{\SI{75}{\percent} of measurements\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_11249.jpg}}%
+    \subcaptionbox{\SI{100}{\percent} of measurements\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/mesh_update/52760/truth.jpg}}
+    \caption[Asteroid 52760 shape reconstruction with uncertainty]{Incremental reconstruction of asteroid 52760.
+The images colored according to the shape uncertainty.
+Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:52760_weights_reconstruction}}
+\end{figure}
 
-A sample equation is included here, formatted using the preceding instructions:
+\paragraph{Asteroid 4769 Castalia Reconstruction}
 
-\begin{equation}
-\label{sample:equation}
-\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = [\sigma r_2/(2\mu_0)]\int^{\infty}_0\exp(-\lambda|z_j-z_i|)\lambda^{-1}J_1 (\lambda r_2)J_0 (\lambda r_i\,\lambda {\rm d}\lambda)
-\end{equation}
+Asteroid 4769 Castalia is a small near Earth asteroid of the Apollo group.
+In addition, it is classified as a potentially hazardous object with a closed approach distance of less than \SI{0.05}{\astronomicalunit}.
+Castalia was discovered in \num{1989} and is the first asteroid to be modeled using radar imagery~\cite{hudson1994}.
+Castalia is composed of two distinct lobes suggesting that it is a contact binary of two smaller objects held together by their mutual gravity.
+\Cref{fig:castalia_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
+In addition~\cref{fig:castalia_weights_reconstruction} displays the vertex uncertainty \( w_i \) as a colormap on the surface. 
+Areas of high uncertainty are denoted in yellow while areas of low uncertainty are in purple/blue.
+Within \SI{50}{\percent} of the simulation span the spacecraft is able to achieve an accurate estimate of the true shape of Castalia.
 
-Be sure that symbols in your equation are defined in the Nomenclature or immediately following the equation.
-Also define abbreviations and acronyms the first time they are used in the main text.
-(Very common abbreviations such as AIAA and NASA, do not have to be defined.)
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_3749.jpg}}%
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_7499.jpg}}
 
-\subsection{General Grammar and Preferred Usage}
-Use only one space after periods or colons.
-Hyphenate complex modifiers: ``zero-field-cooled magnetization.'' Insert a zero before decimal points: ``0.25,'' not ``.25.'' Use ``\si{\centi\meter\squared}'' not ``cc.''
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_11249.jpg}}%
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/mesh_update/castalia/truth.jpg}}
+    \caption[Asteroid Castalia shape reconstruction with uncertainty]{Incremental reconstruction of asteroid Castalia.
+The images colored according to the shape uncertainty.
+Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:castalia_weights_reconstruction}}
+\end{figure}
 
-A parenthetical statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within parenthesis.) Use American, not English, spellings (e.g., “color,” not “colour”).
-The serial comma is preferred: “A, B, and C” instead of “A, B and C.”
+\Cref{fig:castalia_metrics} shows the total normalized uncertainty and percent error for the volume estimate. 
+The plots show that the reconstruction converges to an accurate shape estimate after approximately \SI{8000}{\second}.
+In addition, the volume estimate is initially a much larger value but quickly converges to the true value.
+\begin{figure}[htbp]
+    \centering
+    \input{tikz/castalia_metrics.tikz}
+    \caption{Normalized uncertainty and volume percent error for Castalia\label{fig:castalia_metrics}}
+\end{figure}
+The spacecraft autonomously navigates around asteroid Castalia to best minimize the cost function in~\cref{eq:control_cost}.
 
-Be aware of the different meanings of the homophones “affect” (usually a verb) and “effect” (usually a noun), “complement” and “compliment,” “discreet” and “discrete,” “principal” (e.g., “principal investigator”) and “principle” (e.g., “principle of measurement”).
-Do not confuse “imply” and “infer.”
+% \paragraph{Castalia Landing Site Selection}
 
-\section{Conclusion}
-Although a conclusion may review the main points of the paper, it must not replicate the abstract.
-A conclusion might elaborate on the importance of the work or suggest applications and extensions.
-Do not cite references in the conclusion.
-Note that the conclusion section is the last section of the paper to be numbered.
-The appendix (if present), funding information, other acknowledgments, and references are listed without numbers.
+% With an appropriate shape estimate, the spacecraft can autonomously transition from a shape reconstruction to a landing mode.
+% Based on the shape estimate we seek to determine the best location to land. 
+% In reality, any landing site selection would be based on a wide variety of factors and constraints, however we highlight a few which can be determined autonomously and from the shape estimate.
+% The first metric is related to the surface slope which is computed using the completed shape estimate and~\cref{eq:surface_slope}.
+% Areas which violate the slope constraint of \( \phi < \SI{5}{\degree} \) are excluded from further consideration.
+% \begin{figure}[htbp]
+%     \centering
+%     \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/slope.pdf}}%
+%     \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/slope_masked.pdf}}
+%     \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}
+% \end{figure}
+
+% The next metric is related to the distance from the current spacecraft position to all candidate landing sites on the surface.
+% We utilize~\cref{eq:geodesic_distance} to compute a distance metric to the surface.
+% Landing sites which are closer will be considered preferentially over those at a larger distance.
+% \Cref{fig:distance_castalia_both} shows a surface plot of the distance to the surface. 
+% The area immediately beneath the spacecraft has a small cost while those on the opposite side of the asteroid have a much larger cost.
+% \begin{figure}[htbp]
+%     \centering
+%     \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/dist.pdf}}%
+%     \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/dist_masked.pdf}}
+%     \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
+% \end{figure}
+% We can combine~\cref{fig:distance_castalia_both,fig:surface_slope_castalia_both} to determine the best landing site. 
+% The combination of the two is shown in~\cref{fig:landing_site_cost} with the desired landing site shown by the blue marker.
+% \begin{figure}[htbp]
+%     \centering
+%     \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/cost.pdf}
+%     \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
+% \end{figure}
+% After selecting the appropriate landing site we then prepare for landing by collecting more measurements in the region around the landing area.
+
+% \paragraph{Castalia Landing Site Refinement}
+% One key benefit of an in-situ spacecraft is the ability to measure surface features at a much higher resolution than is possible from the ground. 
+% This detail provides a much higher fidelity data source than ground based measurements. 
+% In order to emulate this in the simulation we augment the shape model of Castalia with several small craters and outcroppings as shown in~\cref{fig:castalia_refinement}.
+% However, these small features would be difficult to capture with the current low resolution shape model of approximately \num{4000} faces.
+% The lower number of faces is useful for the evaluation of the polyhedron potential model, it is not ideal for the capture of minute surface features. 
+% As a result, we utilize the isotropic remeshing operation described previously to selectively increase the fidelity in the region about the desired landing site.
+% \Cref{fig:castalia_refine_density} shows that the vertex density increases by approximately an order of magnitude in region immediately surround the landing site.
+% \begin{figure}[htbp]
+%     \centering
+%     \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/density.pdf}}%
+%     \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/density.pdf}}
+%     \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
+% \end{figure}
+
+% The increased number of faces and vertices in the landing area allows for the capture of the small surface features.
+% \Cref{fig:castalia_refinement} shows that given LIDAR measurements alone and the shape reconstruction algorithm that the small features are effectively estimated.
+% \begin{figure}[htbp]
+%     \centering
+%     \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_true.jpg}}%
+%     \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_est.jpg}}
+%     \caption{Asteroid Castalia with augmented with additional surface features~\label{fig:castalia_refinement}}
+% \end{figure}
+
+\paragraph{Castalia Vertical Descent}
+
+The final phase of the simulation is to utilize the estimated shape model and vertically descend to the desired landing site. 
+This is accomplished using the closed loop control of the vehicle and a trajectory which transitions from the home position to the surface over \SI{3600}{\second}.
+The landing trajectory, using the estimated shape, is visualized in the asteroid frame in~\cref{fig:castalia_landing}.
+During the vertical descent the vehicle is able to accurately track the desired trajectory using the estimated shape to compute the gravitational potential.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/asteroid_trajectory.jpg}
+    \caption{Vertical descent onto 4769 Castalia~\label{fig:castalia_landing}}
+\end{figure}
+
+\section{Conclusions}
+
+This paper developed a Bayesian update scheme to reconstruct the shape of a small body from range measurements. 
+The approach allows for a local update operation that is able to reconstruct the shape in real time. 
+This is in contrast to standard shape reconstruction algorithms which operate over the entire surface and require signification computational resources.
+Next, an optimal guidance scheme is derived which determines the desired state to best update the shape estimate. 
+This allows for a spacecraft to autonomously maneuver and reconstruct the shape of a small body without operator intervention.
+% Finally, a mixed resolution shape representation is presented to allow for an increased fidelity in a specific region of the asteroid.
+% This allows for a much greater shape accuracy in a local area while avoiding the computational costs associated with a uniformly high resolution mesh.
+Several numerical examples were presented which demonstrates the approach on a number of real asteroids.
 
@@
 
-\section*{Acknowledgments}
-An Acknowledgments section, if used, \textbf{immediately precedes} the References.
-Individuals other than the authors who contributed to the underlying research may be acknowledged in this section.
-The use of special facilities and other resources also may be acknowledged.
+\section{Acknowledgement}
+This research is supported in part by NSF under the grant CMMI-1335008.
 
-\bibliography{sample}
+\bibliography{library}
 

### 2018-10-23 manuscript.tex
Add back landing sectino

@@
 
-% \section{Multi-resolution Landing Area Refinement}\label{sec:landing_refinement}
+\section{Multi-resolution Landing Area Refinement}\label{sec:landing_refinement}
 
-% The shape update approach presented is designed with autonomous operations in mind. 
-% It is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
-% Furthermore, the original mesh is uniformly distributed and as a result many small topological features such as rocks or small craters are not be captured by the shape model. 
-% However, these small features are critical for surface operations and safe landings.
-% In addition, it would be computationally prohibitive to have a uniformly high resolution mesh.
-% In this section, we extend the previous shape update approach to enable a much higher fidelity in a specific location.
+The shape update approach presented is designed with autonomous operations in mind. 
+It is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
+Furthermore, the original mesh is uniformly distributed and as a result many small topological features such as rocks or small craters are not be captured by the shape model. 
+However, these small features are critical for surface operations and safe landings.
+In addition, it would be computationally prohibitive to have a uniformly high resolution mesh.
+In this section, we extend the previous shape update approach to enable a much higher fidelity in a specific location.
 
-% Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
-% As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
-% The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
-% As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
-% However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.
+Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
+As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
+The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
+As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
+However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.
 
-% The selection of a landing site will typically require a vast quantity of data and weigh a multitude of possible metrics, such as scientific value, hardware constraints, timing and communication limits, or safety considerations.
-% In our analysis we consider the surface slope, the distance to the surface, and a fictitious science metric in order to determine the best landing site based on the complete shape estimate.
-% This approach allows for a spacecraft to autonomously select and land on small body.
+The selection of a landing site will typically require a vast quantity of data and weigh a multitude of possible metrics, such as scientific value, hardware constraints, timing and communication limits, or safety considerations.
+In our analysis we consider the surface slope, the distance to the surface, and a fictitious science metric in order to determine the best landing site based on the complete shape estimate.
+This approach allows for a spacecraft to autonomously select and land on small body.
 
-% The surface slope is computed according to the method developed in Reference~\cite{scheeres1996}.
-% Due to the small size, and therefore low gravitational attraction, the force at each point on the surface is a combination of the gravitational attraction and the centripetal acceleration.
-% At the center of each face, \( f_i = \begin{bmatrix} f_x & f_y & f_z \end{bmatrix} \), we compute a modified surface acceleration as
-% \begin{align}\label{eq:surface_force}
-%     U_m = \omega^2 \begin{bmatrix} f_x \\ f_y \\ 0 \end{bmatrix} + \begin{bmatrix} U_x \\ U_y \\ U_z \end{bmatrix},
-% \end{align}
-% where \( \omega \in \R^1 \) is the angular velocity of the asteroid and \( U_i \) is computed from~\cref{eq:attraction}.
-% Then the surface slope can be computed from
-% \begin{align}\label{eq:surface_slope}
-%     \cos \parenth{ \pi - \phi } = \frac{\vc{n}_f \cdot U_m}{\norm{U_m}},
-% \end{align}
-% where \( \phi \in \R^1 \) is the surface slope defines the angle between the surface normal \( \vc{n}_f \in \R^3 \) and the force vector at the surface.
-% If \( \phi = \SI{0}{\degree} \) then the force vector and the surface normal are anti-parallel, while \( \phi > \SI{90}{\degree} \) means that a particle on the surface would be thrown off the body as the centripetal force is larger than the gravitational attraction.
+The surface slope is computed according to the method developed in Reference~\cite{scheeres1996}.
+Due to the small size, and therefore low gravitational attraction, the force at each point on the surface is a combination of the gravitational attraction and the centripetal acceleration.
+At the center of each face, \( f_i = \begin{bmatrix} f_x & f_y & f_z \end{bmatrix} \), we compute a modified surface acceleration as
+\begin{align}\label{eq:surface_force}
+    U_m = \omega^2 \begin{bmatrix} f_x \\ f_y \\ 0 \end{bmatrix} + \begin{bmatrix} U_x \\ U_y \\ U_z \end{bmatrix},
+\end{align}
+where \( \omega \in \R^1 \) is the angular velocity of the asteroid and \( U_i \) is computed from~\cref{eq:attraction}.
+Then the surface slope can be computed from
+\begin{align}\label{eq:surface_slope}
+    \cos \parenth{ \pi - \phi } = \frac{\vc{n}_f \cdot U_m}{\norm{U_m}},
+\end{align}
+where \( \phi \in \R^1 \) is the surface slope defines the angle between the surface normal \( \vc{n}_f \in \R^3 \) and the force vector at the surface.
+If \( \phi = \SI{0}{\degree} \) then the force vector and the surface normal are anti-parallel, while \( \phi > \SI{90}{\degree} \) means that a particle on the surface would be thrown off the body as the centripetal force is larger than the gravitational attraction.
 
-% Additionally, we compute the distance, using~\cref{eq:geodesic_distance}, between the spacecraft state and each face of the asteroid. 
-% Finally, we also assign a random science value to the surface in the form of a two dimensional Gaussian.
-% Utilizing these metric, a landing site is chosen to minimize the surface cost given as
-% \begin{align}\label{eq:surface_cost}
-%     J_l =  J_{\text{distance}} - J_{\text{science}},
-% \end{align}
-% where the surface slope is considered a hard constraint such that any candidate landing site must satisfy \( \phi \leq \phi_m \).
+Additionally, we compute the distance, using~\cref{eq:geodesic_distance}, between the spacecraft state and each face of the asteroid. 
+Finally, we also assign a random science value to the surface in the form of a two dimensional Gaussian.
+Utilizing these metric, a landing site is chosen to minimize the surface cost given as
+\begin{align}\label{eq:surface_cost}
+    J_l =  J_{\text{distance}} - J_{\text{science}},
+\end{align}
+where the surface slope is considered a hard constraint such that any candidate landing site must satisfy \( \phi \leq \phi_m \).
 
-% \paragraph{Mesh Refinement}\label{sec:refinement}
+\paragraph{Mesh Refinement}\label{sec:refinement}
 
-% Once a suitable landing site is selected, the surrounding area is isolated and refined by adding new vertices and faces in the specified area.
-% The goal of refinement, or more generally remeshing, is given a mesh ( or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
-% In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL).
-% This algorithm uses an iterative method which repeatedly splits long edges, collapses short edges, and relocates vertices until all edges are approximately the desired target edge length.
-% % TODO Think about adding PMP 6.12 image here
+Once a suitable landing site is selected, the surrounding area is isolated and refined by adding new vertices and faces in the specified area.
+The goal of refinement, or more generally remeshing, is given a mesh ( or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
+In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL).
+This algorithm uses an iterative method which repeatedly splits long edges, collapses short edges, and relocates vertices until all edges are approximately the desired target edge length.
+% TODO Think about adding PMP 6.12 image here
 
-% For example,~\cref{fig:cube_remesh} shows the isotropic remeshing result for the selected faces of a unit cube.
-% The original unit cube is composed of \num{8} vertices and \num{12} faces.
-% The two triangular faces of the visible side of the cube are selected for the isotropic remeshing operation as shown in~\cref{fig:cube_original_mesh}.
-% A target edge length of \num{0.1} is selected for these faces and used to generate~\cref{fig:cube_refine_mesh}.
-% The two large triangular faces are divided into a number of smaller triangular faces.
-% Furthermore, the additional faces are all approximately the same size and preserve the original surface of the cube.
-% After the isotropic remeshing operation the number of vertices has increased from \num{8} to \num{140}.
-% \begin{figure}[htbp]
-%     \centering
-%     \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.25\textwidth]{figures/original_cube.jpg}}~
-%     \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.25\textwidth]{figures/remesh_cube.jpg}}
-%     \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
-% \end{figure}
+For example,~\cref{fig:cube_remesh} shows the isotropic remeshing result for the selected faces of a unit cube.
+The original unit cube is composed of \num{8} vertices and \num{12} faces.
+The two triangular faces of the visible side of the cube are selected for the isotropic remeshing operation as shown in~\cref{fig:cube_original_mesh}.
+A target edge length of \num{0.1} is selected for these faces and used to generate~\cref{fig:cube_refine_mesh}.
+The two large triangular faces are divided into a number of smaller triangular faces.
+Furthermore, the additional faces are all approximately the same size and preserve the original surface of the cube.
+After the isotropic remeshing operation the number of vertices has increased from \num{8} to \num{140}.
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.25\textwidth]{figures/original_cube.jpg}}~
+    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.25\textwidth]{figures/remesh_cube.jpg}}
+    \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
+\end{figure}
 
-% In order to demonstrate the multi resolution surface refinement we require a true shape model that contains small scale surface features.
-% In this dissertation, we utilize the true radar shape model of asteroid 4769 Castalia.
-% However, the shape model is not highly detailed as it does not contain small craters or surface features.
-% In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme shown previously to update the surface.
-% The augmented model of Castalia is shown in~\cref{fig:castalia_refinement}.
-% \Cref{fig:castalia_refinement} shows that the increased resolution is required in order to reconstruct these small surface details.
+In order to demonstrate the multi resolution surface refinement we require a true shape model that contains small scale surface features.
+In this dissertation, we utilize the true radar shape model of asteroid 4769 Castalia.
+However, the shape model is not highly detailed as it does not contain small craters or surface features.
+In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme shown previously to update the surface.
+The augmented model of Castalia is shown in~\cref{fig:castalia_refinement}.
+\Cref{fig:castalia_refinement} shows that the increased resolution is required in order to reconstruct these small surface details.
 

### 2018-10-25 manuscript.tex
Update author

@@
 
-\author{Shankar Kulumani \footnote{PhD, Mechanical and Aerospace Engineering, Address/Mail Stop, and AIAA Member Grade (if any) for first author.} and Taeyoung Lee \footnote{Associate Professor, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for second author.}}
+\author{Shankar Kulumani \footnote{PhD, Mechanical and Aerospace Engineering, \href{skulumani@gwu.edu}{mailto:skulumani@gwu.edu}}
+and
+Taeyoung Lee \footnote{Associate Professor, Mechanical and Aerospace Engineering, \href{tylee@gwu.edu}{mailto:tylee@gwu.edu}}}
 \affil{Goerge Washington University, Washington, DC, 20052}

### 2018-11-04 manuscript.tex
Add todo
Add another todo
Correct typo
Add new material from dissertation

@@
 
+% TODO Think about adding current affiliation as a note, need to ask company
 \author{Shankar Kulumani \footnote{PhD, Mechanical and Aerospace Engineering, \href{skulumani@gwu.edu}{mailto:skulumani@gwu.edu}}
@@
 Taeyoung Lee \footnote{Associate Professor, Mechanical and Aerospace Engineering, \href{tylee@gwu.edu}{mailto:tylee@gwu.edu}}}
-\affil{Goerge Washington University, Washington, DC, 20052}
+\affil{George Washington University, Washington, DC, 20052}
 
@@
 
+% TODO Add more plots from dissertation. All the uncertainty and volume plots
+% TODO Show examples with the other asteroids
+% TODO Mention that the software to do this is available online?
 In this section, we demonstrate the use of the incremental shape reconstruction algorithm.
@@
 
+\subsection{Shape Reconstruction}\label{sec:kinematic_exploration}
+
+The results in this section utilize a kinematics only model of the spacecraft and dynamics instead of the full dynamic simulation. 
+We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction.
+\Cref{tab:kinematic_asteroids} lists the true shape model parameters of asteroids Geographos and Golevka.
+\begin{table}[htbp]
+    \centering
+    \begin{tabular}{lccc}
+        \toprule
+        Asteroid & Semi-major axes (\si{\kilo\meter}) & Vertices & Faces\\
+        \midrule
+        \num{1620} Geographos & \( 2.5 \times 1.0 \times 1.05 \) & \num{8192} & \num{16380}  \\
+        \num{6489} Golevka & \( 0.53 \times 0.53 \times 0.53 \)  & \num{2048} & \num{4092} \\
+        \bottomrule
+    \end{tabular} 
+    \caption{Asteroid properties for kinematic only exploration~\label{tab:kinematic_asteroids}}
+\end{table}
+The spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
+The simulations begin with an triaxial ellipsoid mesh that is sized to match the semi-major axes of each asteroid.
+With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
+\Gls{lidar} measurements are generated until the total uncertainty
+\begin{align*}
+    \sum_i w_i,
+\end{align*}
+is sufficiently small.
+In addition, we compute the volume of the estimate shape throughout the simulation using the algorithm presented in~\cref{sec:polyhedron_volume}.
+
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/geographos/partial_0.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_1872.jpg}}
+
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_3745.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_5617.jpg}}
+
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_7489.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/truth.jpg}}
+    \caption[Asteroid Geographos incremental reconstruction]{Incremental reconstruction of asteroid Geographos~\label{fig:geographos_reconstruction}}
+\end{figure}
+
+\num{1620} Geographos is a highly elongated stony asteroid of the Apollo group.
+Discovered in \num{1951}, Geographos is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
+\Cref{fig:geographos_reconstruction} shows the shape reconstruction for asteroid Geographos at several distinct points during the process.
+Comparing~\cref{fig:geographos_partial_100,fig:geographos_truth} shows that the final shape closely matches the true radar model.
+In~\cref{fig:geographos_metrics} we display the vertex uncertainty and mesh volume as a function of time.
+The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.
+
+\begin{figure}[htbp]
+    \centering
+    \input{tikz/geographos_metrics.tikz}
+    \caption{Normalized uncertainty and volume percent error for Geographos\label{fig:geographos_metrics}}
+\end{figure}
+
+\num{6489} Golevka is a small angular shaped asteroid of the Apollo group.
+Discovered in \num{1995}, Golevka is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
+\Cref{fig:golevka_reconstruction} shows the shape reconstruction for asteroid Golevka at several distinct points during the process.
+Comparing~\cref{fig:golevka_partial_100,fig:golevka_truth} shows that the final shape closely matches the true radar model.
+In~\cref{fig:golevka_metrics} we display the vertex uncertainty and mesh volume as a function of time.
+
+\begin{figure}[htbp]
+    \centering
+    \input{tikz/golevka_metrics.tikz}
+    \caption{Normalized uncertainty and volume percent error for Golevka\label{fig:golevka_metrics}}
+\end{figure}
+
+The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.
+It is interesting to note that the reconstruction of Golevka achieves an accurate shape reconstruction in a much smaller amount of time as compared to Geographos.
+This is primarily due to the smaller size of Golevka and the relatively spherical shape of the body in contrast to the highly elliptical shape of Geographos.
+
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_0.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_1321.jpg}}\\%
+
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_2643.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_3964.jpg}}\\%
+
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_5285.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/truth.jpg}}
+    \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
+\end{figure}
 \paragraph{Asteroid 52760 Reconstruction}
@@
 
-% \paragraph{Castalia Landing Site Selection}
+\paragraph{Castalia Landing Site Selection}
 
-% With an appropriate shape estimate, the spacecraft can autonomously transition from a shape reconstruction to a landing mode.
-% Based on the shape estimate we seek to determine the best location to land. 
-% In reality, any landing site selection would be based on a wide variety of factors and constraints, however we highlight a few which can be determined autonomously and from the shape estimate.
-% The first metric is related to the surface slope which is computed using the completed shape estimate and~\cref{eq:surface_slope}.
-% Areas which violate the slope constraint of \( \phi < \SI{5}{\degree} \) are excluded from further consideration.
-% \begin{figure}[htbp]
-%     \centering
-%     \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/slope.pdf}}%
-%     \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/slope_masked.pdf}}
-%     \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}
-% \end{figure}
+With an appropriate shape estimate, the spacecraft can autonomously transition from a shape reconstruction to a landing mode.
+Based on the shape estimate we seek to determine the best location to land. 
+In reality, any landing site selection would be based on a wide variety of factors and constraints, however we highlight a few which can be determined autonomously and from the shape estimate.
+The first metric is related to the surface slope which is computed using the completed shape estimate and~\cref{eq:surface_slope}.
+Areas which violate the slope constraint of \( \phi < \SI{5}{\degree} \) are excluded from further consideration.
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/slope.pdf}}%
+    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/slope_masked.pdf}}
+    \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}
+\end{figure}
 
-% The next metric is related to the distance from the current spacecraft position to all candidate landing sites on the surface.
-% We utilize~\cref{eq:geodesic_distance} to compute a distance metric to the surface.
-% Landing sites which are closer will be considered preferentially over those at a larger distance.
-% \Cref{fig:distance_castalia_both} shows a surface plot of the distance to the surface. 
-% The area immediately beneath the spacecraft has a small cost while those on the opposite side of the asteroid have a much larger cost.
-% \begin{figure}[htbp]
-%     \centering
-%     \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/dist.pdf}}%
-%     \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/dist_masked.pdf}}
-%     \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
-% \end{figure}
-% We can combine~\cref{fig:distance_castalia_both,fig:surface_slope_castalia_both} to determine the best landing site. 
-% The combination of the two is shown in~\cref{fig:landing_site_cost} with the desired landing site shown by the blue marker.
-% \begin{figure}[htbp]
-%     \centering
-%     \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/cost.pdf}
-%     \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
-% \end{figure}
-% After selecting the appropriate landing site we then prepare for landing by collecting more measurements in the region around the landing area.
+The next metric is related to the distance from the current spacecraft position to all candidate landing sites on the surface.
+We utilize~\cref{eq:geodesic_distance} to compute a distance metric to the surface.
+Landing sites which are closer will be considered preferentially over those at a larger distance.
+\Cref{fig:distance_castalia_both} shows a surface plot of the distance to the surface. 
+The area immediately beneath the spacecraft has a small cost while those on the opposite side of the asteroid have a much larger cost.
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/dist.pdf}}%
+    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/dist_masked.pdf}}
+    \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
+\end{figure}
+We can combine~\cref{fig:distance_castalia_both,fig:surface_slope_castalia_both} to determine the best landing site. 
+The combination of the two is shown in~\cref{fig:landing_site_cost} with the desired landing site shown by the blue marker.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/cost.pdf}
+    \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
+\end{figure}
+After selecting the appropriate landing site we then prepare for landing by collecting more measurements in the region around the landing area.
 
-% \paragraph{Castalia Landing Site Refinement}
-% One key benefit of an in-situ spacecraft is the ability to measure surface features at a much higher resolution than is possible from the ground. 
-% This detail provides a much higher fidelity data source than ground based measurements. 
-% In order to emulate this in the simulation we augment the shape model of Castalia with several small craters and outcroppings as shown in~\cref{fig:castalia_refinement}.
-% However, these small features would be difficult to capture with the current low resolution shape model of approximately \num{4000} faces.
-% The lower number of faces is useful for the evaluation of the polyhedron potential model, it is not ideal for the capture of minute surface features. 
-% As a result, we utilize the isotropic remeshing operation described previously to selectively increase the fidelity in the region about the desired landing site.
-% \Cref{fig:castalia_refine_density} shows that the vertex density increases by approximately an order of magnitude in region immediately surround the landing site.
-% \begin{figure}[htbp]
-%     \centering
-%     \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/density.pdf}}%
-%     \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/density.pdf}}
-%     \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
-% \end{figure}
+\paragraph{Castalia Landing Site Refinement}
+One key benefit of an in-situ spacecraft is the ability to measure surface features at a much higher resolution than is possible from the ground. 
+This detail provides a much higher fidelity data source than ground based measurements. 
+In order to emulate this in the simulation we augment the shape model of Castalia with several small craters and outcroppings as shown in~\cref{fig:castalia_refinement}.
+However, these small features would be difficult to capture with the current low resolution shape model of approximately \num{4000} faces.
+The lower number of faces is useful for the evaluation of the polyhedron potential model, it is not ideal for the capture of minute surface features. 
+As a result, we utilize the isotropic remeshing operation described previously to selectively increase the fidelity in the region about the desired landing site.
+\Cref{fig:castalia_refine_density} shows that the vertex density increases by approximately an order of magnitude in region immediately surround the landing site.
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/density.pdf}}%
+    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/density.pdf}}
+    \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
+\end{figure}
 
-% The increased number of faces and vertices in the landing area allows for the capture of the small surface features.
-% \Cref{fig:castalia_refinement} shows that given LIDAR measurements alone and the shape reconstruction algorithm that the small features are effectively estimated.
-% \begin{figure}[htbp]
-%     \centering
-%     \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_true.jpg}}%
-%     \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_est.jpg}}
-%     \caption{Asteroid Castalia with augmented with additional surface features~\label{fig:castalia_refinement}}
-% \end{figure}
+The increased number of faces and vertices in the landing area allows for the capture of the small surface features.
+\Cref{fig:castalia_refinement} shows that given LIDAR measurements alone and the shape reconstruction algorithm that the small features are effectively estimated.
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_true.jpg}}%
+    \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_est.jpg}}
+    \caption{Asteroid Castalia with augmented with additional surface features~\label{fig:castalia_refinement}}
+\end{figure}
 

### 2018-11-09 manuscript.tex
Fix compiliation of paper

@@
 is sufficiently small.
-In addition, we compute the volume of the estimate shape throughout the simulation using the algorithm presented in~\cref{sec:polyhedron_volume}.
+In addition, we compute the volume of the estimate shape throughout the simulation using the algorithm presented here. 
+% TODO Add polyhedron volume algorithm
 

### 2018-11-13 manuscript.tex
Add extra sentence to abstract and fix email

@@
 % TODO Think about adding current affiliation as a note, need to ask company
-\author{Shankar Kulumani \footnote{PhD, Mechanical and Aerospace Engineering, \href{skulumani@gwu.edu}{mailto:skulumani@gwu.edu}}
+\author{Shankar Kulumani \footnote{PhD, Mechanical and Aerospace Engineering, \href{mailto:skulumani@gwu.edu}{skulumani@gwu.edu}}
 and
-Taeyoung Lee \footnote{Associate Professor, Mechanical and Aerospace Engineering, \href{tylee@gwu.edu}{mailto:tylee@gwu.edu}}}
+Taeyoung Lee \footnote{Associate Professor, Mechanical and Aerospace Engineering, \href{mailto:tylee@gwu.edu}{tylee@gwu.edu}}}
 \affil{George Washington University, Washington, DC, 20052}
@@
     This shape model is then used in a nonlinear controller to track a desired trajectory about the asteroid.
-    % Finally, a multi resolution approach is presented which enables for a higher fidelity shape representation in a specified location while avoiding the inherent burdens of a uniformly high resolution mesh.
+    Finally, a multi resolution approach is presented which enables for a higher fidelity shape representation in a specified location while avoiding the inherent burdens of a uniformly high resolution mesh.
     This approach enables for an accurate shape determination around a potential landing site.

### 2018-11-26 manuscript.tex
adjust figure sizes

@@
     \centering
-    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.25\textwidth]{figures/original_cube.jpg}}~
-    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.25\textwidth]{figures/remesh_cube.jpg}}
+    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.45\textwidth]{figures/original_cube.jpg}}~
+    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.45\textwidth]{figures/remesh_cube.jpg}}
     \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_0.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_1321.jpg}}\\%
+    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_0.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_1321.jpg}}\\%
 
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_2643.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_3964.jpg}}\\%
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_2643.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_3964.jpg}}\\%
 
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_5285.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/truth.jpg}}
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_5285.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/truth.jpg}}
     \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_3749.jpg}}%
-    \subcaptionbox{\SI{50}{\percent} of measurements\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_7499.jpg}}
+    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_3749.jpg}}%
 
-    \subcaptionbox{\SI{75}{\percent} of measurements\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_11249.jpg}}%
-    \subcaptionbox{\SI{100}{\percent} of measurements\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_14998.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/mesh_update/52760/truth.jpg}}
+    \subcaptionbox{\SI{50}{\percent} of measurements\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_7499.jpg}}
+    \subcaptionbox{\SI{75}{\percent} of measurements\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_11249.jpg}}%
+
+    \subcaptionbox{\SI{100}{\percent} of measurements\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/52760/truth.jpg}}
     \caption[Asteroid 52760 shape reconstruction with uncertainty]{Incremental reconstruction of asteroid 52760.
@@
     \centering
-    \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_true.jpg}}%
-    \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_est.jpg}}
+    \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.3\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_true.jpg}}%
+    \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.3\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_est.jpg}}
     \caption{Asteroid Castalia with augmented with additional surface features~\label{fig:castalia_refinement}}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/asteroid_trajectory.jpg}
+    \includegraphics[width=0.8\textwidth]{figures/dynamic_exploration/castalia/land/asteroid_trajectory.jpg}
     \caption{Vertical descent onto 4769 Castalia~\label{fig:castalia_landing}}

### 2018-12-13 manuscript.tex
revised intro

@@
 Taeyoung Lee \footnote{Associate Professor, Mechanical and Aerospace Engineering, \href{mailto:tylee@gwu.edu}{tylee@gwu.edu}}}
-\affil{George Washington University, Washington, DC, 20052}
+\affil{The George Washington University, Washington, DC, 20052}
 
@@
 \begin{abstract}
-    Knowledge of the shape of an asteroid is crucial for spacecraft operations.
-    The standard method of determining the gravitational potential, through the use of a polyhedron potential model, is dependent on the shape model.
-    Furthermore, accurate landing or low altitude operations requires accurate knowledge of the surface topology. 
-    The typical approach to shape determination requires an extensive ``mapping'' phase of the mission over which extensive measurements are collected and transmitted for Earth-based processing.
-    Instead, we present an efficient method for estimating the shape of an asteroid in real time.
-    Range measurements of the surface are used to incrementally correct an initial shape estimate according to Bayesian framework. 
-    Then, an optimal guidance scheme is proposed to control the vantage point of the range sensor to construct a more accurate model of the asteroid shape. 
+    Constructing of the precise shape of an asteroid is critical for spacecraft operations, as the gravitational potential is determined by spatial mass distribution.
+    For example, the standard method of determining the gravitational potential of an asteroid, through the use of a polyhedron potential model, is directly dependent on the shape model.
+    Furthermore, safe landing or close-proximity operations requires accurate knowledge of the surface topology. 
+    The typical approach to shape determination requires a prolonged ``mapping'' phase of the mission over which extensive measurements are collected and transmitted for Earth-based processing.
+    This paper presents a set of approaches to explore an unknown asteroid with onboard calculations, and to land on its surface area selected in an optimal fashion. 
+    The main motivation is to avoid the extended period of mapping phase or preliminary ground observations that are commonly required in spacecraft mission around asteroids. 
+    First, range measurements from spacecraft to the surface are used to incrementally correct an initial shape estimate according to the Bayesian framework. 
+    Then, an optimal guidance scheme is proposed to control the vantage point of the range sensor to construct a complete 3D model of the asteroid shape. 
     This shape model is then used in a nonlinear controller to track a desired trajectory about the asteroid.
-    Finally, a multi resolution approach is presented which enables for a higher fidelity shape representation in a specified location while avoiding the inherent burdens of a uniformly high resolution mesh.
+    Finally, a multi resolution approach is presented to construct a higher fidelity shape representation in a specified location while avoiding the inherent burdens of a uniformly high resolution mesh.
     This approach enables for an accurate shape determination around a potential landing site.
@@
 % we want to generate the shape in real time and then use this shape for updated and better control
-In this paper, we develop a method to compute the surface shape of an asteroid from range measurements.
+This paper presents three techniques to explore an asteroid without need for an extended period of mapping phase or ground based measurements. 
+First, we develop a method to compute the surface shape of an asteroid from onborad range measurements.
+Assuming that a meshed model of an initial estimate, such as an ellipsoidal shape, is available, the radius of any vertex in the measured area is adjusted according to the measurements. 
+This is completed in a stochastic fashion where the degree of confidence in the current shape is compared with the level of measurement noise. 
 Our approach is able to operate in real time and incrementally update the shape model of an asteroid as new range measurements are collected.
 This approach allows for the shape to be continually updated as range measurements are used to locally modify the shape estimate.
-Furthermore, this updated shape is then used in a nonlinear controller to enable the tracking of a landing trajectory to the surface.
-In contrast to previous work, we explicitly consider the gravitational coupling between orbit and attitude dynamics.
-Furthermore, instead of computationally expensive surface reconstruction methods, we present a straightforward and conceptually simple method to enable real time shape updates.
+This technique is verified by numerical examples of shape construction for asteroids Geographos and Golevka.
+
+Next, we present an optimal guidance scheme to construct a complete and accurate shape model of an asteroid. 
+The motivation is to actively control the relative position of the spacecraft such that the range sensor covers the surface area from every perspective. 
+Utilizing the stochastic formulation of the above shape construction method, this is addressed by an optimization to find the pose of the spacecraft that minimizes the degree of uncertainties in the shape model.
+
+Finally, we consider the scenario of landing on the surface of an asteroid. 
+Once a complete shape model is constructed, we study a landing site selection problem. 
+For safety concern, the area with higher slope is excluded. 
+Within the low slope region, a landing site is selected to minimize a control cost subtracted by a measure of scientific interests. 
+Once the landing site is selected, the nearby area is mapped with a higher resolution to create a detailed topological map.  
+The proposed multi resolution mapping yields a high fidelity map without the computational burden of a uniformly high resolution mesh.
+
+The optimal guidance and multi resolution mapping schemes are illustrated by dynamic simulation of landing on the asteroid Castalia. 
+During this simulation, This updated shape model is then used to in a nonlinear controller to track a desired state trajectory for the dynamics of a rigid body spacecraft.
+The dynamics are developed on the nonlinear manifold of rigid body motions, namely the special Euclidean group.
+This formulation is based on an intrinsic geometric description of the motion and accurately captures the coupling between orbit and attitude dynamics.
 
@@
 This type of approach allows for the spacecraft to maneuver and land on the asteroid immediately upon arrival rather than spending several months mapping the surface.
-This updated shape model is then used to in a nonlinear controller to track a desired state trajectory for the dynamics of a rigid body spacecraft.
-The dynamics are developed on the nonlinear manifold of rigid body motions, namely the special euclidean group.
-This formulation is based on an intrinsic geometric description of the motion and accurately captures the coupling between orbit and attitude dynamics. 
-The presented approach allows for a spacecraft to transition directly from arrival to the surface while reconstructing the surface shape in real time.
 

### 2018-12-13 manuscript.tex
revised sec 2

@@
 % \setlength\LTleft{0pt}
+
+\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent
+\marginpar{\textsc{ToDo}} \framebox{\begin{minipage}[c]{0.95
+\textwidth} \tt #1 \end{minipage}}\vspace{5 mm}\par}
+%\newcommand{\todo}[1]{}
 
@@
 Without loss of generality, we define body fixed frames for both the spacecraft and asteroid, which are aligned with the principle axes of each body and originate at their respective center of mass. 
+The axes of the body fixed frame for the spacecraft are denoted by $\{b_1,b_2,b_3\}$, and those for the asteroid are denoted by $\{f_1,f_2,f_3\}$. 
+We also define the inertial frame, whose axes are denoted by $\{e_1,e_2,e_3\}$.
+
 The kinematics of the dumbbell and asteroid are described in the inertial frame by
 \begin{itemize}
-    \item \( \vc{x} \) - the position of the center of mass of the dumbbell spacecraft represented in the inertial frame, \( \vc{e}_i\),
-    \item \( R \) - the rotation matrix which transforms vectors defined in the spacecraft fixed frame, \( \vc{b}_i \), to the inertial frame, \( \vc{e}_i \),
-    \item \( \vc{\Omega} \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame, \( \vc{b}_i \), and
-    \item \( R_A \) - the rotation matrix which transforms vectors defined in the asteroid fixed frame, \( \vc{f}_i \), to the inertial frame, \( \vc{e}_i \).
+    \item \( \vc{x}\in\Re^3 \) - the position of the center of mass of the  spacecraft represented in the inertial frame, \( \vc{e}_i\),
+    \item \( R\in\SO \) - the rotation matrix which transforms vectors defined in the spacecraft fixed frame, \( \vc{b}_i \), to the inertial frame, \( \vc{e}_i \),
+    \item \( \vc{\Omega}\in\Re \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame, \( \vc{b}_i \), and
+    \item \( R_A\in SO \) - the rotation matrix which transforms vectors defined in the asteroid fixed frame, \( \vc{f}_i \), to the inertial frame, \( \vc{e}_i \).
 \end{itemize}
@@
 
+\todo{Add the schematic of dumbbell that you created for the dissertation?}
+
 \subsection{Spacecraft Dynamic Model}
+
+\todo{Define every variable, $m_1,m_2,\rho_1,\ldots$. }
+
 Using Hamilton's principle one can derive the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
@@
 \end{align}
-where the polyhedron potential is defined as 
-\begin{align}
-    U(\vc{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vc{r}_e \cdot \vc{E}_e \cdot \vc{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vc{r}_f \cdot \vc{F}_f \cdot \vc{r}_f \cdot \omega_f,
-\end{align}
-and \( \vc{r}_e\) and \(\vc{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
-The position of each mass \(m_i\) of the dumbbell is defined in the dumbbell fixed frame by the vector \(\vb{\rho}_i\).
+In the above equations, the gravitational potential is denoted by $U$, which is computed by a polyhedron model as described in the subsequent section.
+
+%where the polyhedron potential is defined as 
+%\begin{align}
+    %U(\vc{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vc{r}_e \cdot \vc{E}_e \cdot \vc{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vc{r}_f \cdot \vc{F}_f \cdot \vc{r}_f \cdot \omega_f,
+%\end{align}
+%and \( \vc{r}_e\) and \(\vc{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
+%The position of each mass \(m_i\) of the dumbbell is defined in the dumbbell fixed frame by the vector \(\vb{\rho}_i\).
 

### 2018-12-13 manuscript.tex
revised sec 3

@@
 Furthermore, the number of vertices in the estimate can be scaled according to the desired final accuracy or computational capabilities.
+In this section, we present a stochastic formulation to update the initial estimate of the shape incrementally based on range measurements from spacecraft.
+
+\subsection{Range Measurements}
 
@@
 Assuming accurate knowledge of the pointing direction of the spacecraft, in the form of the rotation matrix \( R \in \R^{3 \times 3 } \), we can compute a direction from the spacecraft to the measurement location on the surface.
-The output of this sensor is a vector, \( \vc{d}_i \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface. 
+The output of this sensor is a vector, \( \vc{d}_i\in\Re^3 \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface. 
 Using the state of the asteroid, we can transform this measurement to the asteroid fixed frame using the simple transformation
 \begin{align*}
-    \vc{p}_i = R_A^T R \vc{d}_i .
+    \vc{p}_i = R_A^T (x+R \vc{d}_i), 
 \end{align*}
+which is the vector from the origin of the asteroid fixed frame to the surface point of the measurement.
+\todo{check the above}
 Given many measurements, \( \vc{p}_i \in \R^3 \), of the asteroid surface we can efficiently update our initial shape estimate to that of the true surface.
@@
 The spacecraft measures the range between itself and the asteroid surface to several points within the field of view of the sensor. 
-These measurements provide a collection of points which lie on the surface of the asteroid, and by combining many points, a so called ``point cloud'', allows us to reconstruct the shape.
+These measurements provide a collection of points which lie on the surface of the asteroid, and by combining many points, a so called \textit{point cloud}, allows us to reconstruct the shape.
 \begin{figure}
@@
 
-\paragraph{Bayesian Shape Update}
+\subsection{Bayesian Shape Update}
 
-Our algorithm applies a Bayesian framework to radially modify each vertex \( \vc{v}_i \in \R^3\) of the shape estimate based on measurement \( \vc{p}_i \in \R^3 \). 
+Our algorithm applies a probabilistic framework to radially modify each vertex \( \vc{v}_i \in \R^3\) of the shape estimate based on measurement \( \vc{p}_i \in \R^3 \). 
+In other words, each vertex from the initial estimate of shape is either stretched or shrunk along its radial direction, without any rotation. 
+This framework is reasonable assuming that both of the initial estimate and the actual shape does not have any hole. 
 This approach alleviates much of complexity of incorporating new vertices or surface triangulation common in surface reconstruction methods~\cite{berg2008}.
-This assumption means that the total number of vertices of the shape model is fixed.
-However, additional detail, in the form of additional vertices, is possible by using standard mesh subdivision algorithms~\cite{orourke1998}.
+This implies that the total number of vertices of the shape model is fixed.
+However, additional detail, in the form of additional vertices, is possible by using standard mesh subdivision algorithms~\cite{orourke1998}, which is discussed in the subsequent section for multi resolution mapping.
 
-The radial distance of each vertex, \( v_i = \norm{\vc{v}_i}\), is assumed to be distributed according to the Gaussian distribution
+The proposed scheme follows the Bayesian estimation, where the degree of confident in the current estimate is compared with that of new measurements. 
+More specifically, the radial distance of each vertex, \( v_i = \norm{\vc{v}_i}\), is assumed to be distributed according to the Gaussian distribution
 \begin{align*}
@@
 where \( r_i \) is the initial estimate of the radial distance of vertex \( \vc{v}_i\) and \( w_i \) is the initial variance, or confidence, in the radial distance.
-The radial distance of each measurement, \( p_{j,i} = \norm{\vc{p}_j}\), is also assumed to be distributed according to the Gaussian distribution
-\begin{align*}
-    p_{j,i} \sim \mathcal{N}(r_{j,i}, w_{j,i}^2)
-\end{align*}
-where \( r_{j,i} = \norm{\vc{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i}\) defines the variance of the measurement with respect to vertex \( \vc{v}_i\).
-Each measurement is defined by the index \( j \) while the associated vertex is defined by \( i \). 
-As a result, the measurement \( p_{j, i} \) defines the distribution of measurement \( j \) with respect to vertex \( i \). 
-Any given measurement may be used to update one or several vertices.
 
-The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vc{v}_i \).
-Here, we use the geodesic distance to parameterize the difference, and hence  uncertainty, of associating the measurement with a given vertex.
-From spherical trigonometry~\cite{gade2010}, the central angle between measurement \( \vc{p}_i \) and vertex \( \vc{v}_i \) of the shape estimate is
+Suppose the $j$-th measurement, namely $p_j\in\Re^3$ is available. 
+As illustrated in \Cref{fig:lidar_example}, the angular resolution of range measurements is assumed to be coarser than the mesh grid of the initial estimate. 
+Consequently, the measurement may not be aligned to any vertex in general. 
+In order to improve the computational efficiency measurement updates are assumed to be local in nature.
+Instead of applying a measurement to all vertices of the mesh, the measurement is only applied to the vertices which are within a specified region of the measurement. 
+From spherical trigonometry~\cite{gade2010}, the central angle between measurement \( \vc{p}_j \) and vertex \( \vc{v}_i \) of the shape estimate is given by
 \begin{align}\label{eq:geodesic_distance}
@@
 \end{align}
-The variance of measurement \( \vc{p}_i \) with respect to vertex \( \vc{v}_i \) is then defined by the geodesic distance as
-\begin{align}
-    w_{j, i} = \norm{\vc{p}_j} \Delta \sigma_{j,i} .
-\end{align}
-This approach relates the uncertainty of the measurement \( \vc{p}_j \) with the geodesic distance to a given vertex, \( \vc{v}_i \).
-As a result, measurements which are far from a vertex, i.e.\ \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty. 
-This approach can be considered as a form of a correlation based sensor model~\cite{thrun2005}.
-The main benefit of a correlation based approach, in contrast to feature extraction is the relative simplicity of implementation.
-However, the resulting correlation values do not posses any physical significance and do not represent the noise or uncertainty characteristics of the sensor.
-
-From Bayes' theorem, the posterior probability is defined as
-\begin{align}
-    p(v_i | p_{j, i}) = \frac{p(p_{j, i} | v_i) p(v_i)}{p( p_{j, i})} \propto p(p_{j,i} | v_i) p(v_i).
-\end{align}
-From the properties of a Gaussian, the posterior probability given a measurement is also distributed according to a Gaussian distribution~\cite{bishop2006} and given by
-\begin{align}\label{eq:posterior_probability}
-    \mathcal{N} \parenth{\frac{w_{j, i}^2 r_i + w_i^2 r_{j, i}}{w_i^2 + w_{j, i}^2} , \frac{w_i^2  w_{j, i}^2}{w_i^2 +  w_{j, i}^2}} .
-\end{align}
-From~\cref{eq:posterior_probability}, the posterior probability conditioned on the measurement is the weighted average of the prior knowledge and the measurement. 
-Measurements that are far from the vertex will have a high uncertainty or variance and will have a reduced impact on the radial position of the vertex.
-Additional measurements are incorporated using a weighted average of prior belief and the measurement uncertainty.
-
-In order to improve the computational efficiency measurement updates are assumed to be local in nature.
-Instead of applying a measurement to all vertices of the mesh, the measurement is only applied to the vertices which are within a specified region of the measurement. 
-We define a region of interest, \( \Delta S \), about each measurement which defines the surface area over which the measurement will affect the mesh estimate.
+We define a area of interest, \( \Delta S\in\Re \), about each measurement which defines the surface area over which the measurement will affect the mesh estimate.
 We relate \( \Delta S \) to an equivalent angular constraint using
@@
 where \( r_b \) defines the Brillouin  sphere radius, or the radius of the circumscribing sphere of the asteroid.
-Only vertices which satisfy \( \Delta \sigma_i \leq \Delta \sigma_{max} \) are considered in the Bayesian update shown in~\cref{eq:posterior_probability}.
+Only vertices which satisfy \( \Delta \sigma_i \leq \Delta \sigma_{max} \) are considered in the Bayesian update defined as follows.
+
+Each measurement is defined by the index \( j \) while the associated vertex satisfying \cref{eq:region_of_interest} is defined by \( i \). 
+As a result, the measurement \( p_{j, i} \) defines the distribution of measurement \( j \) with respect to vertex \( i \). 
+The radial distance of each measurement, \( p_{j,i} = \norm{\vc{p}_j}\), is also assumed to be distributed according to the Gaussian distribution
+\begin{align*}
+    p_{j,i} \sim \mathcal{N}(r_{j,i}, w_{j,i}^2)
+\end{align*}
+where \( r_{j,i} = \norm{\vc{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i}\) defines the variance of the measurement with respect to vertex \( \vc{v}_i\).
+
+The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vc{v}_i \).
+Here, we use the geodesic distance to parameterize the difference, and hence  uncertainty, of associating the measurement with a given vertex.
+More explicitly, the variance of measurement \( \vc{p}_i \) with respect to vertex \( \vc{v}_i \) is then defined by the geodesic distance as
+\begin{align}
+    w_{j, i} = \norm{\vc{p}_j} \Delta \sigma_{j,i} .
+\end{align}
+This approach relates the uncertainty of the measurement \( \vc{p}_j \) with the geodesic distance to a given vertex, \( \vc{v}_i \).
+As a result, measurements which are far from a vertex, i.e.\ \( \Delta \sigma \) is large, will tend to have a larger variance and hence more uncertainty. 
+This approach can be considered as a form of a correlation based sensor model~\cite{thrun2005}.
+The main benefit of a correlation based approach, in contrast to feature extraction is the relative simplicity of implementation.
+However, the resulting correlation values do not precisely represent the noise or uncertainty characteristics of the sensor in a quantitative manner.
+
+From Bayes' theorem, the a posterior probability of the vertex radius is given by
+\begin{align}
+    p(v_i | p_{j, i}) = \frac{p(p_{j, i} | v_i) p(v_i)}{p( p_{j, i})} \propto p(p_{j,i} | v_i) p(v_i).
+\end{align}
+From the properties of Gaussian distributions, the posterior probability given a measurement is also distributed according to a Gaussian distribution~\cite{bishop2006} and given by
+\begin{align}\label{eq:posterior_probability}
+    \mathcal{N} \parenth{\frac{w_{j, i}^2 r_i + w_i^2 r_{j, i}}{w_i^2 + w_{j, i}^2} , \frac{w_i^2  w_{j, i}^2}{w_i^2 +  w_{j, i}^2}} .
+\end{align}
+From~\cref{eq:posterior_probability}, the a posterior mean conditioned on the measurement is the average of the prior knowledge and the measurement weighted by the reciprocal of the variance. 
+As such, it will be closer to the value with a smaller variance. 
+For example, measurements that are far from the vertex will have a high uncertainty or variance and will have a reduced impact on the radial position of the vertex.
 

### 2018-12-13 manuscript.tex
revised sec 4

@@
 %\newcommand{\todo}[1]{}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
     \dot{\vc{x}} &= \vc{v}, \\
-    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2}, \\
+    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2},\label{eq:v_dot} \\
     \dot{R} &= R S(\vc{\Omega}) , \\
@@
 
+\subsection{Numerical Examples}\label{sec:kinematic_exploration}
+
+In this section, we demonstrate the use of the incremental shape reconstruction algorithm with asteroids 1620 Geographos and 6489 Golevka.
+There properties are listed at \Cref{tab:kinematic_asteroids}.
+\begin{table}[htbp]
+    \centering
+    \begin{tabular}{lccc}
+        \toprule
+        Asteroid & Semi-major axes (\si{\kilo\meter}) & Vertices & Faces\\
+        \midrule
+        \num{1620} Geographos & \( 2.5 \times 1.0 \times 1.05 \) & \num{8192} & \num{16380}  \\
+        \num{6489} Golevka & \( 0.53 \times 0.53 \times 0.53 \)  & \num{2048} & \num{4092} \\
+        \bottomrule
+    \end{tabular} 
+    \caption{Asteroid properties for kinematic only exploration~\label{tab:kinematic_asteroids}}
+\end{table}
+
+The results in this section utilize a kinematics only model of the spacecraft and dynamics instead of the full dynamic simulation. 
+We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction, and the spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
+The simulations begin with an triaxial ellipsoid mesh that is sized to match the semi-major axes of each asteroid.
+With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
+LIDAR measurements are generated until the total uncertainty
+\begin{align*}
+    \sum_i w_i,
+\end{align*}
+is sufficiently small.
+In addition, we compute the volume of the estimate shape throughout the simulation using the algorithm presented here. 
+% TODO Add polyhedron volume algorithm
+
+\todo{explain how the location of spacecraft is selected. cite the reference for the shape model, clarify the above meaning of small uncertainty}
+
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/geographos/partial_0.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_1872.jpg}}
+
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_3745.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_5617.jpg}}
+
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_7489.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/truth.jpg}}
+    \caption[Asteroid Geographos incremental reconstruction]{Incremental reconstruction of asteroid Geographos~\label{fig:geographos_reconstruction}}
+\end{figure}
+
+\num{1620} Geographos is a highly elongated stony asteroid of the Apollo group.
+Discovered in \num{1951}, Geographos is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
+\Cref{fig:geographos_reconstruction} shows the shape reconstruction for asteroid Geographos at several distinct points during the process.
+Comparing~\cref{fig:geographos_partial_100,fig:geographos_truth} shows that the final shape closely matches the true radar model.
+In~\cref{fig:geographos_metrics} we display the vertex uncertainty and mesh volume as a function of time.
+The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.
+
+\begin{figure}[htbp]
+    \centering
+    \input{tikz/geographos_metrics.tikz}
+    \caption{Normalized uncertainty and volume percent error for Geographos\label{fig:geographos_metrics}}
+\end{figure}
+
+\num{6489} Golevka is a small angular shaped asteroid of the Apollo group.
+Discovered in \num{1995}, Golevka is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
+\Cref{fig:golevka_reconstruction} shows the shape reconstruction for asteroid Golevka at several distinct points during the process.
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_0.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_1321.jpg}}\\%
+
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_2643.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_3964.jpg}}\\%
+
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_5285.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/truth.jpg}}
+    \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
+\end{figure}
+Comparing~\cref{fig:golevka_partial_100,fig:golevka_truth} shows that the final shape closely matches the true radar model.
+In~\cref{fig:golevka_metrics} we display the vertex uncertainty and mesh volume as a function of time.
+
+\begin{figure}[htbp]
+    \centering
+    \input{tikz/golevka_metrics.tikz}
+    \caption{Normalized uncertainty and volume percent error for Golevka\label{fig:golevka_metrics}}
+\end{figure}
+
+The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.
+It is interesting to note that the reconstruction of Golevka achieves an accurate shape reconstruction in a much smaller amount of time as compared to Geographos.
+This is primarily due to the smaller size of Golevka and the relatively spherical shape of the body in contrast to the highly elliptical shape of Geographos.
+
+\clearpage\newpage
 \section{Optimal Guidance for Shape Reconstruction}\label{sec:explore_asteroid}
 
-The mesh update algorithm presented does not offer a method to determine which portion of the surface needs to be updated. 
-In this section, we present an optimal approach for the guidance of the vehicle in order to update the shape estimate.
-A nonlinear geometric controller is utilized which allows the spacecraft to maneuver to the best location that will update the shape estimate~\cite{kulumani2017b}.
-This guidance schemes enables autonomous operations around a small body.
+The shape reconstruction algorithm presented in the preceding section does not offer a method to determine which portion of the surface needs to be measured. 
+In this section, we present a guidance scheme or a motion planning scheme in order to direct the spacecraft into the most uncertain region. 
+This is to reduce the shape uncertainty in an optimal fashion while considering the control cost to change the orbital properties of the spacecraft. 
+Then, a nonlinear geometric controller is utilized which allows the spacecraft to maneuver to the optimized location that will update the shape estimate~\cite{kulumani2017b}.
 
-We define a cost associated with each vertex \( \vc{v}_i \) of the shape estimate
+\subsection{Optimal Guidance}
+
+We define a cost associated with each vertex \( \vc{v}_i \) of the shape estimate as
 \begin{align}\label{eq:explore_cost}
@@
 \end{align}
-where \( w_i \) is the uncertainty of vertex \( i \) and \( w_m \) is a maximum uncertainty used to scale the values.
+where \( w_i \) is the uncertainty of vertex \( i \), which is defined as the variance of the radius in the preceding section, and \( w_m \in\Re \) is a maximum uncertainty used to scale the values.
 The term \( J_{d_i} \) represents the scaled geodesic distance between the current state of the spacecraft and vertex \( i \),
@@
 \end{align}
-Then a trajectory \( x_d(\theta) \) as
+Then a desired trajectory \( x_d(\theta) \) as
 \begin{align}\label{eq:spherical_waypoint}
@@
 where \( \theta : \bracket{0, \frac{\rpos \cdot \vc{v}_i}{\norm{\rpos}\norm{\vc{v}_i}}} \to \R^1\) parameterizes the desired trajectory.
-\Cref{eq:spherical_waypoint} simply describes a portion of a great circle trajectory between the current state, \( \rpos \), and the desired vertex \( \vc{v}_i \)~\cite{chen2016}.
-The altitude of the spacecraft, \( r_d \in \R \), can be chosen based on sensor characteristics of safety concerns.
+\Cref{eq:spherical_waypoint} simply describes a portion of a great circle trajectory between the current state, \( \rpos \), and the desired vertex \( \vc{v}_i \)~\cite{chen2016}, with a desired radius $r_d$.
+The radius of the spacecraft, \( r_d \in \R \), can be chosen based on sensor characteristics of safety concerns.
 For example, \( r_d \) can be chosen as the distance of the Biroullin sphere with an additional safety margin to mitigate any surface collision~\cite{scheeres2012a}.
-We assume that the tracking errors are small, such that \( e_x, e_v \) are negligible, therefore the control becomes
+
+We assume $\theta$ varies linearly with respect to $t$, and substitute the desired trajectory into \Cref{eq:v_dot} to obtain the control force required to follow the desired trajectory in the absence of any tracking error:
 \begin{align}\label{eq:tracking_control_cost}
@@
 \end{align}
-where the external force is defined by the polyhedron potential model given in~\cref{eq:attraction}.
+which is computed by the polyhedron potential model given in~\cref{eq:attraction}.
 The control cost is then defined as the integral over the desired trajectory~\cref{eq:spherical_waypoint} between the current state and the desired vertex as
@@
 
+\todo{Augment dynamic model with the control force and the torque}
+
 The vertex which minimizes~\cref{eq:explore_cost} 
 \begin{align*}
-    \vc{v}_{min} = \min_{i} J_i(x, R, R_A),
+    \vc{v}_{min} = \argmin_{i} \{J_i(x, R, R_A)\},
 \end{align*}
-is determined and used to determine the optimum vertex of the shape model to measure.
-This vertex is then used to determine the required state of the spacecraft in order to collect a measurement.
-We assume that the spacecraft will maneuver to a location directly above the selected vertex, \( \vc{v}_{min} \), and point in the nadir direction to collect a measurement.
-The desired state is transformed into the inertial frame and chosen as a location above \( \vc{v}_{min} \) as
-\begin{align}
-    x_d = r_d R_A \vc{v}_{min}, 
-\end{align}
-where \( r_d \) is again chosen to ensure a safety margin above the surface.
-The desired attitude command, \( R_d\), is chosen such that the spacecraft camera axis, \( \vc{b}_1 \), is directed along the nadir towards the small body.
+is determined.
+This vertex is then used to determine the desired trajectory of the spacecraft in order to collect a measurement as in~\Cref{eq:spherical_waypoint}.
+
+Next, the desired attitude command, \( R_d\), is chosen such that the spacecraft camera axis, \( \vc{b}_1 \), is directed along the nadir towards the asteroid.
 It is sufficient to define two orthogonal vectors to uniquely determine the attitude of the spacecraft.
@@
 This form of \( R_d \) will direct the \( b_1 \) axis towards the small body, and can be modified for a different camera orientation.
+
+\subsection{Geometric Tracking Control}
+
+We utilize a geometric tracking control system to follow the desired trajectory for the position and the attitude defined above.
+
+\todo{add description of control}
+
+\subsection{Numerical Examples}
+
+We utilize radar shape models of asteroids \num{4769} Castalia and (\num{52760}) \num{1998} \(\text{ML}_{14}\).
+The examples demonstrate the full dynamic simulation of a rigid spacecraft with an autonomous closed loop control scheme to both reconstruct the asteroid shape.
+More specifically, the nonlinear controllers described previously are used to control both the translational and rotational states of the vehicle, where the control inputs are computed using the current shape estimate of the asteroid.
+As measurements are collected, the spacecraft autonomously updates its shape estimate and uses this estimate to compute the control inputs and desired future states.
+As such, both the shape model and the gravitational potential available to the controller will be gradually refined. 
+However, throughout the simulation, the actual spacecraft dynamics are computed with the gravity computed by the full shape model unknown to the controller.
+These demonstrate the ability of a spacecraft to autonomously explore and maneuver around an initially-unknown asteroids while incrementally updating the shape model.
+
+We consider two simulations about asteroids \num{52760} and Castalia.
+The asteroids are assumed to constantly rotate about the \( \vc{f}_3 = \vc{e}_3\) axis according to the parameters given in~\cref{tab:dynamic_asteroids}.
+Furthermore, the state of the asteroid, namely the rotation matrix \( R_A \), is assumed to be known based on ground measurements or previous data.
+\begin{table}[htbp]
+    \centering
+    \begin{tabular}{lcc}
+        \toprule
+        Property & \num{4769} Castalia & (\num{52760}) \num{1998} \(\text{ML}_{14}\) \\
+        \midrule
+        Semi-major axes(\si{\kilo\meter}) & \( 0.8065 \times 0.4905 \times 0.413 \) & \( 1.1 \times 1.1 \times 1.1 \) \\
+        Rotational Period (\si{\hour}) & \num{4.095} & \num{14.98} \\
+        Density (\si{\gram\per\centi\meter^3}) & \num{2.1} & \num{2.1} \\
+        Vertices & \num{2048}  & \num{8192} \\
+        Faces & \num{4092} & \num{16320} \\
+        \bottomrule
+    \end{tabular}
+    \caption{Asteroid properties for dynamic exploration~\label{tab:dynamic_asteroids}}
+\end{table}
+At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( x_0 = \begin{bmatrix} x_0 & 0 & 0 \end{bmatrix} \si{\kilo\meter} \).
+In addition, at the initial state the spacecraft is orientated such that the \( b_1 \) axis is aligned with the inertial \( e_2 \) axis.
+In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat{e}_3)\).
+The shape reconstruction phase of the simulation is performed over \SI{15000}{\second}, over which time the spacecraft will take LIDAR measurements of the surface at \SI{1}{\hertz}.
+Once the total uncertainty has been reduced sufficiently the spacecraft maneuvers to a ``home'' position aligned with the \( f_1 \) axis of the asteroid.
+
+\paragraph{Asteroid 52760 Reconstruction}
+
+Asteroid (\num{52760}) \num{1998} \(\text{ML}_{14}\) was discovered in \num{1998} and is near Earth asteroid of the Apollo group and classified as a potentially hazardous body.
+The asteroid is roughly spherical with a mean radius of approximately \SI{1}{\kilo\meter}.
+The initial shape estimate is assumed to be spherical with approximately the same number of vertices as the truth model.
+\Cref{fig:52760_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
+Due to the roughly spherical shape of the asteroid large portions of the surface are quickly modified to match the measurements.
+In addition~\cref{fig:52760_weights_reconstruction} displays the vertex uncertainty \( w_i \) as a colormap on the surface. 
+Areas of high uncertainty are denoted in yellow while areas of low uncertainty are in purple/blue.
+
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_3749.jpg}}%
+
+    \subcaptionbox{\SI{50}{\percent} of measurements\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_7499.jpg}}
+    \subcaptionbox{\SI{75}{\percent} of measurements\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_11249.jpg}}%
+
+    \subcaptionbox{\SI{100}{\percent} of measurements\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/52760/truth.jpg}}
+    \caption[Asteroid 52760 shape reconstruction with uncertainty]{Incremental reconstruction of asteroid 52760.
+The images colored according to the shape uncertainty.
+Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:52760_weights_reconstruction}}
+\end{figure}
+
+\paragraph{Asteroid 4769 Castalia Reconstruction}
+
+Asteroid 4769 Castalia is a small near Earth asteroid of the Apollo group.
+In addition, it is classified as a potentially hazardous object with a closed approach distance of less than \SI{0.05}{\astronomicalunit}.
+Castalia was discovered in \num{1989} and is the first asteroid to be modeled using radar imagery~\cite{hudson1994}.
+Castalia is composed of two distinct lobes suggesting that it is a contact binary of two smaller objects held together by their mutual gravity.
+\Cref{fig:castalia_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
+In addition~\cref{fig:castalia_weights_reconstruction} displays the vertex uncertainty \( w_i \) as a colormap on the surface. 
+Areas of high uncertainty are denoted in yellow while areas of low uncertainty are in purple/blue.
+Within \SI{50}{\percent} of the simulation span the spacecraft is able to achieve an accurate estimate of the true shape of Castalia.
+
+\begin{figure}[htbp]
+    \centering
+    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_3749.jpg}}%
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_7499.jpg}}
+
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_11249.jpg}}%
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/mesh_update/castalia/truth.jpg}}
+    \caption[Asteroid Castalia shape reconstruction with uncertainty]{Incremental reconstruction of asteroid Castalia.
+The images colored according to the shape uncertainty.
+Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:castalia_weights_reconstruction}}
+\end{figure}
+
+\Cref{fig:castalia_metrics} shows the total normalized uncertainty and percent error for the volume estimate. 
+The plots show that the reconstruction converges to an accurate shape estimate after approximately \SI{8000}{\second}.
+In addition, the volume estimate is initially a much larger value but quickly converges to the true value.
+\begin{figure}[htbp]
+    \centering
+    \input{tikz/castalia_metrics.tikz}
+    \caption{Normalized uncertainty and volume percent error for Castalia\label{fig:castalia_metrics}}
+\end{figure}
+The spacecraft autonomously navigates around asteroid Castalia to best minimize the cost function in~\cref{eq:control_cost}.
 
@@
 % TODO Mention that the software to do this is available online?
-In this section, we demonstrate the use of the incremental shape reconstruction algorithm.
-The approach is used to iteratively reconstruct the shape of several asteroid given LIDAR measurements.
-We utilize radar shape models of asteroids \num{4769} Castalia and (\num{52760}) \num{1998} \(\text{ML}_{14}\).
-The examples demonstrate the full dynamic simulation of a rigid spacecraft with an autonomous closed loop control scheme to both reconstruct the asteroid shape.
-
-The nonlinear controllers described previously are used to control both the translational and rotational states of the vehicle.
-Throughout the simulation the control inputs are computed using the current shape estimate of the asteroid. 
-As measurements are collected, the spacecraft autonomously updates its shape estimate and uses this estimate to compute the control inputs and desired future states.
-These simulations demonstrate the ability of a spacecraft to autonomously explore and maneuver around an unknown small body.
-
-We consider two simulations about asteroids \num{52760} and Castalia.
-The asteroids are assumed to constantly rotate about the \( \vc{f}_3 = \vc{e}_3\) axis according to the parameters given in~\cref{tab:dynamic_asteroids}.
-Furthermore, the state of the asteroid, namely the rotation matrix \( R_A \), is assumed to be known based on ground measurements or previous data.
-\begin{table}[htbp]
-    \centering
-    \begin{tabular}{lcc}
-        \toprule
-        Property & \num{4769} Castalia & (\num{52760}) \num{1998} \(\text{ML}_{14}\) \\
-        \midrule
-        Semi-major axes(\si{\kilo\meter}) & \( 0.8065 \times 0.4905 \times 0.413 \) & \( 1.1 \times 1.1 \times 1.1 \) \\
-        Rotational Period (\si{\hour}) & \num{4.095} & \num{14.98} \\
-        Density (\si{\gram\per\centi\meter^3}) & \num{2.1} & \num{2.1} \\
-        Vertices & \num{2048}  & \num{8192} \\
-        Faces & \num{4092} & \num{16320} \\
-        \bottomrule
-    \end{tabular}
-    \caption{Asteroid properties for dynamic exploration~\label{tab:dynamic_asteroids}}
-\end{table}
-At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( x_0 = \begin{bmatrix} x_0 & 0 & 0 \end{bmatrix} \si{\kilo\meter} \).
-In addition, at the initial state the spacecraft is orientated such that the \( b_1 \) axis is aligned with the inertial \( e_2 \) axis.
-In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat{e}_3)\).
-The shape reconstruction phase of the simulation is performed over \SI{15000}{\second}, over which time the spacecraft will take LIDAR measurements of the surface at \SI{1}{\hertz}.
-Once the total uncertainty has been reduced sufficiently the spacecraft maneuvers to a ``home'' position aligned with the \( f_1 \) axis of the asteroid.
-
-\subsection{Shape Reconstruction}\label{sec:kinematic_exploration}
-
-The results in this section utilize a kinematics only model of the spacecraft and dynamics instead of the full dynamic simulation. 
-We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction.
-\Cref{tab:kinematic_asteroids} lists the true shape model parameters of asteroids Geographos and Golevka.
-\begin{table}[htbp]
-    \centering
-    \begin{tabular}{lccc}
-        \toprule
-        Asteroid & Semi-major axes (\si{\kilo\meter}) & Vertices & Faces\\
-        \midrule
-        \num{1620} Geographos & \( 2.5 \times 1.0 \times 1.05 \) & \num{8192} & \num{16380}  \\
-        \num{6489} Golevka & \( 0.53 \times 0.53 \times 0.53 \)  & \num{2048} & \num{4092} \\
-        \bottomrule
-    \end{tabular} 
-    \caption{Asteroid properties for kinematic only exploration~\label{tab:kinematic_asteroids}}
-\end{table}
-The spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
-The simulations begin with an triaxial ellipsoid mesh that is sized to match the semi-major axes of each asteroid.
-With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
-LIDAR measurements are generated until the total uncertainty
-\begin{align*}
-    \sum_i w_i,
-\end{align*}
-is sufficiently small.
-In addition, we compute the volume of the estimate shape throughout the simulation using the algorithm presented here. 
-% TODO Add polyhedron volume algorithm
-
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/geographos/partial_0.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_1872.jpg}}
-
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_3745.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_5617.jpg}}
-
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_7489.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/truth.jpg}}
-    \caption[Asteroid Geographos incremental reconstruction]{Incremental reconstruction of asteroid Geographos~\label{fig:geographos_reconstruction}}
-\end{figure}
-
-\num{1620} Geographos is a highly elongated stony asteroid of the Apollo group.
-Discovered in \num{1951}, Geographos is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
-\Cref{fig:geographos_reconstruction} shows the shape reconstruction for asteroid Geographos at several distinct points during the process.
-Comparing~\cref{fig:geographos_partial_100,fig:geographos_truth} shows that the final shape closely matches the true radar model.
-In~\cref{fig:geographos_metrics} we display the vertex uncertainty and mesh volume as a function of time.
-The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.
-
-\begin{figure}[htbp]
-    \centering
-    \input{tikz/geographos_metrics.tikz}
-    \caption{Normalized uncertainty and volume percent error for Geographos\label{fig:geographos_metrics}}
-\end{figure}
-
-\num{6489} Golevka is a small angular shaped asteroid of the Apollo group.
-Discovered in \num{1995}, Golevka is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
-\Cref{fig:golevka_reconstruction} shows the shape reconstruction for asteroid Golevka at several distinct points during the process.
-Comparing~\cref{fig:golevka_partial_100,fig:golevka_truth} shows that the final shape closely matches the true radar model.
-In~\cref{fig:golevka_metrics} we display the vertex uncertainty and mesh volume as a function of time.
-
-\begin{figure}[htbp]
-    \centering
-    \input{tikz/golevka_metrics.tikz}
-    \caption{Normalized uncertainty and volume percent error for Golevka\label{fig:golevka_metrics}}
-\end{figure}
-
-The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.
-It is interesting to note that the reconstruction of Golevka achieves an accurate shape reconstruction in a much smaller amount of time as compared to Geographos.
-This is primarily due to the smaller size of Golevka and the relatively spherical shape of the body in contrast to the highly elliptical shape of Geographos.
-
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_0.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_1321.jpg}}\\%
-
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_2643.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_3964.jpg}}\\%
-
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_5285.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/truth.jpg}}
-    \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
-\end{figure}
-\paragraph{Asteroid 52760 Reconstruction}
-
-Asteroid (\num{52760}) \num{1998} \(\text{ML}_{14}\) was discovered in \num{1998} and is near Earth asteroid of the Apollo group and classified as a potentially hazardous body.
-The asteroid is roughly spherical with a mean radius of approximately \SI{1}{\kilo\meter}.
-The initial shape estimate is assumed to be spherical with approximately the same number of vertices as the truth model.
-\Cref{fig:52760_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
-Due to the roughly spherical shape of the asteroid large portions of the surface are quickly modified to match the measurements.
-In addition~\cref{fig:52760_weights_reconstruction} displays the vertex uncertainty \( w_i \) as a colormap on the surface. 
-Areas of high uncertainty are denoted in yellow while areas of low uncertainty are in purple/blue.
-
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_3749.jpg}}%
-
-    \subcaptionbox{\SI{50}{\percent} of measurements\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_7499.jpg}}
-    \subcaptionbox{\SI{75}{\percent} of measurements\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_11249.jpg}}%
-
-    \subcaptionbox{\SI{100}{\percent} of measurements\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_14998.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/52760/truth.jpg}}
-    \caption[Asteroid 52760 shape reconstruction with uncertainty]{Incremental reconstruction of asteroid 52760.
-The images colored according to the shape uncertainty.
-Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:52760_weights_reconstruction}}
-\end{figure}
-
-\paragraph{Asteroid 4769 Castalia Reconstruction}
-
-Asteroid 4769 Castalia is a small near Earth asteroid of the Apollo group.
-In addition, it is classified as a potentially hazardous object with a closed approach distance of less than \SI{0.05}{\astronomicalunit}.
-Castalia was discovered in \num{1989} and is the first asteroid to be modeled using radar imagery~\cite{hudson1994}.
-Castalia is composed of two distinct lobes suggesting that it is a contact binary of two smaller objects held together by their mutual gravity.
-\Cref{fig:castalia_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
-In addition~\cref{fig:castalia_weights_reconstruction} displays the vertex uncertainty \( w_i \) as a colormap on the surface. 
-Areas of high uncertainty are denoted in yellow while areas of low uncertainty are in purple/blue.
-Within \SI{50}{\percent} of the simulation span the spacecraft is able to achieve an accurate estimate of the true shape of Castalia.
-
-\begin{figure}[htbp]
-    \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_3749.jpg}}%
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_7499.jpg}}
-
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_11249.jpg}}%
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_14998.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/mesh_update/castalia/truth.jpg}}
-    \caption[Asteroid Castalia shape reconstruction with uncertainty]{Incremental reconstruction of asteroid Castalia.
-The images colored according to the shape uncertainty.
-Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:castalia_weights_reconstruction}}
-\end{figure}
-
-\Cref{fig:castalia_metrics} shows the total normalized uncertainty and percent error for the volume estimate. 
-The plots show that the reconstruction converges to an accurate shape estimate after approximately \SI{8000}{\second}.
-In addition, the volume estimate is initially a much larger value but quickly converges to the true value.
-\begin{figure}[htbp]
-    \centering
-    \input{tikz/castalia_metrics.tikz}
-    \caption{Normalized uncertainty and volume percent error for Castalia\label{fig:castalia_metrics}}
-\end{figure}
-The spacecraft autonomously navigates around asteroid Castalia to best minimize the cost function in~\cref{eq:control_cost}.
-
 \paragraph{Castalia Landing Site Selection}

### 2018-12-13 manuscript.tex
revisec sec 5

@@
 
-We consider two simulations about asteroids \num{52760} and Castalia.
 The asteroids are assumed to constantly rotate about the \( \vc{f}_3 = \vc{e}_3\) axis according to the parameters given in~\cref{tab:dynamic_asteroids}.
@@
 
-The shape update approach presented is designed with autonomous operations in mind. 
-It is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
-Furthermore, the original mesh is uniformly distributed and as a result many small topological features such as rocks or small craters are not be captured by the shape model. 
+In this section, we consider a scenario of autonomous landing on the surface of asteroid, once its shape is constructed as described above.
+The shape reconstruction scheme is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
+Consequently, the original mesh is uniformly distributed with a relatively large mesh size and many small topological features such as rocks or small craters may not be captured accurately.
 However, these small features are critical for surface operations and safe landings.
@@
 
-Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
-As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
-The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
-As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
-However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.
+\subsection{Landing Site Determination}
 
@@
 Finally, we also assign a random science value to the surface in the form of a two dimensional Gaussian.
+This can be modified depending on the specific objective of the mission.
+
 Utilizing these metric, a landing site is chosen to minimize the surface cost given as
@@
 \end{align}
-where the surface slope is considered a hard constraint such that any candidate landing site must satisfy \( \phi \leq \phi_m \).
+subject to a hard inequality constraint requiring that the surface slope is less than a threshold, i.e., \( \phi \leq \phi_m \).
 
-\paragraph{Mesh Refinement}\label{sec:refinement}
+\todo{rewrite the above equation as a function of a candidate landing site location; we also need to describe how many points are considered for minimization; is it just the set of vertices}
+
+\subsection{High-Resolution Mapping}\label{sec:refinement}
+
+Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
+As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
+The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
+As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
+However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.
 
@@
 In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL).
+\todo{add reference to CGAL}
 This algorithm uses an iterative method which repeatedly splits long edges, collapses short edges, and relocates vertices until all edges are approximately the desired target edge length.
@@
 
-In order to demonstrate the multi resolution surface refinement we require a true shape model that contains small scale surface features.
-In this dissertation, we utilize the true radar shape model of asteroid 4769 Castalia.
-However, the shape model is not highly detailed as it does not contain small craters or surface features.
-In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme shown previously to update the surface.
-The augmented model of Castalia is shown in~\cref{fig:castalia_refinement}.
-\Cref{fig:castalia_refinement} shows that the increased resolution is required in order to reconstruct these small surface details.
+Once the area around the landing site is remeshed, the preceding shape reconstruction scheme is applied to those area to develop a high-fidelity topological map.
 
-\section{Numerical Examples}\label{sec:reconstruction_examples}
+\subsection{Numerical Example}
+
+The proposed schemes for landing site selection and refinement are applied to Castalia.
+
+%\section{Numerical Examples}\label{sec:reconstruction_examples}
 
@@
 % TODO Mention that the software to do this is available online?
+
 \paragraph{Castalia Landing Site Selection}
@@
 \paragraph{Castalia Landing Site Refinement}
+
+%In order to demonstrate the multi resolution surface refinement we require a true shape model that contains small scale surface features.
+%Here, we utilize the true radar shape model of asteroid 4769 Castalia.
+%However, the shape model is not highly detailed as it does not contain small craters or surface features.
+%In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme shown previously to update the surface.
+%The augmented model of Castalia is shown in~\cref{fig:castalia_refinement}.
+%\Cref{fig:castalia_refinement} shows that the increased resolution is required in order to reconstruct these small surface details.
+
 One key benefit of an in-situ spacecraft is the ability to measure surface features at a much higher resolution than is possible from the ground. 
@@
 As a result, we utilize the isotropic remeshing operation described previously to selectively increase the fidelity in the region about the desired landing site.
+
 \Cref{fig:castalia_refine_density} shows that the vertex density increases by approximately an order of magnitude in region immediately surround the landing site.
@@
 
+\todo{as the nonlinear controller is added, we may want to add more plots for tracking errors; we can add a link to videos}
+
 \section{Conclusions}
@@
 Next, an optimal guidance scheme is derived which determines the desired state to best update the shape estimate. 
+Finally, a mixed resolution shape representation is presented to allow for an increased fidelity in a specific region of the asteroid.
+This allows for a much greater shape accuracy in a local area while avoiding the computational costs associated with a uniformly high resolution mesh.
 This allows for a spacecraft to autonomously maneuver and reconstruct the shape of a small body without operator intervention.
-% Finally, a mixed resolution shape representation is presented to allow for an increased fidelity in a specific region of the asteroid.
-% This allows for a much greater shape accuracy in a local area while avoiding the computational costs associated with a uniformly high resolution mesh.
 Several numerical examples were presented which demonstrates the approach on a number of real asteroids.
 
-\section*{Appendix}
+Throughout this paper, it is considered that the position of the spacecraft relative the asteroid is available. 
+Future works include integrating a localization technique with the proposed shape reconstruction scheme such that the relative location and the shape model are estimated simultaneously.
 
-An Appendix, if needed, appears \textbf{before} research funding information and other acknowledgments.
+%\section*{Appendix}
 
-\section*{Funding Sources}
+%An Appendix, if needed, appears \textbf{before} research funding information and other acknowledgments.
 
-Sponsorship information and acknowledgments of financial support should be included here.
+%\section*{Funding Sources}
+
+%Sponsorship information and acknowledgments of financial support should be included here.
 \textbf{Authors are responsible for accurately reporting funding data relevant to their research.} Please confirm that you have correctly entered \textbf{all sources} of funding and grant/award numbers \textbf{for all authors} in this section of your article.

### 2019-02-03 utilities/setup_repo.sh
Update manuscript

@@ -1,16 +1,14 @@
 #!/bin/bash
 
 # add the correct remote repositories
-git_repo="git@github.com:skulumani/2018_aas_manuscript.git"
-bb_repo="git@bitbucket.org:shankarkulumani/2018_aas_manuscript.git"
-fdcl_repo="git@github.com:fdcl-gwu/2018_aas_manuscript.git"
+git_repo="git@github.com:skulumani/2018_JGCD.git"
+fdcl_repo="git@github.com:fdcl-gwu/2018_JGCD.git"
 
 printf "Setting the origin remote to point to Github and Bitbucket:\n\n"
 printf "Github: $git_repo\n"
 printf "Bitbucket: $bb_repo\n\n"
 
-git remote set-url origin --push --add $bb_repo
-git remote set-url origin --push --add $git_repo
+git remote add origin ${git_repo}
 git remote add fdcl ${fdcl_repo}
 
 printf "Finished! The new remotes are listed.\n"

### 2019-02-03 manuscript.tex
revisd title
Update manuscript
Add dumbbell model picture

@@
 
-\title{Real Time Adaptive Shape Reconstruction for Asteroid Landing}
+\title{Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids}
 
@@
 \noindent(Nomenclature entries should have the units identified)
-
+\noindent{Add elements}
 % {\renewcommand\arraystretch{1.0}
@@
 
+% TODO Reduce some of these paragraphs since they're wordy
 % we want to generate the shape in real time and then use this shape for updated and better control
@@
 The dumbbell model captures the important interactions of the coupling between orbital and attitude dynamics.
-In this model, the spacecraft consists of two masses connected by a massless rod.
+The dumbbell is defined by two spherical masses of radius \( r_1, r_2 \in \R \) with masses \( m_1, m_2 \in  \R\).
+The masses are separated by a massless rod of length \( l \) and attached to the centers of each mass.
+\Cref{fig:dumbbell_sc} shows the model and associated parameters.
+\begin{figure}[htbp]
+    \centering
+    \input{tikz/dumbbell.tikz}
+    \caption{Dumbbell Model of Rigid Spacecraft\label{fig:dumbbell_sc}}
+\end{figure}
+Without loss of generality, we define body fixed frames for both the spacecraft and asteroid, which are aligned with the principle axes of each body and originate at their respective center of mass. 
+The spacecraft body fixed frame is centered at the center of mass of the vehicle.
+The \( b_1 \)  axis is aligned with the connecting rod and directed along the axis of symmetry.
+The \( b_2, b_3 \) axes span the plane orthogonal to the axis of symmetry of the dumbbell.
+The distance from the center of mass to each spherical mass is defined as
+\begin{align}\label{eq:dumbbell_mass_distances}
+    l_1 &= \frac{m_2}{m_1 + m_2} l, \\
+    l_2 &= l - l_1.
+\end{align}
 The asteroid is modeled as a constant density polyhedron with constant, and known, spin about its maximum moment of inertia. 
-Without loss of generality, we define body fixed frames for both the spacecraft and asteroid, which are aligned with the principle axes of each body and originate at their respective center of mass. 
-The axes of the body fixed frame for the spacecraft are denoted by $\{b_1,b_2,b_3\}$, and those for the asteroid are denoted by $\{f_1,f_2,f_3\}$. 
+The axes of the body fixed frame for the asteroid are denoted by $\{f_1,f_2,f_3\}$. 
 We also define the inertial frame, whose axes are denoted by $\{e_1,e_2,e_3\}$.
@@
     \item \( R\in\SO \) - the rotation matrix which transforms vectors defined in the spacecraft fixed frame, \( \vc{b}_i \), to the inertial frame, \( \vc{e}_i \),
-    \item \( \vc{\Omega}\in\Re \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame, \( \vc{b}_i \), and
-    \item \( R_A\in SO \) - the rotation matrix which transforms vectors defined in the asteroid fixed frame, \( \vc{f}_i \), to the inertial frame, \( \vc{e}_i \).
+    \item \( \vc{\Omega}\in\Re^3 \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame, \( \vc{b}_i \), and
+    \item \( R_A\in \SO \) - the rotation matrix which transforms vectors defined in the asteroid fixed frame, \( \vc{f}_i \), to the inertial frame, \( \vc{e}_i \).
 \end{itemize}

### 2019-02-03 manuscript.tex
Updating dynamic model to define all variable

@@
 
-\todo{Add the schematic of dumbbell that you created for the dissertation?}
-
 \subsection{Spacecraft Dynamic Model}
@@
     \dot{\vc{x}} &= \vc{v}, \\
-    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2},\label{eq:v_dot} \\
+    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2} + u_f,\label{eq:v_dot} \\
     \dot{R} &= R S(\vc{\Omega}) , \\
-    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2.
+    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2 + u_m.
 \end{align}
@@
     \vc{z}_1 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_1} , \\
-    \vc{z}_2 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_2}.
+    \vc{z}_2 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_2},
 \end{align}
+where \( \rho_i \) defines the position of each mass in the spacecraft fixed body frame.
+The control inputs to the spacecraft are defined by \( u_f, u_m \in \Re^3 \) which define the control force represented in the inertial frame and the control moment represented in the spacecraft frame, respectively.
 The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as

### 2019-02-03 manuscript.tex
Add moment of inertia

@@
 The control inputs to the spacecraft are defined by \( u_f, u_m \in \Re^3 \) which define the control force represented in the inertial frame and the control moment represented in the spacecraft frame, respectively.
+
+The inertia tensor/matrix of a rigid body is defined~\cite{greenwood1988} as
+\begin{align}\label{eq:moi_definition}
+    J_I = \int_{\mathcal{B}} \bracket{ \parenth{\brho{}^T \brho{} }I - \brho{}\brho{}^T} dm, 
+\end{align}
+where \( \vc{\rho} \in \R^3 \) is the position of a mass element \( dm \) in the body fixed frame of the spacecraft.
+One can also use~\cref{eq:xTx} to define the inertia matrix in several other equivalent forms
+\begin{align*}
+    J_I &= \int_{\mathcal{B}} \bracket{ \parenth{\vc{\rho}^T \vc{\rho} }I - \vc{\rho}\vc{\rho}^T} dm, \\
+        &= \int_{\mathcal{B}} \tr{\vc{\rho}\vc{\rho}^T} I - \vc{\rho}\vc{\rho}^T, \\
+        &= \int_{\mathcal{B}} \vh{\rho}^T \vh{\rho} dm.
+\end{align*}
+The location of an infinitesimal mass element \( dm \) can be decomposed into
+\begin{align}\label{eq:mass_element_position}
+    \vc{\rho}_i = \vc{\zeta} + \vc{\eta}_i, 
+\end{align}
+where \( \vc{\zeta} \) is the location of the center of \( m_i \) in the spacecraft fixed frame while \( \vc{\eta} \) the position of \( dm \) with respect to the center of \( m_i \) and expressed in the spacecraft fixed frame.
+\Cref{fig:dumbbell_sc} shows the configuration of the vectors \( \vc{\zeta}, \vc{\eta} \) in the spacecraft fixed frame.
+Using~\cref{eq:mass_element_position}, the moment of inertia can be expanded as
+\begin{align*}
+    J_I &= \sum_i^n \int_{\mathcal{B}_i} \parenth{\vc{\zeta}_i + \vc{\eta}_i}^T \parenth{\vc{\zeta}_i + \vc{\eta}_i } I  - \parenth{\vc{\zeta}_i + \vc{\eta}_i} \parenth{\vc{\zeta}_i + \vc{\eta}_i}^T dm .
+\end{align*}
+Expanding the product terms leads to
+\begin{align*}
+    J_I = \sum_i^n \int_{\mathcal{B}_i} \parenth{\vc{\zeta}_i^T \vc{\zeta}_i}I - \vc{\zeta}_i \vc{\zeta}_i^T + \vc{\eta}_i^T \vc{\eta}_i I - \vc{\eta}_i \vc{\eta}_i^T dm.
+\end{align*}
+Since the cross terms include an integration over the constant density sphere, the terms of the form
+\begin{align*}
+    \int_{\mathcal{B}_i} \vc{\eta}_i dm = 0,
+\end{align*}
+all become zero.
+The integration is now split into two components: an integration within each sphere consisting of \( \vc{\eta}_i \) terms and an integration involving the location of the sphere in the spacecraft fixed frame consisting of \( \vc{\zeta}_i \) terms.
+As a result, the final moment of inertia of a system of rigid spherical masses is 
+\begin{align}\label{eq:dumbbell_moment_of_inertia}
+    J_I = \sum_i^n J_i + m_i \parenth{\vc{\zeta}_i^T \vc{\zeta}_i I - \vc{\zeta}_i \vc{\zeta}_i^T} , 
+\end{align}
+where \( \vc{\zeta}_i \) is the position of \( m_i \) in the spacecraft fixed frame and the moment of inertia of each sphere is
+\begin{align}\label{eq:sphere_moment_of_inertia}
+    J_i = \begin{bmatrix} 
+        \frac{2}{5} m_i r_i^2 & 0 & 0 \\
+        0 & \frac{2}{5} m_i r_i^2 & 0 \\
+        0 & 0 & \frac{2}{5} m_i r_i^2 
+    \end{bmatrix}.
+\end{align}
+\Cref{eq:dumbbell_moment_of_inertia} is consistent with the well-known parallel-axis theorem~\cite{greenwood1988}.
+
+\paragraph{Nonstandard Moment of Inertia}\label{sec:nonstandard_moi}
+The standard moment of inertia \( J \in \R^{3 \times 3} \) of a rigid body is given by
+\begin{align}\label{eq:standard_moment_of_inertia}
+    J = \int_{\mathcal{B}} \vh{\rho}^T \vh{\rho} dm 
+    = \int_{\mathcal{B}}  
+    \begin{bmatrix} 
+        y^2 + z^2 & -xy & -zx \\
+        -xy & z^2 + x^2 & -yz \\
+        -zx & yz & x^2 + y^2
+    \end{bmatrix} dm, 
+\end{align}
+where \( \vc{\rho} = \begin{bmatrix} x & y & z \end{bmatrix}^T\) and defines the position of the mass element \( dm \) in the body fixed frame.
+A nonstandard moment of inertia matrix \( J_d \in \R^{3 \times 3 } \) is defined as
+\begin{align} \label{eq:nonstandard_moment_of_inertia}
+    J_d = \int_{\mathcal{B}} \vc{\rho} \vc{\rho}^T dm = \int_{\mathcal{B}} 
+    \begin{bmatrix}
+        x^2 & xy & zx \\
+        xy & y^2 & yz \\
+        zx & yz & z^2
+    \end{bmatrix} dm.
+\end{align}
+Using~\cref{eq:xTx} and the properties of the outer product, it can be shown that
+\begin{subequations}\label{eq:moi_transformation}
+    \begin{align}
+        J &= \tr{J_d} I - J_d, \label{eq:moi_ns2s}\\
+        J_d &= \frac{1}{2} \tr{J} I - J.\label{eq:moi_s2ns}
+    \end{align}
+\end{subequations}     
+In addition, the following equation is also satisfied for any \( \vc{\Omega} \in \R^3 \)
+\begin{align}\label{eq:moi_hat_prop}
+    \parenth{J \vc{\Omega}}^\wedge = \vh{\Omega} J_d + J_d \vh{\Omega}.
+\end{align}
+\Cref{eq:moi_hat_prop} is easy to prove by substituting \( \vc{\Omega} = \begin{bmatrix} \Omega_1 & \Omega_2 & \Omega_3 \end{bmatrix}^T \) and expanding both sides of~\cref{eq:moi_hat_prop} to
+\begin{align*}
+    \begin{bmatrix}
+        \parenth{J_{yy} + J_{zz}} \Omega_1 - J_{xy} \Omega_2 - J_{zx} \Omega_3 \\
+        -J_{xy}\Omega_1 + \parenth{J_{zz} + J_{xx}} \Omega_2 - J_{yz}\Omega_3 \\
+        -J_{zx}\Omega_1 - J_{yz}\Omega_2 + \parenth{J_{xx} + J_{yy}} \Omega_3
+    \end{bmatrix}^\wedge,
+\end{align*}
+where \( J_{xy} = \int_{\mathcal{B}} xy dm \in \R \) and the other terms are defined similarly.
+
 The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as
@@
 In the above equations, the gravitational potential is denoted by $U$, which is computed by a polyhedron model as described in the subsequent section.
+
+% TODO add definition of the moment of inertia tensor
 

### 2019-02-03 manuscript.tex
Update moment of inertia

--- 2019-02-03 manuscript.tex
@@
 The control inputs to the spacecraft are defined by \( u_f, u_m \in \Re^3 \) which define the control force represented in the inertial frame and the control moment represented in the spacecraft frame, respectively.
+The standard moment of inertia of the dumbbell model is 
+\begin{align}\label{eq:dumbbell_moment_of_inertia}
+    J_I = \sum_i^n J_i + m_i \parenth{\vc{\zeta}_i^T \vc{\zeta}_i I - \vc{\zeta}_i \vc{\zeta}_i^T} , 
+\end{align}
+where \( \vc{\zeta}_i \) is the position of \( m_i \) in the spacecraft fixed frame and the moment of inertia of each sphere is
+\begin{align}\label{eq:sphere_moment_of_inertia}
+    J_i = \begin{bmatrix} 
+        \frac{2}{5} m_i r_i^2 & 0 & 0 \\
+        0 & \frac{2}{5} m_i r_i^2 & 0 \\
+        0 & 0 & \frac{2}{5} m_i r_i^2 
+    \end{bmatrix}.
+\end{align}
+\Cref{eq:dumbbell_moment_of_inertia} is consistent with the well-known parallel-axis theorem~\cite{greenwood1988}.
+We utilize a nonstandard moment of inertia in the equations of motion, \( J_d \in \R^{3 \times 3 } \), which is related to the standard moment of inertia by
+\begin{subequations}\label{eq:moi_transformation}
+    \begin{align}
+        J &= \tr{J_d} I - J_d, \label{eq:moi_ns2s}\\
+        J_d &= \frac{1}{2} \tr{J} I - J.\label{eq:moi_s2ns}
+    \end{align}
+\end{subequations}     
 The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as

### 2019-02-03 manuscript.tex
Remove extended discussion of polyhedron potential model

@@
 References~\cite{werner1994} and~\cite{werner1996} give a detailed derivation of the polyhedron model.
-Here, we summarize the key developments and equations required for implementation.
+Here, we summarize the key equations required for implementation.
 
-Consider three vectors \( \vc{v}_1, \vc{v}_2, \vc{v}_3 \in \R^{3 \times 1} \), assumed to be ordered in a counterclockwise direction about an outward facing normal vector, which define a face.
-For each face we define the face dyad \( \vc{F}_f \) as
-\begin{align}\label{eq:face_dyad}
-    \vc{F}_f &= \hat{\vc{n}}_f \hat{\vc{n}}_f \in \R^{3 \times 3}.
-\end{align}
-Each edge is a member of two faces and has an outward pointing edge normal vector, perpendicular to both the edge and the face normal.
-For the edge connecting the vectors \( \vc{v}_1 \) and \( \vc{v}_2 \), which are shared between the faces \(A\) and \( B\), the per edge dyad is given by
-\begin{align}\label{eq:edge_dyad}
-    \vc{E}_{12} = \hat{\vc{n}}_A \hat{\vc{n}}_{12}^A + \hat{\vc{n}}_B \hat{\vc{n}}_{21}^B \in \R^{3 \times 3}.
-\end{align}
-The edge dyad \( \vc{E}_e  \), is defined for each edge and is a function of the two adjacent faces meeting at that edge.
-The face dyad \( \vc{F}_f \), is defined for each face and is a function of the face normal vectors.
-
-Let \( \vc{r}_i \in \R^{3 \times 1} \) be the vector from the spacecraft to the vertex \( \vc{v}_i \) and it's length is given by \( r_i = \norm{\vc{r}_i} \in \R^{1} \).
-The per-edge factor \( L_e \in \R^{1}\), for the edge connecting vertices \( \vc{v}_i \) and \( \vc{v}_j \), with a constant length \( e_{ij} = \norm{\vc{e}_{ij}} \in \R^1\) is
-\begin{align}\label{eq:edge_factor}
-    L_e &= \ln \frac{r_i + r_j + e_{ij}}{r_i + r_j - e_{ij}}.
-\end{align}
-For the face defined by the vertices \( \vc{v}_i, \vc{v}_j, \vc{v}_k \) the per-face factor \( \omega_f \in \R^{1} \) is
-\begin{align}\label{eq:face_factor}
-    \omega_f &= 2 \arctan \frac{\vc{r}_i \cdot \vc{r}_j \times \vc{r}_k}{r_i r_j r_k + r_i \parenth{\vc{r}_j \cdot \vc{r}_k} + r_j \parenth{\vc{r}_k \cdot \vc{r}_i} + r_k \parenth{\vc{r}_i \cdot \vc{r}_j}} .
-\end{align}
-The gravitational potential due to a constant density polyhedron is given as
-\begin{align}\label{eq:potential}
-    U(\vc{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vc{r}_e \cdot \vc{E}_e \cdot \vc{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vc{r}_f \cdot \vc{F}_f \cdot \vc{r}_f \cdot \omega_f \in \R^1,
-\end{align}
-where \( \vc{r}_e\) and \(\vc{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
-Furthermore we can use these definitions to define the attraction, gravity gradient matrix, and Laplacian as
+We define the attraction, gravity gradient matrix, and Laplacian as
 \begin{align}
@@
 \end{align}
-
 One interesting thing to note is that both~\cref{eq:face_dyad,eq:edge_dyad} can be precomputed without knowledge of the position of the satellite.
@@
 
-\section{Incremental Shape Reconstruction}\label{sec:radius_update}
+\section{Bayesian Shape Reconstruction}\label{sec:radius_update}
 

### 2019-02-03 manuscript.tex
Update bayesian update section

@@
 which is the vector from the origin of the asteroid fixed frame to the surface point of the measurement.
-\todo{check the above}
+
 Given many measurements, \( \vc{p}_i \in \R^3 \), of the asteroid surface we can efficiently update our initial shape estimate to that of the true surface.
@@
 
-The proposed scheme follows the Bayesian estimation, where the degree of confident in the current estimate is compared with that of new measurements. 
+The proposed scheme follows a Bayesian estimation scheme, where the degree of confidence in the current estimate is compared with that of new measurements. 
 More specifically, the radial distance of each vertex, \( v_i = \norm{\vc{v}_i}\), is assumed to be distributed according to the Gaussian distribution
@@
 
-Suppose the $j$-th measurement, namely $p_j\in\Re^3$ is available. 
-As illustrated in \Cref{fig:lidar_example}, the angular resolution of range measurements is assumed to be coarser than the mesh grid of the initial estimate. 
-Consequently, the measurement may not be aligned to any vertex in general. 
-In order to improve the computational efficiency measurement updates are assumed to be local in nature.
-Instead of applying a measurement to all vertices of the mesh, the measurement is only applied to the vertices which are within a specified region of the measurement. 
-From spherical trigonometry~\cite{gade2010}, the central angle between measurement \( \vc{p}_j \) and vertex \( \vc{v}_i \) of the shape estimate is given by
-\begin{align}\label{eq:geodesic_distance}
-    \Delta \sigma_{j,i} = \arctan \parenth{\frac{\norm{\vc{p}_j \times \vc{v}_i}}{\vc{p}_j \cdot \vc{v}_i }}.
-\end{align}
-We define a area of interest, \( \Delta S\in\Re \), about each measurement which defines the surface area over which the measurement will affect the mesh estimate.
+In order to reduce the computational demands, which are typical in point cloud applications, we do not update the complete shape model for each measurement.
+Instead we define an area of interest, \( \Delta S\in\Re \), about each measurement which defines the surface area over which the measurement will affect the mesh estimate.
 We relate \( \Delta S \) to an equivalent angular constraint using
@@
 \begin{align}
-    w_{j, i} = \norm{\vc{p}_j} \Delta \sigma_{j,i} .
+    w_{j, i} = c \norm{\vc{p}_j} \Delta \sigma_{j,i} ,
 \end{align}
+where \( c \) is an additional scaling constant.
 This approach relates the uncertainty of the measurement \( \vc{p}_j \) with the geodesic distance to a given vertex, \( \vc{v}_i \).
@@
 However, the resulting correlation values do not precisely represent the noise or uncertainty characteristics of the sensor in a quantitative manner.
+
+Suppose the $j$-th measurement, namely $p_j\in\Re^3$ is available. 
+As illustrated in \Cref{fig:lidar_example}, the angular resolution of range measurements is assumed to be coarser than the mesh grid of the initial estimate. 
+Consequently, the measurement may not be aligned to any vertex in general. 
+In order to improve the computational efficiency measurement updates are assumed to be local in nature.
+Instead of applying a measurement to all vertices of the mesh, the measurement is only applied to the vertices which are within a specified region of the measurement. 
+From spherical trigonometry~\cite{gade2010}, the central angle between measurement \( \vc{p}_j \) and vertex \( \vc{v}_i \) of the shape estimate is given by
+\begin{align}\label{eq:geodesic_distance}
+    \Delta \sigma_{j,i} = \arctan \parenth{\frac{\norm{\vc{p}_j \times \vc{v}_i}}{\vc{p}_j \cdot \vc{v}_i }}.
+\end{align}
 

### 2019-02-03 manuscript.tex
Update explanation of numeerical example

@@
 We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction, and the spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
+The spacecraft remains at a fixed orbital radius defined as twice the maximum semi-major axis of the asteroid.
 The simulations begin with an triaxial ellipsoid mesh that is sized to match the semi-major axes of each asteroid.
 With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
-LIDAR measurements are generated until the total uncertainty
+LIDAR measurements are generated until the total uncertainty of the model
 \begin{align*}
@@
 is sufficiently small.
-In addition, we compute the volume of the estimate shape throughout the simulation using the algorithm presented here. 
-% TODO Add polyhedron volume algorithm
-
-\todo{explain how the location of spacecraft is selected. cite the reference for the shape model, clarify the above meaning of small uncertainty}
+This uncertainty metric is the summation of the uncertainty of each vertex of the shape estimate.
+As a result, a small total uncertainty is used to indicate that additional measurements would not substantially modify the shape.
+In addition, we compute the volume of the estimated shape and compare against the volume of the truth shape model~\cite{neese2004}.
 

### 2019-02-03 manuscript.tex
Add translational control

@@
 
-\todo{Augment dynamic model with the control force and the torque}
-
 The vertex which minimizes~\cref{eq:explore_cost} 
@@
 We utilize a geometric tracking control system to follow the desired trajectory for the position and the attitude defined above. 
+The spacecraft is assumed to be fully controllable and as a result the translational and rotational dynamics can be decoupled.
+We first derive a translational controller to track an arbitrary position and velocity followed by an attitude controller.
 
+The required translational control are defined in terms of the position and velocity tracking errors.
+The tracking error vectors are easier to define as they evolve on a Euclidean space rather than a nonlinear manifold and are given by
+\begin{subequations}\label{eq:translation_error_variables}
+\begin{align}
+    e_x &= x - x_d ,\\
+    e_v &= v - \dot{x}_d.
+\end{align}
+\end{subequations}
+The error dynamics are given by
+\begin{subequations}\label{eq:translation_error_dynamics}
+\begin{align}
+    \dot{e}_x &= v - \dot{x}_d, \\
+    \dot{e}_v &= \dot{v} - \ddot{x}_d .
+\end{align}
+\end{subequations}
+A control input, \( u_f \), is derived to ensure asymptotic trajectory tracking for the translational dynamics.
+\begin{prop}[Control for Translation Dynamics]\label{prop:translational_control}
+    Given a desired trajectory \( \vc{x}_d \) and positive constants \( k_x, k_v, c \in \R \) we define a control input \( \vc{u}_f \in \R \) as follows:
+    \begin{align}\label{eq:translational_control}
+        \vc{u}_f = -k_x e_x - k_v e_v - F_{ext} + m \ddot{x}_d .
+    \end{align}
+    If \( c \) is chosen such that
+    \begin{align}\label{eq:translational_control_gain_bound}
+        0 < c < \min \braces{\sqrt{k_x m}, \frac{4 k_x k_v m}{ k_v \parenth{4 k_x m - k_v} }   }
+    \end{align}
+    then the zero equilibrium of the error vectors~\cref{eq:translation_error_variables} is stable in the sense of Lyapunov.
+    Furthermore, \( e_x, e_v \to 0 \) as \( t \to \infty\).
+\end{prop}
+\begin{proof}
+The translational dynamics can be defined as
+\begin{align}\label{eq:translation_dynamics_simple}
+    \dot{x} &= v , \\
+    m \dot{v} &= F_{ext} + u_f ,
+\end{align}
+where \( m \in \R \) is defined as the total mass of the vehicle while \( F_{ext} \) is the total external force.
+
+Consider the Lyapunov function
+\begin{align}\label{eq:translational_lyapunov}
+    V = \frac{1}{2} k_x e_x^T e_x + \frac{1}{2} m e_v^T e_v + c e_x^T e_x.
+\end{align}
+\Cref{eq:translational_lyapunov} is also equivalent to
+\begin{align}\label{eq:translational_lyapunov_matrix}
+    V = z^T W_1 z , 
+\end{align}
+where \( z = \begin{bmatrix} \norm{e_x} & \norm{e_v} \end{bmatrix}^T \) and \( W_1\in \R^2\) is defined as
+\begin{align}\label{eq:translational_lyapunov_W}
+    W_1 = \begin{bmatrix}
+        \frac{1}{2} k_x & \frac{1}{2} c \\
+        \frac{1}{2} c & \frac{1}{2} m 
+    \end{bmatrix}.
+\end{align}
+The time derivative of~\cref{eq:translational_lyapunov} can then be defined as
+\begin{align}\label{eq:translation_lyapunov_derivative}
+    \dot{\mathcal{V} } = - \parenth{k_v - c} e_v^T e_v - \frac{k_x c}{m} e_x^T e_x - \frac{k_v c}{m} e_x^T e_v, 
+\end{align}
+where we used~\cref{eq:translational_control,eq:translation_error_variables,eq:translation_error_dynamics}.
+\Cref{eq:translation_lyapunov_derivative} can also be redefined as
+\begin{align}\label{eq:translational_lyapunov_derivative_matrix}
+    \dot{\mathcal{V}} = - z^T W_2 z, 
+\end{align}
+where \( W_2 \in \R^2 \) is defined as
+\begin{align}\label{eq:translational_lyapunov_W2}
+    W_2 = \begin{bmatrix}
+        \frac{k_x c}{m} & \frac{k_v^2 c^2}{2 m^2} \\
+        \frac{k_v c}{2 m} & k_v - c
+    \end{bmatrix}.
+\end{align}
+If \( c \) is chosen such that~\cref{eq:translational_control_gain_bound} is satisfied then \( W_1, W_2 \) will be positive definite.
+As a result, this shows that \( \mathcal{V} > 0 , \dot{ \mathcal{V}} < 0 \) and that the zero equilibrium of the error variables, namely \( x_d, \dot{x}_d \) is asymptotically stable~\cite{khalil1996}.
+\end{proof}
+
+The control gains are chosen based on the desired closed-loop system response. 
+A variety of techniques are available to choose these gains, but a simple linear analysis offers a straightforward and systematic approach to choosing suitable values. 
+We use the control inputs defined in~\cref{eq:translational_control,eqn:adaptive_control} and substitute them into the dynamic equations of motion in~\cref{eq:inertial_position_dynamics,eq:inertial_velocity_dynamics,eq:inertial_attitude_dynamics,eq:inertial_angvel_dynamics}.
 \todo{add description of control}

### 2019-02-03 manuscript.tex
Add geometric control

@@
 The spacecraft is assumed to be fully controllable and as a result the translational and rotational dynamics can be decoupled.
-We first derive a translational controller to track an arbitrary position and velocity followed by an attitude controller.
+We first present an geometric attitude controller used to track the desired attitude command \( R_d \).
+This is followed by a translational controller to track the desired position \( x_d \).
+
+First, an attitude error function \(A : \SO \times \SO  \to \R \), an attitude error vector \( e_R : \SO \times \SO \to \R \), and an angular velocity error \( e_\Omega : \SO \times \R^3 \times \SO \times \R^3 \) are defined as
+\begin{subequations}\label{eq:attitude_error_function}
+\begin{align}
+    A(R, R_d) &= \frac{1}{2}  \tr{G\parenth{I - R_d^T R}}, \label{eq:A} \\
+    e_R &= \frac{1}{2} G \parenth{R_d^T R - R^T R_d^\vee}, \label{eq:eRA}\\
+    e_\Omega &= \Omega - R^T R_d \Omega_d \label{eq:eWA}.
+\end{align}
+\end{subequations}
+Then the following properties hold:
+\begin{enumerate}
+    \item \label{item:prop_A_psd} \( A \) is  positive definite about \( R = R_d \) on \( \SO \).
+    \item \label{item:prop_eRA} The variation of \( A \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
+	\begin{align}\label{eq:dirDiff_A}
+		\dirDiff{A}{R} &= \eta \cdot e_{R} ,
+	\end{align}
+	where the notation \( \dirDiff{A}{R} \) represents the directional derivative of $A$ with respect to $R$ along the direction $\delta R$.
+\item \label{item:prop_A_critical_points} The critical points of \( A \), where \( e_R = 0 \) are \( \braces{R_d} \cup \braces{R_d \exp(\pi \hat s) } \) for \( s \in \braces{e_1, e_2, e_3}\)
+    \item \label{item:prop_A_quadratic} \( \Psi \) is a locally quadratic function, which means there exist constants \( 0 < n_1 \leq n_2 \) such that
+    \begin{align}\label{eq:A_bound}
+        n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 ,
+    \end{align}
+    for $0<\psi < h_1 $ where the constants \( n_1 = \frac{h_1}{h_2 + h_3} \) and \( n_2 = \frac{h_1 h_4}{h_5 \parenth{h1 - \psi} }\) for
+	\begin{align*}
+		h_1 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
+		h_2 &= \max\braces{\parenth{g_1 -g_2}^2,\parenth{g_2 -g_3}^2 , \parenth{g_3 -g_1}^2} ,\\
+		h_3 &= \max\braces{\parenth{g_1 + g_2}^2, \parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2}, \\		
+        h_4 &= \max\braces{g_1 + g_, g_2 +g_3, g_3 + g_1}, \\
+        h_5 &= \max\braces{\parenth{g_1 + g_2}^2, \parenth{g_2 + g_3}^2, \parenth{g_3 + g_1}^2}.
+	\end{align*}
+\end{enumerate}
+The proof of these properties is available~\cref{proof:attitude_configuration_error}.
+
+With the appropriate attitude configuration error we now present the error dynamics in~\cref{prop:attractive_error_dynamics}, which are used in the subsequent development of the nonlinear control system.
+The attitude error dynamics for \( A(R, R_d), e_\Omega \) satisfy
+\begin{gather}
+    \diff{}{t} \parenth{A(R)} = e_{R_A} \cdot e_\Omega , \label{eq:A_dot} \\
+    \diff{}{t} \parenth{e_{R_A}} = E(R, R_d) e_\Omega , \label{eq:eRA_dot} \\
+    \diff{}{t} \parenth{e_\Omega} = J^{-1} \parenth{-\hat{\Omega} J \Omega + u_m + M_{ext}} , \label{eq:eW_dot}
+\end{gather}
+where the matrix \(E(R,R_d)\in \R^{3\times3} \) is given by
+\begin{align}
+    E(R,R_d) = &\frac{1}{2} \parenth{\tr{R^T R_d G}I - R^T R_d G} , \label{eq:E} \\
+\end{align}
+The proof is show in~\Cref{proof:attractive_error_dynamics}
+With the appropriate attitude configuration error we now present an attitude controller for attitude stabilization and tracking of the inertial attitude dynamics given in~\cref{eq:inertial_attitude_dynamics,eq:inertial_angvel_dynamics}.
+
+Given a desired attitude command \( \parenth{R_d, \Omega_d = 0} \) and positive constants \( k_R, k_\Omega \in \R \) we define a control input \( u \in \R^3 \) as follows
+\begin{gather}
+    u = -k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - M_{ext}. \label{eqn:nodist_control}
+\end{gather}
+Then the zero equilibrium of the attitude error is asymptotically stable.
+The proof is show in~\cref{proof:attitude_controller}.
 
@@
 A control input, \( u_f \), is derived to ensure asymptotic trajectory tracking for the translational dynamics.
-\begin{prop}[Control for Translation Dynamics]\label{prop:translational_control}
     Given a desired trajectory \( \vc{x}_d \) and positive constants \( k_x, k_v, c \in \R \) we define a control input \( \vc{u}_f \in \R \) as follows:
@@
     Furthermore, \( e_x, e_v \to 0 \) as \( t \to \infty\).
-\end{prop}
-\begin{proof}
-The translational dynamics can be defined as
-\begin{align}\label{eq:translation_dynamics_simple}
-    \dot{x} &= v , \\
-    m \dot{v} &= F_{ext} + u_f ,
-\end{align}
-where \( m \in \R \) is defined as the total mass of the vehicle while \( F_{ext} \) is the total external force.
-
-Consider the Lyapunov function
-\begin{align}\label{eq:translational_lyapunov}
-    V = \frac{1}{2} k_x e_x^T e_x + \frac{1}{2} m e_v^T e_v + c e_x^T e_x.
-\end{align}
-\Cref{eq:translational_lyapunov} is also equivalent to
-\begin{align}\label{eq:translational_lyapunov_matrix}
-    V = z^T W_1 z , 
-\end{align}
-where \( z = \begin{bmatrix} \norm{e_x} & \norm{e_v} \end{bmatrix}^T \) and \( W_1\in \R^2\) is defined as
-\begin{align}\label{eq:translational_lyapunov_W}
-    W_1 = \begin{bmatrix}
-        \frac{1}{2} k_x & \frac{1}{2} c \\
-        \frac{1}{2} c & \frac{1}{2} m 
-    \end{bmatrix}.
-\end{align}
-The time derivative of~\cref{eq:translational_lyapunov} can then be defined as
-\begin{align}\label{eq:translation_lyapunov_derivative}
-    \dot{\mathcal{V} } = - \parenth{k_v - c} e_v^T e_v - \frac{k_x c}{m} e_x^T e_x - \frac{k_v c}{m} e_x^T e_v, 
-\end{align}
-where we used~\cref{eq:translational_control,eq:translation_error_variables,eq:translation_error_dynamics}.
-\Cref{eq:translation_lyapunov_derivative} can also be redefined as
-\begin{align}\label{eq:translational_lyapunov_derivative_matrix}
-    \dot{\mathcal{V}} = - z^T W_2 z, 
-\end{align}
-where \( W_2 \in \R^2 \) is defined as
-\begin{align}\label{eq:translational_lyapunov_W2}
-    W_2 = \begin{bmatrix}
-        \frac{k_x c}{m} & \frac{k_v^2 c^2}{2 m^2} \\
-        \frac{k_v c}{2 m} & k_v - c
-    \end{bmatrix}.
-\end{align}
-If \( c \) is chosen such that~\cref{eq:translational_control_gain_bound} is satisfied then \( W_1, W_2 \) will be positive definite.
-As a result, this shows that \( \mathcal{V} > 0 , \dot{ \mathcal{V}} < 0 \) and that the zero equilibrium of the error variables, namely \( x_d, \dot{x}_d \) is asymptotically stable~\cite{khalil1996}.
-\end{proof}
+The proof is shown in~\cref{proof:translational_control}.
 
@@
 
-%\section*{Appendix}
-
-%An Appendix, if needed, appears \textbf{before} research funding information and other acknowledgments.
-
+\section*{Appendix}
+
+\subsection*{Proof of Attitude Configuration Error}\label{proof:attitude_configuration_error}
+To prove~\cref{item:prop_psi_psd}, we first seek to show that \( A(R_d) \) is a critical point by showing that the first derivative is zero at \( R_d \).
+The infinitesimal variation of a rotation matrix is defined as
+\begin{align*}
+    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta}.
+\end{align*}
+Using this, the variation of~\cref{eq:A} is taken with respect to \( R \) as
+\begin{align*}
+	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee ,
+%	&= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
+\end{align*}
+where we used~\cref{eqn:hat1} to achieve the simplified form.
+\Cref{eq:dirDiff_A} also proves~\cref{item:prop_eRA}.
+Evaluating~\cref{eq:dirDiff_A} at \( R = R_d \) demonstrates that \( R_d \) is a critical point of \( A \).
+Next, the second derivative of \( A \) is computed as
+\begin{align*}
+    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T \delta R - \delta R^T R_d G}^\vee  \\
+    &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee\\
+    &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee  \\
+    &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
+\end{align*}
+where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
+Evaluating the Hessian at \( R = R_d \)
+\begin{align}\label{eq:A_hessian}
+    \Hess(A)\cdot (\delta R,\delta R)\big|_{R=R_d} = \eta \cdot \frac{1}{2} \parenth{\tr{G}I -  G} \eta 
+\end{align}
+shows that the Hessian is positive definite at \( R_d \) and therefore the critical point is a minimum for any variation \( \eta \) and proves~\cref{item:prop_A_psd}.
+
+To prove~\cref{item:prop_A_critical_points} we must first determine the critical points of~\cref{eq:eRA}.
+The derivations are originally presented in~\cite{bullo2004,chaturvedi2011a} and we present and expand on their original descriptions.
+We define the relative attitude error as \( Q = R_d^T R \) and expand~\cref{eq:eRA} as
+\begin{align*}
+    e_{R_A} &= \frac{1}{2} \parenth{G Q - Q^T G} ^ \vee, \\
+            &= \frac{1}{2} \parenth{%
+            \begin{bmatrix} g_1 & 0 & 0 \\ 0 & g_2 & 0 \\ 0 & 0 & g_3 \end{bmatrix}
+            \begin{bmatrix} q_{11} & q_{12} & q_{13} \\ q_{21} & q_{22} & q_{23} \\ q_{31} & q_{32} & q_{33}\end{bmatrix}
+            -
+            \begin{bmatrix} q_{11} & q_{21} & q_{31} \\ q_{12} & q_{22} & q_{32} \\ q_{13} & q_{23} & q_{33}\end{bmatrix}
+            \begin{bmatrix} g_1 & 0 & 0 \\ 0 & g_2 & 0 \\ 0 & 0 & g_3 \end{bmatrix}
+            }^\vee , \\
+            &= \frac{1}{2} \begin{bmatrix} g_3 q_{32} - g_2 q_{23} \\ g_1 q_{13} - g_3 q_{31} \\ g_2 q_{21} - g_1 q_{12}\end{bmatrix}
+\end{align*}
+At a critical point, the following equations must be satisfied
+\begin{subequations}\label{eq:erA_critical_conditons}
+    \begin{align}
+        g_3q_{32} &= g_2 q_{23}, \\
+        g_1 q_{13} &= g_3 q_{31}, \\
+        g_2 q_{21} &= g_1 q_{12}.
+    \end{align}
+\end{subequations}     
+Using the conditions in~\cref{eq:erA_critical_conditons} the relative attitude error \( Q \) becomes
+\begin{align}\label{eq:relative_attitude_error}
+    Q = R_d^T R_e =
+    \begin{bmatrix} 
+        q_{11} & q_{12} & q_{13} \\ 
+        \frac{g_1}{g_2} q_{12} & q_{22} & q_{23} \\
+        \frac{g_1}{g_3} q_{13} & \frac{g_2}{g_3} q_{23} & q_{33}
+    \end{bmatrix}
+    \in \SO
+\end{align}
+Since, \( Q = R_d^T R \) is orthonormal the main diagonal of \( QQ^T \) is equal to \num{1} and each column of \( Q \) is unit length.
+\begin{align*}
+    Q Q^T &= I, \\
+          &= \begin{bmatrix}
+    Q_{11} & Q_{12} & Q_{13} \\ 
+    Q_{21} & Q_{22} & Q_{23} \\ 
+    Q_{31} & Q_{32} & Q_{33} 
+\end{bmatrix}, 
+\end{align*}
+where
+\begin{align*}
+    Q_{11} &= q_{11}^2 + q_{12}^2 + q_{13}^2 ,\\
+    Q_{12} &= q_{11}q_{12}\frac{g_1}{g_2} + q_{12}q_{22} + q_{13}q_{23} ,\\
+    Q_{13} &= q_{11}q_{13}\frac{g_1}{g_3} + q_{12}q_{23}\frac{g_2}{g_3} + q_{13}q_{33},\\
+    Q_{21} &= q_{11}q_{12}\frac{g_1}{g_2}  + q_{12}q_{22} + q_{23}q_{13} ,\\
+    Q_{22} &= \frac{g_1^2}{g_2^2}q_{12}^2 + q_{22}^2 + q_{23}^2 ,\\
+    Q_{23} &= \frac{g_1^2}{g_2g_3} q_{12}q_{13} + \frac{g_2}{g_3}q_{23}q_{22} + q_{23}q_{33},\\
+    Q_{31} &= \frac{g_1}{g_3} q_{11}q_{13} + \frac{g_2}{g_3}q_{23}q_{12} + q_{33}q_{13},\\
+    Q_{32} &= \frac{g_1^2}{g_3 g_2} q_{12}q_{13} + \frac{g_2}{g_3} q_{23}q_{22} + q_{33} q_{23},\\
+    Q_{33} &= \frac{g_1^2}{g_3^2}q_{13}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 + q_{33}^2.
+\end{align*}
+As a result the following \num{6} conditions must be satisfied when \( e_{R_A} = 0 \):
+\begin{align}
+    q_{11}^2 + q_{12}^2 + q_{13}^2 &= 1,\label{eq:orthogonal_1} \\
+    \frac{g_1^2}{g_2^2}q_{12}^2 + q_{22}^2 + q_{23}^2 &= 1, \label{eq:orthogonal_2}\\
+    \frac{g_1^2}{g_3^2}q_{13}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 + q_{33}^2 &= 1, \label{eq:orthogonal_3}\\
+    q_{11}^2 + \frac{g_1^2}{g_2^2}q_{12}^2 + \frac{g_1^2}{g_3^2}q_{13}^2 &= 1, \label{eq:unit_norm_1}\\
+    q_{12} + q_{22}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 &= 1, \label{eq:unit_norm_2}\\
+    q_{13}^2 + q_{23}^2 + q_{33}^2 &= 1.\label{eq:unit_norm_3}
+\end{align}
+We can further simplify these relationships by rewriting~\cref{eq:orthogonal_1,eq:orthogonal_2,eq:orthogonal_3} as
+\begin{align}
+    q_{11}^2 &= 1 - q_{12}^2 - q_{13}^2 , \\
+    q_{22}^2 &= 1 - \frac{g_1^2}{g_2^2} q_{12}^2 - q_{23}^2, \\
+    q_{33}^2 &= 1 - \frac{g_1^2}{g_3^2}q_{13}^2 - \frac{g_2^2}{g_3^2}q_{23}^2 
+\end{align}
+and substituting these relationships into~\cref{eq:unit_norm_1,eq:unit_norm_2,eq:unit_norm_3} to arrive at
+\begin{subequations}\label{eq:era_critical_point_conditions}
+\begin{align}
+    \parenth{1 - \frac{g_1^2}{g_2^2} } q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 , \label{eq:era_condition_1}\\
+    \parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}}q_{23}^2 &= 0 , \label{eq:era_condition_2}\\
+    \parenth{1 - \frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0.\label{eq:era_condition_3}
+\end{align}
+\end{subequations}     
+The relationships in~\cref{eq:era_critical_point_conditions} are equivalent to the statement that \( e_{R_A} = 0 \) and must also be satisfied at each critical point.
+Since each \( g_i \) is distinct and greater than zero, the solution to~\cref{eq:erA_critical_conditons}, or equivalently \( e_{R_A} = 0 \), must satisfy one of two possible conditions:
+\begin{enumerate}[label=(\roman*)]
+    \item \label{item:condition_1} \( q_{12} = q_{13} = q_{23} =0\)
+    \item \label{item:condition_2} \( q_{ij} \neq 0 \; \forall \; i \neq j \)
+\end{enumerate}
+These conditions can be determined by noticing that~\cref{item:condition_1} is the trivial solution.
+For~\cref{item:condition_2}, consider the situation that \( q_{12} \neq 0 \) then from the fact that \( g_i \) are distinct yields the fact that \( \parenth{1 - \frac{g_1^2}{g_2^2} } \neq 0 \) and \( \parenth{1 - \frac{g_1^2}{g_3^2} } \neq 0 \) which means that \( q_{13}^2 \neq 0 \) since the terms must add to zero.
+Similar arguments can be made for the other relations in~\cref{eq:era_critical_point_conditions} which means that the solutions must satisfy either~\cref{item:condition_1} or~\cref{item:condition_2}.
+
+Now consider~\cref{item:condition_2} and assume that \( g_2 > g_1 \) and \( q_{12}, q_{13}, q_{23} \neq 0 \).
+From~\cref{eq:era_condition_1} this implies that \( \parenth{1 - \frac{g_1^2}{g_2^2} } q_{12}^2 > 0\) since \( q_{12}^2 > 0\).
+Therefore, in order for~\cref{eq:era_condition_1} to be satisfied means that \( \parenth{1 - \frac{g_1^2}{g_3^2} } q_{13}^2 < 0 \) which further implies that \( g_1 > g_3 \).
+As a result, \( g_2 > g_1 > g_3 \).
+Using this inequality in~\cref{eq:era_condition_3} implies that
+\begin{align*}
+    \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23} < 0, \quad \parenth{1 - \frac{g_1^2}{g_3^2}} q_{13}^2 < 0.
+\end{align*}
+Therefore the left hand side of~\cref{eq:era_condition_3} is negative and a contradiction.
+Applying a similar logic for the case \( g_1 > g_2 \) shows that~\cref{item:condition_2} is not possible and therefore~\cref{item:condition_1} must be satisfied.
+Substituting~\cref{item:condition_1} into~\cref{eq:relative_attitude_error} shows that the main diagonal of \( Q \) must be composed of \( + 1 \) or \( -1 \).
+Thus, the critical points of \( A(R) \) are those provided in~\cref{item:prop_A_critical_points}.
+These critical points correspond to additional rotations of \SI{180}{\degree} about each axes, or more explicitly \( R_e = \braces{R_d, R_\alpha, R_\beta, R_\gamma} \) where
+\begin{align}
+    R_\alpha &= R_d \begin{bmatrix} 1 & 0 & 0 \\ 0 & -1 & 0 \\ 0 & 0 & -1 \end{bmatrix} , \\
+    R_\beta &= R_d \begin{bmatrix} -1 & 0 & 0 \\ 0 & -1 & 0 \\ 0 & 0 & 1 \end{bmatrix} , \\
+    R_\gamma &= R_d \begin{bmatrix} -1 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & -1 \end{bmatrix}.
+\end{align}
+
+The original proof for~\cref{item:prop_psi_quadratic} is presented in~\cite{lee2011a} and summarized in this section.
+Define \( Q = R_d^T R = \exp \hat{\vc{x}} \in \SO \) for any \( \vc{x} \in \R^3 \) from Rodrigues' formula
+\begin{align}\label{eq:rodrigues_formula}
+    Q = \exp{\theta \hat{\vc{x}}} = I + \sin \theta \vh{x} + \parenth{1 - \cos \theta} \vh{x}^2 \in \SO.
+\end{align}
+Using a symbolic computation tool one can then find
+\begin{align}\label{eq:psi_rodrigues}
+    A &= \frac{1 - \cos \norm \vc{x}}{2\norm{\vc{x}^2}} \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i + g_j} x_k^2, \\
+    \norm{e_{R_A}}^2 &= \frac{\parenth{1 - \cos \norm{\vc{x}}^2} }{4 \norm{\vc{x}}^4}  \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i - g_j}^2 x_i^2 x_j^2 + \frac{\sin^2 \norm{\vc{x}}}{4 \norm{\vc{x}}^2} \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i + g_j}^2 x_k^2,
+\end{align}
+where \( \mathcal{C} = \braces{ \parenth{1, 2, 3} , \parenth{2, 3, 1} , \parenth{3, 1, 2} } \).
+Using~\cref{eq:psi_rodrigues} one can show
+\begin{align}
+    \frac{\norm{e_{R_A}}^2}{A} \leq \frac{h_2 + h_3}{h_1} , \quad \frac{A}{\norm{e_{R_A}}^2} \leq \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi} } ,
+\end{align}
+which proves~\cref{item:prop_A_quadratic}.
+
+\section{Proof of~\Cref{prop:attractive_error_dynamics}}\label{proof:attractive_error_dynamics}
+From the kinematics \( \dot{R} = R \hat{\Omega}\), and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
+\begin{gather*}
+	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega.
+\end{gather*}
+Applying this to the time derivative of~\cref{eq:A} gives
+\begin{gather*}
+	\diff{}{t} (A) = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega}.
+\end{gather*}
+Applying~\cref{eqn:hat1} into this shows~\cref{eq:A_dot}.
+
+The time derivative of the attractive attitude error vector, \( e_{R_A} \), is given by
+\begin{gather*}
+	\diff{}{t} ( e_{R_A}) = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee.
+\end{gather*}
+Using the hat map property given in~\cref{eqn:xAAx} this is further reduced to~\cref{eq:eRA_dot,eq:E}.
+
+% TODO Add link to dynamics that includes both external force and a disturbance
+We show~\cref{eq:eW_dot} by rearranging~\cref{eq:Wdot} as 
+\begin{align*}
+    \diff{}{t} e_\Omega = \dot{\Omega} = J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta +M_{ext}}.
+\end{align*}
+
+\subsection*{Proof of Attitude Controller}\label{proof:attitude_controller}
+Consider the following Lyapunov function:
+\begin{gather*}%\label{eqn:v_nodist}
+	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d). 
+\end{gather*}
+From~\cref{item:prop_psi_psd} of~\Cref{prop:attitude_control_configuration_error}, \(\mathcal{V} \geq 0 \).
+Using~\cref{eq:eW_dot,eq:A_dot} with \( \Delta = 0 \), the time derivative of \( \mathcal{V} \) is given by
+\begin{align*}%\label{eqn:vdot_nodist}
+	\dot{\mathcal{V}} &= -k_\Omega \norm{e_\Omega}^2. 
+%	e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
+\end{align*}
+Since \( \mathcal{V} \) is positive definite and \( \dot{\mathcal{V}} \) is negative semi-definite, the zero equilibrium point \( e_R, e_\Omega \) is stable in the sense of Lyapunov. 
+This also implies \( \lim_{t\to\infty} \norm{e_\Omega} = 0 \) and \( \norm{e_{R_A}} \) is uniformly bounded, as the Lyapunov function is non-increasing.
+From~\cref{eq:eRA_dot}, $\lim_{t\to\infty} \dot e_R =0$.
+One can show that \( \norm{\ddot{e}_R} \) is bounded.
+From Barbalat's Lemma, it follows \( \lim_{t\to\infty}\norm{\dot{e}_R} = 0 \)~\cite[Lemma 8.2]{khalil1996}. 
+Therefore, the equilibrium is asymptotically stable.
+
+Furthermore, since \( \dot{\mathcal{V}} \leq 0 \) the Lyapunov function is uniformly bounded which implies 
+\begin{align*}
+	A(R(t)) \leq \mathcal{V}(t) \leq \mathcal{V}(0).
+\end{align*}
+
+An Appendix, if needed, appears \textbf{before} research funding information and other acknowledgments.
+
+\subsection*{Proof of Translational Control}\label{proof:translational_control}
+
+The translational dynamics can be defined as
+\begin{align}\label{eq:translation_dynamics_simple}
+    \dot{x} &= v , \\
+    m \dot{v} &= F_{ext} + u_f ,
+\end{align}
+where \( m \in \R \) is defined as the total mass of the vehicle while \( F_{ext} \) is the total external force.
+
+Consider the Lyapunov function
+\begin{align}\label{eq:translational_lyapunov}
+    V = \frac{1}{2} k_x e_x^T e_x + \frac{1}{2} m e_v^T e_v + c e_x^T e_x.
+\end{align}
+\Cref{eq:translational_lyapunov} is also equivalent to
+\begin{align}\label{eq:translational_lyapunov_matrix}
+    V = z^T W_1 z , 
+\end{align}
+where \( z = \begin{bmatrix} \norm{e_x} & \norm{e_v} \end{bmatrix}^T \) and \( W_1\in \R^2\) is defined as
+\begin{align}\label{eq:translational_lyapunov_W}
+    W_1 = \begin{bmatrix}
+        \frac{1}{2} k_x & \frac{1}{2} c \\
+        \frac{1}{2} c & \frac{1}{2} m 
+    \end{bmatrix}.
+\end{align}
+The time derivative of~\cref{eq:translational_lyapunov} can then be defined as
+\begin{align}\label{eq:translation_lyapunov_derivative}
+    \dot{\mathcal{V} } = - \parenth{k_v - c} e_v^T e_v - \frac{k_x c}{m} e_x^T e_x - \frac{k_v c}{m} e_x^T e_v, 
+\end{align}
+where we used~\cref{eq:translational_control,eq:translation_error_variables,eq:translation_error_dynamics}.
+\Cref{eq:translation_lyapunov_derivative} can also be redefined as
+\begin{align}\label{eq:translational_lyapunov_derivative_matrix}
+    \dot{\mathcal{V}} = - z^T W_2 z, 
+\end{align}
+where \( W_2 \in \R^2 \) is defined as
+\begin{align}\label{eq:translational_lyapunov_W2}
+    W_2 = \begin{bmatrix}
+        \frac{k_x c}{m} & \frac{k_v^2 c^2}{2 m^2} \\
+        \frac{k_v c}{2 m} & k_v - c
+    \end{bmatrix}.
+\end{align}
+If \( c \) is chosen such that~\cref{eq:translational_control_gain_bound} is satisfied then \( W_1, W_2 \) will be positive definite.
+As a result, this shows that \( \mathcal{V} > 0 , \dot{ \mathcal{V}} < 0 \) and that the zero equilibrium of the error variables, namely \( x_d, \dot{x}_d \) is asymptotically stable~\cite{khalil1996}.
 %\section*{Funding Sources}

### 2019-02-03 manuscript.tex
Fix cost function

@@
 
-Utilizing these metric, a landing site is chosen to minimize the surface cost given as
+Utilizing these metrics, a landing site is chosen to minimize the surface cost given as
 \begin{align}\label{eq:surface_cost}
-    J_l =  J_{\text{distance}} - J_{\text{science}},
+    \min_{v_i} J_l(x, v_i) =  J_{\text{distance}}(x, v_i) - J_{\text{science}}(v_i),
 \end{align}
 subject to a hard inequality constraint requiring that the surface slope is less than a threshold, i.e., \( \phi \leq \phi_m \).
-
-\todo{rewrite the above equation as a function of a candidate landing site location; we also need to describe how many points are considered for minimization; is it just the set of vertices}
 

### 2019-02-03 manuscript.tex
Add link to cgal

@@
 The goal of refinement, or more generally remeshing, is given a mesh ( or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
-In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL).
-\todo{add reference to CGAL}
+In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL)~\cite{cgalproject2018}.
 This algorithm uses an iterative method which repeatedly splits long edges, collapses short edges, and relocates vertices until all edges are approximately the desired target edge length.

### 2019-02-15 manuscript.tex
Add link to videos
Updating manuscript

@@
 
-\section*{Nomenclature}
-
-\noindent(Nomenclature entries should have the units identified)
-\noindent{Add elements}
+% \section*{Nomenclature}
+
+% \noindent(Nomenclature entries should have the units identified)
+% \noindent{Add elements}
 % {\renewcommand\arraystretch{1.0}
@@
 
-\todo{Define every variable, $m_1,m_2,\rho_1,\ldots$. }
-
 Using Hamilton's principle one can derive the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
@@
 Here, we summarize the key equations required for implementation.
-
 We define the attraction, gravity gradient matrix, and Laplacian as
@@
 \end{align}
-One interesting thing to note is that both~\cref{eq:face_dyad,eq:edge_dyad} can be precomputed without knowledge of the position of the satellite.
-They are both solely functions of the vertices and edges of the polyhedral shape model and are computed once and stored.
-Once a position vector \( \vc{r} \) is defined, the scalars given in~\cref{eq:edge_factor,eq:face_factor} can be computed for each face and edge.
-Finally,~\cref{eq:potential} is used to compute the gravitational potential on the spacecraft.
 The Laplacian, defined in~\cref{eq:laplacian}, gives a simple method to determine if the spacecraft has collided with the body~\cite{werner1996}.
@@
 \end{enumerate}
-The proof of these properties is available~\cref{proof:attitude_configuration_error}.
-
-With the appropriate attitude configuration error we now present the error dynamics in~\cref{prop:attractive_error_dynamics}, which are used in the subsequent development of the nonlinear control system.
+The proof of these properties is available~\cite{kulumani2017a}.
+
+With the appropriate attitude configuration error we now present the error dynamics, which are used in the subsequent development of the nonlinear control system.
 The attitude error dynamics for \( A(R, R_d), e_\Omega \) satisfy
@@
 \begin{align}
-    E(R,R_d) = &\frac{1}{2} \parenth{\tr{R^T R_d G}I - R^T R_d G} , \label{eq:E} \\
-\end{align}
-The proof is show in~\Cref{proof:attractive_error_dynamics}
-With the appropriate attitude configuration error we now present an attitude controller for attitude stabilization and tracking of the inertial attitude dynamics given in~\cref{eq:inertial_attitude_dynamics,eq:inertial_angvel_dynamics}.
-
+    E(R,R_d) = &\frac{1}{2} \parenth{\tr{R^T R_d G}I - R^T R_d G} , \label{eq:E}
+\end{align}
+The proof is available in~\cite{kulumani2017a}.
+
+Using these properties we can now define an attitude control input to allow the vehicle to track attitude errors.
 Given a desired attitude command \( \parenth{R_d, \Omega_d = 0} \) and positive constants \( k_R, k_\Omega \in \R \) we define a control input \( u \in \R^3 \) as follows
@@
 Then the zero equilibrium of the attitude error is asymptotically stable.
-The proof is show in~\cref{proof:attitude_controller}.
+The proof is show in~\cite{kulumani2017a}.
 
@@
     Furthermore, \( e_x, e_v \to 0 \) as \( t \to \infty\).
-The proof is shown in~\cref{proof:translational_control}.
+    The proof is shown in~\cite{kulumani2017a}.
 
@@
 \end{figure}
-
-\todo{as the nonlinear controller is added, we may want to add more plots for tracking errors; we can add a link to videos}
+A number of videos are available at \url{http://bit.ly/shape_reconstruction} which demonstrate these results.
+% \todo{as the nonlinear controller is added, we may want to add more plots for tracking errors; we can add a link to videos}
 

### 2019-02-15 manuscript.tex
Update manuscript

@@
 \begin{align}
-    \dot{\vc{x}} &= \vc{v}, \\
+    \dot{\vc{x}} &= \vc{v}, \label{eq:x_dot}\\
     \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2} + u_f,\label{eq:v_dot} \\
-    \dot{R} &= R S(\vc{\Omega}) , \\
-    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2 + u_m.
+    \dot{R} &= R S(\vc{\Omega}) , \label{eq:R_dot}\\
+    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2 + u_m. \label{eq:omega_dot}
 \end{align}
@@
 A variety of techniques are available to choose these gains, but a simple linear analysis offers a straightforward and systematic approach to choosing suitable values. 
-We use the control inputs defined in~\cref{eq:translational_control,eqn:adaptive_control} and substitute them into the dynamic equations of motion in~\cref{eq:inertial_position_dynamics,eq:inertial_velocity_dynamics,eq:inertial_attitude_dynamics,eq:inertial_angvel_dynamics}.
-\todo{add description of control}
+We use the control inputs defined in~\cref{eq:translational_control,eqn:nodist_control} and substitute them into the dynamic equations of motion in~\cref{eq:x_dot,eq:v_dot,eq:R_dot,eq:omega_dot}.
 
@@
 
-\section*{Appendix}
-
-\subsection*{Proof of Attitude Configuration Error}\label{proof:attitude_configuration_error}
-To prove~\cref{item:prop_psi_psd}, we first seek to show that \( A(R_d) \) is a critical point by showing that the first derivative is zero at \( R_d \).
-The infinitesimal variation of a rotation matrix is defined as
-\begin{align*}
-    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta}.
-\end{align*}
-Using this, the variation of~\cref{eq:A} is taken with respect to \( R \) as
-\begin{align*}
-	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee ,
-%	&= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
-\end{align*}
-where we used~\cref{eqn:hat1} to achieve the simplified form.
-\Cref{eq:dirDiff_A} also proves~\cref{item:prop_eRA}.
-Evaluating~\cref{eq:dirDiff_A} at \( R = R_d \) demonstrates that \( R_d \) is a critical point of \( A \).
-Next, the second derivative of \( A \) is computed as
-\begin{align*}
-    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T \delta R - \delta R^T R_d G}^\vee  \\
-    &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee\\
-    &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee  \\
-    &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
-\end{align*}
-where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
-Evaluating the Hessian at \( R = R_d \)
-\begin{align}\label{eq:A_hessian}
-    \Hess(A)\cdot (\delta R,\delta R)\big|_{R=R_d} = \eta \cdot \frac{1}{2} \parenth{\tr{G}I -  G} \eta 
-\end{align}
-shows that the Hessian is positive definite at \( R_d \) and therefore the critical point is a minimum for any variation \( \eta \) and proves~\cref{item:prop_A_psd}.
-
-To prove~\cref{item:prop_A_critical_points} we must first determine the critical points of~\cref{eq:eRA}.
-The derivations are originally presented in~\cite{bullo2004,chaturvedi2011a} and we present and expand on their original descriptions.
-We define the relative attitude error as \( Q = R_d^T R \) and expand~\cref{eq:eRA} as
-\begin{align*}
-    e_{R_A} &= \frac{1}{2} \parenth{G Q - Q^T G} ^ \vee, \\
-            &= \frac{1}{2} \parenth{%
-            \begin{bmatrix} g_1 & 0 & 0 \\ 0 & g_2 & 0 \\ 0 & 0 & g_3 \end{bmatrix}
-            \begin{bmatrix} q_{11} & q_{12} & q_{13} \\ q_{21} & q_{22} & q_{23} \\ q_{31} & q_{32} & q_{33}\end{bmatrix}
-            -
-            \begin{bmatrix} q_{11} & q_{21} & q_{31} \\ q_{12} & q_{22} & q_{32} \\ q_{13} & q_{23} & q_{33}\end{bmatrix}
-            \begin{bmatrix} g_1 & 0 & 0 \\ 0 & g_2 & 0 \\ 0 & 0 & g_3 \end{bmatrix}
-            }^\vee , \\
-            &= \frac{1}{2} \begin{bmatrix} g_3 q_{32} - g_2 q_{23} \\ g_1 q_{13} - g_3 q_{31} \\ g_2 q_{21} - g_1 q_{12}\end{bmatrix}
-\end{align*}
-At a critical point, the following equations must be satisfied
-\begin{subequations}\label{eq:erA_critical_conditons}
-    \begin{align}
-        g_3q_{32} &= g_2 q_{23}, \\
-        g_1 q_{13} &= g_3 q_{31}, \\
-        g_2 q_{21} &= g_1 q_{12}.
-    \end{align}
-\end{subequations}     
-Using the conditions in~\cref{eq:erA_critical_conditons} the relative attitude error \( Q \) becomes
-\begin{align}\label{eq:relative_attitude_error}
-    Q = R_d^T R_e =
-    \begin{bmatrix} 
-        q_{11} & q_{12} & q_{13} \\ 
-        \frac{g_1}{g_2} q_{12} & q_{22} & q_{23} \\
-        \frac{g_1}{g_3} q_{13} & \frac{g_2}{g_3} q_{23} & q_{33}
-    \end{bmatrix}
-    \in \SO
-\end{align}
-Since, \( Q = R_d^T R \) is orthonormal the main diagonal of \( QQ^T \) is equal to \num{1} and each column of \( Q \) is unit length.
-\begin{align*}
-    Q Q^T &= I, \\
-          &= \begin{bmatrix}
-    Q_{11} & Q_{12} & Q_{13} \\ 
-    Q_{21} & Q_{22} & Q_{23} \\ 
-    Q_{31} & Q_{32} & Q_{33} 
-\end{bmatrix}, 
-\end{align*}
-where
-\begin{align*}
-    Q_{11} &= q_{11}^2 + q_{12}^2 + q_{13}^2 ,\\
-    Q_{12} &= q_{11}q_{12}\frac{g_1}{g_2} + q_{12}q_{22} + q_{13}q_{23} ,\\
-    Q_{13} &= q_{11}q_{13}\frac{g_1}{g_3} + q_{12}q_{23}\frac{g_2}{g_3} + q_{13}q_{33},\\
-    Q_{21} &= q_{11}q_{12}\frac{g_1}{g_2}  + q_{12}q_{22} + q_{23}q_{13} ,\\
-    Q_{22} &= \frac{g_1^2}{g_2^2}q_{12}^2 + q_{22}^2 + q_{23}^2 ,\\
-    Q_{23} &= \frac{g_1^2}{g_2g_3} q_{12}q_{13} + \frac{g_2}{g_3}q_{23}q_{22} + q_{23}q_{33},\\
-    Q_{31} &= \frac{g_1}{g_3} q_{11}q_{13} + \frac{g_2}{g_3}q_{23}q_{12} + q_{33}q_{13},\\
-    Q_{32} &= \frac{g_1^2}{g_3 g_2} q_{12}q_{13} + \frac{g_2}{g_3} q_{23}q_{22} + q_{33} q_{23},\\
-    Q_{33} &= \frac{g_1^2}{g_3^2}q_{13}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 + q_{33}^2.
-\end{align*}
-As a result the following \num{6} conditions must be satisfied when \( e_{R_A} = 0 \):
-\begin{align}
-    q_{11}^2 + q_{12}^2 + q_{13}^2 &= 1,\label{eq:orthogonal_1} \\
-    \frac{g_1^2}{g_2^2}q_{12}^2 + q_{22}^2 + q_{23}^2 &= 1, \label{eq:orthogonal_2}\\
-    \frac{g_1^2}{g_3^2}q_{13}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 + q_{33}^2 &= 1, \label{eq:orthogonal_3}\\
-    q_{11}^2 + \frac{g_1^2}{g_2^2}q_{12}^2 + \frac{g_1^2}{g_3^2}q_{13}^2 &= 1, \label{eq:unit_norm_1}\\
-    q_{12} + q_{22}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 &= 1, \label{eq:unit_norm_2}\\
-    q_{13}^2 + q_{23}^2 + q_{33}^2 &= 1.\label{eq:unit_norm_3}
-\end{align}
-We can further simplify these relationships by rewriting~\cref{eq:orthogonal_1,eq:orthogonal_2,eq:orthogonal_3} as
-\begin{align}
-    q_{11}^2 &= 1 - q_{12}^2 - q_{13}^2 , \\
-    q_{22}^2 &= 1 - \frac{g_1^2}{g_2^2} q_{12}^2 - q_{23}^2, \\
-    q_{33}^2 &= 1 - \frac{g_1^2}{g_3^2}q_{13}^2 - \frac{g_2^2}{g_3^2}q_{23}^2 
-\end{align}
-and substituting these relationships into~\cref{eq:unit_norm_1,eq:unit_norm_2,eq:unit_norm_3} to arrive at
-\begin{subequations}\label{eq:era_critical_point_conditions}
-\begin{align}
-    \parenth{1 - \frac{g_1^2}{g_2^2} } q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 , \label{eq:era_condition_1}\\
-    \parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}}q_{23}^2 &= 0 , \label{eq:era_condition_2}\\
-    \parenth{1 - \frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0.\label{eq:era_condition_3}
-\end{align}
-\end{subequations}     
-The relationships in~\cref{eq:era_critical_point_conditions} are equivalent to the statement that \( e_{R_A} = 0 \) and must also be satisfied at each critical point.
-Since each \( g_i \) is distinct and greater than zero, the solution to~\cref{eq:erA_critical_conditons}, or equivalently \( e_{R_A} = 0 \), must satisfy one of two possible conditions:
-\begin{enumerate}[label=(\roman*)]
-    \item \label{item:condition_1} \( q_{12} = q_{13} = q_{23} =0\)
-    \item \label{item:condition_2} \( q_{ij} \neq 0 \; \forall \; i \neq j \)
-\end{enumerate}
-These conditions can be determined by noticing that~\cref{item:condition_1} is the trivial solution.
-For~\cref{item:condition_2}, consider the situation that \( q_{12} \neq 0 \) then from the fact that \( g_i \) are distinct yields the fact that \( \parenth{1 - \frac{g_1^2}{g_2^2} } \neq 0 \) and \( \parenth{1 - \frac{g_1^2}{g_3^2} } \neq 0 \) which means that \( q_{13}^2 \neq 0 \) since the terms must add to zero.
-Similar arguments can be made for the other relations in~\cref{eq:era_critical_point_conditions} which means that the solutions must satisfy either~\cref{item:condition_1} or~\cref{item:condition_2}.
-
-Now consider~\cref{item:condition_2} and assume that \( g_2 > g_1 \) and \( q_{12}, q_{13}, q_{23} \neq 0 \).
-From~\cref{eq:era_condition_1} this implies that \( \parenth{1 - \frac{g_1^2}{g_2^2} } q_{12}^2 > 0\) since \( q_{12}^2 > 0\).
-Therefore, in order for~\cref{eq:era_condition_1} to be satisfied means that \( \parenth{1 - \frac{g_1^2}{g_3^2} } q_{13}^2 < 0 \) which further implies that \( g_1 > g_3 \).
-As a result, \( g_2 > g_1 > g_3 \).
-Using this inequality in~\cref{eq:era_condition_3} implies that
-\begin{align*}
-    \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23} < 0, \quad \parenth{1 - \frac{g_1^2}{g_3^2}} q_{13}^2 < 0.
-\end{align*}
-Therefore the left hand side of~\cref{eq:era_condition_3} is negative and a contradiction.
-Applying a similar logic for the case \( g_1 > g_2 \) shows that~\cref{item:condition_2} is not possible and therefore~\cref{item:condition_1} must be satisfied.
-Substituting~\cref{item:condition_1} into~\cref{eq:relative_attitude_error} shows that the main diagonal of \( Q \) must be composed of \( + 1 \) or \( -1 \).
-Thus, the critical points of \( A(R) \) are those provided in~\cref{item:prop_A_critical_points}.
-These critical points correspond to additional rotations of \SI{180}{\degree} about each axes, or more explicitly \( R_e = \braces{R_d, R_\alpha, R_\beta, R_\gamma} \) where
-\begin{align}
-    R_\alpha &= R_d \begin{bmatrix} 1 & 0 & 0 \\ 0 & -1 & 0 \\ 0 & 0 & -1 \end{bmatrix} , \\
-    R_\beta &= R_d \begin{bmatrix} -1 & 0 & 0 \\ 0 & -1 & 0 \\ 0 & 0 & 1 \end{bmatrix} , \\
-    R_\gamma &= R_d \begin{bmatrix} -1 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & -1 \end{bmatrix}.
-\end{align}
-
-The original proof for~\cref{item:prop_psi_quadratic} is presented in~\cite{lee2011a} and summarized in this section.
-Define \( Q = R_d^T R = \exp \hat{\vc{x}} \in \SO \) for any \( \vc{x} \in \R^3 \) from Rodrigues' formula
-\begin{align}\label{eq:rodrigues_formula}
-    Q = \exp{\theta \hat{\vc{x}}} = I + \sin \theta \vh{x} + \parenth{1 - \cos \theta} \vh{x}^2 \in \SO.
-\end{align}
-Using a symbolic computation tool one can then find
-\begin{align}\label{eq:psi_rodrigues}
-    A &= \frac{1 - \cos \norm \vc{x}}{2\norm{\vc{x}^2}} \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i + g_j} x_k^2, \\
-    \norm{e_{R_A}}^2 &= \frac{\parenth{1 - \cos \norm{\vc{x}}^2} }{4 \norm{\vc{x}}^4}  \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i - g_j}^2 x_i^2 x_j^2 + \frac{\sin^2 \norm{\vc{x}}}{4 \norm{\vc{x}}^2} \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i + g_j}^2 x_k^2,
-\end{align}
-where \( \mathcal{C} = \braces{ \parenth{1, 2, 3} , \parenth{2, 3, 1} , \parenth{3, 1, 2} } \).
-Using~\cref{eq:psi_rodrigues} one can show
-\begin{align}
-    \frac{\norm{e_{R_A}}^2}{A} \leq \frac{h_2 + h_3}{h_1} , \quad \frac{A}{\norm{e_{R_A}}^2} \leq \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi} } ,
-\end{align}
-which proves~\cref{item:prop_A_quadratic}.
-
-\section{Proof of~\Cref{prop:attractive_error_dynamics}}\label{proof:attractive_error_dynamics}
-From the kinematics \( \dot{R} = R \hat{\Omega}\), and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
-\begin{gather*}
-	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega.
-\end{gather*}
-Applying this to the time derivative of~\cref{eq:A} gives
-\begin{gather*}
-	\diff{}{t} (A) = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega}.
-\end{gather*}
-Applying~\cref{eqn:hat1} into this shows~\cref{eq:A_dot}.
-
-The time derivative of the attractive attitude error vector, \( e_{R_A} \), is given by
-\begin{gather*}
-	\diff{}{t} ( e_{R_A}) = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee.
-\end{gather*}
-Using the hat map property given in~\cref{eqn:xAAx} this is further reduced to~\cref{eq:eRA_dot,eq:E}.
-
-% TODO Add link to dynamics that includes both external force and a disturbance
-We show~\cref{eq:eW_dot} by rearranging~\cref{eq:Wdot} as 
-\begin{align*}
-    \diff{}{t} e_\Omega = \dot{\Omega} = J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta +M_{ext}}.
-\end{align*}
-
-\subsection*{Proof of Attitude Controller}\label{proof:attitude_controller}
-Consider the following Lyapunov function:
-\begin{gather*}%\label{eqn:v_nodist}
-	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d). 
-\end{gather*}
-From~\cref{item:prop_psi_psd} of~\Cref{prop:attitude_control_configuration_error}, \(\mathcal{V} \geq 0 \).
-Using~\cref{eq:eW_dot,eq:A_dot} with \( \Delta = 0 \), the time derivative of \( \mathcal{V} \) is given by
-\begin{align*}%\label{eqn:vdot_nodist}
-	\dot{\mathcal{V}} &= -k_\Omega \norm{e_\Omega}^2. 
-%	e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
-\end{align*}
-Since \( \mathcal{V} \) is positive definite and \( \dot{\mathcal{V}} \) is negative semi-definite, the zero equilibrium point \( e_R, e_\Omega \) is stable in the sense of Lyapunov. 
-This also implies \( \lim_{t\to\infty} \norm{e_\Omega} = 0 \) and \( \norm{e_{R_A}} \) is uniformly bounded, as the Lyapunov function is non-increasing.
+%\section*{Appendix}
+
+%\subsection*{Proof of Attitude Configuration Error}\label{proof:attitude_configuration_error}
+%To prove~\cref{item:prop_psi_psd}, we first seek to show that \( A(R_d) \) is a critical point by showing that the first derivative is zero at \( R_d \).
+%The infinitesimal variation of a rotation matrix is defined as
+%\begin{align*}
+%    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta}.
+%\end{align*}
+%Using this, the variation of~\cref{eq:A} is taken with respect to \( R \) as
+%\begin{align*}
+%	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee ,
+%%	&= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
+%\end{align*}
+%where we used~\cref{eqn:hat1} to achieve the simplified form.
+%\Cref{eq:dirDiff_A} also proves~\cref{item:prop_eRA}.
+%Evaluating~\cref{eq:dirDiff_A} at \( R = R_d \) demonstrates that \( R_d \) is a critical point of \( A \).
+%Next, the second derivative of \( A \) is computed as
+%\begin{align*}
+%    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T \delta R - \delta R^T R_d G}^\vee  \\
+%    &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee\\
+%    &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee  \\
+%    &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
+%\end{align*}
+%where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
+%Evaluating the Hessian at \( R = R_d \)
+%\begin{align}\label{eq:A_hessian}
+%    \Hess(A)\cdot (\delta R,\delta R)\big|_{R=R_d} = \eta \cdot \frac{1}{2} \parenth{\tr{G}I -  G} \eta 
+%\end{align}
+%shows that the Hessian is positive definite at \( R_d \) and therefore the critical point is a minimum for any variation \( \eta \) and proves~\cref{item:prop_A_psd}.
+
+%To prove~\cref{item:prop_A_critical_points} we must first determine the critical points of~\cref{eq:eRA}.
+%The derivations are originally presented in~\cite{bullo2004,chaturvedi2011a} and we present and expand on their original descriptions.
+%We define the relative attitude error as \( Q = R_d^T R \) and expand~\cref{eq:eRA} as
+%\begin{align*}
+%    e_{R_A} &= \frac{1}{2} \parenth{G Q - Q^T G} ^ \vee, \\
+%            &= \frac{1}{2} \parenth{%
+%            \begin{bmatrix} g_1 & 0 & 0 \\ 0 & g_2 & 0 \\ 0 & 0 & g_3 \end{bmatrix}
+%            \begin{bmatrix} q_{11} & q_{12} & q_{13} \\ q_{21} & q_{22} & q_{23} \\ q_{31} & q_{32} & q_{33}\end{bmatrix}
+%            -
+%            \begin{bmatrix} q_{11} & q_{21} & q_{31} \\ q_{12} & q_{22} & q_{32} \\ q_{13} & q_{23} & q_{33}\end{bmatrix}
+%            \begin{bmatrix} g_1 & 0 & 0 \\ 0 & g_2 & 0 \\ 0 & 0 & g_3 \end{bmatrix}
+%            }^\vee , \\
+%            &= \frac{1}{2} \begin{bmatrix} g_3 q_{32} - g_2 q_{23} \\ g_1 q_{13} - g_3 q_{31} \\ g_2 q_{21} - g_1 q_{12}\end{bmatrix}
+%\end{align*}
+%At a critical point, the following equations must be satisfied
+%\begin{subequations}\label{eq:erA_critical_conditons}
+%    \begin{align}
+%        g_3q_{32} &= g_2 q_{23}, \\
+%        g_1 q_{13} &= g_3 q_{31}, \\
+%        g_2 q_{21} &= g_1 q_{12}.
+%    \end{align}
+%\end{subequations}     
+%Using the conditions in~\cref{eq:erA_critical_conditons} the relative attitude error \( Q \) becomes
+%\begin{align}\label{eq:relative_attitude_error}
+%    Q = R_d^T R_e =
+%    \begin{bmatrix} 
+%        q_{11} & q_{12} & q_{13} \\ 
+%        \frac{g_1}{g_2} q_{12} & q_{22} & q_{23} \\
+%        \frac{g_1}{g_3} q_{13} & \frac{g_2}{g_3} q_{23} & q_{33}
+%    \end{bmatrix}
+%    \in \SO
+%\end{align}
+%Since, \( Q = R_d^T R \) is orthonormal the main diagonal of \( QQ^T \) is equal to \num{1} and each column of \( Q \) is unit length.
+%\begin{align*}
+%    Q Q^T &= I, \\
+%          &= \begin{bmatrix}
+%    Q_{11} & Q_{12} & Q_{13} \\ 
+%    Q_{21} & Q_{22} & Q_{23} \\ 
+%    Q_{31} & Q_{32} & Q_{33} 
+%\end{bmatrix}, 
+%\end{align*}
+%where
+%\begin{align*}
+%    Q_{11} &= q_{11}^2 + q_{12}^2 + q_{13}^2 ,\\
+%    Q_{12} &= q_{11}q_{12}\frac{g_1}{g_2} + q_{12}q_{22} + q_{13}q_{23} ,\\
+%    Q_{13} &= q_{11}q_{13}\frac{g_1}{g_3} + q_{12}q_{23}\frac{g_2}{g_3} + q_{13}q_{33},\\
+%    Q_{21} &= q_{11}q_{12}\frac{g_1}{g_2}  + q_{12}q_{22} + q_{23}q_{13} ,\\
+%    Q_{22} &= \frac{g_1^2}{g_2^2}q_{12}^2 + q_{22}^2 + q_{23}^2 ,\\
+%    Q_{23} &= \frac{g_1^2}{g_2g_3} q_{12}q_{13} + \frac{g_2}{g_3}q_{23}q_{22} + q_{23}q_{33},\\
+%    Q_{31} &= \frac{g_1}{g_3} q_{11}q_{13} + \frac{g_2}{g_3}q_{23}q_{12} + q_{33}q_{13},\\
+%    Q_{32} &= \frac{g_1^2}{g_3 g_2} q_{12}q_{13} + \frac{g_2}{g_3} q_{23}q_{22} + q_{33} q_{23},\\
+%    Q_{33} &= \frac{g_1^2}{g_3^2}q_{13}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 + q_{33}^2.
+%\end{align*}
+%As a result the following \num{6} conditions must be satisfied when \( e_{R_A} = 0 \):
+%\begin{align}
+%    q_{11}^2 + q_{12}^2 + q_{13}^2 &= 1,\label{eq:orthogonal_1} \\
+%    \frac{g_1^2}{g_2^2}q_{12}^2 + q_{22}^2 + q_{23}^2 &= 1, \label{eq:orthogonal_2}\\
+%    \frac{g_1^2}{g_3^2}q_{13}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 + q_{33}^2 &= 1, \label{eq:orthogonal_3}\\
+%    q_{11}^2 + \frac{g_1^2}{g_2^2}q_{12}^2 + \frac{g_1^2}{g_3^2}q_{13}^2 &= 1, \label{eq:unit_norm_1}\\
+%    q_{12} + q_{22}^2 + \frac{g_2^2}{g_3^2}q_{23}^2 &= 1, \label{eq:unit_norm_2}\\
+%    q_{13}^2 + q_{23}^2 + q_{33}^2 &= 1.\label{eq:unit_norm_3}
+%\end{align}
+%We can further simplify these relationships by rewriting~\cref{eq:orthogonal_1,eq:orthogonal_2,eq:orthogonal_3} as
+%\begin{align}
+%    q_{11}^2 &= 1 - q_{12}^2 - q_{13}^2 , \\
+%    q_{22}^2 &= 1 - \frac{g_1^2}{g_2^2} q_{12}^2 - q_{23}^2, \\
+%    q_{33}^2 &= 1 - \frac{g_1^2}{g_3^2}q_{13}^2 - \frac{g_2^2}{g_3^2}q_{23}^2 
+%\end{align}
+%and substituting these relationships into~\cref{eq:unit_norm_1,eq:unit_norm_2,eq:unit_norm_3} to arrive at
+%\begin{subequations}\label{eq:era_critical_point_conditions}
+%\begin{align}
+%    \parenth{1 - \frac{g_1^2}{g_2^2} } q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 , \label{eq:era_condition_1}\\
+%    \parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}}q_{23}^2 &= 0 , \label{eq:era_condition_2}\\
+%    \parenth{1 - \frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0.\label{eq:era_condition_3}
+%\end{align}
+%\end{subequations}     
+%The relationships in~\cref{eq:era_critical_point_conditions} are equivalent to the statement that \( e_{R_A} = 0 \) and must also be satisfied at each critical point.
+%Since each \( g_i \) is distinct and greater than zero, the solution to~\cref{eq:erA_critical_conditons}, or equivalently \( e_{R_A} = 0 \), must satisfy one of two possible conditions:
+%\begin{enumerate}[label=(\roman*)]
+%    \item \label{item:condition_1} \( q_{12} = q_{13} = q_{23} =0\)
+%    \item \label{item:condition_2} \( q_{ij} \neq 0 \; \forall \; i \neq j \)
+%\end{enumerate}
+%These conditions can be determined by noticing that~\cref{item:condition_1} is the trivial solution.
+%For~\cref{item:condition_2}, consider the situation that \( q_{12} \neq 0 \) then from the fact that \( g_i \) are distinct yields the fact that \( \parenth{1 - \frac{g_1^2}{g_2^2} } \neq 0 \) and \( \parenth{1 - \frac{g_1^2}{g_3^2} } \neq 0 \) which means that \( q_{13}^2 \neq 0 \) since the terms must add to zero.
+%Similar arguments can be made for the other relations in~\cref{eq:era_critical_point_conditions} which means that the solutions must satisfy either~\cref{item:condition_1} or~\cref{item:condition_2}.
+
+%Now consider~\cref{item:condition_2} and assume that \( g_2 > g_1 \) and \( q_{12}, q_{13}, q_{23} \neq 0 \).
+%From~\cref{eq:era_condition_1} this implies that \( \parenth{1 - \frac{g_1^2}{g_2^2} } q_{12}^2 > 0\) since \( q_{12}^2 > 0\).
+%Therefore, in order for~\cref{eq:era_condition_1} to be satisfied means that \( \parenth{1 - \frac{g_1^2}{g_3^2} } q_{13}^2 < 0 \) which further implies that \( g_1 > g_3 \).
+%As a result, \( g_2 > g_1 > g_3 \).
+%Using this inequality in~\cref{eq:era_condition_3} implies that
+%\begin{align*}
+%    \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23} < 0, \quad \parenth{1 - \frac{g_1^2}{g_3^2}} q_{13}^2 < 0.
+%\end{align*}
+%Therefore the left hand side of~\cref{eq:era_condition_3} is negative and a contradiction.
+%Applying a similar logic for the case \( g_1 > g_2 \) shows that~\cref{item:condition_2} is not possible and therefore~\cref{item:condition_1} must be satisfied.
+%Substituting~\cref{item:condition_1} into~\cref{eq:relative_attitude_error} shows that the main diagonal of \( Q \) must be composed of \( + 1 \) or \( -1 \).
+%Thus, the critical points of \( A(R) \) are those provided in~\cref{item:prop_A_critical_points}.
+%These critical points correspond to additional rotations of \SI{180}{\degree} about each axes, or more explicitly \( R_e = \braces{R_d, R_\alpha, R_\beta, R_\gamma} \) where
+%\begin{align}
+%    R_\alpha &= R_d \begin{bmatrix} 1 & 0 & 0 \\ 0 & -1 & 0 \\ 0 & 0 & -1 \end{bmatrix} , \\
+%    R_\beta &= R_d \begin{bmatrix} -1 & 0 & 0 \\ 0 & -1 & 0 \\ 0 & 0 & 1 \end{bmatrix} , \\
+%    R_\gamma &= R_d \begin{bmatrix} -1 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & -1 \end{bmatrix}.
+%\end{align}
+
+%The original proof for~\cref{item:prop_psi_quadratic} is presented in~\cite{lee2011a} and summarized in this section.
+%Define \( Q = R_d^T R = \exp \hat{\vc{x}} \in \SO \) for any \( \vc{x} \in \R^3 \) from Rodrigues' formula
+%\begin{align}\label{eq:rodrigues_formula}
+%    Q = \exp{\theta \hat{\vc{x}}} = I + \sin \theta \vh{x} + \parenth{1 - \cos \theta} \vh{x}^2 \in \SO.
+%\end{align}
+%Using a symbolic computation tool one can then find
+%\begin{align}\label{eq:psi_rodrigues}
+%    A &= \frac{1 - \cos \norm \vc{x}}{2\norm{\vc{x}^2}} \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i + g_j} x_k^2, \\
+%    \norm{e_{R_A}}^2 &= \frac{\parenth{1 - \cos \norm{\vc{x}}^2} }{4 \norm{\vc{x}}^4}  \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i - g_j}^2 x_i^2 x_j^2 + \frac{\sin^2 \norm{\vc{x}}}{4 \norm{\vc{x}}^2} \sum_{\parenth{i, j, k} \in \mathcal{C}} \parenth{g_i + g_j}^2 x_k^2,
+%\end{align}
+%where \( \mathcal{C} = \braces{ \parenth{1, 2, 3} , \parenth{2, 3, 1} , \parenth{3, 1, 2} } \).
+%Using~\cref{eq:psi_rodrigues} one can show
+%\begin{align}
+%    \frac{\norm{e_{R_A}}^2}{A} \leq \frac{h_2 + h_3}{h_1} , \quad \frac{A}{\norm{e_{R_A}}^2} \leq \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi} } ,
+%\end{align}
+%which proves~\cref{item:prop_A_quadratic}.
+
+%\section{Proof of~\Cref{prop:attractive_error_dynamics}}\label{proof:attractive_error_dynamics}
+%From the kinematics \( \dot{R} = R \hat{\Omega}\), and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
+%\begin{gather*}
+%	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega.
+%\end{gather*}
+%Applying this to the time derivative of~\cref{eq:A} gives
+%\begin{gather*}
+%	\diff{}{t} (A) = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega}.
+%\end{gather*}
+%Applying~\cref{eqn:hat1} into this shows~\cref{eq:A_dot}.
+
+%The time derivative of the attractive attitude error vector, \( e_{R_A} \), is given by
+%\begin{gather*}
+%	\diff{}{t} ( e_{R_A}) = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee.
+%\end{gather*}
+%Using the hat map property given in~\cref{eqn:xAAx} this is further reduced to~\cref{eq:eRA_dot,eq:E}.
+
+%% TODO Add link to dynamics that includes both external force and a disturbance
+%We show~\cref{eq:eW_dot} by rearranging~\cref{eq:Wdot} as 
+%\begin{align*}
+%    \diff{}{t} e_\Omega = \dot{\Omega} = J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta +M_{ext}}.
+%\end{align*}
+
+%\subsection*{Proof of Attitude Controller}\label{proof:attitude_controller}
+%Consider the following Lyapunov function:
+%\begin{gather*}%\label{eqn:v_nodist}
+%	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d). 
+%\end{gather*}
+%From~\cref{item:prop_psi_psd} of~\Cref{prop:attitude_control_configuration_error}, \(\mathcal{V} \geq 0 \).
+%Using~\cref{eq:eW_dot,eq:A_dot} with \( \Delta = 0 \), the time derivative of \( \mathcal{V} \) is given by
+%\begin{align*}%\label{eqn:vdot_nodist}
+%	\dot{\mathcal{V}} &= -k_\Omega \norm{e_\Omega}^2. 
+%%	e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
+%\end{align*}
+%Since \( \mathcal{V} \) is positive definite and \( \dot{\mathcal{V}} \) is negative semi-definite, the zero equilibrium point \( e_R, e_\Omega \) is stable in the sense of Lyapunov. 
+%This also implies \( \lim_{t\to\infty} \norm{e_\Omega} = 0 \) and \( \norm{e_{R_A}} \) is uniformly bounded, as the Lyapunov function is non-increasing.
 From~\cref{eq:eRA_dot}, $\lim_{t\to\infty} \dot e_R =0$.
-One can show that \( \norm{\ddot{e}_R} \) is bounded.
-From Barbalat's Lemma, it follows \( \lim_{t\to\infty}\norm{\dot{e}_R} = 0 \)~\cite[Lemma 8.2]{khalil1996}. 
-Therefore, the equilibrium is asymptotically stable.
-
-Furthermore, since \( \dot{\mathcal{V}} \leq 0 \) the Lyapunov function is uniformly bounded which implies 
-\begin{align*}
-	A(R(t)) \leq \mathcal{V}(t) \leq \mathcal{V}(0).
-\end{align*}
-
-An Appendix, if needed, appears \textbf{before} research funding information and other acknowledgments.
-
-\subsection*{Proof of Translational Control}\label{proof:translational_control}
-
-The translational dynamics can be defined as
-\begin{align}\label{eq:translation_dynamics_simple}
-    \dot{x} &= v , \\
-    m \dot{v} &= F_{ext} + u_f ,
-\end{align}
-where \( m \in \R \) is defined as the total mass of the vehicle while \( F_{ext} \) is the total external force.
-
-Consider the Lyapunov function
-\begin{align}\label{eq:translational_lyapunov}
-    V = \frac{1}{2} k_x e_x^T e_x + \frac{1}{2} m e_v^T e_v + c e_x^T e_x.
-\end{align}
-\Cref{eq:translational_lyapunov} is also equivalent to
-\begin{align}\label{eq:translational_lyapunov_matrix}
-    V = z^T W_1 z , 
-\end{align}
-where \( z = \begin{bmatrix} \norm{e_x} & \norm{e_v} \end{bmatrix}^T \) and \( W_1\in \R^2\) is defined as
-\begin{align}\label{eq:translational_lyapunov_W}
-    W_1 = \begin{bmatrix}
-        \frac{1}{2} k_x & \frac{1}{2} c \\
-        \frac{1}{2} c & \frac{1}{2} m 
-    \end{bmatrix}.
-\end{align}
-The time derivative of~\cref{eq:translational_lyapunov} can then be defined as
-\begin{align}\label{eq:translation_lyapunov_derivative}
-    \dot{\mathcal{V} } = - \parenth{k_v - c} e_v^T e_v - \frac{k_x c}{m} e_x^T e_x - \frac{k_v c}{m} e_x^T e_v, 
-\end{align}
-where we used~\cref{eq:translational_control,eq:translation_error_variables,eq:translation_error_dynamics}.
-\Cref{eq:translation_lyapunov_derivative} can also be redefined as
-\begin{align}\label{eq:translational_lyapunov_derivative_matrix}
-    \dot{\mathcal{V}} = - z^T W_2 z, 
-\end{align}
-where \( W_2 \in \R^2 \) is defined as
-\begin{align}\label{eq:translational_lyapunov_W2}
-    W_2 = \begin{bmatrix}
-        \frac{k_x c}{m} & \frac{k_v^2 c^2}{2 m^2} \\
-        \frac{k_v c}{2 m} & k_v - c
-    \end{bmatrix}.
-\end{align}
-If \( c \) is chosen such that~\cref{eq:translational_control_gain_bound} is satisfied then \( W_1, W_2 \) will be positive definite.
-As a result, this shows that \( \mathcal{V} > 0 , \dot{ \mathcal{V}} < 0 \) and that the zero equilibrium of the error variables, namely \( x_d, \dot{x}_d \) is asymptotically stable~\cite{khalil1996}.
+%One can show that \( \norm{\ddot{e}_R} \) is bounded.
+%From Barbalat's Lemma, it follows \( \lim_{t\to\infty}\norm{\dot{e}_R} = 0 \)~\cite[Lemma 8.2]{khalil1996}. 
+%Therefore, the equilibrium is asymptotically stable.
+
+%Furthermore, since \( \dot{\mathcal{V}} \leq 0 \) the Lyapunov function is uniformly bounded which implies 
+%\begin{align*}
+%	A(R(t)) \leq \mathcal{V}(t) \leq \mathcal{V}(0).
+%\end{align*}
+
+%An Appendix, if needed, appears \textbf{before} research funding information and other acknowledgments.
+
+%\subsection*{Proof of Translational Control}\label{proof:translational_control}
+
+%The translational dynamics can be defined as
+%\begin{align}\label{eq:translation_dynamics_simple}
+%    \dot{x} &= v , \\
+%    m \dot{v} &= F_{ext} + u_f ,
+%\end{align}
+%where \( m \in \R \) is defined as the total mass of the vehicle while \( F_{ext} \) is the total external force.
+
+%Consider the Lyapunov function
+%\begin{align}\label{eq:translational_lyapunov}
+%    V = \frac{1}{2} k_x e_x^T e_x + \frac{1}{2} m e_v^T e_v + c e_x^T e_x.
+%\end{align}
+%\Cref{eq:translational_lyapunov} is also equivalent to
+%\begin{align}\label{eq:translational_lyapunov_matrix}
+%    V = z^T W_1 z , 
+%\end{align}
+%where \( z = \begin{bmatrix} \norm{e_x} & \norm{e_v} \end{bmatrix}^T \) and \( W_1\in \R^2\) is defined as
+%\begin{align}\label{eq:translational_lyapunov_W}
+%    W_1 = \begin{bmatrix}
+%        \frac{1}{2} k_x & \frac{1}{2} c \\
+%        \frac{1}{2} c & \frac{1}{2} m 
+%    \end{bmatrix}.
+%\end{align}
+%The time derivative of~\cref{eq:translational_lyapunov} can then be defined as
+%\begin{align}\label{eq:translation_lyapunov_derivative}
+%    \dot{\mathcal{V} } = - \parenth{k_v - c} e_v^T e_v - \frac{k_x c}{m} e_x^T e_x - \frac{k_v c}{m} e_x^T e_v, 
+%\end{align}
+%where we used~\cref{eq:translational_control,eq:translation_error_variables,eq:translation_error_dynamics}.
+%\Cref{eq:translation_lyapunov_derivative} can also be redefined as
+%\begin{align}\label{eq:translational_lyapunov_derivative_matrix}
+%    \dot{\mathcal{V}} = - z^T W_2 z, 
+%\end{align}
+%where \( W_2 \in \R^2 \) is defined as
+%\begin{align}\label{eq:translational_lyapunov_W2}
+%    W_2 = \begin{bmatrix}
+%        \frac{k_x c}{m} & \frac{k_v^2 c^2}{2 m^2} \\
+%        \frac{k_v c}{2 m} & k_v - c
+%    \end{bmatrix}.
+%\end{align}
+%If \( c \) is chosen such that~\cref{eq:translational_control_gain_bound} is satisfied then \( W_1, W_2 \) will be positive definite.
+%As a result, this shows that \( \mathcal{V} > 0 , \dot{ \mathcal{V}} < 0 \) and that the zero equilibrium of the error variables, namely \( x_d, \dot{x}_d \) is asymptotically stable~\cite{khalil1996}.
 %\section*{Funding Sources}

### 2019-02-21 manuscript.tex
minor edits

@@
 \end{align}
-The asteroid is modeled as a constant density polyhedron with constant, and known, spin about its maximum moment of inertia. 
+The asteroid is modeled as a constant density polyhedron with constant, and known, spin about the axis of its maximum moment of inertia. 
 The axes of the body fixed frame for the asteroid are denoted by $\{f_1,f_2,f_3\}$. 
@@
     \item \( \vc{x}\in\Re^3 \) - the position of the center of mass of the  spacecraft represented in the inertial frame, \( \vc{e}_i\),
-    \item \( R\in\SO \) - the rotation matrix which transforms vectors defined in the spacecraft fixed frame, \( \vc{b}_i \), to the inertial frame, \( \vc{e}_i \),
+    \item \( R\in\SO \) - the rotation matrix which transforms the representation of vectors defined in the spacecraft fixed frame, \( \vc{b}_i \), to the inertial frame, \( \vc{e}_i \),
     \item \( \vc{\Omega}\in\Re^3 \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame, \( \vc{b}_i \), and
-    \item \( R_A\in \SO \) - the rotation matrix which transforms vectors defined in the asteroid fixed frame, \( \vc{f}_i \), to the inertial frame, \( \vc{e}_i \).
+    \item \( R_A\in \SO \) - the rotation matrix which transforms the representation of vectors defined in the asteroid fixed frame, \( \vc{f}_i \), to the inertial frame, \( \vc{e}_i \).
 \end{itemize}
 In this work, we assume that the asteroid is much more massive than the spacecraft and its motion is not affected by that of the spacecraft.
-This assumption allows us to treat the motion of the vehicle independently from that of the asteroid.
+This assumption allows us to treat the motion of the vehicle independently from the dynamics of the asteroid, which is assumed to spin at a fixed rate.
 
@@
 \end{align}
-The vectors \( \vc{z}_1 \) and \( \vc{z}_2\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
+The vectors \( \vc{z}_1 \) and \( \vc{z}_2\in\Re^3\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
 \begin{align}
@@
 \end{align}
-where \( \rho_i \) defines the position of each mass in the spacecraft fixed body frame.
+where \( \rho_i \in\Re^3 \) defines the position of each mass in the spacecraft fixed body frame.
 The control inputs to the spacecraft are defined by \( u_f, u_m \in \Re^3 \) which define the control force represented in the inertial frame and the control moment represented in the spacecraft frame, respectively.
@@
 \end{align}
-In the above equations, the gravitational potential is denoted by $U$, which is computed by a polyhedron model as described in the subsequent section.
+In the above equations, the gravitational potential is denoted by $U\in\Re$, which is computed by a polyhedron model as described in the subsequent section.
 
@@
 References~\cite{werner1994} and~\cite{werner1996} give a detailed derivation of the polyhedron model.
+
 Here, we summarize the key equations required for implementation.
+The polyhedron potential is defined as 
+\begin{align}
+    U(\vc{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vc{r}_e \cdot \vc{E}_e \cdot \vc{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vc{r}_f \cdot \vc{F}_f \cdot \vc{r}_f \cdot \omega_f,
+\end{align}
+and \( \vc{r}_e\) and \(\vc{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\in\Re\) is the universal gravitational constant, and \( \sigma\in\Re \) is the constant density of the asteroid.
 We define the attraction, gravity gradient matrix, and Laplacian as
@@
 The Laplacian, defined in~\cref{eq:laplacian}, gives a simple method to determine if the spacecraft has collided with the body~\cite{werner1996}. 
+These equations are utilized to compute the gravitational potential of  the presented dumbbell spacecraft model.
 
@@
 Furthermore, the number of vertices in the estimate can be scaled according to the desired final accuracy or computational capabilities.
-In this section, we present a stochastic formulation to update the initial estimate of the shape incrementally based on range measurements from spacecraft.
+In this section, we present a stochastic formulation to update the initial estimate of the shape incrementally based on range measurements from spacecraft in real time.
 
@@
 \end{align*}
-where \( r_i \) is the initial estimate of the radial distance of vertex \( \vc{v}_i\) and \( w_i \) is the initial variance, or confidence, in the radial distance.
+where \( r_i\in\Re \) is the initial estimate of the radial distance of the $i$-th vertex \( \vc{v}_i\in\Re\), and \( w_i\in\Re \) is the initial variance, or confidence, in the radial distance.
 
@@
 
-Suppose the $j$-th measurement, namely $p_j\in\Re^3$ is available. 
-As illustrated in \Cref{fig:lidar_example}, the angular resolution of range measurements is assumed to be coarser than the mesh grid of the initial estimate. 
-Consequently, the measurement may not be aligned to any vertex in general. 
-In order to improve the computational efficiency measurement updates are assumed to be local in nature.
-Instead of applying a measurement to all vertices of the mesh, the measurement is only applied to the vertices which are within a specified region of the measurement. 
+%Suppose the $j$-th measurement, namely $p_j\in\Re^3$ is available. 
+%As illustrated in \Cref{fig:lidar_example}, the angular resolution of range measurements is assumed to be coarser than the mesh grid of the initial estimate. 
+%Consequently, the measurement may not be aligned to any vertex in general. 
+%In order to improve the computational efficiency measurement updates are assumed to be local in nature.
+%Instead of applying a measurement to all vertices of the mesh, the measurement is only applied to the vertices which are within a specified region of the measurement.
+
 From spherical trigonometry~\cite{gade2010}, the central angle between measurement \( \vc{p}_j \) and vertex \( \vc{v}_i \) of the shape estimate is given by
@@
 In this section, we demonstrate the use of the incremental shape reconstruction algorithm with asteroids 1620 Geographos and 6489 Golevka.
-There properties are listed at \Cref{tab:kinematic_asteroids}.
+\todo{ add references to the true shape model we are using}.
+Their properties are listed at \Cref{tab:kinematic_asteroids}.
 \begin{table}[htbp]
@@
 
+\paragraph{Asteroid \num{1620} Geographos Reconstruction} 
 \num{1620} Geographos is a highly elongated stony asteroid of the Apollo group.
@@
 
-\num{6489} Golevka is a small angular shaped asteroid of the Apollo group.
+\paragraph{Asteroid \num{6489} Golevka Reconstruction} 
+Next, \num{6489} Golevka is a small angular shaped asteroid of the Apollo group.
 Discovered in \num{1995}, Golevka is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
@@
 The shape reconstruction algorithm presented in the preceding section does not offer a method to determine which portion of the surface needs to be measured. 
-In this section, we present a guidance scheme or a motion planning scheme in order to direct the spacecraft into the most uncertain region. 
+In this section, we present a guidance scheme or a motion planning scheme in order to guide the spacecraft into the most uncertain region. 
 This is to reduce the shape uncertainty in an optimal fashion while considering the control cost to change the orbital properties of the spacecraft. 
@@
 The examples demonstrate the full dynamic simulation of a rigid spacecraft with an autonomous closed loop control scheme to both reconstruct the asteroid shape.
+The proposed optimal guidance scheme is executed in the outer-loop to generate the desired trajectory, which is followed by the nonlinear control scheme in the inner-loop. 
 More specifically, the nonlinear controllers described previously are used to control both the translational and rotational states of the vehicle, where the control inputs are computed using the current shape estimate of the asteroid.
@@
 \end{table}
-At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( x_0 = \begin{bmatrix} x_0 & 0 & 0 \end{bmatrix} \si{\kilo\meter} \).
+At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( x_0 = [ x_0,\, 0,\,  0 ]\, \si{\kilo\meter} \).
 In addition, at the initial state the spacecraft is orientated such that the \( b_1 \) axis is aligned with the inertial \( e_2 \) axis.
@@
 
-In this section, we consider a scenario of autonomous landing on the surface of asteroid, once its shape is constructed as described above.
+In this section, we consider a scenario of autonomous landing on the surface of asteroid, after its shape is constructed as described above.
 The shape reconstruction scheme is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
@@
 Due to the small size, and therefore low gravitational attraction, the force at each point on the surface is a combination of the gravitational attraction and the centripetal acceleration.
-At the center of each face, \( f_i = \begin{bmatrix} f_x & f_y & f_z \end{bmatrix} \), we compute a modified surface acceleration as
+At the center of each face, \( f_i = [ f_x,\,  f_y,\,  f_z ] \), we compute a modified surface acceleration as
 \begin{align}\label{eq:surface_force}
@@
 As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
+\todo{ resolve the undefined reference to eq:potential}
 The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
@@
 Based on the shape estimate we seek to determine the best location to land. 
-In reality, any landing site selection would be based on a wide variety of factors and constraints, however we highlight a few which can be determined autonomously and from the shape estimate.
+In reality, any landing site selection would be based on a wide variety of factors and constraints. 
+However we highlight a few which can be determined autonomously and from the shape estimate.
 The first metric is related to the surface slope which is computed using the completed shape estimate and~\cref{eq:surface_slope}.

### 2019-03-03 manuscript.tex
Cite truth shape model and correct equation ref

@@
 In this section, we demonstrate the use of the incremental shape reconstruction algorithm with asteroids 1620 Geographos and 6489 Golevka.
-\todo{ add references to the true shape model we are using}.
 Their properties are listed at \Cref{tab:kinematic_asteroids}.
+Truth shape models for Geographos adn Golevka are computed based on Earth based radar measurements~\cite{neese2004}.
 \begin{table}[htbp]
@@
 As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
-\todo{ resolve the undefined reference to eq:potential}
-The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
+The computational cost of the polyhedron potential model, given by~\cref{eq:attraction}, is roughly proportional to the number of faces in the shape model.
 As a result, a uniformly high resolution shape would quickly become intractable for real time operations.

### 2019-03-05 manuscript.tex
Move some images to top level

@@
     \centering
-    \input{tikz/dumbbell.tikz}
+    \input{dumbbell.tikz}
     \caption{Dumbbell Model of Rigid Spacecraft\label{fig:dumbbell_sc}}
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{figures/castalia_raycasting_plot.jpg}
+    \includegraphics[width=0.75\textwidth]{castalia_raycasting_plot.jpg}
     \caption{Simulated LIDAR measurements of asteroid Castalia~\label{fig:lidar_example}}
@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/geographos/partial_0.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_1872.jpg}}
-
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_3745.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_5617.jpg}}
-
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_7489.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/truth.jpg}}
+    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{mesh_update_geographos_partial_0.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{mesh_update_geographos_partial_1872.jpg}}
+
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{mesh_update_geographos_partial_3745.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{mesh_update_geographos_partial_5617.jpg}}
+
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{mesh_update_geographos_partial_7489.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{mesh_update_geographos_truth.jpg}}
     \caption[Asteroid Geographos incremental reconstruction]{Incremental reconstruction of asteroid Geographos~\label{fig:geographos_reconstruction}}

### 2019-03-05 manuscript.tex
Move some more figures

@@
     \centering
-    \input{tikz/geographos_metrics.tikz}
+    \input{geographos_metrics.tikz}
     \caption{Normalized uncertainty and volume percent error for Geographos\label{fig:geographos_metrics}}
@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_0.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_1321.jpg}}\\%
-
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_2643.jpg}}%
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_3964.jpg}}\\%
-
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_5285.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/truth.jpg}}
+    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_0.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_1321.jpg}}\\%
+
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_2643.jpg}}%
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_3964.jpg}}\\%
+
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_5285.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_truth.jpg}}
     \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
@@
     \centering
-    \input{tikz/golevka_metrics.tikz}
+    \input{golevka_metrics.tikz}
     \caption{Normalized uncertainty and volume percent error for Golevka\label{fig:golevka_metrics}}
@@
 
-\clearpage\newpage
 \section{Optimal Guidance for Shape Reconstruction}\label{sec:explore_asteroid}
@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_3749.jpg}}%
-
-    \subcaptionbox{\SI{50}{\percent} of measurements\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_7499.jpg}}
-    \subcaptionbox{\SI{75}{\percent} of measurements\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_11249.jpg}}%
-
-    \subcaptionbox{\SI{100}{\percent} of measurements\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_14998.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/52760/truth.jpg}}
+    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{dynamic_exploration_52760_partial_weights_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{dynamic_exploration_52760_partial_weights_3749.jpg}}%
+
+    \subcaptionbox{\SI{50}{\percent} of measurements\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{dynamic_exploration_52760_partial_weights_7499.jpg}}
+    \subcaptionbox{\SI{75}{\percent} of measurements\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{dynamic_exploration_52760_partial_weights_11249.jpg}}%
+
+    \subcaptionbox{\SI{100}{\percent} of measurements\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{dynamic_exploration_52760_partial_weights_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{mesh_update_52760_truth.jpg}}
     \caption[Asteroid 52760 shape reconstruction with uncertainty]{Incremental reconstruction of asteroid 52760.

### 2019-03-05 manuscript.tex
Move even more figures

@@
     \centering
-    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_1.jpg}}%
-    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_3749.jpg}}%
-    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_7499.jpg}}
-
-    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_11249.jpg}}%
-    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_14998.jpg}}%
-    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/mesh_update/castalia/truth.jpg}}
+    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{dynamic_exploration_castalia_partial_weights_1.jpg}}%
+    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{dynamic_exploration_castalia_partial_weights_3749.jpg}}%
+    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{dynamic_exploration_castalia_partial_weights_7499.jpg}}
+
+    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{dynamic_exploration_castalia_partial_weights_11249.jpg}}%
+    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{dynamic_exploration_castalia_partial_weights_14998.jpg}}%
+    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{mesh_update_castalia_truth.jpg}}
     \caption[Asteroid Castalia shape reconstruction with uncertainty]{Incremental reconstruction of asteroid Castalia.

### 2019-03-05 manuscript.tex
Move more figures
Move more figures.
JGCD sucks

@@
     \centering
-    \input{tikz/castalia_metrics.tikz}
+    \input{castalia_metrics.tikz}
     \caption{Normalized uncertainty and volume percent error for Castalia\label{fig:castalia_metrics}}
@@
     \centering
-    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.45\textwidth]{figures/original_cube.jpg}}~
-    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.45\textwidth]{figures/remesh_cube.jpg}}
+    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.45\textwidth]{original_cube.jpg}}~
+    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.45\textwidth]{remesh_cube.jpg}}
     \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}

### 2019-03-05 manuscript.tex
Moving another set of figures

@@
     \centering
-    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/slope.pdf}}%
-    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/slope_masked.pdf}}
+    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=0.5\textwidth]{dynamic_exploration_castalia_refine_slope.pdf}}%
+    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_slope_masked.pdf}}
     \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}

### 2019-03-05 manuscript.tex
Move figures

@@
     \centering
-    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/dist.pdf}}%
-    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/dist_masked.pdf}}
+    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{dynamic_exploration_castalia_refine_dist.pdf}}%
+    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_dist_masked.pdf}}
     \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
@@
     \centering
-    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/cost.pdf}
+    \includegraphics[width=0.75\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_cost.pdf}
     \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}

### 2019-03-05 manuscript.tex
Move figures

@@
     \centering
-    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/density.pdf}}%
-    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/density.pdf}}
+    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{dynamic_exploration_castalia_refine_density.pdf}}%
+    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{dynamic_exploration_castalia_land_density.pdf}}
     \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
@@
     \centering
-    \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.3\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_true.jpg}}%
-    \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.3\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_est.jpg}}
+    \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.3\textheight,width=0.5\textwidth]{dynamic_exploration_castalia_bump_true.jpg}}%
+    \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.3\textheight,width=0.5\textwidth]{dynamic_exploration_castalia_bump_est.jpg}}
     \caption{Asteroid Castalia with augmented with additional surface features~\label{fig:castalia_refinement}}

### 2019-03-09 manuscript.tex
Move final figure
Update manuscript to satisfy JGCD

@@
 For operations around asteroids, the ratio is relatively large which causes a much larger coupling between the translational and rotational states.
-References~\citenum{elmasri2005} and~\citenum{sanyal2004a} investigated the coupling of an elastic dumbbell spacecraft in orbit about a central body, but only considered the case of a spherically symmetric central body.
+\citeauthor{elmasri2005}~\cite{elmasri2005} and \citeauthor{sanyal2004a}~\cite{sanyal2004a} investigated the coupling of an elastic dumbbell spacecraft in orbit about a central body, but only considered the case of a spherically symmetric central body.
 Furthermore, the spacecraft model is assumed to remain in a planar orbit.
 As a result, these developments are not directly applicable to motion about an asteroid, which experiences highly non-Keplerian motion.
-Reference~\citenum{misra2015b} investigated the effect of coupled motion on long term trajectories around asteroids.
+\citeauthor{misra2015b}~\cite{misra2015b} investigated the effect of coupled motion on long term trajectories around asteroids.
 However, the analysis only considered a second order spherical harmonic gravitational potential model. 
@@
     \centering
-    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=0.5\textwidth]{dynamic_exploration_castalia_refine_slope.pdf}}%
-    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_slope_masked.pdf}}
+    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=\textwidth]{dynamic_exploration_castalia_refine_slope.pdf}}\\
+    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_slope_masked.pdf}}
     \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}
@@
     \centering
-    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{dynamic_exploration_castalia_refine_dist.pdf}}%
-    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_dist_masked.pdf}}
+    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=\textwidth]{dynamic_exploration_castalia_refine_dist.pdf}}\\
+    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_dist_masked.pdf}}
     \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
@@
     \centering
-    \includegraphics[width=0.75\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_cost.pdf}
+    \includegraphics[width=\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_cost.pdf}
     \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
@@
     \centering
-    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{dynamic_exploration_castalia_refine_density.pdf}}%
-    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{dynamic_exploration_castalia_land_density.pdf}}
+    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=\textwidth]{dynamic_exploration_castalia_refine_density.pdf}}\\
+    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=\textwidth]{dynamic_exploration_castalia_land_density.pdf}}
     \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{figures/dynamic_exploration/castalia/land/asteroid_trajectory.jpg}
+    \includegraphics[width=0.8\textwidth]{dynamic_exploration_castalia_land_asteroid_trajectory.jpg}
     \caption{Vertical descent onto 4769 Castalia~\label{fig:castalia_landing}}

### 2019-10-04 resp.tex
template for response letter

\documentclass[11pt]{article}
\usepackage[letterpaper,text={6.5in,8.6in},centering]{geometry}
\usepackage{amssymb,amsmath,amsthm,times,url}
\usepackage{xr,xcite,color}
\usepackage{threeparttable,booktabs}
\usepackage{pdfpages}
\usepackage{algpseudocode,cases}

\newcommand{\norm}[1]{\ensuremath{\left\| #1 \right\|}}
\newcommand{\bracket}[1]{\ensuremath{\left[ #1 \right]}}
\newcommand{\braces}[1]{\ensuremath{\left\{ #1 \right\}}}
\newcommand{\parenth}[1]{\ensuremath{\left( #1 \right)}}
\newcommand{\pair}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\met}[1]{\ensuremath{\langle\langle #1 \rangle\rangle}}
\newcommand{\refeqn}[1]{(\ref{eqn:#1})}
\newcommand{\reffig}[1]{Fig. \ref{fig:#1}}
\newcommand{\tr}[1]{\mathrm{tr}\ensuremath{\negthickspace\bracket{#1}}}
\newcommand{\trs}[1]{\mathrm{tr}\ensuremath{[#1]}}
\newcommand{\deriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}
\newcommand{\SO}{\ensuremath{\mathsf{SO(3)}}}
\newcommand{\T}{\ensuremath{\mathsf{T}}}
\renewcommand{\L}{\ensuremath{\mathsf{L}}}
\newcommand{\so}{\ensuremath{\mathfrak{so}(3)}}
\newcommand{\SE}{\ensuremath{\mathsf{SE(3)}}}
\newcommand{\se}{\ensuremath{\mathfrak{se}(3)}}
\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
\newcommand{\aSE}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&1\end{bmatrix}}}
\newcommand{\ase}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&0\end{bmatrix}}}
\newcommand{\D}{\ensuremath{\mathbf{D}}}
\newcommand{\Sph}{\ensuremath{\mathsf{S}}}
\renewcommand{\S}{\Sph}
\newcommand{\J}{\ensuremath{\mathbf{J}}}
\newcommand{\Ad}{\ensuremath{\mathrm{Ad}}}
\newcommand{\intp}{\ensuremath{\mathbf{i}}}
\newcommand{\extd}{\ensuremath{\mathbf{d}}}
\newcommand{\hor}{\ensuremath{\mathrm{hor}}}
\newcommand{\ver}{\ensuremath{\mathrm{ver}}}
\newcommand{\dyn}{\ensuremath{\mathrm{dyn}}}
\newcommand{\geo}{\ensuremath{\mathrm{geo}}}
\newcommand{\Q}{\ensuremath{\mathsf{Q}}}
\newcommand{\G}{\ensuremath{\mathsf{G}}}
\newcommand{\g}{\ensuremath{\mathfrak{g}}}
\newcommand{\Hess}{\ensuremath{\mathrm{Hess}}}
\newcommand{\refprop}[1]{Proposition \ref{prop:#1}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newtheorem{definition}{Definition}%[section]
\newtheorem{lem}{Lemma}%[section]
\newtheorem{prop}{Proposition}%[section]
\newtheorem{remark}{Remark}%[section]
\newtheorem{theorem}{Theorem}%[section]

\newenvironment{correction}{\begin{list}{}{\setlength{\leftmargin}{1cm}\setlength{\rightmargin}{1cm}}\vspace{\parsep}\item[]``}{''\end{list}}
\newcommand{\comment}[1]{\item \itshape #1 \normalfont}

\externaldocument{manuscript}
\externalcitedocument{manuscript}

\begin{document}

%\pagestyle{empty}

\section*{Response to the Reviewers' Comments for  2019-03-G004445}

The author would like to thank the reviewers for their thoughtful comments, which are aimed
towards improving the quality of the paper and the clarity of the results. In accordance with the comments and suggestions, the manuscript has been revised, and the answers to all comments are addressed as follows.

(In the revised manuscript, the citation numbers for equations, assumptions, propositions, and references are changed. This answer is written according to the new item numbers.)

\subsection*{Associate Editor}

\setlength{\leftmargini}{0pt}
\begin{itemize}\setlength{\itemsep}{2\parsep}

\comment{The reviews regarding the contributions are mildly favorable, yet include some valid technical questions/issues as well as hesitations regarding the language, style, and clarity. The paper is not publishable in the current form. A revised manuscript submission does not guarantee success. To remain under consideration, all issues must be addressed in a satisfactory manner.   
In this revision, please include 
1) a line-by-line response (action taken, rebuttal, justification), etc.) to each of the reviewer and editor comments, along with explicitly stating any action taken in the revised manuscript, as appropriate.  Please color code the response to include different colors for the reviewer comments, author response, and action taken.  
2) in your revised copy include a different color font for to indicate portions of the paper that have significant changes/additions compared to the previous submitted one.  please keep the original font colors from earlier revisions.
}

Thanks for the comments. All of the comments have been addressed in the response letter, and the manuscript has been revised accordingly. The detailed responses to each comment are given in the subsequent pages.

\end{itemize}

\clearpage\newpage
\subsection*{Reviewer 1}
\begin{itemize}\setlength{\itemsep}{2\parsep}
    \comment{Comments by Reviewer 1: to be added}

    Response to be added.
\end{itemize}

\clearpage\newpage
\subsection*{Reviewer 2}

\begin{itemize}\setlength{\itemsep}{2\parsep}

\comment{This paper discusses a method for using a range sensor to compute a 3D model of an asteroid, a guidance algorithm for designing an optimal trajectory for building such a model, and a multi-resolution approach for landing. While the paper does have a few nice contributions, it has a number of serious flaws that must be addressed before it is suitable for publication.}

\comment{
Major issues to address:
1.      The construction of the measurement presented on pg. 8 requires that you know the asteroid attitude $R_A$. Where does the knowledge of the asteroid attitude come from? This is almost never known in the type of scenarios the authors are suggesting in this paper. By knowing $R$, $R_A$, and $x$ in the equation on pg. 8, the authors assume pose is known. Indeed, the unknown relative attitude (and, often, relative position as well) between the asteroid and the spacecraft at any point in time is one of the principal challenges that makes this problem hard---and to ignore this problem is to solve a problem of questionable relevance. A review of the literature of LIDAR-based modeling for asteroids (or other space objects) will show that much of the effort is spent simultaneously solving for the asteroid orientation (or pole and spin) and its shape (usually while assuming the spacecraft’s own inertial state is known). This essentially becomes a form of the simultaneous localization and mapping (SLAM) problem.}

\comment{2.      If you must assume knowledge of the asteroid attitude, I suggest you consider only knowing the pole and spin (and not $R_A$ explicitly). If this is the route you choose, please discuss sensitivity of your algorithm to deterioration of knowledge in these two parameters. I expect things to fall apart pretty quickly as spin knowledge degrades as you will no longer be computing the range to the correct point on the surface.}

\comment{Minor issues to address:
1.      The authors are encouraged to conduct a more thorough literature review on image-based and LIDAR-based 3D modeling of asteroids.  Here are a few suggestions:\\
a.      Bercovici, B., and McMahon, J., “Robust Autonomous Small-Body Shape Reconstruction and Relative Navigation Using Range Images,” Journal of Guidance, Control, and Dynamics, 2019.\\
b.      Kirk, R.L., Kraus, E.H., and Rosiek, M., “Recent planetary topographic mapping at the USGS, Flagstaff: Moon, Mars, Venus, and beyond,” International Archives of Photogrammetry and Remote Sensing, Vol. XXXIII, Part B4. Amsterdam, 2000.\\
c.      Gaskell, R.W., Barnouin, O.S., Scheers, D.J., Konopliv, A.S., Mukai, T., Abe, S., Saito, J., Ishiguro, M., Kubota, T., Hashimoto, T., Kawaguchi, J., Yoshikawa, M., Shirakawa, K., Kominato, T., Hirata, N., and Demura, H., “Characterizing and navigating small bodies with imaging data,” Meteoritics \& Planetary Science, Vol. 43, No. 6, 2008, pp. 1049–1061. https://doi.org/10.1111/j.1945-5100.2008.tb00692.x}

\comment{2.      Page 3, line 23: It is probably more accurate to say “on board camera” than “on board telescope” in this context. Also, the word “radar” has been erroneously added into the LIDAR definition.}

\comment{3.      Page 7, Eqs. 13-16: Many terms in these equations aren’t defined. The notation is very confusing without having to read Refs. [7] and [16]. Either fully define all terms or simply point the reader to the appropriate references.}

\comment{4.      Section III.B: By only adjusting the height of a vertex this method assumes that each radial direction has a single-valued height. This greatly limits the variety of shapes that can be modeled. Also, by scaling the radial distance of a uniformly sampled initial mesh (e.g., a sphere or ellipsoid), the parts of the asteroid closer to the origin will tend to have a higher vertex density (resolution) than those farther away. I suppose this may be addressed by remeshing if things get too bad. Do the authors have any thoughts on addressing this issue? Has it impacted performance in any of the examples?}

\comment{5.      Page 10, line 10: Your notation for $p_j$, $p_{j,i}$, and $r_{j,i}$  isn’t very clear. I suggest rewording the discussion or, perhaps, altering notation. Adding a figure may also help. }

\comment{6.      Page 10, line 10: Change “variance” to “standard deviation.” Based on the equation at the top of the page, $w_{j,i}$ is the standard deviation. Its square is the variance.}

\comment{7.      Page 10: A figure would be very helpful in explaining what you’re doing with Eqs. 18 and 19. I had to read through this a few times and a figure would have helped me get it the first time.}

\comment{8.      The optimal guidance law appears to work by selecting the lowest cost vertex ($v_{min}$) from equation at bottom of pg. 16). Would it not be better to consider how the vertex uncertainties are improved along the entire trajectory from Eq. 26?}

\comment{9.      Page 24: How are you changing the pointing of the range sensor during the descent? I would presume you would have to scan the surface during the descent to get the improved resolution you desire? Or are you suggesting that you change the mesh resolution and simply re-process the existing data set? The proposed strategy is not 100\% clear.}

\comment{Editorial comments:
1.      The notation is hard to follow and seems inconsistent in places. I suggest using font or typesetting to differentiate between matrices, vectors, and scalars. }

\comment{2.      AIAA journals require papers be written in third person. This paper is written in first person.}
\end{itemize}

\end{document}

### 2020-07-17 manuscript.tex
JAS submission 0

@@
-\documentclass[journal]{new-aiaa}
-%\documentclass[conf]{new-aiaa} for conference papers
+%% The following three lines were added to by pass an error
+%% See https://tex.stackexchange.com/questions/108394/tex-capacity-exceeded-sorry-input-stacksize-5000
+\makeatletter
+\def\cl@chapter{}
+\makeatother
+%%
+\documentclass[smallextended]{svjour3}       % onecolumn (second format)
 \usepackage{AAS_packages}
+%\usepackage[numbers]{natbib}
 % \usepackage[utf8]{inputenc}
@@
 
-% TODO Think about adding current affiliation as a note, need to ask company
-\author{Shankar Kulumani \footnote{PhD, Mechanical and Aerospace Engineering, \href{mailto:skulumani@gwu.edu}{skulumani@gwu.edu}}
-and
-Taeyoung Lee \footnote{Associate Professor, Mechanical and Aerospace Engineering, \href{mailto:tylee@gwu.edu}{tylee@gwu.edu}}}
-\affil{The George Washington University, Washington, DC, 20052}
+\author{Shankar Kulumani         \and
+        Taeyoung Lee %etc.
+}
+
+%\authorrunning{Short form of author list} % if too long for running head
+
+% todo: we may update the affiliation and the address of Shankar 
+\institute{S. Kulumani (corresponding author) \at
+              Mechanical and Aerospace Engineering, The George Washington University, Washington DC, 20052\\
+              \email{shanks.k@gmail.com}           %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+           \and
+           T. Lee,  \at
+              Mechanical and Aerospace Engineering, The George Washington University, Washington DC, 20052\\
+              \email{tylee@gwu.edu}
+}
 
@@
     Constructing of the precise shape of an asteroid is critical for spacecraft operations, as the gravitational potential is determined by spatial mass distribution.
-    For example, the standard method of determining the gravitational potential of an asteroid, through the use of a polyhedron potential model, is directly dependent on the shape model.
-    Furthermore, safe landing or close-proximity operations requires accurate knowledge of the surface topology. 
+    %For example, the standard method of determining the gravitational potential of an asteroid, through the use of a polyhedron potential model, is directly dependent on the shape model.
+    %Furthermore, safe landing or close-proximity operations requires accurate knowledge of the surface topology. 
     The typical approach to shape determination requires a prolonged ``mapping'' phase of the mission over which extensive measurements are collected and transmitted for Earth-based processing.
@@
     We demonstrate this approach using several radar shape models of asteroids and provide a full dynamic simulation about asteroid 4769 Castalia.
+    \keywords{Asteroids \and Shape Construction \and Guidance \and Optimization}
 \end{abstract}
@@
 For operations around asteroids, the ratio is relatively large which causes a much larger coupling between the translational and rotational states.
-\citeauthor{elmasri2005}~\cite{elmasri2005} and \citeauthor{sanyal2004a}~\cite{sanyal2004a} investigated the coupling of an elastic dumbbell spacecraft in orbit about a central body, but only considered the case of a spherically symmetric central body.
+In~\cite{elmasri2005} and \cite{sanyal2004a}, the coupling of an elastic dumbbell spacecraft in orbit about a central body is considered, assuming that the central body is spherically symmetric.
 Furthermore, the spacecraft model is assumed to remain in a planar orbit.
 As a result, these developments are not directly applicable to motion about an asteroid, which experiences highly non-Keplerian motion.
-\citeauthor{misra2015b}~\cite{misra2015b} investigated the effect of coupled motion on long term trajectories around asteroids.
+In~\cite{misra2015b}, the effect of coupled motion is investigated for long term trajectories around asteroids.
 However, the analysis only considered a second order spherical harmonic gravitational potential model. 
@@
 Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
-As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
+As shown in Reference~\cite{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
 The computational cost of the polyhedron potential model, given by~\cref{eq:attraction}, is roughly proportional to the number of faces in the shape model.
@@
 
-\section{Acknowledgement}
-This research is supported in part by NSF under the grant CMMI-1335008.
-
+%\section{Acknowledgement}
+%This research is supported in part by NSF under the grant CMMI-1335008.
+
+\bibliographystyle{IEEEtran}
 \bibliography{library}

### 2021-12-06 jas_response.tex
Start on JAS response

\documentclass[11pt]{article}
\usepackage[letterpaper,text={6.5in,8.6in},centering]{geometry}
\usepackage{amssymb,amsmath,amsthm,times,url}
\usepackage{xr,xcite,color}
\usepackage{threeparttable,booktabs}
\usepackage{pdfpages}
\usepackage{algpseudocode,cases}

\newcommand{\norm}[1]{\ensuremath{\left\| #1 \right\|}}
\newcommand{\bracket}[1]{\ensuremath{\left[ #1 \right]}}
\newcommand{\braces}[1]{\ensuremath{\left\{ #1 \right\}}}
\newcommand{\parenth}[1]{\ensuremath{\left( #1 \right)}}
\newcommand{\pair}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\met}[1]{\ensuremath{\langle\langle #1 \rangle\rangle}}
\newcommand{\refeqn}[1]{(\ref{eqn:#1})}
\newcommand{\reffig}[1]{Fig. \ref{fig:#1}}
\newcommand{\tr}[1]{\mathrm{tr}\ensuremath{\negthickspace\bracket{#1}}}
\newcommand{\trs}[1]{\mathrm{tr}\ensuremath{[#1]}}
\newcommand{\deriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}
\newcommand{\SO}{\ensuremath{\mathsf{SO(3)}}}
\newcommand{\T}{\ensuremath{\mathsf{T}}}
\renewcommand{\L}{\ensuremath{\mathsf{L}}}
\newcommand{\so}{\ensuremath{\mathfrak{so}(3)}}
\newcommand{\SE}{\ensuremath{\mathsf{SE(3)}}}
\newcommand{\se}{\ensuremath{\mathfrak{se}(3)}}
\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
\newcommand{\aSE}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&1\end{bmatrix}}}
\newcommand{\ase}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&0\end{bmatrix}}}
\newcommand{\D}{\ensuremath{\mathbf{D}}}
\newcommand{\Sph}{\ensuremath{\mathsf{S}}}
\renewcommand{\S}{\Sph}
\newcommand{\J}{\ensuremath{\mathbf{J}}}
\newcommand{\Ad}{\ensuremath{\mathrm{Ad}}}
\newcommand{\intp}{\ensuremath{\mathbf{i}}}
\newcommand{\extd}{\ensuremath{\mathbf{d}}}
\newcommand{\hor}{\ensuremath{\mathrm{hor}}}
\newcommand{\ver}{\ensuremath{\mathrm{ver}}}
\newcommand{\dyn}{\ensuremath{\mathrm{dyn}}}
\newcommand{\geo}{\ensuremath{\mathrm{geo}}}
\newcommand{\Q}{\ensuremath{\mathsf{Q}}}
\newcommand{\G}{\ensuremath{\mathsf{G}}}
\newcommand{\g}{\ensuremath{\mathfrak{g}}}
\newcommand{\Hess}{\ensuremath{\mathrm{Hess}}}
\newcommand{\refprop}[1]{Proposition \ref{prop:#1}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newtheorem{definition}{Definition}%[section]
\newtheorem{lem}{Lemma}%[section]
\newtheorem{prop}{Proposition}%[section]
\newtheorem{remark}{Remark}%[section]
\newtheorem{theorem}{Theorem}%[section]

\newenvironment{correction}{\begin{list}{}{\setlength{\leftmargin}{1cm}\setlength{\rightmargin}{1cm}}\vspace{\parsep}\item[]``}{''\end{list}}
\newcommand{\comment}[1]{\item \itshape #1 \normalfont}

\externaldocument{manuscript}
\externalcitedocument{manuscript}

\begin{document}

%\pagestyle{empty}

\section*{Response to the Reviewers' Comments for JASS-D-20-00049}

The author would like to thank the reviewers for their thoughtful comments, which are aimed towards improving the quality of the paper and the clarity of the results.
In accordance with the comments and suggestions, the manuscript has been revised, and the answers to all comments are addressed as follows.

(In the revised manuscript, the citation numbers for equations, assumptions, propositions, and references are changed. This answer is written according to the new item numbers.)

\subsection*{Associate Editor}

\setlength{\leftmargini}{0pt}
\begin{itemize}\setlength{\itemsep}{2\parsep}

\comment{
    Based on the advice received, I have decided that your manuscript could be reconsidered for publication should you be prepared to incorporate major revisions. 
    When preparing your revised manuscript, you are asked to carefully consider the reviewer comments which can be found below, and submit a list of responses to the comments. 
    You are kindly requested to also check the website for possible reviewer attachment(s).
}

Thanks for the comments. All of the comments have been addressed in the following response letter, and the manuscript has been revised accordingly. 
The detailed responses to each comment are given in the subsequent pages.

\end{itemize}

\clearpage\newpage
\subsection*{Reviewer 2}
\begin{itemize}\setlength{\itemsep}{2\parsep}

    \comment{The article proposes a scheme to construct the shape of an asteroid from range measurements using a LIDAR or a similar instrument. 
        It also presents a method to further refine the shape construction by using an optimal guidance scheme to maneuver the spacecraft. 
        It seems to me that the proposed schemes work well; the construction of shapes in the examples considered is accurate with low computational cost. 
        The article is innovative and will be of interest to researchers working on asteroid missions.

        I have a couple of questions:
    }

\comment{(1) The spacecraft dynamics model considered in the article is that of a dumbbell. 
Why was such a model chosen instead of an arbitrary rigid spacecraft?
Is it because the RHS of equations (4) and (6) will be more complicated for a rigid spacecraft ?
Also, equation (12) will be an integral and the shape construction scheme will be more computationally intensive.
Some comments addressing this point in the article may be useful.}

Dumbell is a decent approximation for a rigid spacecraft.
Can easily extend from a dumbell, 2 masses to arbitary number of masses to handle more general spacecraft. 
In the limit an arbitrary number of masses can then approximate a general rigid body.

\comment{(2) In addition to range measurements for the asteroid surface, I think that inertial positions of the centers of mass of the asteroid and the spacecraft will be necessary.
How are these obtained?}

Inertial positions not required.

Add relative equations of motions

The formulation presented assumes that the inertial orentation of the asteroid is available.

\end{itemize}

\clearpage\newpage
\subsection*{Reviewer 4}

\begin{itemize}\setlength{\itemsep}{2\parsep}

\comment{    Dear authors,
This paper is very well written and discusses an important topic in the spacecraft exploration of small bodies - how can we simplify current approaches and proximity operations, and also not rely as much on ground in the loop support? The techniques are well described and the presentation is easy to follow.
My first concern is the lack of references to recent missions such as Rosetta, Hayabusa2, and Osiris-Rex, and the discussion or comparison to approaches taken in these missions for going from approach to landing. Although the techniques presented in this paper are very interesting and seem to simplify proximity operations at small bodies, it is difficult to clearly see the benefits since there is no comparisons to the recent techniques implemented in the more recent missions than those referenced.
My second concern is the impact of spacecraft state uncertainties and non-gravitational accelerations on the results presented. Although the authors seem to include this as future work, it would be best to include this discussion in this paper to some extend, as these inputs usually drive uncertainties in determining shape modeling and defining landing areas.  
Finally, the authors should augment the paper discussing onboard requirements to allow implementation of the techniques presented, since portability can also be a challenge.

Specific comments:
}

\comment{A few possible typos:
- I would write "dynamical" instead of dynamic at a number of places, but this might be a writing style: Intro line 25 \& 30, page 19 line 31.
}

\comment{
Page 3, line 33-34, the citations of Hayabusa1 and NEAR seem mis-used. Hayabusa stayed 3 months at Itokawa and the mission operations team did not report requiring a polyhedron potential model for landing (if so, a reference would be needed). NEAR did orbit about 1 year from orbit insertion to landing.
There could be references to more recent missions highlighting the specifics of the proximity operation implementations and their lacks.
}

\comment{
Page 3 line 41-42 with reference 13, The asteroid redirect mission has been canceled, and so this reference seems somewhat irrelevant when trying to highlight long delays in implementing operations that would require mapping and a better defined potential. A reference to OREx would be more appropriate. The specifics of how the techniques proposed in the paper could have changed the proximity operations of OREx need to be included and described better.
}

\comment{
Page 3, line 48-49, saying "The dependency on expensive ground-based shape reconstruction technique limits the ability of spacecraft to autonomously operate at asteroids." seems misleading. What does "expensive" mean or refer to? The ability of spacecraft to autonomously operate at asteroids is limited by the lack of portable solutions and/or opportunities to test those portable solutions, rather than being able to use ground-based techniques.
}

Add additional detail on limitations. 
Ground based sensors are also limited in number, in disrepair and over taxed (cite a reference on the DSN/Arecibo collapsing)

\comment{
Page 4 line 7, "onboard" as opposed to "onborad".
}

\comment{
Page 4, line 37, "During this simulation, this update shape model is then used in a nonlinear controller...". The second "this" should not have a capital "T", and should be "used in" as opposed to "used to in" .
}

\comment{
Page 8, line 1-2, the authors should augment the statement made citing reference 7 with one or two sentences for the unfamiliar reader.  
}

\comment{
In 3.1, the authors should discuss range measurements done with recent missions, what was successful and what was not, to distinguish their approach more efficiently. 
References 17 and 18 seem outdated. References to more recent work or missions are needed.
}

Find more recent references

\comment{
Page 8, line 31, the equation for "d" should be "(Delta TOF * c)/2" not "(Delta TOF)/(2c)". I would assume the equation is correct in the code but the authors should check.
}

Good catch. 
Don't actually simulate time of flight of a sensor. 
instead utilizing ray intersection algorithms to determine distance. 
This equation used to relate distance in simulation to a time of flight as would be measured in reality.

\comment{
In 3.2, it is unclear how the boundaries of areas being updated are being treated, whereas it seems discontinuity could easily be seen in results but would need to be addressed to some extend? It may be good to add a few sentences about boundary conditions and how these are treated.
}

\comment{
In 3.3, the authors should discuss the impact of spacecraft state errors and non-gravitational accelerations on the results of this technique. Is this assumed to be a task left for ground operations?
I also noticed this seems to be part of future work. It may be good to mention in the text also.
}

\comment{
In 4.3, references should be added for the shape models used for this work.
In 4.3, line 45 - 47, "asteroids" should have no "s". Also, mentioning "initially unknown asteroid" is contradicting earlier statements and the following paragraph since a simple shape model is required for this technique.
In 4.3, page 20, statement starting on line 17, do the asteroid size and rotation period have no impact on the reconstruction time required? What amount of data does this mean? it is difficult to gauge what is needed for this onboard processing to be possible, or if this would be readily feasible.
As for my comment for 3.3, it would be best to describe the impact of spacecraft uncertainties on these results.
The spacecraft orbit seems to resemble that of Hayabusa - this is inferred from using the "home position" nomenclature. Is the technique best used with this kind of approach as opposed to following some orbits like what was done with the OREx mission? A discussion might be required here.
How does this translate in terms of fuel consumption? or delta-V imparted to the spacecraft?  
}

\comment{
Fig 7 \& 8, what causes some areas to remain with high uncertainties? This would need to be discussed for both ML14 and Castalia.
}

\comment{
As part of section 5, the authors should discuss impacts of more complex criteria for landing or surface sampling, for instance, types of material on the surface, poles versus equatorial areas, etc. It may be good to look at sampling requirements and criteria of recent missions to see how they would affect the technique described.
}

\comment{
Conclusion:
Page 30, line 45, "significant" instead of "signification".
}

\comment{
The future works mentioned are definitely of interest!
}

\end{itemize}

\end{document}

### 2021-12-11 jas_response.tex
Update response

@@
 
-Dumbell is a decent approximation for a rigid spacecraft.
+The use of the dumbbell approximation allows use to avoid having to evaluate the integral over the extended body in the equations of motion.
+The dumbbell model allows us to approximate an extended body with a miminimum of additional complexity.
+Additional comments have been added to the manuscript explaining this decision and copied here.
+
+The dumbbell is in some sense the simplest approximation of an extended rigid body.
+It allows for simple analytical solution for the moment of inertia and greatly simplifies the equations of motion.
+Dumbell is an approximation for a rigid spacecraft and is used widely 
 Can easily extend from a dumbell, 2 masses to arbitary number of masses to handle more general spacecraft. 
@@
 
-Inertial positions not required.
-
-Add relative equations of motions
-
-The formulation presented assumes that the inertial orentation of the asteroid is available.
+In our analyis, we have assumed that the inertial position of both the asteroid and vehicle are available.
+For both bodies we assume that ground based tracking/orbit determination is available prior to arrival.
+This provides the inertial state of both bodies and is a requirement for the orbital rendezvous prior to any surface mapping operation.
+Additional comments have been added to the manuscript and are repeated here.
 
@@
 
+Thank you for the comments aimed at improving the quality of the manuscript. 
+Additional references and discussion related to more recent missions have been included.
+
+In addition, additional detail concerning spacecraft/state uncertainties and perturbing forces has been added to the manuscript.
+The discussion discusses the current limitations of the presented approach and discuses this as an area of future work.
+The additional discussion is presented here.
+
 \comment{A few possible typos:
@@
 }
+
+Thank you for this comment. 
+We have replaced ''dynamic`` with ''dynamical`` in several locations throughout the manuscript.
+We do not repeat the corrections here for simplicity.
 
@@
 
+Depending on the specific mission objectives the preliminary mapping phase may serve multiple purposes. 
+In this week, we seek to utilize the mapping phase to create a polyhedron potential model and select an appropriate landing site. 
+We added additional discussion related to more recent missions and copied below.
+
 \comment{
@@
 }
+
+The citation to the asteroid redirect mission has been removed and additional discussion related to the OSIRIS-REX mission has been incorporated.
+The additional discussion has been copied below.
 
@@
 
-Add additional detail on limitations. 
-Ground based sensors are also limited in number, in disrepair and over taxed (cite a reference on the DSN/Arecibo collapsing)
+This sentence has been removed and replaced with the following:
+
+Onboard shape reconstruction techniques enable autonomous operations which allow for a greater range of spacecraft operations.
 
@@
 }
+This typo has been corrected and is copied below.
 
@@
 }
+Additional detail describing the polyhedron potential model is added and copied below.
+
+The polyhedron potential model is based on a triangular faceted shape model of an asteroid.
+In this approach, the shape of the asteroid is used to directly compute the exterior potential.
 
@@
 In 3.1, the authors should discuss range measurements done with recent missions, what was successful and what was not, to distinguish their approach more efficiently. 
-References 17 and 18 seem outdated. References to more recent work or missions are needed.
+References 17 and 18 seem outdated. 
+References to more recent work or missions are needed.
 }
@@
 
-Good catch. 
-Don't actually simulate time of flight of a sensor. 
-instead utilizing ray intersection algorithms to determine distance. 
-This equation used to relate distance in simulation to a time of flight as would be measured in reality.
+The equation has been corrected and is copied below.
 

### 2021-12-11 jas_response.tex
Update response

@@
 \usepackage{algpseudocode,cases}
+\usepackage{siunitx}
+\usepackage{cleveref}
 
@@
 
+Each measurement is used to only update vertices which lie within some user defined angular constraint, \( \Delta \sigma_{max} \).
+In this approach only the radial distance of each vertex is changed as a function of the measurements. 
+As a result the topology of the polyhedron shape does not vary and the model remains watertight and closed.
+In addition, the correlation based sensor model used in this approach ensures that vertices further from the measurement have a higher variance and therefore reduced displacement for a given measurement.
+The scaling factor \( c \) and the angular constraint \( \Delta \sigma_{max} \) can also be used to adjust the region of impact of a given measurement. 
+Adjusting these scalars, in addition to the a priori probability of the initial shape model can be utilized to ensure that steep gradients on the surface are not artificially introduced during the mapping process.
+Additional detail has been added to the manuscript and is shown below.
+
+\begin{correction}
+    The parameters \( c \) and \( \Delta \sigma_{max} \) are used to define the region of impact of each measurement. 
+    The angular constraint \( \Delta \sigma_{max} \) sets a hard constraint on the vertices which need to be updated for a given measurement.
+    The scalar \( c \) may then be used to adjust the variance \( w_{j,i} \) as a function of the distance between measurement \( j \) and vertex \( i \).
+    These two parameters may be used to minimize steep gradients that may occur during the shape reconstruction process.
+\end{correction}
+
 \comment{
-In 3.3, the authors should discuss the impact of spacecraft state errors and non-gravitational accelerations on the results of this technique. Is this assumed to be a task left for ground operations?
+In 3.3, the authors should discuss the impact of spacecraft state errors and non-gravitational accelerations on the results of this technique. 
+Is this assumed to be a task left for ground operations?
 I also noticed this seems to be part of future work. It may be good to mention in the text also.
@@
 
+Additional detail regarding the impact of spacecraft state uncertainty and non-gravitational accelerations have been included in the manuscript and are shown below.
+
+\begin{correction}
+    In this numerical example we have assumed perfect state knowledge of the spacecraft.
+    This is a strong assumption that would not exist in any realistic situation. 
+    However, the measurement model defined in the previous section may be extended to consider the uncertainty in both the state \( x \) and the range measurement \( d \) rather than combining them into a single random variable \( p \).
+    In addition, the dynamics defined by~\crefrange{eq:x_dot}{eq:omega_dot} do not consider any non-gravitational accelerations such as solar radiation pressure on the vehicle.
+    In general, these types of external forces will primarily serve to increase state uncertainty and cause large errors in the closed loop control system.
+    Adaptive control techniques have been demonstrated in the past to address both fixed and time varying disturbances of this kind~\cite{kulumani2017a}.
+    The authors will relax these assumptions in future work.
+\end{correction}
+
 \comment{
-In 4.3, references should be added for the shape models used for this work.
+In 4.3, references should be added for the shape models used for this work.}
+
+A reference for the radar shape models has been added.
+
+\begin{correction}
+We utilize radar shape models of asteroid \num{4769} Castalia and (\num{52760}) \num{1998} \(\text{ML}_{14}\)~\cite{neese2004}.
+\end{correction}
+
+\comment{
 In 4.3, line 45 - 47, "asteroids" should have no "s". 
+}
+
+The ''s`` has been removed and the corrected sentence is shown in the previous response.
+
+\comment{
 Also, mentioning "initially unknown asteroid" is contradicting earlier statements and the following paragraph since a simple shape model is required for this technique.
+}
+
+The sentence has been reworded to more accurately reflect the level of knowledge required.
+It is copied here as:
+
+\begin{correction}
+These demonstrate the ability of a spacecraft to autonomously explore and maneuver around an initially poorly modeled asteroid while incrementally updating the shape model.
+\end{correction}
+
+\comment{
 In 4.3, page 20, statement starting on line 17, do the asteroid size and rotation period have no impact on the reconstruction time required? 
@@
 it is difficult to gauge what is needed for this onboard processing to be possible, or if this would be readily feasible.
+}
+
+The shape refinement process defined in~\cref{sec:radius_update} is by definition a local refinement process.
+Rather than operating on the entire shape model only the region defined by the angular constraint \( \Delta \sigma_{max}\) is considered in each measurement update. 
+The user can adjust this parameter to ensure a constant number of vertices are considered for each measurement update and therefore maintain a constant number of computations based on processor capabilities.
+In addition, the refinement process introduced in~\cref{sec:landing_refinement} can be utilized to allow for higher fidelity in a small region.
+An appropriate choice of \( \Delta \sigma_{max} \) is again crucial to maintain constant computational requirements.
+Additional discussion has been added to the manuscript discussing this feature of our approach and is copied below.
+
+\begin{correction}
+    The angular constraint \( \Delta \sigma_{max} \) may be used to adjust the computational requirements of the shape refinement process.
+    Larger values of \( \Delta \sigma_{max} \) result in a greater computational demand as a given measurement ray is used to update a larger number of vertices.
+    \Cref{sec:landing_refinement} presents an approach to allow for a higher resolution mesh in certain regions to capture finer surface details without excessive resources. 
+\end{correction}
+
+\comment{
 As for my comment for 3.3, it would be best to describe the impact of spacecraft uncertainties on these results.
 The spacecraft orbit seems to resemble that of Hayabusa - this is inferred from using the "home position" nomenclature. 
-Is the technique best used with this kind of approach as opposed to following some orbits like what was done with the OREx mission?
-A discussion might be required here.
+Is the technique best used with this kind of approach as opposed to following some orbits like what was done with the OREx mission? A discussion might be required here.
 How does this translate in terms of fuel consumption? or delta-V imparted to the spacecraft?  
 }
+
+The guidance scheme presented in~\cref{sec:explore_asteroid} will drive the vehicle towards states which will best reduce the total uncertainty of the shape model.
+As a result the vehicle in general may take an arbitrary trajectory about the body and utilize much larger control effort compared to utilizing the natural dynamics of the system. 
+We do not duplicate the motion of Hayabusa but did utilize the ''home position`` term to describe the numerical example.
+Our shape refinement approach is not limited to our guidance scheme but rather is an example of combining closed loop control with our shape refinement method.
+We will consider incorporating control effort constraints in our optimal guidance scheme in a future work.
 
@@
 
+These figures show the shape model uncertainty during the refinement process.
+Areas that have not been measured by the vehicle will have large uncertainties compared to those areas already surveyed. 
+Only after the vehicle has measured the entire surface will the shape model have a near constant uncertainty defined by 
+\begin{align*}
+    \sum_i w_i.
+\end{align*}
+An additional comment has been added to the figure captions and is shown below.
+
+\begin{correction}
+    Areas of high uncertainty are in yellow while areas of low uncertainty are in purple.
+    The guidance scheme continually selects regions of high uncertainty until the total shape uncertainty is sufficiently small.
+\end{correction}
+
 \comment{
@@
 }
+Our landing site selection algorithm is relatively simple as it is a direct function of the shape model.
+The approach was chosen as an example to demonstrate how a vehicle can autonomously model the shape of the asteroid, then utilize that shape model to chose a landing site. 
+Additional costs such as surface material or location on the body can be added as additional criteria in~\cref{eq:surface_cost}.
+We have added additional discussion concerning the landing site selection approach.
+
+\begin{correction}
+    The surface cost described here is relatively simple and chosen to be solely a function of the current spacecraft position and shape model.
+    Additional scientific criteria such as surface material or location on the body, e.g. equatorial vs. polar regions, can be utilized instead of a random science value as presented here.
+\end{correction}
 
@@
 }
+The typo has been corrected and is shown below.
+
+\begin{correction}
+This is in contrast to standard shape reconstruction algorithms which operate over the entire surface and require significant computational resources.
+\end{correction}
 
@@
 
+Thank you and we look forward to future work in this area.
+
 \end{itemize}

### 2021-12-13 jas_response.tex
Update response

@@
 \newcommand{\refprop}[1]{Proposition \ref{prop:#1}}
+\newcommand{\todo}{{\large \textcolor{red}{TODO: }}}
 
@@
 The detailed responses to each comment are given in the subsequent pages.  
+As a note, reference numbers to citations or equations may not match the manuscript in this response.
 
@@
 
-The use of the dumbbell approximation allows use to avoid having to evaluate the integral over the extended body in the equations of motion.
-The dumbbell model allows us to approximate an extended body with a miminimum of additional complexity.
+The primary benefit of the dumbbell approximation is to avoid the additional integral over the entire body.
+While conceptually and analytically simple the dumbbell model still captures the important rigid body effects on the system, namely the coupling of attitude and translational states through the external forces and moments.
+In addition, this type of spacecraft model is prevelant in the field~\cite{kulumani2017b,lee2006a,lee2007a,elmasri2005}.
 Additional comments have been added to the manuscript explaining this decision and copied here.
 
-The dumbbell is in some sense the simplest approximation of an extended rigid body.
-It allows for simple analytical solution for the moment of inertia and greatly simplifies the equations of motion.
-Dumbell is an approximation for a rigid spacecraft and is used widely 
-Can easily extend from a dumbell, 2 masses to arbitary number of masses to handle more general spacecraft. 
-In the limit an arbitrary number of masses can then approximate a general rigid body.
+\begin{correction}
+The dumbbell model is in some sense the simplest approximation of an extended rigid body.
+This model captures the important dynamics of an extended rigid body with a minmum of additional complexity and is prevelant the literature~\cite{kulumani2017b,lee2006a,lee2007a,elmasri2005}.
+In addition, the developments of the dumbbell model can be trivially extended to include a larger number of discrete masses to better approximate a more complicated spacecraft model.
+\end{correction}
 
@@
 
-In our analyis, we have assumed that the inertial position of both the asteroid and vehicle are available.
-For both bodies we assume that ground based tracking/orbit determination is available prior to arrival.
-This provides the inertial state of both bodies and is a requirement for the orbital rendezvous prior to any surface mapping operation.
+In our analyis, we have assumed that the inertial position of both the asteroid and vehicle are available prior to the mapping operations.
+This data is typically available as ground based measurements are required to rendezvous with the asteroid prior to mapping.
 Additional comments have been added to the manuscript and are repeated here.
+
+\todo Add to second paragraph of Section 4.3 Numerical example immediately after the sentence: ''In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat e_3)\).``
+
+\begin{correction}
+    We assume that the initial intertial state of the vehicle is available. 
+    This data is typically available from a ground based orbit determination scheme which enabled the original orbital rendezvous. 
+\end{correction}
 
@@
 The discussion discusses the current limitations of the presented approach and discuses this as an area of future work.
-The additional discussion is presented here.
+Specific comments related to these comments have been included below.
 
@@
 
+\todo Use dynamical throughout manuscript
+
 \comment{
@@
 
-Depending on the specific mission objectives the preliminary mapping phase may serve multiple purposes. 
-In this week, we seek to utilize the mapping phase to create a polyhedron potential model and select an appropriate landing site. 
-We added additional discussion related to more recent missions and copied below.
+Depending on the specific mission objectives the mapping phase may serve multiple purposes, such as landing site selection or shape modelling.
+In this work, we seek to utilize the mapping phase to create a shape model.
+The shape model is then used for multiple purposes including the polyhedron potential model and landing site selection.
+We have added additional discussion related to more recent missions and copied below.
+
+\todo Add to introduction section - replacing the sentence: ''After arrival, a spacecraft will generally spend months or years in a mapping mission phase.``
+\begin{correction}
+After arrival, space will generally spend upwards of several months in a mapping mission phase~\cite{williams2018,kubota2003,cole1998}.
+For example, the recent OSIRIS-REx mission used global imagery to create digital terrain maps over the span of approximately seven months~\cite{williams2018}.
+
+\end{correction}
 
@@
 
-The citation to the asteroid redirect mission has been removed and additional discussion related to the OSIRIS-REX mission has been incorporated.
+\todo Remove citation ''gates2015`` in the introduction.
+
+\todo add following citations~\cite{williams2018} instead.
+
+The citation to the asteroid redirect mission has been removed and additional discussion related to the OSIRIS-REx mission has been incorporated.
 The additional discussion has been copied below.
+
+\todo Add following after sentence: ''Depending on the mission type, this long period of mapping is curicial to the mission, such as sample collection.``
+\begin{correction}
+For example, the OSIRIS-REx mission spent approximately seven months in mapping phase where digitial terrain maps and a shape model were constructed in support of main sample collection mission.
+\end{correction}
 
@@
 
+\todo Remove sentence and replace
+
+\begin{correction}
 Onboard shape reconstruction techniques enable autonomous operations which allow for a greater range of spacecraft operations.
+\end{correction}
 
@@
 }
-This typo has been corrected and is copied below.
+
+This typo has been corrected.
+
+\todo Correct typo.
 
@@
 }
-This typo has been corrected and is copied below.
+
+\todo Correct typo
+This typo has been corrected and the corrected sentence is shown below.
+
+\begin{correction}
+During this simulation, this updated shape model is then used in a nonlinear controller to track a desired state trajectory for the dynamics of a rigid body spacecraft.
+\end{correction}
 
@@
 
-The polyhedron potential model is based on a triangular faceted shape model of an asteroid.
-In this approach, the shape of the asteroid is used to directly compute the exterior potential.
+\begin{correction}
+    The sum \( \sum \omega_f \) vanishes when outside the body and equals \( -4 \pi \) inside.
+\end{correction}
 
@@
 
-Find more recent references
+More recent references from the OSIRIS-REx mission have been included and additional discussion is copied below.
+
+\begin{correction}
+We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid~\cite{zuber1997,zuber2000}.
+Recent missions such as OSIRIS-REx have featured a scanning LIDAR system which allows for much higher measurement rates compared to previous missions~\cite{lauretta2017,daly2017}.
+In these mission, ranging measurements are combined with imagery to derive a shape model using a ground based method~\cite{gaskell2008}.
+In constrast to previous missions, the scanning LIDAR system on OSIRIS-REx enables for high surface sample rates in spite of the low ground-track velocities~\cite{daly2017}.
+\end{correction}
 
@@
 The equation has been corrected and is copied below.
+
+\todo Correct the equation
+
+\begin{correction}
+    \(d = \frac{\Delta TOF c}{2} \) 
+\end{correction}
 
@@
 Additional detail has been added to the manuscript and is shown below.
+
+\todo Copy into paper after equation 19.
 
@@
 
+\todo Copy into section 4.3. Either the first paragraph or a new second paragraph
+
 \begin{correction}
@@
 A reference for the radar shape models has been added.
+
+\todo Add to paper
 
@@
 
+\todo Correct in paper
+
 \begin{correction}
@@
 Additional discussion has been added to the manuscript discussing this feature of our approach and is copied below.
+
+\todo Correct in paper
 
@@
 
+\todo Correct in paper
+
 \comment{
@@
 
+\todo Correct in paper
 \begin{correction}
@@
 
+\bibliographystyle{IEEEtran}
+\bibliography{library}
+
 \end{document}

### 2021-12-15 jas_response.tex
minor edits to the response by TL

@@
 
-The primary benefit of the dumbbell approximation is to avoid the additional integral over the entire body.
+The motivation is to capture the effects of the relative attitude between spacecraft and asteroid on the corresponding gravitational force and moment. 
+The primary benefit of the dumbbell approximation is that the additional integral over the entire body is avoided. 
 While conceptually and analytically simple the dumbbell model still captures the important rigid body effects on the system, namely the coupling of attitude and translational states through the external forces and moments.
 In addition, this type of spacecraft model is prevelant in the field~\cite{kulumani2017b,lee2006a,lee2007a,elmasri2005}.
-Additional comments have been added to the manuscript explaining this decision and copied here.
+To clarify these, additional comments have been added to the manuscript explaining this decision and copied here.
 
@@
 
-Specific comments:
+%Specific comments:
 }
@@
 Thank you for this comment. 
-We have replaced ''dynamic`` with ''dynamical`` in several locations throughout the manuscript.
+We have replaced ``dynamic'' with ``dynamical'' in several locations throughout the manuscript.
 We do not repeat the corrections here for simplicity.
@@
 
+Thank you for the comment.
 This sentence has been removed and replaced with the following:
@@
 }
+
 Additional detail describing the polyhedron potential model is added and copied below.
@@
 
-More recent references from the OSIRIS-REx mission have been included and additional discussion is copied below.
+More recent references from the OSIRIS-REx mission have been included and additional discussion is added as copied below.
 
@@
 The equation has been corrected and is copied below.
+The code has been rechecked.
 
@@
 \begin{correction}
-    In this numerical example we have assumed perfect state knowledge of the spacecraft.
+    In this numerical example we have assumed the perfect knowledge of the spacecraft state. 
     This is a strong assumption that would not exist in any realistic situation. 
@@
     Adaptive control techniques have been demonstrated in the past to address both fixed and time varying disturbances of this kind~\cite{kulumani2017a}.
-    The authors will relax these assumptions in future work.
+    However, these topics are beyond the scope of this paper focusing on optimal guidance for Bayesian shape reconstruction, and relegated to future works. 
 \end{correction}
@@
 As a result the vehicle in general may take an arbitrary trajectory about the body and utilize much larger control effort compared to utilizing the natural dynamics of the system. 
-We do not duplicate the motion of Hayabusa but did utilize the ''home position`` term to describe the numerical example.
+We do not duplicate the motion of Hayabusa but did utilize the ``home position'' term to describe the numerical example.
 Our shape refinement approach is not limited to our guidance scheme but rather is an example of combining closed loop control with our shape refinement method.
@@
 }
-Our landing site selection algorithm is relatively simple as it is a direct function of the shape model.
+
+Our landing site selection algorithm is relatively simple as it is directly evaluated by the shape model.
 The approach was chosen as an example to demonstrate how a vehicle can autonomously model the shape of the asteroid, then utilize that shape model to chose a landing site. 

### 2021-12-19 jas_response.tex
Update manuscript with comments

@@
 
-\todo Add to second paragraph of Section 4.3 Numerical example immediately after the sentence: ''In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat e_3)\).``
-
 \begin{correction}
@@
 
-\todo Use dynamical throughout manuscript
-
 \comment{
@@
 
-\todo Add to introduction section - replacing the sentence: ''After arrival, a spacecraft will generally spend months or years in a mapping mission phase.``
 \begin{correction}
@@
 
-\todo Remove citation ''gates2015`` in the introduction.
-
-\todo add following citations~\cite{williams2018} instead.
-
 The citation to the asteroid redirect mission has been removed and additional discussion related to the OSIRIS-REx mission has been incorporated.
@@
 
-\todo Add following after sentence: ''Depending on the mission type, this long period of mapping is curicial to the mission, such as sample collection.``
 \begin{correction}
@@
 
-\todo Remove sentence and replace
-
 \begin{correction}
@@
 
-\todo Correct typo.
-
 \comment{
@@
 
-\todo Correct typo
 This typo has been corrected and the corrected sentence is shown below.
@@
 
-\todo Correct the equation
-
 \begin{correction}
@@
 
-\todo Copy into paper after equation 19.
-
 \begin{correction}
@@
 
-\todo Copy into section 4.3. Either the first paragraph or a new second paragraph
-
 \begin{correction}
@@
 A reference for the radar shape models has been added.
-
-\todo Add to paper
 
@@
 
-\todo Correct in paper
-
 \begin{correction}
@@
 Additional discussion has been added to the manuscript discussing this feature of our approach and is copied below.
-
-\todo Correct in paper
 
@@
 
-\todo Correct in paper
-
 \comment{
@@
 
-\todo Correct in paper
 \begin{correction}

### 2021-12-19 manuscript.tex
Update manuscript with comments

@@
     This approach enables for an accurate shape determination around a potential landing site.
-    We demonstrate this approach using several radar shape models of asteroids and provide a full dynamic simulation about asteroid 4769 Castalia.
+    We demonstrate this approach using several radar shape models of asteroids and provide a full dynamical simulation about asteroid 4769 Castalia.
     \keywords{Asteroids \and Shape Construction \and Guidance \and Optimization}
@@
 % dynamics are difficult around asteroids
-The dynamic environment around asteroids is strongly perturbed and challenging for analysis and mission operations~\cite{scheeres2012}.
+The dynamical environment around asteroids is strongly perturbed and challenging for analysis and mission operations~\cite{scheeres2012}.
 Due to their low mass, which in turn causes a low gravitational attraction, asteroids may have irregular shapes.
 Furthermore, asteroids may also have a chaotic spin state due to the absorption and emittance of solar radiation~\cite{rubincam2000}.
-As a result, approaches utilizing an inverse square gravitational model do not capture the  true dynamic environment.
+As a result, approaches utilizing an inverse square gravitational model do not capture the  true dynamical environment.
 In addition, the vast majority of asteroids are difficult to track and characterize using ground based sensors.
 Due to their small size, frequently with a maximum radius less than \SI{1}{\kilo\meter}, and low albedo, the reflected energy of these asteroids is insufficient for reliable detection or tracking.
-Therefore, the dynamics model of the asteroid is relatively coarse prior to in situ measurements from a dedicated spacecraft.
-As a result, any spacecraft mission to an asteroid must include the ability to update the dynamic model given in situ measurements and remain robust to unmodelled forces.
-
-Another key dynamic consideration is the coupling between rotational and translational states around the asteroid.
+Therefore, the dynamical model of the asteroid is relatively coarse prior to in situ measurements from a dedicated spacecraft.
+As a result, any spacecraft mission to an asteroid must include the ability to update the dynamical model given in situ measurements and remain robust to unmodelled forces.
+
+Another key dynamical consideration is the coupling between rotational and translational states around the asteroid.
 The coupling is induced due to the different gravitational forces experienced on various portions of the spacecraft. 
@@
 On approach to an asteroid, spacecraft navigation and guidance is primarily based on ground measurements.
-After arrival, a spacecraft will generally spend months or years in a mapping mission phase~\cite{kubota2003,cole1998}.
+After arrival, space will generally spend upwards of several months in a mapping mission phase~\cite{williams2018,kubota2003,cole1998}.
+For example, the recent OSIRIS-REx mission used global imagery to create digital terrain maps over the span of approximately seven months~\cite{williams2018}.
 During this period, spacecraft sensors, such as on board optical telescopes or Light radio Detection and Ranging (LIDAR), are used to characterize the asteroid.
@@
 During this mapping phase the spacecraft must remain in a quiescent state devoted entirely to mapping the surface.
-Depending on the mission type, this long period of mapping is crucial to the mission, such as sample collection~\cite{gates2015}. 
+Depending on the mission type, this long period of mapping is crucial to the mission, such as sample collection~\cite{williams2018}. 
+For example, the OSIRIS-REx mission spent approximately seven months in mapping phase where digitial terrain maps and a shape model were constructed in support of main sample collection mission.
 However, other missions, such as asteroid mitigation, may be severely limited by the time and ground resources required to generate a surface shape.
@@
 Similarly, during landing the spacecraft will require the ability to sense and model the surface topography in order to safely land in an unknown environment.
-The dependency on expensive ground-based shape reconstruction techniques limits the ability of spacecraft to autonomously operate at asteroids.
+Onboard shape reconstruction techniques enable autonomous operations which allow for a greater range of spacecraft operations.
 Mitigation of this ground based surface modeling will greatly expand the range of missions possible.
@@
 This paper presents three techniques to explore an asteroid without need for an extended period of mapping phase or ground based measurements. 
-First, we develop a method to compute the surface shape of an asteroid from onborad range measurements.
+First, we develop a method to compute the surface shape of an asteroid from onboard range measurements.
 Assuming that a meshed model of an initial estimate, such as an ellipsoidal shape, is available, the radius of any vertex in the measured area is adjusted according to the measurements. 
@@
 
-The optimal guidance and multi resolution mapping schemes are illustrated by dynamic simulation of landing on the asteroid Castalia. 
-During this simulation, This updated shape model is then used to in a nonlinear controller to track a desired state trajectory for the dynamics of a rigid body spacecraft.
+The optimal guidance and multi resolution mapping schemes are illustrated by dynamical simulation of landing on the asteroid Castalia. 
+During this simulation, this updated shape model is then used in a nonlinear controller to track a desired state trajectory for the dynamics of a rigid body spacecraft.
 The dynamics are developed on the nonlinear manifold of rigid body motions, namely the special Euclidean group.
@@
 \end{figure}
+The dumbbell model is in some sense the simplest approximation of an extended rigid body.
+This model captures the important dynamics of an extended rigid body with a minmum of additional complexity and is prevelant the literature~\cite{kulumani2017b,lee2006a,lee2007a,elmasri2005}.
+In addition, the developments of the dumbbell model can be trivially extended to include a larger number of discrete masses to better approximate a more complicated spacecraft model.
+
 Without loss of generality, we define body fixed frames for both the spacecraft and asteroid, which are aligned with the principle axes of each body and originate at their respective center of mass. 
@@
 
-\subsection{Spacecraft Dynamic Model}
+\subsection{Spacecraft Dynamical Model}
 
@@
 The Laplacian, defined in~\cref{eq:laplacian}, gives a simple method to determine if the spacecraft has collided with the body~\cite{werner1996}. 
+The sum \( \sum \omega_f \) vanishes when outside the body and equals \( -4 \pi \) inside.
 These equations are utilized to compute the gravitational potential of  the presented dumbbell spacecraft model.
@@
 We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid~\cite{zuber1997,zuber2000}.
+Recent missions such as OSIRIS-REx have featured a scanning LIDAR system which allows for much higher measurement rates compared to previous missions~\cite{lauretta2017,daly2017}.
+In these mission, ranging measurements are combined with imagery to derive a shape model using a ground based method~\cite{gaskell2008}.
+In constrast to previous missions, the scanning LIDAR system on OSIRIS-REx enables for high surface sample rates in spite of the low ground-track velocities~\cite{daly2017}.
 This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
-Given the time total time of flight, the distance can be accurately computed using \( d = \frac{\Delta TOF}{2 c} \) where \( c = \SI{2.998e8}{\meter\per\second}\) is the constant speed of light.
+Given the time total time of flight, the distance can be accurately computed using \( d = \frac{\Delta TOF }{2} \) where \( c = \SI{2.998e8}{\meter\per\second}\) is the constant speed of light.
 Assuming accurate knowledge of the pointing direction of the spacecraft, in the form of the rotation matrix \( R \in \R^{3 \times 3 } \), we can compute a direction from the spacecraft to the measurement location on the surface.
@@
 In other words, each vertex from the initial estimate of shape is either stretched or shrunk along its radial direction, without any rotation. 
-This framework is reasonable assuming that both of the initial estimate and the actual shape does not have any hole. 
+We assume that the initial intertial state of the vehicle is available. 
+This data is typically available from a ground based orbit determination scheme which enabled the original orbital rendezvous. 
+The approach presented here is reasonable assuming that both the initial estimate and the actual shape of the body does not have any hole. 
 This approach alleviates much of complexity of incorporating new vertices or surface triangulation common in surface reconstruction methods~\cite{berg2008}.
@@
 \end{align}
+The parameters \( c \) and \( \Delta \sigma_{max} \) are used to define the region of impact of each measurement. 
+The angular constraint \( \Delta \sigma_{max} \) may be used to adjust the computational requirements of the shape refinement process.
+Larger values of \( \Delta \sigma_{max} \) result in a greater computational demand as a given measurement ray is used to update a larger number of vertices.
+\Cref{sec:landing_refinement} presents an approach to allow for a higher resolution mesh in certain regions to capture finer surface details without excessive resources. 
+The scalar \( c \) may then be used to adjust the variance \( w_{j,i} \) as a function of the distance between measurement \( j \) and vertex \( i \).
+These two parameters may be used to minimize steep gradients that may occur during the shape reconstruction process.
 
@@
 
-The results in this section utilize a kinematics only model of the spacecraft and dynamics instead of the full dynamic simulation. 
+The results in this section utilize a kinematics only model of the spacecraft instead of the full dynamical simulation. 
 We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction, and the spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
@@
 A variety of techniques are available to choose these gains, but a simple linear analysis offers a straightforward and systematic approach to choosing suitable values. 
-We use the control inputs defined in~\cref{eq:translational_control,eqn:nodist_control} and substitute them into the dynamic equations of motion in~\cref{eq:x_dot,eq:v_dot,eq:R_dot,eq:omega_dot}.
+We use the control inputs defined in~\cref{eq:translational_control,eqn:nodist_control} and substitute them into the dynamical equations of motion in~\cref{eq:x_dot,eq:v_dot,eq:R_dot,eq:omega_dot}.
 
@@
 
-We utilize radar shape models of asteroids \num{4769} Castalia and (\num{52760}) \num{1998} \(\text{ML}_{14}\).
-The examples demonstrate the full dynamic simulation of a rigid spacecraft with an autonomous closed loop control scheme to both reconstruct the asteroid shape.
+We utilize radar shape models of asteroid \num{4769} Castalia and (\num{52760}) \num{1998} \(\text{ML}_{14}\)~\cite{neese2004}.
+The examples demonstrate the full dynamical simulation of a rigid spacecraft with an autonomous closed loop control scheme to both reconstruct the asteroid shape.
 The proposed optimal guidance scheme is executed in the outer-loop to generate the desired trajectory, which is followed by the nonlinear control scheme in the inner-loop. 
@@
 However, throughout the simulation, the actual spacecraft dynamics are computed with the gravity computed by the full shape model unknown to the controller.
-These demonstrate the ability of a spacecraft to autonomously explore and maneuver around an initially-unknown asteroids while incrementally updating the shape model.
+These demonstrate the ability of a spacecraft to autonomously explore and maneuver around an initially poorly modeled asteroid while incrementally updating the shape model.
+
+In this numerical example we have assumed the perfect knowledge of the spacecraft state. 
+This is a strong assumption that would not exist in any realistic situation. 
+However, the measurement model defined in the previous section may be extended to consider the uncertainty in both the state \( x \) and the range measurement \( d \) rather than combining them into a single random variable \( p \).
+In addition, the dynamics defined by~\crefrange{eq:x_dot}{eq:omega_dot} do not consider any non-gravitational accelerations such as solar radiation pressure on the vehicle.
+In general, these types of external forces will primarily serve to increase state uncertainty and cause large errors in the closed loop control system.
+Adaptive control techniques have been demonstrated in the past to address both fixed and time varying disturbances of this kind~\cite{kulumani2017a}.
+However, these topics are beyond the scope of this paper focusing on optimal guidance for Bayesian shape reconstruction, and relegated to future works.
 
@@
     \end{tabular}
-    \caption{Asteroid properties for dynamic exploration~\label{tab:dynamic_asteroids}}
+    \caption{Asteroid properties for dynamical exploration~\label{tab:dynamic_asteroids}}
 \end{table}
@@
 The images colored according to the shape uncertainty.
-Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:52760_weights_reconstruction}}
+Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.
+    The guidance scheme continually selects regions of high uncertainty until the total shape uncertainty is sufficiently small.~\label{fig:52760_weights_reconstruction}}
 \end{figure}
@@
 The images colored according to the shape uncertainty.
-Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:castalia_weights_reconstruction}}
+Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.
+    The guidance scheme continually selects regions of high uncertainty until the total shape uncertainty is sufficiently small.
+    ~\label{fig:castalia_weights_reconstruction}}
 \end{figure}
@@
 subject to a hard inequality constraint requiring that the surface slope is less than a threshold, i.e., \( \phi \leq \phi_m \).
+The surface cost described here is relatively simple and chosen to be solely a function of the current spacecraft position and shape model.
+Additional scientific criteria such as surface material or location on the body, e.g. equatorial vs. polar regions, can be utilized instead of a random science value as presented here.
 
@@
 The approach allows for a local update operation that is able to reconstruct the shape in real time. 
-This is in contrast to standard shape reconstruction algorithms which operate over the entire surface and require signification computational resources.
+This is in contrast to standard shape reconstruction algorithms which operate over the entire surface and require significant computational resources.
 Next, an optimal guidance scheme is derived which determines the desired state to best update the shape estimate. 

### 2021-12-22 manuscript.tex
TL minor edits

@@
 In this paper, we consider the motion of a dumbbell model of spacecraft around an asteroid.
-The dumbbell model captures the important interactions of the coupling between orbital and attitude dynamics.
 The dumbbell is defined by two spherical masses of radius \( r_1, r_2 \in \R \) with masses \( m_1, m_2 \in  \R\).
@@
 \begin{align}\label{eq:dumbbell_moment_of_inertia}
-    J_I = \sum_i^n J_i + m_i \parenth{\vc{\zeta}_i^T \vc{\zeta}_i I - \vc{\zeta}_i \vc{\zeta}_i^T} , 
+    J_I = \sum_i^n J_i + m_i \parenth{\vc{\zeta}_i^T \vc{\zeta}_i I_{3\times 3} - \vc{\zeta}_i \vc{\zeta}_i^T} , 
 \end{align}
@@
     \begin{align}
-        J &= \tr{J_d} I - J_d, \label{eq:moi_ns2s}\\
-        J_d &= \frac{1}{2} \tr{J} I - J.\label{eq:moi_s2ns}
+        J &= \tr{J_d} I_{3\times 3} - J_d, \label{eq:moi_ns2s}\\
+        J_d &= \frac{1}{2} \tr{J} I_{3\times 3} - J.\label{eq:moi_s2ns}
     \end{align}
@@
 This shape can be a coarse estimate computed from ground measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid.
-Additionally, we assume that the shape estimate is closed and a triangular faceted surface mesh, emulating those used in practice to represent asteroids.
+Additionally, we assume that the shape estimate is a triangular faceted, closed surface mesh, emulating those used in practice to represent asteroids.
 Furthermore, the number of vertices in the estimate can be scaled according to the desired final accuracy or computational capabilities.
@@
 This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
-Given the time total time of flight, the distance can be accurately computed using \( d = \frac{\Delta TOF }{2} \) where \( c = \SI{2.998e8}{\meter\per\second}\) is the constant speed of light.
+Given the time total time of flight ($\Delta TOF$) the distance can be accurately computed using \( d = \frac{c \Delta TOF }{2} \) where \( c = \SI{2.998e8}{\meter\per\second}\) is the constant speed of light.
 Assuming accurate knowledge of the pointing direction of the spacecraft, in the form of the rotation matrix \( R \in \R^{3 \times 3 } \), we can compute a direction from the spacecraft to the measurement location on the surface.
@@
 The spacecraft measures the range between itself and the asteroid surface to several points within the field of view of the sensor. 
-These measurements provide a collection of points which lie on the surface of the asteroid, and by combining many points, a so called \textit{point cloud}, allows us to reconstruct the shape.
+These measurements provide a collection of points to form so called \textit{point cloud}, which allows us to reconstruct the shape.
 \begin{figure}
@@
 % shankar: brillouin is correct. https://arc.aiaa.org/doi/10.2514/6.2014-4302
-where \( r_b \) defines the Brillouin  sphere radius, or the radius of the circumscribing sphere of the asteroid.
+where \( r_b \in \Re \) defines the Brillouin  sphere radius, or the radius of the circumscribing sphere of the asteroid.
 Only vertices which satisfy \( \Delta \sigma_i \leq \Delta \sigma_{max} \) are considered in the Bayesian update defined as follows.
@@
 \end{align*}
-where \( r_{j,i} = \norm{\vc{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i}\) defines the variance of the measurement with respect to vertex \( \vc{v}_i\).
+where \( r_{j,i} = \norm{\vc{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i} \in\Re\) defines the variance of the measurement with respect to vertex \( \vc{v}_i\).
 
@@
 
-From Bayes' theorem, the a posterior probability of the vertex radius is given by
+From Bayes' theorem, the a posteriori probability of the vertex radius is given by
 \begin{align}
@@
 As a result, a small total uncertainty is used to indicate that additional measurements would not substantially modify the shape.
-In addition, we compute the volume of the estimated shape and compare against the volume of the truth shape model~\cite{neese2004}.
+In addition, we compute the volume of the estimated shape and compare it against the volume of the truth shape model~\cite{neese2004}.
 
@@
 \num{1620} Geographos is a highly elongated stony asteroid of the Apollo group.
-Discovered in \num{1951}, Geographos is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
+Discovered in \num{1951}, Geographos is a potentially hazardous asteroid which passes sufficiently close to the Earth.
 \Cref{fig:geographos_reconstruction} shows the shape reconstruction for asteroid Geographos at several distinct points during the process.
@@
 Next, \num{6489} Golevka is a small angular shaped asteroid of the Apollo group.
-Discovered in \num{1995}, Golevka is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
+Discovered in \num{1995}, Golevka is another potentially hazardous asteroid which passes close to the Earth.
 \Cref{fig:golevka_reconstruction} shows the shape reconstruction for asteroid Golevka at several distinct points during the process.
@@
 \end{align}
-where the weighting factors \( \alpha_w, \alpha_d, \alpha_c \in \R^1 \) are chosen such that \( \alpha_w + \alpha_d + \alpha_c = 1 \).
+where the weighting factors \( \alpha_w, \alpha_d, \alpha_c \in \R \) are chosen such that \( \alpha_w + \alpha_d + \alpha_c = 1 \).
 The cost function is defined as a function of the current inertial position, \( x \in \R^3 \), and the attitude, \( R \in \R^{3\times3}\) of the spacecraft.
-Furthermore, knowledge of the small body rotation is required in order to determine the position of the spacecraft in the small body fixed frame, \( x_r = R_A^T x\).
+Furthermore, the knowledge of the small body rotation is required in order to determine the position of the spacecraft in the small body fixed frame, \( x_r = R_A^T x\).
 
@@
 \end{align}
-where \( \theta : \bracket{0, \frac{\rpos \cdot \vc{v}_i}{\norm{\rpos}\norm{\vc{v}_i}}} \to \R^1\) parameterizes the desired trajectory.
+where \( \theta : \bracket{0, \frac{\rpos \cdot \vc{v}_i}{\norm{\rpos}\norm{\vc{v}_i}}} \to \R\) parameterizes the desired trajectory.
 \Cref{eq:spherical_waypoint} simply describes a portion of a great circle trajectory between the current state, \( \rpos \), and the desired vertex \( \vc{v}_i \)~\cite{chen2016}, with a desired radius $r_d$.
@@
 In our analysis we consider the surface slope, the distance to the surface, and a fictitious science metric in order to determine the best landing site based on the complete shape estimate.
-This approach allows for a spacecraft to autonomously select and land on small body.
+This approach allows for a spacecraft to autonomously select and to land on small body.
 
@@
 \end{align}
-where \( \phi \in \R^1 \) is the surface slope defines the angle between the surface normal \( \vc{n}_f \in \R^3 \) and the force vector at the surface.
+where \( \phi \in \R \) is the surface slope defines the angle between the surface normal \( \vc{n}_f \in \R^3 \) and the force vector at the surface.
 If \( \phi = \SI{0}{\degree} \) then the force vector and the surface normal are anti-parallel, while \( \phi > \SI{90}{\degree} \) means that a particle on the surface would be thrown off the body as the centripetal force is larger than the gravitational attraction.

### 2021-12-22 manuscript.tex
Correct some typos

@@
 \begin{abstract}
-    Constructing of the precise shape of an asteroid is critical for spacecraft operations, as the gravitational potential is determined by spatial mass distribution.
+    Construction of the precise shape of an asteroid is critical for spacecraft operations as the gravitational potential is determined by spatial mass distribution.
     %For example, the standard method of determining the gravitational potential of an asteroid, through the use of a polyhedron potential model, is directly dependent on the shape model.
@@
     This paper presents a set of approaches to explore an unknown asteroid with onboard calculations, and to land on its surface area selected in an optimal fashion. 
-    The main motivation is to avoid the extended period of mapping phase or preliminary ground observations that are commonly required in spacecraft mission around asteroids. 
-    First, range measurements from spacecraft to the surface are used to incrementally correct an initial shape estimate according to the Bayesian framework. 
+    The main motivation is to avoid the extended period of mapping or preliminary ground observations that are commonly required in spacecraft missions around asteroids. 
+    First, range measurements from the spacecraft to the surface are used to incrementally correct an initial shape estimate according to the Bayesian framework. 
     Then, an optimal guidance scheme is proposed to control the vantage point of the range sensor to construct a complete 3D model of the asteroid shape. 
@@
 On approach to an asteroid, spacecraft navigation and guidance is primarily based on ground measurements.
-After arrival, space will generally spend upwards of several months in a mapping mission phase~\cite{williams2018,kubota2003,cole1998}.
+After arrival, spacecraft will generally spend upwards of several months in a mapping mission phase~\cite{williams2018,kubota2003,cole1998}.
 For example, the recent OSIRIS-REx mission used global imagery to create digital terrain maps over the span of approximately seven months~\cite{williams2018}.
@@
 Depending on the mission type, this long period of mapping is crucial to the mission, such as sample collection~\cite{williams2018}. 
-For example, the OSIRIS-REx mission spent approximately seven months in mapping phase where digitial terrain maps and a shape model were constructed in support of main sample collection mission.
+For example, the OSIRIS-REx mission spent approximately seven months in mapping phase where digitial terrain maps and a shape model were constructed in support of the main sample collection mission.
 However, other missions, such as asteroid mitigation, may be severely limited by the time and ground resources required to generate a surface shape.
@@
 % we want to generate the shape in real time and then use this shape for updated and better control
-This paper presents three techniques to explore an asteroid without need for an extended period of mapping phase or ground based measurements. 
+This paper presents three techniques to explore an asteroid without need for an extended period of mapping or reliance on ground based measurements. 
 First, we develop a method to compute the surface shape of an asteroid from onboard range measurements.
@@
 \begin{itemize}
-    \item \( \vc{x}\in\Re^3 \) - the position of the center of mass of the  spacecraft represented in the inertial frame, \( \vc{e}_i\),
+    \item \( \vc{x}\in\R^3 \) - the position of the center of mass of the  spacecraft represented in the inertial frame, \( \vc{e}_i\),
     \item \( R\in\SO \) - the rotation matrix which transforms the representation of vectors defined in the spacecraft fixed frame, \( \vc{b}_i \), to the inertial frame, \( \vc{e}_i \),
-    \item \( \vc{\Omega}\in\Re^3 \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame, \( \vc{b}_i \), and
+    \item \( \vc{\Omega}\in\R^3 \) - the angular velocity of the spacecraft body fixed frame relative to the inertial frame and represented in the dumbbell body fixed frame, \( \vc{b}_i \), and
     \item \( R_A\in \SO \) - the rotation matrix which transforms the representation of vectors defined in the asteroid fixed frame, \( \vc{f}_i \), to the inertial frame, \( \vc{e}_i \).
@@
 \end{align}
-The vectors \( \vc{z}_1 \) and \( \vc{z}_2\in\Re^3\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
+The vectors \( \vc{z}_1 \) and \( \vc{z}_2\in\R^3\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
 \begin{align}
@@
 \end{align}
-where \( \rho_i \in\Re^3 \) defines the position of each mass in the spacecraft fixed body frame.
-The control inputs to the spacecraft are defined by \( u_f, u_m \in \Re^3 \) which define the control force represented in the inertial frame and the control moment represented in the spacecraft frame, respectively.
+where \( \rho_i \in\R^3 \) defines the position of each mass in the spacecraft fixed body frame.
+The control inputs to the spacecraft are defined by \( u_f, u_m \in \R^3 \) which define the control force represented in the inertial frame and the control moment represented in the spacecraft frame, respectively.
 The standard moment of inertia of the dumbbell model is 
@@
 \end{align}
-In the above equations, the gravitational potential is denoted by $U\in\Re$, which is computed by a polyhedron model as described in the subsequent section.
+In the above equations, the gravitational potential is denoted by $U\in\R$, which is computed by a polyhedron model as described in the subsequent section.
 
@@
 \end{align}
-and \( \vc{r}_e\) and \(\vc{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\in\Re\) is the universal gravitational constant, and \( \sigma\in\Re \) is the constant density of the asteroid.
+and \( \vc{r}_e\) and \(\vc{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\in\R\) is the universal gravitational constant, and \( \sigma\in\R \) is the constant density of the asteroid.
 We define the attraction, gravity gradient matrix, and Laplacian as
@@
 Given the time total time of flight ($\Delta TOF$) the distance can be accurately computed using \( d = \frac{c \Delta TOF }{2} \) where \( c = \SI{2.998e8}{\meter\per\second}\) is the constant speed of light.
-Assuming accurate knowledge of the pointing direction of the spacecraft, in the form of the rotation matrix \( R \in \R^{3 \times 3 } \), we can compute a direction from the spacecraft to the measurement location on the surface.
-The output of this sensor is a vector, \( \vc{d}_i\in\Re^3 \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface. 
+Assuming accurate knowledge of the pointing direction of the spacecraft, in the form of the rotation matrix \( R \in \SO \), we can compute a direction from the spacecraft to the measurement location on the surface.
+The output of this sensor is a vector, \( \vc{d}_i\in\R^3 \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface. 
 Using the state of the asteroid, we can transform this measurement to the asteroid fixed frame using the simple transformation
@@
 \end{align*}
-where \( r_i\in\Re \) is the initial estimate of the radial distance of the $i$-th vertex \( \vc{v}_i\in\Re\), and \( w_i\in\Re \) is the initial variance, or confidence, in the radial distance.
+where \( r_i \in \R \) is the initial estimate of the radial distance of the $i$-th vertex \( \vc{v}_i\in\R\), and \( w_i\in\R \) is the initial variance, or confidence, in the radial distance.
 
 In order to reduce the computational demands, which are typical in point cloud applications, we do not update the complete shape model for each measurement.
-Instead we define an area of interest, \( \Delta S\in\Re \), about each measurement which defines the surface area over which the measurement will affect the mesh estimate.
+Instead we define an area of interest, \( \Delta S\in\R \), about each measurement which defines the surface area over which the measurement will affect the mesh estimate.
 We relate \( \Delta S \) to an equivalent angular constraint using
@@
 % shankar: brillouin is correct. https://arc.aiaa.org/doi/10.2514/6.2014-4302
-where \( r_b \in \Re \) defines the Brillouin  sphere radius, or the radius of the circumscribing sphere of the asteroid.
+where \( r_b \in \R \) defines the Brillouin  sphere radius, or the radius of the circumscribing sphere of the asteroid.
 Only vertices which satisfy \( \Delta \sigma_i \leq \Delta \sigma_{max} \) are considered in the Bayesian update defined as follows.
@@
 \end{align*}
-where \( r_{j,i} = \norm{\vc{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i} \in\Re\) defines the variance of the measurement with respect to vertex \( \vc{v}_i\).
+where \( r_{j,i} = \norm{\vc{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i} \in\R\) defines the variance of the measurement with respect to vertex \( \vc{v}_i\).
 
@@
 Their properties are listed at \Cref{tab:kinematic_asteroids}.
-Truth shape models for Geographos adn Golevka are computed based on Earth based radar measurements~\cite{neese2004}.
+Truth shape models for Geographos and Golevka are computed based on Earth based radar measurements~\cite{neese2004}.
 \begin{table}[htbp]
@@
 where the weighting factors \( \alpha_w, \alpha_d, \alpha_c \in \R \) are chosen such that \( \alpha_w + \alpha_d + \alpha_c = 1 \).
-The cost function is defined as a function of the current inertial position, \( x \in \R^3 \), and the attitude, \( R \in \R^{3\times3}\) of the spacecraft.
+The cost function is defined as a function of the current inertial position, \( x \in \R^3 \), and the attitude, \( R \in \SO \) of the spacecraft.
 Furthermore, the knowledge of the small body rotation is required in order to determine the position of the spacecraft in the small body fixed frame, \( x_r = R_A^T x\).
@@
 \end{align}
-where \( w_i \) is the uncertainty of vertex \( i \), which is defined as the variance of the radius in the preceding section, and \( w_m \in\Re \) is a maximum uncertainty used to scale the values.
+where \( w_i \) is the uncertainty of vertex \( i \), which is defined as the variance of the radius in the preceding section, and \( w_m \in\R \) is a maximum uncertainty used to scale the values.
 The term \( J_{d_i} \) represents the scaled geodesic distance between the current state of the spacecraft and vertex \( i \),
@@
 \end{align}
-This form of \( R_d \) will direct the \( b_1 \) axis towards the small body, and can be modified for a different camera orientation.
+This form of \( R_d \) will direct the \( b_1 \) axis towards the small body, and can be modified for a different camera orientations~\cite{kulumani2017a}.
 
@@
 \end{enumerate}
-The proof of these properties is available~\cite{kulumani2017a}.
+The proof of these properties is available in Reference~\cite{kulumani2017a}.
 
@@
 Then the zero equilibrium of the attitude error is asymptotically stable.
-The proof is show in~\cite{kulumani2017a}.
+The proof is show in Reference~\cite{kulumani2017a}.
 
@@
 Once a suitable landing site is selected, the surrounding area is isolated and refined by adding new vertices and faces in the specified area.
-The goal of refinement, or more generally remeshing, is given a mesh ( or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
+The goal of refinement, or more generally remeshing, is given a mesh (or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
 In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL)~\cite{cgalproject2018}.

### 2021-12-22 manuscript.tex
Update affliation and change objective function J

@@
 \institute{S. Kulumani (corresponding author) \at
-              Mechanical and Aerospace Engineering, The George Washington University, Washington DC, 20052\\
-              \email{shanks.k@gmail.com}           %  \\
+              The Johns Hopkins University, Applied Physics Laboratory, Laurel, MD 20723\\
+              \email{shankar.kulumani@jhuapl.edu}           %  \\
 %             \emph{Present address:} of F. Author  %  if needed
@@
 \Cref{eq:dumbbell_moment_of_inertia} is consistent with the well-known parallel-axis theorem~\cite{greenwood1988}.
-We utilize a nonstandard moment of inertia in the equations of motion, \( J_d \in \R^{3 \times 3 } \), which is related to the standard moment of inertia by
-\begin{subequations}\label{eq:moi_transformation}
-    \begin{align}
-        J &= \tr{J_d} I_{3\times 3} - J_d, \label{eq:moi_ns2s}\\
-        J_d &= \frac{1}{2} \tr{J} I_{3\times 3} - J.\label{eq:moi_s2ns}
-    \end{align}
-\end{subequations}     
+% We utilize a nonstandard moment of inertia in the equations of motion, \( J_d \in \R^{3 \times 3 } \), which is related to the standard moment of inertia by
+% \begin{subequations}\label{eq:moi_transformation}
+%     \begin{align}
+%         J &= \tr{J_d} I_{3\times 3} - J_d, \label{eq:moi_ns2s}\\
+%         J_d &= \frac{1}{2} \tr{J} I_{3\times 3} - J.\label{eq:moi_s2ns}
+%     \end{align}
+% \end{subequations}     
 The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as
@@
 \begin{align}\label{eq:explore_cost}
-    J_i (x, R, R_A) = \alpha_w J_{w_i} + \alpha_d J_{d_i}(x_r) + \alpha_c J_{c_i}(x_r)
+    \mathcal{J}_i (x, R, R_A) = \alpha_w \mathcal{J}_{w_i} + \alpha_d \mathcal{J}_{d_i}(x_r) + \alpha_c \mathcal{J}_{c_i}(x_r)
 \end{align}
@@
 
-The term \( J_{w_i} \in \R^1 \) represents the cost associated with the uncertainty of vertex \( i \) as
+The term \( \mathcal{J}_{w_i} \in \R^1 \) represents the cost associated with the uncertainty of vertex \( i \) as
 \begin{align}\label{eq:weight_cost}
-    J_{w_i} &= - \frac{w_i}{w_m}
+    \mathcal{J}_{w_i} &= - \frac{w_i}{w_m}
 \end{align}
 where \( w_i \) is the uncertainty of vertex \( i \), which is defined as the variance of the radius in the preceding section, and \( w_m \in\R \) is a maximum uncertainty used to scale the values.
-The term \( J_{d_i} \) represents the scaled geodesic distance between the current state of the spacecraft and vertex \( i \),
+The term \( \mathcal{J}_{d_i} \) represents the scaled geodesic distance between the current state of the spacecraft and vertex \( i \),
 \begin{align}\label{eq:distance_cost}
-    J_{d_i}(\rpos) &= \frac{1}{\pi} \arctan \parenth{ \frac{\norm{\rpos \times \vc{v}_i}}{\rpos \cdot \vc{v}_i}}.
+    \mathcal{J}_{d_i}(\rpos) &= \frac{1}{\pi} \arctan \parenth{ \frac{\norm{\rpos \times \vc{v}_i}}{\rpos \cdot \vc{v}_i}}.
 \end{align}
@@
 \begin{align}\label{eq:control_cost}
-    J_{c_i}(\rpos) = \frac{1}{u_m} \int_{\theta_0}^{\theta_f} u_f(\theta)^T R u_f(\theta) d\theta,
+    \mathcal{J}_{c_i}(\rpos) = \frac{1}{u_m} \int_{\theta_0}^{\theta_f} u_f(\theta)^T R u_f(\theta) d\theta,
 \end{align}
@@
 \begin{align*}
-    \vc{v}_{min} = \argmin_{i} \{J_i(x, R, R_A)\},
+    \vc{v}_{min} = \argmin_{i} \{\mathcal{J}_i(x, R, R_A)\},
 \end{align*}
@@
 \begin{align}\label{eq:surface_cost}
-    \min_{v_i} J_l(x, v_i) =  J_{\text{distance}}(x, v_i) - J_{\text{science}}(v_i),
+    \min_{v_i} \mathcal{J}_l(x, v_i) =  \mathcal{J}_{\text{distance}}(x, v_i) - \mathcal{J}_{\text{science}}(v_i),
 \end{align}

### 2022-03-12 manuscript.tex
Switch to article class

@@
 %%
-\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+\documentclass[]{article}       % onecolumn (second format)
+\usepackage{fancyhdr}
+\usepackage[margin=1in]{geometry}
 \usepackage{AAS_packages}
@@
 % \setlength\LTleft{0pt}
+
+\setlength{\headheight}{17pt}
+\pagestyle{fancyplain}
+\lhead[]{}
+\chead[]{}
+\rhead[]{}
+\fancyhf[C]{\color{red}{Please use citation: Kulumani, S., Lee, T.
+Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids.
+J Astronaut Sci (2022).
+\url{https://doi.org/10.1007/s40295-022-00310-6}}}
 
@@
 
-\author{Shankar Kulumani         \and
-        Taeyoung Lee %etc.
+\author{
+    Shankar Kulumani \and Taeyoung Lee
 }
@@
 
-% todo: we may update the affiliation and the address of Shankar 
-\institute{S. Kulumani (corresponding author) \at
-              The Johns Hopkins University, Applied Physics Laboratory, Laurel, MD 20723\\
-              \email{shankar.kulumani@jhuapl.edu}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           T. Lee,  \at
-              Mechanical and Aerospace Engineering, The George Washington University, Washington DC, 20052\\
-              \email{tylee@gwu.edu}
-}
+% % todo: we may update the affiliation and the address of Shankar 
+% \institute{S. Kulumani (corresponding author) \at
+%               The Johns Hopkins University, Applied Physics Laboratory, Laurel, MD 20723\\
+%               \email{shankar.kulumani@jhuapl.edu}           %  \\
+% %             \emph{Present address:} of F. Author  %  if needed
+%            \and
+%            T. Lee,  \at
+%               Mechanical and Aerospace Engineering, The George Washington University, Washington DC, 20052\\
+%               \email{tylee@gwu.edu}
+% }
 
@@
     We demonstrate this approach using several radar shape models of asteroids and provide a full dynamical simulation about asteroid 4769 Castalia.
-    \keywords{Asteroids \and Shape Construction \and Guidance \and Optimization}
+    % \keywords{Asteroids \and Shape Construction \and Guidance \and Optimization}
 \end{abstract}
